### 2025-03-18 DGMM2025/paper.tex
Start point of paper

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
\usepackage{hyperref}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
\usepackage{color}
\renewcommand\UrlFont{\color{blue}\rmfamily}
\urlstyle{rm}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{environ}

\usepackage{changes}
\setauthormarkup{}
\definechangesauthor[name=jo, color=magenta]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

\input{./macros}

%
\begin{document}
%
\title{Fast and exact visibility on digitized shapes and application to feature-aware normal estimation and pattern detection}
%
\titlerunning{Fast and exact visibility on digitized shapes}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Romain Negro\inst{1}\orcidID{0000-XXXX-YYYY-ZZZZ} \and
  Jacques-Olivier Lachaud\inst{1}\orcidID{0000-0003-4236-2133}}
%
\authorrunning{R. Negro and J.-O. Lachaud}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Universit\'e Savoie Mont Blanc, CNRS, LAMA, F-73000 Chambéry, France\\
  \email{\{romain.negro|jacques-olivier.lachaud\}@univ-smb.fr}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
  Our abstract
\keywords{Visibility \and Geometric inference \and Digital normal estimation \and Digital geometry} 
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

\end{document}

### 2025-03-20 DGMM2025/paper.tex
Skeleton of paper
Figures and visibility definition

@@
 \usepackage{changes}
+\usepackage{amstex}
 \setauthormarkup{}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
     \section{Introduction}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+    \section{Visibility through tangency of chords}
+
+    Introduce full convexity and tangency. \cite{lachaud:2021-dgmm,lachaud:2022-jmiv}.
+
+    \begin{definition}
+        Two points \( p \) and \( q \) on \( K \) are visible if and only if the segment \([p, q]\) is included in \(\text{Star}(K)\), i.e., [p, q] \subseteq \text{Star}(K)\).
+    \end{definition}
+
+    % Examples of visibility in 2D
+    \begin{figure}
+        \centering
+        \begin{tikzpicture}
+            \draw[dashed] (0,0) -- (4,2);
+            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p1};
+            \filldraw[black] (4,2) circle (0.05) node[anchor=north] {q1};
+            \draw (0,0) -- (1,0) -- (2,0) -- (2,1) -- (3,1) -- (3,2) -- (4,2);
+            \draw[dashed=gray] (-1,0) -- (-1,1) -- (0,1) -- (1,1) -- (1,2) -- (2,2) -- (2,3) -- (3,3) -- (4,3) -- (5,3) -- (5,2) -- (5,1) -- (4,1) -- (4,0) -- (3,0) -- (3,-1) -- (2,-1) -- (1,-1) -- (0,-1) -- (-1,-1) -- (-1,0);
+        \end{tikzpicture}
+        \hspace{\floatsep}
+        \begin{tikzpicture}
+            \draw[red,dashed] (0,0) -- (3,2);
+            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p2};
+            \filldraw[black] (3,2) circle (0.05) node[anchor=north] {q2};
+            \draw (0,0) -- (0,1) -- (0,2) -- (1,2) -- (1,3) -- (2,3) -- (2,2) -- (3,2);
+            \draw[dashed=gray] (-1,0) -- (-1,1) -- (-1,2) -- (-1,3) -- (0,3) -- (0,4) -- (1,4) -- (2,4) -- (3,4) -- (3,3) -- (4,3) -- (4,2) -- (4,1) -- (3,1) -- (2,1) -- (1,1) -- (1,0) -- (1,-1) -- (0,-1) -- (-1,-1) -- (-1,0);
+        \end{tikzpicture}
+        \newline
+        \newline
+        \begin{tikzpicture}
+            \draw[red,dashed] (0,0) -- (2,0);
+            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p3};
+            \filldraw[black] (2,0) circle (0.05) node[anchor=north] {q3};
+            \draw (0,0) -- (0,1) -- (0,2) -- (1,2) -- (2,2) -- (2,1) -- (2,0);
+            \draw[dashed=gray] (-1,-1) -- (-1,3) -- (3,3) -- (3,-1) -- (1,-1) -- (1,1) -- (1,-1) -- (-1,-1);
+        \end{tikzpicture}
+        \hspace{\floatsep}
+        \begin{tikzpicture}
+            \draw[red,dashed] (0,0) -- (2,2);
+            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p4};
+            \filldraw[black] (2,2) circle (0.05) node[anchor=north] {q4};
+            \draw (0,0) -- (0,1) -- (0,2) -- (1,2) -- (2,2);
+            \draw[dashed=gray] (-1,0) -- (-1,1) -- (-1,2) -- (-1,3) -- (0,3) -- (1,3) -- (2,3) -- (3,3) -- (3,2) -- (3,1) -- (2,1) -- (1,1) -- (1,0) -- (1,-1) -- (0,-1) -- (-1,-1) -- (-1,0);
+        \end{tikzpicture}
+        \caption{Examples of visibility in 2D, only q1 is visible from p1, q2 is not visible from p2 (gets out of the star), q3 is not visible from p3 (gets out of the star from a 1-d cell), q4 is not visible from p4 (gets out of the star from a 0-d cell).}
+        \label{fig:visibility-2d}
+    \end{figure}
+
+    % Example of visibility not necessarily connected
+    % Path from p to q : r u r u r r r r r u r
+    \begin{figure}
+        \centering
+        \begin{tikzpicture}
+            \draw (0,0) -- (1,0) -- (1,1) -- (2,1) -- (2,2) -- (3,2) -- (4,2) -- (5,2) -- (6,2) -- (7,2) -- (7,3);
+            \draw [black, dashed] (0,0) -- (7,3);
+            \draw [red, dashed] (0,0) -- (7,2);
+            \draw [red, dashed] (0,0) -- (6,2);
+            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p};
+            \filldraw[gray] (1,0) circle (0.05);
+            \filldraw[gray] (1,1) circle (0.05);
+            \filldraw[gray] (2,1) circle (0.05);
+            \filldraw[gray] (2,2) circle (0.05);
+            \filldraw[gray] (3,2) circle (0.05);
+            \filldraw[gray] (4,2) circle (0.05);
+            \filldraw[gray] (5,2) circle (0.05);
+            \filldraw[red] (6,2) circle (0.05);
+            \filldraw[red] (7,2) circle (0.05);
+            \filldraw[black] (7,3) circle (0.05) node[anchor=west] {q};
+            \draw[dashed=gray] (-1,-1) -- (-1,1) -- (0,1) -- (0,2) -- (1,2) -- (1,3) -- (6,3) -- (6,4) -- (8,4) -- (8,1) -- (3,1) -- (3,0) -- (2,0) -- (2,-1) -- (-1,-1);
+        \end{tikzpicture}
+        \caption{Example of non connex visibility in 2D, q is visible from p while the visibility points are not 26-connected.}
+        \label{fig:visibility-2d-not-connected}
+    \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+    \section{Fast computation using integer intervals intersections}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+    \section{Feature-aware normal estimation on digital surfaces}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+    \section{Conclusion}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    \begin{credits}
+        \subsubsection{\ackname}
+        This work is partially supported by the French National Research Agency
+        within the StableProxies project (ANR-22-CE46-0006).
+%% \subsubsection{\discintname}
+%% It is now necessary to declare any competing interests or to specifically
+%% state that the authors have no competing interests. Please place the
+%% statement with a bold run-in heading in small font size beneath the
+%% (optional) acknowledgments\footnote{If EquinOCS, our proceedings submission
+%% system, is used, then the disclaimer can be provided directly in the system.},
+%% for example: The authors have no competing interests to declare that are
+%% relevant to the content of this article. Or: Author A has received research
+%% grants from Company W. Author B has received a speaker honorarium from
+%% Company X and owns stock in Company Y. Author C is a member of committee Z.
+    \end{credits}
+%
+% ---- Bibliography ----
+%
+% BibTeX users should specify bibliography style 'splncs04'.
+% References will then be sorted and formatted in the correct style.
+%
+    \bibliographystyle{splncs04}
+    \bibliography{biblio}
+
 \end{document}

### 2025-03-21 DGMM2025/paper.tex
Small fix

--- 2025-03-18 DGMM2025/paper.tex
@@
 %
-\title{Fast and exact visibility on digitized shapes and application to feature-aware normal estimation and pattern detection}
+\title{Fast and exact visibility on digitized shapes and application to feature-aware normal estimation}
 %
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Visibility through tangency of chords}
+
+Introduce full convexity and tangency. \cite{lachaud:2021-dgmm,Lachaud:2022-jmiv}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Fast computation using integer intervals intersections}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Feature-aware normal estimation on digital surfaces}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{credits}
+  \subsubsection{\ackname}
+  This work is partially supported by the French National Research Agency
+  within the StableProxies project (ANR-22-CE46-0006).
+%% \subsubsection{\discintname}
+%% It is now necessary to declare any competing interests or to specifically
+%% state that the authors have no competing interests. Please place the
+%% statement with a bold run-in heading in small font size beneath the
+%% (optional) acknowledgments\footnote{If EquinOCS, our proceedings submission
+%% system, is used, then the disclaimer can be provided directly in the system.},
+%% for example: The authors have no competing interests to declare that are
+%% relevant to the content of this article. Or: Author A has received research
+%% grants from Company W. Author B has received a speaker honorarium from
+%% Company X and owns stock in Company Y. Author C is a member of committee Z.
+\end{credits}
+%
+% ---- Bibliography ----
+%
+% BibTeX users should specify bibliography style 'splncs04'.
+% References will then be sorted and formatted in the correct style.
+%
+\bibliographystyle{splncs04}
+\bibliography{biblio}
+
 \end{document}

### 2025-03-22 DGMM2025/paper.tex

--- 2025-03-20 DGMM2025/paper.tex
@@
 \usepackage{changes}
-\usepackage{amstex}
+%\usepackage{amstex}
 \setauthormarkup{}
@@
 %
-    \title{Fast and exact visibility on digitized shapes and application to feature-aware normal estimation and pattern detection}
+\title{Fast and exact visibility on digitized shapes and application to feature-aware normal estimation}
 %
@@
     \begin{definition}
-        Two points \( p \) and \( q \) on \( K \) are visible if and only if the segment \([p, q]\) is included in \(\text{Star}(K)\), i.e., [p, q] \subseteq \text{Star}(K)\).
+        Two points \( p \) and \( q \) on \( K \) are visible if and only if the segment \([p, q]\) is included in \(\text{Star}(K)\), i.e., \( [p, q] \subseteq \text{Star}(K)\).
     \end{definition}

### 2025-03-24 DGMM2025/paper.tex
latex algorithm

@@
 \usepackage{changes}
-%\usepackage{amstex}
+\usepackage{amstex}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\usepackage{varwidth}
 \setauthormarkup{}
@@
     \section{Introduction}
+
+    Definition Zd
+    Definition Cell complex
+    Definition Star
 
@@
 
+    \begin{algorithm}
+        \caption{Given a cell complex C and a radius \(r\), compute the visibility at every point of C up to distance \(r\).}
+        \label{alg:visibility}
+        \begin{algorithmic}
+
+            \Function{CheckI}{$I$: Interval, ComplexI: list of Interval}
+                \State $[a, b] \gets I$
+                \State $Result \gets \emptyset$
+                \For{each interval $J$ in ComplexI}
+                    \State $[c, d] \gets J$
+                    \If{$\text{Size}(I) \leq \text{Size}(J)$}
+                        \State $Result \gets Result \cup [c-a,d-b+1]$
+                    \EndIf
+                \EndFor
+                \State \Return Result
+            \EndFunction
+
+            \Function{MatchVector}{\text{CurrentIResult}: list of Interval, VectorI: list of Interval, ComplexI: list of Interval}
+                \For{each interval $I$ in VectorI}
+                    \State $\text{CurrentIResult} \gets \text{CurrentIResult} \cap \Call{CheckI}{I, \text{ComplexI}}$
+                \EndFor
+                \State \Return \text{CurrentIResult}
+            \EndFunction
+
+            \Function{Visibility}{\text{C}: Cell complex, \text{Radius}: integer}
+                \State $FigLattices \gets \Call{GetStarFigLattices}{C}$
+                \State $Vectors \gets \Call{GetAllPrimalVectors}{Radius}$
+                \State $Visibility: \text{list of boolean} \gets \emptyset$
+                \State $minFInterval, maxFInterval \gets \Call{GetMinMaxInterval}{FigLattices}$
+                \For{each $V$ in $Vectors$}
+                    \State $VLattice \gets \Call{GetLattice}{\text{V}}$
+                    \For{every shift $tx, ty$ in $FigLattices$}
+                        \State $CurrentIResult \gets [minFInterval, maxFInterval]$
+                        \State $StartingPoint \gets \Call{GetStartingPoint}{tx, ty}$
+                        \For{each $Lattice$ in $VStarLattice$}
+                            \State \begin{varwidth}[t]{\linewidth}
+                                       $CurrentIResult~\gets~MatchVector(CurrentIResult,$\par
+                                       \hskip\algorithmicindent $Lattice.intervals,$\par
+                                       \hskip\algorithmicindent $\text{FigLattices}[StartingPoint + Lattice.position])$
+                            \end{varwidth}
+                        \EndFor
+                        \State \Call{UpdateVisibility}{$Visibility$, $CurrentIResult$}
+                    \EndFor
+                \EndFor
+                \State \Return $Visibility$
+            \EndFunction
+
+        \end{algorithmic}
+    \end{algorithm}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2025-03-24 main.cpp
no interface + mean visibility distance calculation

@@ -52,7 +52,7 @@ int VisibilityRadius = 10;
 double gridstep = 1.0;
 int OMP_max_nb_threads = 1;
 double Time = 0.0;
-bool interface = false;
+bool noInterface = false;
 
 // Constants
 const auto emptyIE = IntegerVector();
@@ -326,6 +326,7 @@ void computeVisibilityOmp(int radius) {
     int minTx, maxTx, minTy, maxTy;
     for (auto segmentIdx = chunkIdx * chunkSize;
          segmentIdx < std::min((chunkIdx + 1) * chunkSize, segmentList.size()); segmentIdx++) {
+      latticeVector = getLatticeVector(segment, axis).data();
       minTx = digital_dimensions[axises_idx[1] + 3] - std::min(0, segment[axises_idx[1]]);
       maxTx = digital_dimensions[axises_idx[1] + 6] + 1 - std::max(0, segment[axises_idx[1]]);
       minTy = digital_dimensions[axises_idx[2] + 3] - std::min(0, segment[axises_idx[2]]);
@@ -454,6 +455,29 @@ void checkParallelism() {
 }
 
 
+void computeMeanDistanceVisibility() {
+  // Print the gridstep
+  std::cout << "Gridstep = " << gridstep << std::endl;
+
+  // Print measure radius
+  std::cout << "Visibility radius = " << VisibilityRadius << std::endl;
+
+  // Print the mean distance between any two visible points
+  double meanDistance = 0;
+  int nbVisiblePairs = 0;
+  for (int i = 0; i < pointels.size(); i++) {
+    auto kdTree = LinearKDTree<Point, 3>(pointels);
+    for (auto point_idx: kdTree.pointsInBall(pointels[i], VisibilityRadius)) {
+      auto tmp = kdTree.position(point_idx);
+      if (isPointLowerThan(pointels[i], tmp) && visibility.isVisible(pointels[i], tmp) && tmp != pointels[i]) {
+        meanDistance += (tmp - pointels[i]).norm();
+        nbVisiblePairs++;
+      }
+    }
+  }
+  std::cout << "Mean distance between visible points = " << meanDistance / nbVisiblePairs << std::endl;
+}
+
 void myCallback() {
   // Select a vertex with the mouse
   if (polyscope::pick::haveSelection()) {
@@ -489,6 +513,9 @@ void myCallback() {
     computeVisibilityOmp(VisibilityRadius);
     Time = trace.endBlock();
   }
+  if (ImGui::Button("Measure Mean Distance Visibility")) {
[…]

### 2025-03-28 DGMM2025/paper.tex
introduction and basic definitions

@@
 
-    Definition Zd
-    Definition Cell complex
-    Definition Star
+    Visibility is a fundamental concept in computational geometry and digital topology, with applications ranging from computer vision to geometric modeling.
+    In this work, we explore visibility through the lens of chord tangency, introducing a novel approach that builds on discrete geometric structures.
+    Our framework leverages the discrete setting of and cell complexes, providing a rigorous foundation for analyzing visibility properties in digital spaces.
+
+    We recall essential definitions from previous works, particularly the notions of , cell complexes, and the star operator as formalized in~\cite{lachaud:2021-dgmm} and~\cite{lachaud:2022-jmiv}.
+    The integer grid serves as our primary space of study, where geometric structures are discretized using cell complexes.
+    A cell complex is a decomposition of space into elementary units—vertices, edges, faces, and higher-dimensional counterparts—forming a combinatorial representation of geometric objects.
+    The star of a cell, as defined in these works, consists of all higher-dimensional cells that contain it, a crucial concept for analyzing local neighborhoods and connectivity.
+
+    Building on these foundations, our study focuses on visibility as determined by the tangency of chords in discrete geometry.
+    We define and analyze how visibility relationships emerge in this context and investigate their combinatorial and topological implications.
+    This approach provides a new perspective on discrete visibility, offering potential applications in digital imaging, surface reconstruction, and computational topology.
+
+    The remainder of this paper is structured as follows.
+    In Section 2, we formalize the concept of chord tangency and its role in visibility analysis.
+    Section 3 enters into the usage of integer intervals intersections to quickly scan the figure in order to recover this visibiltiy.
+    Section 4 presents our main results, using this visibility to compute normals using the CNC estimator~\cite*{lachaud:2022-dcg}.
+    Finally, Section 5 concludes with some other applications of integer intervals intersections in the field.
 
@@
 
+    Let $\Z^d$ be the d-dimensional digital space, $d$ > 0.
+    Let $\mathcal{C}^d$ be the (cubical) cell complex induced by the lattice $\Z^d$ : its 0-cells are the points of $\Z^d$, its 1-cells are the open unit segments joining two 0-cells at distance 1, its 2-cells are the open unit squares, etc., and its d-cells are the d-dimensional open unit hypercubes with vertices in $\Z^d$.
+    We denote $\mathcal{C}^d_k$ the set of its k-cells.
+    In the following, a cell will always designate an element of $\mathcal{C}^d$, and the term subcomplex always designates a subset of $\mathcal{C}^d$.
+
+    A cell $\sigma$ is a face of another cell $\tau$ whenever $\sigma$ is a subset of the topological closure $\bar{\tau}$ of $\tau$, written $\sigma \preccurlyeq \tau$.
+    Given any subcomplex K of $\mathcal{C}^d$, the star $Star(K)$ of K is $\{\tau \in \mathcal{C}^d, s.t.\ \exists\sigma \in K,\sigma \preccurlyeq \tau\}$
+
     Introduce full convexity and tangency. \cite{lachaud:2021-dgmm,lachaud:2022-jmiv}.
@@
     \begin{definition}
-        Two points \( p \) and \( q \) on \( K \) are visible if and only if the segment \([p, q]\) is included in \(\text{Star}(K)\), i.e., \( [p, q] \subseteq \text{Star}(K)\).
+        Two points \( p \) and \( q \) on \( K \) are visible if and only if the segment \([p, q]\) is included in \(\text{Star}(K)\), i.e.,\ \( [p, q] \subseteq \text{Star}(K)\)
     \end{definition}

### 2025-03-28 DGMM2025/paper.tex
citation fix
statement visibility not 26-connected

@@
 
-    We recall essential definitions from previous works, particularly the notions of , cell complexes, and the star operator as formalized in~\cite{lachaud:2021-dgmm} and~\cite{lachaud:2022-jmiv}.
+    We recall essential definitions from previous works, particularly the notions of cell complexes and the star operator as formalized in~\cite{lachaud:2021-dgmm} and~\cite{lachaud:2022-jmiv}.
     The integer grid serves as our primary space of study, where geometric structures are discretized using cell complexes.
@@
     Section 3 enters into the usage of integer intervals intersections to quickly scan the figure in order to recover this visibiltiy.
-    Section 4 presents our main results, using this visibility to compute normals using the CNC estimator~\cite*{lachaud:2022-dcg}.
+    Section 4 presents our main results, using this visibility to compute normals using the CNC estimator~\cite{lachaud:2022-dcg}.
     Finally, Section 5 concludes with some other applications of integer intervals intersections in the field.
@@
     Given any subcomplex K of $\mathcal{C}^d$, the star $Star(K)$ of K is $\{\tau \in \mathcal{C}^d, s.t.\ \exists\sigma \in K,\sigma \preccurlyeq \tau\}$
-
-    Introduce full convexity and tangency. \cite{lachaud:2021-dgmm,lachaud:2022-jmiv}.
 
@@
     \end{figure}
+
+    We note that one particular aspect of this visibility definition is that all visible points from a given point taken as a separate complex are not necessarily 26-connected~\ref{fig:visibility-2d-not-connected}.
+    Furthermore, we conjecture that they even may not be $n$-connected for $n$ arbitrarily large.
+    This characteristic has implications for the applicability of Algorithm 3 from~\cite{lachaud:2022-jmiv}, as the algorithm assumes that visited points are 26-connected, potentially leading to incomplete collection of visible points.
 

### 2025-03-31 DGMM2025/paper.tex
fixing compilation errors

@@
 \usepackage{changes}
-\usepackage{amstex}
 \usepackage{algorithm}
@@
     The integer grid serves as our primary space of study, where geometric structures are discretized using cell complexes.
-    A cell complex is a decomposition of space into elementary units—vertices, edges, faces, and higher-dimensional counterparts—forming a combinatorial representation of geometric objects.
+    A cell complex is a decomposition of space into elementary units (vertices, edges, faces, and higher-dimensional counterparts) forming a combinatorial representation of geometric objects.
     The star of a cell, as defined in these works, consists of all higher-dimensional cells that contain it, a crucial concept for analyzing local neighborhoods and connectivity.

### 2025-04-03 main.cpp
sampling

@@ -454,6 +454,16 @@ void checkParallelism() {
   OMP_max_nb_threads = cnt_max[0];
 }
 
+std::unordered_set<int> pickSet(int N, int k, std::mt19937 &gen) {
+  std::uniform_int_distribution<> dis(1, N);
+  std::unordered_set<int> elems;
+
+  while (elems.size() < k) {
+    elems.insert(dis(gen));
+  }
+
+  return elems;
+}
 
 void computeMeanDistanceVisibility() {
   // Print the gridstep
@@ -465,7 +475,14 @@ void computeMeanDistanceVisibility() {
   // Print the mean distance between any two visible points
   double meanDistance = 0;
   int nbVisiblePairs = 0;
-  for (int i = 0; i < pointels.size(); i++) {
+
+  // pick 100 random pointels
+
+  unsigned seed = std::chrono::system_clock::now().time_since_epoch().count();
+  std::mt19937 gen(seed);
+  auto pointelsSample = pickSet(pointels.size(), 100, gen);
+
+  for (int i = 0; i < pointelsSample.size(); i++) {
     auto kdTree = LinearKDTree<Point, 3>(pointels);
     for (auto point_idx: kdTree.pointsInBall(pointels[i], VisibilityRadius)) {
       auto tmp = kdTree.position(point_idx);

### 2025-04-03 DGMM2025/paper.tex
adjusted visibility examples to better see line splittings
fix ?

@@
         \begin{tikzpicture}
-            \draw[dashed] (0,0) -- (4,2);
+            \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.75,2.75);
+            \draw[dashed] (0,0) -- (2,1);
             \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p1};
-            \filldraw[black] (4,2) circle (0.05) node[anchor=north] {q1};
-            \draw (0,0) -- (1,0) -- (2,0) -- (2,1) -- (3,1) -- (3,2) -- (4,2);
-            \draw[dashed=gray] (-1,0) -- (-1,1) -- (0,1) -- (1,1) -- (1,2) -- (2,2) -- (2,3) -- (3,3) -- (4,3) -- (5,3) -- (5,2) -- (5,1) -- (4,1) -- (4,0) -- (3,0) -- (3,-1) -- (2,-1) -- (1,-1) -- (0,-1) -- (-1,-1) -- (-1,0);
+            \filldraw[black] (2,1) circle (0.05) node[anchor=north] {q1};
+            \draw [thick] (0,0) -- (0.5,0) -- (1,0) -- (1,0.5) -- (1.5,0.5) -- (1.5,1) -- (2,1);
+            \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,0.5) -- (0.5,0.5) -- (0.5,1) -- (1,1) -- (1,1.5) -- (2.5,1.5) -- (2.5,0.5) -- (2,0.5) -- (2,0) -- (1.5,0) -- (1.5,-0.5) -- (-0.5,-0.5);
         \end{tikzpicture}
-        \hspace{\floatsep}
         \begin{tikzpicture}
-            \draw[red,dashed] (0,0) -- (3,2);
+            \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.25,3.25);
+            \draw[red,dashed,thick] (0,0) -- (1.5,1);
             \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p2};
-            \filldraw[black] (3,2) circle (0.05) node[anchor=north] {q2};
-            \draw (0,0) -- (0,1) -- (0,2) -- (1,2) -- (1,3) -- (2,3) -- (2,2) -- (3,2);
-            \draw[dashed=gray] (-1,0) -- (-1,1) -- (-1,2) -- (-1,3) -- (0,3) -- (0,4) -- (1,4) -- (2,4) -- (3,4) -- (3,3) -- (4,3) -- (4,2) -- (4,1) -- (3,1) -- (2,1) -- (1,1) -- (1,0) -- (1,-1) -- (0,-1) -- (-1,-1) -- (-1,0);
+            \filldraw[black] (1.5,1) circle (0.05) node[anchor=north] {q2};
+            \draw [thick] (0,0) -- (0,1) -- (0.5,1) -- (0.5,1.5) -- (1,1.5) -- (1,1) -- (1.5,1);
+            \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (0,1.5) -- (0,2) -- (1.5,2) -- (1.5,1.5) -- (2,1.5)  -- (2,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
         \end{tikzpicture}
-        \newline
-        \newline
         \begin{tikzpicture}
-            \draw[red,dashed] (0,0) -- (2,0);
+            \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
+            \draw[red,dashed,thick] (0,0) -- (1,0);
             \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p3};
-            \filldraw[black] (2,0) circle (0.05) node[anchor=north] {q3};
-            \draw (0,0) -- (0,1) -- (0,2) -- (1,2) -- (2,2) -- (2,1) -- (2,0);
-            \draw[dashed=gray] (-1,-1) -- (-1,3) -- (3,3) -- (3,-1) -- (1,-1) -- (1,1) -- (1,-1) -- (-1,-1);
+            \filldraw[black] (1,0) circle (0.05) node[anchor=north] {q3};
+            \draw [thick] (0,0) -- (0,1) -- (1,1) -- (1,0);
+            \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,-0.5) -- (-0.5,-0.5) -- (0.5,-0.5) -- (0.5,0.5);
         \end{tikzpicture}
-        \hspace{\floatsep}
         \begin{tikzpicture}
-            \draw[red,dashed] (0,0) -- (2,2);
+            \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
+            \draw[red,dashed,thick] (0,0) -- (1,1);
             \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p4};
-            \filldraw[black] (2,2) circle (0.05) node[anchor=north] {q4};
-            \draw (0,0) -- (0,1) -- (0,2) -- (1,2) -- (2,2);
-            \draw[dashed=gray] (-1,0) -- (-1,1) -- (-1,2) -- (-1,3) -- (0,3) -- (1,3) -- (2,3) -- (3,3) -- (3,2) -- (3,1) -- (2,1) -- (1,1) -- (1,0) -- (1,-1) -- (0,-1) -- (-1,-1) -- (-1,0);
+            \filldraw[black] (1,1) circle (0.05) node[anchor=north] {q4};
+            \draw [thick] (0,0) -- (0,1) -- (1,1);
+            \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
         \end{tikzpicture}
@@
 
-            \Function{CheckI}{$I$: Interval, ComplexI: list of Interval}
+            \Function{Translation}{$I$: Interval, L: list of Interval}
                 \State $[a, b] \gets I$
                 \State $Result \gets \emptyset$
-                \For{each interval $J$ in ComplexI}
+                \For{each interval $J$ in L}
                     \State $[c, d] \gets J$
                     \If{$\text{Size}(I) \leq \text{Size}(J)$}
-                        \State $Result \gets Result \cup [c-a,d-b+1]$
+                        \State $Result \gets Result \cup [c-a,d-b]$
                     \EndIf
@@
 
-            \Function{MatchVector}{\text{CurrentIResult}: list of Interval, VectorI: list of Interval, ComplexI: list of Interval}
+            \Function{MatchVector}{\text{CurrentIResult}: list of Interval, VectorI: list of Interval, L: list of Interval}
                 \For{each interval $I$ in VectorI}
-                    \State $\text{CurrentIResult} \gets \text{CurrentIResult} \cap \Call{CheckI}{I, \text{ComplexI}}$
+                    \State $\text{CurrentIResult} \gets \text{CurrentIResult} \cap \Call{Translation}{I, \text{L}}$
                 \EndFor
@@
 
+        \end{algorithmic}
+    \end{algorithm}
+
+    \begin{algorithm}
+        \caption{Given 2 lists of intervals I and J, find $I \cup J$, the intersection of those 2 lists}
+        \label{alg:intersection}
+        \begin{algorithmic}
+            \Function{Intersection (\cup)}{\text{I, J}: list of Intervals}
+                \State R \gets \emptyset
+                \State k1, k2 = 0
+                \While{k1 < I.nbIntervals \And k2 < J.nbIntervals}
+                    \State i \gets I[k1]
+                    \State j \gets J[k2]
+
+                \EndWhile
+            \EndFunction
         \end{algorithmic}

### 2025-04-03 main.cpp

@@ -257,11 +257,11 @@ LatticeSet getLatticeVector(const IntegerVector &segment, Dimension axis) {
 IntegralIntervals<Integer>
 checkInterval(const std::pair<int, int> toCheck, const IntegralIntervals<Integer> &figIntervals) {
   IntegralIntervals<Integer> result;
-  result.clear();
+  result.reserve(figIntervals.size());
   auto toCheckSize = toCheck.second - toCheck.first;
   for (auto interval: figIntervals.data()) {
     if (interval.second - interval.first >= toCheckSize) {
-      result.insert(interval.first - toCheck.first, interval.second - toCheck.second + 1);
+      result.push_back(interval.first - toCheck.first, interval.second - toCheck.second);
     }
   }
   return result;

### 2025-04-03 main.cpp
fix ?

@@ -257,11 +257,11 @@ LatticeSet getLatticeVector(const IntegerVector &segment, Dimension axis) {
 IntegralIntervals<Integer>
 checkInterval(const std::pair<int, int> toCheck, const IntegralIntervals<Integer> &figIntervals) {
   IntegralIntervals<Integer> result;
-  result.reserve(figIntervals.size());
+  result.data().reserve(figIntervals.size());
   auto toCheckSize = toCheck.second - toCheck.first;
   for (auto interval: figIntervals.data()) {
     if (interval.second - interval.first >= toCheckSize) {
-      result.push_back(interval.first - toCheck.first, interval.second - toCheck.second);
+      result.data().emplace_back(interval.first - toCheck.first, interval.second - toCheck.second);
     }
   }
   return result;

### 2025-04-03 main.cpp
IntegralInterval removal from code

@@ -24,10 +24,12 @@ typedef PointVector<3, Integer> IntegerVector;
 typedef std::vector<IntegerVector> IntegerVectors;
 typedef Shortcuts<KSpace> SH3;
 typedef ShortcutsGeometry<KSpace> SHG3;
-typedef PointVector<3, Integer> IntegerVector;
-typedef std::vector<IntegerVector> IntegerVectors;
 typedef DigitalConvexity<KSpace> Convexity;
 typedef typename Convexity::LatticeSet LatticeSet;
+typedef IntegerVector Point;
+
+typedef std::pair<Integer, Integer> Interval;
+typedef std::vector<Interval> Intervals;
 
 // Polyscope
 polyscope::PointCloud *psVisibility = nullptr;
@@ -116,9 +118,9 @@ public:
     return true;
   }
 
-  void set(const Point &offset, const IntegralIntervals<Integer> &value, const size_t vectorIdx) {
+  void set(const Point &offset, const Intervals &value, const size_t vectorIdx) {
     auto p = offset;
-    for (auto &interval: value.data()) {
+    for (auto &interval: value) {
       for (int i = interval.first / 2; i <= interval.second / 2; i++) {
         p[mainAxis] = i;
         visibles[this->getPointIdx(p) * vectorsSize + vectorIdx] = true;
@@ -254,32 +256,29 @@ LatticeSet getLatticeVector(const IntegerVector &segment, Dimension axis) {
  * @param figIntervals
  * @return
  */
-IntegralIntervals<Integer>
-checkInterval(const std::pair<int, int> toCheck, const IntegralIntervals<Integer> &figIntervals) {
-  IntegralIntervals<Integer> result;
-  result.data().reserve(figIntervals.size());
+Intervals
+checkInterval(const std::pair<int, int> toCheck, const Intervals &figIntervals) {
+  Intervals result;
+  result.reserve(figIntervals.size());
   auto toCheckSize = toCheck.second - toCheck.first;
-  for (auto interval: figIntervals.data()) {
+  for (auto interval: figIntervals) {
     if (interval.second - interval.first >= toCheckSize) {
-      result.data().emplace_back(interval.first - toCheck.first, interval.second - toCheck.second);
+      result.emplace_back(interval.first - toCheck.first, interval.second - toCheck.second);
     }
   }
   return result;
 }
 
[…]

### 2025-04-03 main.cpp
wip fixing changements

@@ -26,7 +26,6 @@ typedef Shortcuts<KSpace> SH3;
 typedef ShortcutsGeometry<KSpace> SHG3;
 typedef DigitalConvexity<KSpace> Convexity;
 typedef typename Convexity::LatticeSet LatticeSet;
-typedef IntegerVector Point;
 
 typedef std::pair<Integer, Integer> Interval;
 typedef std::vector<Interval> Intervals;
@@ -257,7 +256,7 @@ LatticeSet getLatticeVector(const IntegerVector &segment, Dimension axis) {
  * @return
  */
 Intervals
-checkInterval(const std::pair<int, int> toCheck, const Intervals &figIntervals) {
+checkInterval(const Interval toCheck, const Intervals &figIntervals) {
   Intervals result;
   result.reserve(figIntervals.size());
   auto toCheckSize = toCheck.second - toCheck.first;

### 2025-04-07 DGMM2025/paper.tex
tmpfix

@@
 \usepackage{varwidth}
+\usepackage{algc}
 \setauthormarkup{}
@@
     \begin{definition}
-        Two points \( p \) and \( q \) on \( K \) are visible if and only if the segment \([p, q]\) is included in \(\text{Star}(K)\), i.e.,\ \( [p, q] \subseteq \text{Star}(K)\)
+        Two points \( p \) and \( q \) on \( K \) are visible if and only if the segment \([p, q]\) is included in \(\text{Star}(K)\), i.e., \( [p, q] \subseteq \text{Star}(K)\)
     \end{definition}
@@
 
+    \begin{definition}
+        An interval $I$ is defined as the pair $[a,b], a \leq b, st. \forall a \leq n \leq b, n \in I$
+    \end{definition}
+
     \begin{algorithm}
@@
 
-            \Function{Translation}{$I$: Interval, L: list of Interval}
+            \Function{Translation}{$I$: Interval, L: Intervals}
                 \State $[a, b] \gets I$
@@
 
-            \Function{MatchVector}{\text{CurrentIResult}: list of Interval, VectorI: list of Interval, L: list of Interval}
+            \Function{MatchVector}{\text{CurrentIResult}: Intervals, VectorI: Intervals, L: Intervals}
                 \For{each interval $I$ in VectorI}
@@
                 \State $Vectors \gets \Call{GetAllPrimalVectors}{Radius}$
-                \State $Visibility: \text{list of boolean} \gets \emptyset$
+                \State $Visibility: \text{vector of boolean} \gets \emptyset$
                 \State $minFInterval, maxFInterval \gets \Call{GetMinMaxInterval}{FigLattices}$
@@
     \begin{algorithm}
-        \caption{Given 2 lists of intervals I and J, find $I \cup J$, the intersection of those 2 lists}
+        \caption{Given 2 lists of intervals K and L, find $K \cup L$, the intersection of those 2 lists}
         \label{alg:intersection}
         \begin{algorithmic}
-            \Function{Intersection (\cup)}{\text{I, J}: list of Intervals}
-                \State R \gets \emptyset
-                \State k1, k2 = 0
-                \While{k1 < I.nbIntervals \And k2 < J.nbIntervals}
-                    \State i \gets I[k1]
-                    \State j \gets J[k2]
-
+            \Function{Intersection ($\cap$)}{\text{K, L}: Intervals}
+                \State $R \gets \emptyset$
+                \State $k, l \gets 0$
+                \While{$k < K.nbIntervals \And l < L.nbIntervals$}
+                    \State $[a,b] \gets K[k]$
+                    \State $[c,d] \gets L[l]$
+                    \State $cMin \gets max(a, c)$
+                    \State $cMax \gets max(b, d)$
+                    \If{$cMax < cMin$}
+                        \State $R.append([cMin, cMax])$
+                    \EndIf
+                    \If{$a \leq d$}
+                        \State $k \gets k+1$
+                    \EndIf
+                    \If{$c \leq b$}
+                        \State $l \gets l+1$
+                    \EndIf
                 \EndWhile
+                \State \Return $R$
             \EndFunction

### 2025-04-07 DGMM2025/paper.tex
removing the ghost package

@@
 \usepackage{varwidth}
-\usepackage{algc}
 \setauthormarkup{}
@@
     \begin{algorithm}
-        \caption{Given a cell complex C and a radius \(r\), compute the visibility at every point of C up to distance \(r\).}
+        \caption{Given a cell complex C and a radius $r$, compute the visibility at every point of C up to distance $r$.}
         \label{alg:visibility}
         \begin{algorithmic}
-
-            \Function{Translation}{$I$: Interval, L: Intervals}
+            \Function{Translation}{I: Interval, L: Intervals}
                 \State $[a, b] \gets I$
@@
                     \If{$\text{Size}(I) \leq \text{Size}(J)$}
-                        \State $Result \gets Result \cup [c-a,d-b]$
+                        \State $Result \gets Result \cap [c-a,d-b]$
                     \EndIf
@@
     \begin{algorithm}
-        \caption{Given 2 lists of intervals K and L, find $K \cup L$, the intersection of those 2 lists}
+        \caption{Given 2 lists of intervals K and L, find $K \cap L$, the intersection of those 2 lists}
         \label{alg:intersection}

### 2025-04-07 DGMM2025/paper.tex
removing the ghost package
added interval definitions

@@
 \usepackage{varwidth}
+\usepackage{mathtools}
 \setauthormarkup{}
@@
 
+    \begin{definition}
+        $\forall A = [a,b], B = [c,d] \in interval, A < B \Leftrightarrow b < c$
+    \end{definition}
+
+    \begin{definition}
+        An intervals $L$ is an ordered list of intervals ${L_1,\ldots,L_n}$ st. $\forall i \in \mathbb{N}, L_i < L_{i+1}$
+    \end{definition}
+
+    \begin{definition}
+        A translation of an interval $A$ is defined as $A+t \coloneqq [a+t, b+t]$
+    \end{definition}
+
+    \begin{definition}
+        All translations $T$ of an interval $A$ on an intervals $L$ is defined as $\{t, st. A+t \subset L\}$
+    \end{definition}
+
     \begin{algorithm}
@@
 
-            \Function{MatchVector}{\text{CurrentIResult}: Intervals, VectorI: Intervals, L: Intervals}
-                \For{each interval $I$ in VectorI}
-                    \State $\text{CurrentIResult} \gets \text{CurrentIResult} \cap \Call{Translation}{I, \text{L}}$
-                \EndFor
-                \State \Return \text{CurrentIResult}
-            \EndFunction
-
             \Function{Visibility}{\text{C}: Cell complex, \text{Radius}: integer}
@@
                         \For{each $Lattice$ in $VStarLattice$}
-                            \State \begin{varwidth}[t]{\linewidth}
-                                       $CurrentIResult~\gets~MatchVector(CurrentIResult,$\par
-                                       \hskip\algorithmicindent $Lattice.intervals,$\par
-                                       \hskip\algorithmicindent $\text{FigLattices}[StartingPoint + Lattice.position])$
-                            \end{varwidth}
+                            \For{each interval $I$ in $Lattice.intervals$}
+                                \State $\text{CurrentIResult} \gets \text{CurrentIResult} \cap \Call{Translation}{I, \text{FigLattices}[StartingPoint + Lattice.position])}$
+                            \EndFor
                         \EndFor
@@
                     \State $[c,d] \gets L[l]$
-                    \State $cMin \gets max(a, c)$
-                    \State $cMax \gets max(b, d)$
+                    \State $cMin \gets \max(a, c)$
+                    \State $cMax \gets \max(b, d)$
                     \If{$cMax < cMin$}

### 2025-04-07 DGMM2025/paper.tex
reworked figures and algorithms

@@
 \usepackage{algorithm}
-\usepackage{algpseudocode}
+\usepackage[noend]{algpseudocode}
 \usepackage{varwidth}
@@
         \centering
+        \begin{tabular}{cc|cc}
             \begin{tikzpicture}
@@
                 \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,0.5) -- (0.5,0.5) -- (0.5,1) -- (1,1) -- (1,1.5) -- (2.5,1.5) -- (2.5,0.5) -- (2,0.5) -- (2,0) -- (1.5,0) -- (1.5,-0.5) -- (-0.5,-0.5);
-        \end{tikzpicture}
+            \end{tikzpicture}&&&
             \begin{tikzpicture}
@@
                 \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (0,1.5) -- (0,2) -- (1.5,2) -- (1.5,1.5) -- (2,1.5)  -- (2,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
-        \end{tikzpicture}
+            \end{tikzpicture}\\
+            Visible&&&Non Visible\\\\
+            \hline\\
             \begin{tikzpicture}
@@
                 \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,-0.5) -- (-0.5,-0.5) -- (0.5,-0.5) -- (0.5,0.5);
-        \end{tikzpicture}
+            \end{tikzpicture}&&&
             \begin{tikzpicture}
@@
                 \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
-        \end{tikzpicture}
-        \caption{Examples of visibility in 2D, only q1 is visible from p1, q2 is not visible from p2 (gets out of the star), q3 is not visible from p3 (gets out of the star from a 1-d cell), q4 is not visible from p4 (gets out of the star from a 0-d cell).}
+            \end{tikzpicture}\\
+            Non Visible (from a 1-d cell)&&&Non Visible (from a 0-d cell)
+        \end{tabular}
+        \caption{Examples of visibility in 2D.}
         \label{fig:visibility-2d}
@@
         \begin{tikzpicture}
-            \draw (0,0) -- (1,0) -- (1,1) -- (2,1) -- (2,2) -- (3,2) -- (4,2) -- (5,2) -- (6,2) -- (7,2) -- (7,3);
-            \draw [black, dashed] (0,0) -- (7,3);
-            \draw [red, dashed] (0,0) -- (7,2);
-            \draw [red, dashed] (0,0) -- (6,2);
+            \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (5.25,3.25);
+            \draw[thick] (0,0) -- (0.5,0) -- (0.5,0.5) -- (1,0.5) -- (1,1) -- (3.5,1) -- (3.5,1.5);
+            \draw [black, dashed] (0,0) -- (3.5,1.5);
+            \draw [red, dashed] (0,0) -- (3.5,1);
+            \draw [red, dashed] (0,0) -- (3,1);
             \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p};
-            \filldraw[gray] (1,0) circle (0.05);
+            \filldraw[gray] (0.5,0) circle (0.05);
+            \filldraw[gray] (0.5,0.5) circle (0.05);
+            \filldraw[gray] (1,0.5) circle (0.05);
             \filldraw[gray] (1,1) circle (0.05);
+            \filldraw[gray] (1.5,1) circle (0.05);
             \filldraw[gray] (2,1) circle (0.05);
-            \filldraw[gray] (2,2) circle (0.05);
-            \filldraw[gray] (3,2) circle (0.05);
-            \filldraw[gray] (4,2) circle (0.05);
-            \filldraw[gray] (5,2) circle (0.05);
-            \filldraw[red] (6,2) circle (0.05);
-            \filldraw[red] (7,2) circle (0.05);
-            \filldraw[black] (7,3) circle (0.05) node[anchor=west] {q};
-            \draw[dashed=gray] (-1,-1) -- (-1,1) -- (0,1) -- (0,2) -- (1,2) -- (1,3) -- (6,3) -- (6,4) -- (8,4) -- (8,1) -- (3,1) -- (3,0) -- (2,0) -- (2,-1) -- (-1,-1);
+            \filldraw[gray] (2.5,1) circle (0.05);
+            \filldraw[red] (3,1) circle (0.05);
+            \filldraw[red] (3.5,1) circle (0.05);
+            \filldraw[black] (3.5,1.5) circle (0.05) node[anchor=west] {q};
+            \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,0.5) -- (0,0.5) -- (0,1) -- (0.5,1) -- (0.5,1.5) -- (3,1.5) -- (3,2) -- (4,2) -- (4,0.5) -- (1.5,0.5) -- (1.5,0) -- (1,0) -- (1,-0.5) -- (-0.5,-0.5);
         \end{tikzpicture}
@@
 
-    \begin{definition}
-        An interval $I$ is defined as the pair $[a,b], a \leq b, st. \forall a \leq n \leq b, n \in I$
-    \end{definition}
+    To improve computation time, we will use lattice sets of integer intervals.
 
     \begin{definition}
-        $\forall A = [a,b], B = [c,d] \in interval, A < B \Leftrightarrow b < c$
-    \end{definition}
-
-    \begin{definition}
-        An intervals $L$ is an ordered list of intervals ${L_1,\ldots,L_n}$ st. $\forall i \in \mathbb{N}, L_i < L_{i+1}$
+        A sequence of intervals is an ordered list of intervals $L = ([a_i,b_i])_{i=1,\ldots,n}$ such that $b_i + 1 < a_{i+1}$, i.e., disjoint intervals with at least a missing integer.
     \end{definition}
@@
     \begin{definition}
-        All translations $T$ of an interval $A$ on an intervals $L$ is defined as $\{t, st. A+t \subset L\}$
+        A translation of a sequence of intervals $L$ is the sequence defined as $L+t \coloneqq \{L_1+t,\ldots,L_n+t\}$
     \end{definition}
 
+    \begin{definition}
+        All translations $T$ of an interval or a sequence of intervals $A$ in a sequence of intervals $L$ are defined as $ T \coloneqq t, st. A+t \subset L\}$
+    \end{definition}
+
+    We will consider the lattices as a map from points $p \in \R^{d-1}$ to a sequence of intervals, where all coordinates are doubled, so that the represented cell $\forall c \in \R^d$ will have a dimension equal to $\sum_{i=1}^d \left(c[i]\mod2\right)$.
+
+    \begin{figure}
+        \centering
+        \caption{Representation of a 2d cell complex (here the star of a given curve) as lattices}
+        \label{fig:lattice-representation}
+        \usetikzlibrary {arrows.meta,decorations.shapes}
+        \begin{tabular}{c c}
+            \begin{tikzpicture}
+                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.25,-0.25) grid (7.25,7.25);
+                \filldraw[black] (1,4) circle (0.05);
+                \filldraw[black] (1,5) circle (0.05);
+                \filldraw[black] (2,5) circle (0.05);
+                \filldraw[black] (3,5) circle (0.05);
+                \filldraw[black] (3,4) circle (0.05);
+                \filldraw[black] (3,3) circle (0.05);
+                \filldraw[black] (3,2) circle (0.05);
+                \filldraw[black] (2,2) circle (0.05);
+                \filldraw[black] (2,1) circle (0.05);
+                \filldraw[black] (1,1) circle (0.05);
+                \filldraw[black] (1,0) circle (0.05);
+                \filldraw[black] (2,0) circle (0.05);
+                \filldraw[black] (3,0) circle (0.05);
+                \filldraw[black] (3,1) circle (0.05);
+                \filldraw[black] (4,1) circle (0.05);
+                \filldraw[black] (5,1) circle (0.05);
+                \draw[-{Stealth[length=3mm]}=black] (-1,-1) -- (-1,6.5);
+                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=10mm}] {(-1,-1) -- (-1,7)};
+                \draw[black] (1,4) -- (1,5) -- (3,5) -- (3,2) -- (2,2) -- (2,1) -- (1,1) -- (1,0) -- (3,0) -- (3,1) -- (5,1);
+                \draw[thick,dashed] (1,3) -- (1,2) -- (0,2) -- (0,-1) -- (4,-1) -- (4,0) -- (6,0) -- (6,2) -- (4,2) -- (4,6) -- (0,6) -- (0,3) -- (2,3) -- (2,4);
+            \end{tikzpicture} &
+            %      \begin{tikzpicture}
+            %     \foreach \y in {1,1.5,...,6} {
+            %       \draw[thin, lightgray,xshift=-1cm,yshift=-1cm] (0.75,\y) -- (6.25,\y);
+            %     }
+            %     \draw[-{Stealth[length=3mm]}=black] (0,0) -- (0,5.5);
+            %     \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=10mm}] {(0,0) -- (0,5)};
+            %     \draw[black] (1,4) -- (1,5) -- (3,5) -- (3,2) -- (2,2) -- (2,1) -- (1,1) -- (1,0) -- (3,0) -- (3,1) -- (5,1);
+            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,5)--(3.1,5);
+            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,4.5)--(1.1,4.5);
+            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,4.5)--(3.1,4.5);
+            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,4)--(1.1,4);
+            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,4)--(3.1,4);
+            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,3.5)--(3.1,3.5);
+            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,3)--(3.1,3);
+            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,2.5)--(3.1,2.5);
+            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.9,2)--(3.1,2);
+            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.9,1.5)--(2.1,1.5);
+            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,1)--(2.1,1);
+            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,1)--(5.1,1);
+            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,0.5)--(1.1,0.5);
+            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,0.5)--(3.1,0.5);
+            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,0)--(3.1,0);
+            %     \filldraw[white,yshift=-1cm] (0,0) circle (0.01); % readjust the height to match the original path
+            % \end{tikzpicture} &
+            \begin{tikzpicture}
+                \foreach \y in {0,0.5,...,7} {
+                    \draw[thin, lightgray,xshift=-1cm,yshift=-1cm] (-0.25,\y) -- (7.25,\y);
+                }
+                \draw[-{Stealth[length=3mm]}=black] (-1,-1) -- (-1,6.5);
+                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=10mm}] {(-1,-1) -- (-1,6.5)};
+                \draw[thick,dashed] (1,3) -- (1,2) -- (0,2) -- (0,-1) -- (4,-1) -- (4,0) -- (6,0) -- (6,2) -- (4,2) -- (4,6) -- (0,6) -- (0,3) -- (2,3) -- (2,4);
+                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,5.5)--(3.6,5.5);
+                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,5)--(3.6,5);
+                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,4.5)--(3.6,4.5);
+                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,4)--(1.6,4);
+                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,4)--(3.6,4);
+                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,3.5)--(1.6,3.5);
+                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,3.5)--(3.6,3.5);
+                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,3)--(3.6,3);
+                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2.5)--(3.6,2.5);
+                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2)--(3.6,2);
+                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,1.5)--(5.6,1.5);
+                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,1)--(5.6,1);
+                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,0.5)--(5.6,0.5);
+                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,0)--(3.6,0);
+                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,-0.5)--(3.6,-0.5);
+                \filldraw[white,yshift=-1.25cm] (0,0) circle (0.01); % readjust the height to match the original path
+            \end{tikzpicture}
+        \end{tabular}
+
+    \end{figure}
+
     \begin{algorithm}
-        \caption{Given a cell complex C and a radius $r$, compute the visibility at every point of C up to distance $r$.}
+        \caption{Given a cell complex C and a radius $r$, compute the visibility at every point of C up to distance $r$. We assume z being the lattice main axis, x and y being the auxiliary axises}
         \label{alg:visibility}
         \begin{algorithmic}
-            \Function{Translation}{I: Interval, L: Intervals}
-                \State $[a, b] \gets I$
-                \State $Result \gets \emptyset$
-                \For{each interval $J$ in L}
-                    \State $[c, d] \gets J$
-                    \If{$\text{Size}(I) \leq \text{Size}(J)$}
-                        \State $Result \gets Result \cap [c-a,d-b]$
-                    \EndIf
+            \Function{Visibility}{\text{C}: Cell complex, \text{r}: Integer}
+                \State $\Omega \gets \Call{Star}{C}$ \Comment{Lattices of the star of the studied cell complex}
+                \State $Vectors \gets \Call{GetAllPrimalVectors}{r}$
+                \State $V: \text{vector of boolean} \gets [0, \ldots, 0]$ \Comment{length $Size(Vectors) * PointelsAmount$}
+                \State $low, high \gets \Call{BoundingBoxZ}{\Omega}$
+                \ForAll{$v$ in $Vectors$}
+                    \State $VStar \gets \Call{Star}{\text{v}}$
+                    \ForAll{shift $tx, ty$ in $\Omega$}
+                        \State $R \gets [low, high]$
+                        \State $S: \R^3 \gets [2tx, 2ty,0]$
+                        \ForAll{lattice $L$ in $VStar$}
+                            \State $\text{R} \gets \text{R} \cap \Call{Translations}{L.intervals,\Omega[S + L.position]}$
                         \EndFor
-                \State \Return Result
-            \EndFunction
-
-            \Function{Visibility}{\text{C}: Cell complex, \text{Radius}: integer}
-                \State $FigLattices \gets \Call{GetStarFigLattices}{C}$
-                \State $Vectors \gets \Call{GetAllPrimalVectors}{Radius}$
-                \State $Visibility: \text{vector of boolean} \gets \emptyset$
-                \State $minFInterval, maxFInterval \gets \Call{GetMinMaxInterval}{FigLattices}$
-                \For{each $V$ in $Vectors$}
-                    \State $VLattice \gets \Call{GetLattice}{\text{V}}$
-                    \For{every shift $tx, ty$ in $FigLattices$}
-                        \State $CurrentIResult \gets [minFInterval, maxFInterval]$
-                        \State $StartingPoint \gets \Call{GetStartingPoint}{tx, ty}$
-                        \For{each $Lattice$ in $VStarLattice$}
-                            \For{each interval $I$ in $Lattice.intervals$}
-                                \State $\text{CurrentIResult} \gets \text{CurrentIResult} \cap \Call{Translation}{I, \text{FigLattices}[StartingPoint + Lattice.position])}$
+                        \State \Call{UpdateVisibility}{$V$, $R$}
                     \EndFor
                 \EndFor
-                        \State \Call{UpdateVisibility}{$Visibility$, $CurrentIResult$}
-                    \EndFor
-                \EndFor
-                \State \Return $Visibility$
+                \State \Return $V$
             \EndFunction
-
         \end{algorithmic}
@@
     \begin{algorithm}
-        \caption{Given 2 lists of intervals K and L, find $K \cap L$, the intersection of those 2 lists}
+        \caption{Given 2 lists of intervals $K$ and $L$, find $K \cap L$, the intersection of those 2 lists}
         \label{alg:intersection}
@@
                     \State $[c,d] \gets L[l]$
-                    \State $cMin \gets \max(a, c)$
-                    \State $cMax \gets \max(b, d)$
-                    \If{$cMax < cMin$}
-                        \State $R.append([cMin, cMax])$
+                    \State $e \gets \max(a, c)$
+                    \State $f \gets \min(b, d)$
+                    \If{$e < f$}
+                        \State $R.append([e, f])$
                     \EndIf
-                    \If{$a \leq d$}
+                    \If{$b \leq d$}
                         \State $k \gets k+1$
                     \EndIf
-                    \If{$c \leq b$}
+                    \If{$d \leq b$}
                         \State $l \gets l+1$

### 2025-04-08 DGMM2025/paper.tex
small reformat
scaling down the lattice examples

@@
                 \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,0.5) -- (0.5,0.5) -- (0.5,1) -- (1,1) -- (1,1.5) -- (2.5,1.5) -- (2.5,0.5) -- (2,0.5) -- (2,0) -- (1.5,0) -- (1.5,-0.5) -- (-0.5,-0.5);
-            \end{tikzpicture}&&&
+            \end{tikzpicture} & & &
             \begin{tikzpicture}
@@
                 \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (0,1.5) -- (0,2) -- (1.5,2) -- (1.5,1.5) -- (2,1.5)  -- (2,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
-            \end{tikzpicture}\\
-            Visible&&&Non Visible\\\\
+            \end{tikzpicture} \\
+            Visible                       & & & Non Visible                   \\\\
             \hline\\
@@
                 \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,-0.5) -- (-0.5,-0.5) -- (0.5,-0.5) -- (0.5,0.5);
-            \end{tikzpicture}&&&
+            \end{tikzpicture} & & &
             \begin{tikzpicture}
@@
             \end{tikzpicture}\\
-            Non Visible (from a 1-d cell)&&&Non Visible (from a 0-d cell)
+            Non Visible (from a 1-d cell) & & & Non Visible (from a 0-d cell)
         \end{tabular}
@@
         \begin{tabular}{c c}
-            \begin{tikzpicture}
+            \begin{tikzpicture}[scale=0.75]
                 \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.25,-0.25) grid (7.25,7.25);
@@
                 \draw[-{Stealth[length=3mm]}=black] (-1,-1) -- (-1,6.5);
-                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=10mm}] {(-1,-1) -- (-1,7)};
+                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=21.5pt}] {(-1,-1) -- (-1,7)};
                 \draw[black] (1,4) -- (1,5) -- (3,5) -- (3,2) -- (2,2) -- (2,1) -- (1,1) -- (1,0) -- (3,0) -- (3,1) -- (5,1);
@@
             % \end{tikzpicture} &
-            \begin{tikzpicture}
+            \begin{tikzpicture}[scale=0.75]
                 \foreach \y in {0,0.5,...,7} {
@@
                 \draw[-{Stealth[length=3mm]}=black] (-1,-1) -- (-1,6.5);
-                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=10mm}] {(-1,-1) -- (-1,6.5)};
+                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=21.5pt}] {(-1,-1) -- (-1,6.5)};
                 \draw[thick,dashed] (1,3) -- (1,2) -- (0,2) -- (0,-1) -- (4,-1) -- (4,0) -- (6,0) -- (6,2) -- (4,2) -- (4,6) -- (0,6) -- (0,3) -- (2,3) -- (2,4);

### 2025-04-08 main.cpp
intersection fix & tests

@@ -70,10 +70,10 @@ bool isPointLowerThan(const Point &p1, const Point &p2) {
 
 class Visibility {
 public:
-  Dimension mainAxis = 0;
+  Dimension mainAxis;
   std::vector<bool> visibles;
-  size_t vectorsSize = 0;
-  size_t pointsSize = 0;
+  size_t vectorsSize;
+  size_t pointsSize;
   std::map<Point, size_t> pointIdxs;
   std::map<IntegerVector, size_t> vectorIdxs;
 
@@ -277,7 +277,7 @@ Intervals intersect(const Intervals &l1, const Intervals &l2) {
     auto interval2 = l2[k2];
     auto i = std::max(interval1.first, interval2.first);
     auto j = std::min(interval1.second, interval2.second);
-    if (i < j) result.emplace_back(i, j);
+    if (i <= j) result.emplace_back(i, j);
     if (interval1.second <= interval2.second) k1++;
     if (interval1.second >= interval2.second) k2++;
   }
@@ -397,7 +397,7 @@ void computeVisibility(int radius) {
         const Point pInterest(axis == 0 ? 0 : 2 * tx, axis == 1 ? 0 : 2 * (axis == 0 ? tx : ty),
                               axis == 2 ? 0 : 2 * ty);
         for (const auto &cInfo: latticeVector) {
-          eligibles = matchVector(eligibles, cInfo.second, figLattices.at(pInterest + cInfo.first));
+          eligibles = matchVector(eligibles, cInfo.second, figLattices[pInterest + cInfo.first]);
           if (eligibles.empty()) break;
         }
         if (!eligibles.empty()) {
@@ -550,11 +550,29 @@ void myCallback() {
   ImGui::Text("nb threads = %d", OMP_max_nb_threads);
 }
 
+void testIntersection() {
+  // 1|2 4|5 7|9
+  for (auto v:intersect(Intervals({Interval(0,9)}),Intervals({Interval(1,2),Interval(4,5),Interval(7,10)}))) {
+    std::cout << v << " ";
+  }
+  std::cout << std::endl;
+
+  // 2|3 5|6 8|10
+  for (auto v:intersect(Intervals({Interval(0,3),Interval(5,10)}),Intervals({Interval(2,6),Interval(8,12)}))) {
+    std::cout << v << " ";
+  }
+  std::cout << std::endl;
+
+  // 1|3 6|7 9|10 12|12 14|15
[…]

### 2025-04-08 main.cpp
fix no reset vector lattice

@@ -322,13 +322,13 @@ void computeVisibilityOmp(int radius) {
 #pragma omp for schedule(dynamic)
   for (auto chunkIdx = 0; chunkIdx < chunkAmount + shouldHaveOneMoreChunk; chunkIdx++) {
     IntegerVector segment;
-    std::map<Point, Intervals> latticeVector;
     Intervals eligibles;
     int minTx, maxTx, minTy, maxTy;
     for (auto segmentIdx = chunkIdx * chunkSize;
          segmentIdx < std::min((chunkIdx + 1) * chunkSize, segmentList.size()); segmentIdx++) {
       segment = segmentList[segmentIdx];
       auto tmp = getLatticeVector(segment, axis).data();
+      std::map<Point, Intervals> latticeVector;
       for (auto p:tmp) {
         latticeVector[p.first] = p.second.data();
       }
@@ -372,7 +372,6 @@ void computeVisibility(int radius) {
   const auto axises_idx = std::vector<Dimension>{axis, axis == 0 ? 1U : 0U, axis == 2 ? 1U : 2U};
   IntegerVector segment;
   Intervals eligibles;
-  std::map<Point, Intervals> latticeVector;
   auto segmentList = getAllVectors(radius);
   visibility = Visibility(axis, segmentList, pointels);
   int minTx, maxTx, minTy, maxTy;
@@ -383,6 +382,7 @@ void computeVisibility(int radius) {
     if (segmentIdx % 100 == 0) start = std::chrono::high_resolution_clock::now();
     segment = segmentList[segmentIdx];
     auto tmp = getLatticeVector(segment, axis).data();
+    std::map<Point, Intervals> latticeVector;
     for (auto p:tmp) {
       latticeVector[p.first] = p.second.data();
     }

### 2025-04-10 job.sh
job machine multithread

@@ -1,0 +1,12 @@
+#!/bin/bash
+#SBATCH --job-name=visibilityTest
+#SBATCH --partition=dayGPU
+#SBATCH --nodes=1
+#SBATCH --ntasks=1
+#SBATCH --cpus-per-task=1
+#SBATCH --gres=gpu:1
+#SBATCH --mem=60GB
+#SBATCH --time=00:10:00
+
+
+./visibilityLattices -i ../../VolGallery/Stanford-bunny/bunny-64.vol --noInterface -r 20

### 2025-04-10 job.sh
fix job path

@@ -9,4 +9,4 @@
 #SBATCH --time=00:10:00
 
 
-./visibilityLattices -i ../../VolGallery/Stanford-bunny/bunny-64.vol --noInterface -r 20
+/home/romain/VisibilityLattices/build/visibilityLattices -i ../../VolGallery/Stanford-bunny/bunny-64.vol --noInterface -r 20

### 2025-04-10 job.sh
fix job path

@@ -9,4 +9,4 @@
 #SBATCH --time=00:10:00
 
 
-/home/romain/VisibilityLattices/build/visibilityLattices -i ../../VolGallery/Stanford-bunny/bunny-64.vol --noInterface -r 20
+/home/negror/VisibilityLattices/build/visibilityLattices -i ../../VolGallery/Stanford-bunny/bunny-64.vol --noInterface -r 20

### 2025-04-10 job.sh
fix job path

@@ -9,4 +9,4 @@
 #SBATCH --time=00:10:00
 
 
-/home/negror/VisibilityLattices/build/visibilityLattices -i ../../VolGallery/Stanford-bunny/bunny-64.vol --noInterface -r 20
+/home/negror/VisibilityLattices/build/visibilityLattices -i /home/negror/VolGallery/Stanford-bunny/bunny-64.vol --noInterface -r 20

### 2025-04-10 job.sh
fix job path

@@ -8,5 +8,5 @@
 #SBATCH --mem=60GB
 #SBATCH --time=00:10:00
 
-
+echo $CUDA_VISIBLE_DEVICES
 /home/negror/VisibilityLattices/build/visibilityLattices -i /home/negror/VolGallery/Stanford-bunny/bunny-64.vol --noInterface -r 20

### 2025-04-10 job.sh
fix job path

@@ -8,5 +8,6 @@
 #SBATCH --mem=60GB
 #SBATCH --time=00:10:00
 
+export CUDA_VISIBLE_DEVICES=0
 echo $CUDA_VISIBLE_DEVICES
 /home/negror/VisibilityLattices/build/visibilityLattices -i /home/negror/VolGallery/Stanford-bunny/bunny-64.vol --noInterface -r 20

### 2025-04-10 job.sh
check cpu

@@ -1,13 +1,15 @@
 #!/bin/bash
 #SBATCH --job-name=visibilityTest
-#SBATCH --partition=dayGPU
+#SBATCH --partition=dayCPU
 #SBATCH --nodes=1
 #SBATCH --ntasks=1
-#SBATCH --cpus-per-task=1
-#SBATCH --gres=gpu:1
+#SBATCH --cpus-per-task=64
+## SBATCH --gres=gpu:1
 #SBATCH --mem=60GB
 #SBATCH --time=00:10:00
 
-export CUDA_VISIBLE_DEVICES=0
-echo $CUDA_VISIBLE_DEVICES
+# export CUDA_VISIBLE_DEVICES=0
+# echo $CUDA_VISIBLE_DEVICES
+
+
 /home/negror/VisibilityLattices/build/visibilityLattices -i /home/negror/VolGallery/Stanford-bunny/bunny-64.vol --noInterface -r 20

### 2025-04-10 job.sh
thread am

@@ -11,5 +11,7 @@
 # export CUDA_VISIBLE_DEVICES=0
 # echo $CUDA_VISIBLE_DEVICES
 
+export OMP_NUM_THREADS=64
+echo $OMP_NUM_THREADS
 
 /home/negror/VisibilityLattices/build/visibilityLattices -i /home/negror/VolGallery/Stanford-bunny/bunny-64.vol --noInterface -r 20

### 2025-04-10 job.sh
bigger job

@@ -14,4 +14,4 @@
 export OMP_NUM_THREADS=64
 echo $OMP_NUM_THREADS
 
-/home/negror/VisibilityLattices/build/visibilityLattices -i /home/negror/VolGallery/Stanford-bunny/bunny-64.vol --noInterface -r 20
+/home/negror/VisibilityLattices/build/visibilityLattices -i /home/negror/VolGallery/Stanford-bunny/bunny-256.vol --noInterface -r 40

### 2025-04-10 job.sh
bigger job

@@ -14,4 +14,4 @@
 export OMP_NUM_THREADS=64
 echo $OMP_NUM_THREADS
 
-/home/negror/VisibilityLattices/build/visibilityLattices -i /home/negror/VolGallery/Stanford-bunny/bunny-256.vol --noInterface -r 40
+/home/negror/VisibilityLattices/build/visibilityLattices -i /home/negror/VolGallery/Stanford-bunny/bunny-1024.vol --noInterface -r 60

### 2025-04-10 job.sh
bigger job

@@ -3,15 +3,15 @@
 #SBATCH --partition=dayCPU
 #SBATCH --nodes=1
 #SBATCH --ntasks=1
-#SBATCH --cpus-per-task=64
+#SBATCH --cpus-per-task=128
 ## SBATCH --gres=gpu:1
-#SBATCH --mem=60GB
+#SBATCH --mem=200GB
 #SBATCH --time=00:10:00
 
 # export CUDA_VISIBLE_DEVICES=0
 # echo $CUDA_VISIBLE_DEVICES
 
-export OMP_NUM_THREADS=64
+export OMP_NUM_THREADS=128
 echo $OMP_NUM_THREADS
 
 /home/negror/VisibilityLattices/build/visibilityLattices -i /home/negror/VolGallery/Stanford-bunny/bunny-1024.vol --noInterface -r 60

### 2025-04-10 job.sh
bigger job

@@ -1,6 +1,6 @@
 #!/bin/bash
 #SBATCH --job-name=visibilityTest
-#SBATCH --partition=dayCPU
+#SBATCH --partition=weekend
 #SBATCH --nodes=1
 #SBATCH --ntasks=1
 #SBATCH --cpus-per-task=128

### 2025-04-10 job.sh
bigger job

@@ -6,7 +6,7 @@
 #SBATCH --cpus-per-task=128
 ## SBATCH --gres=gpu:1
 #SBATCH --mem=200GB
-#SBATCH --time=00:10:00
+#SBATCH --time=10:00:00
 
 # export CUDA_VISIBLE_DEVICES=0
 # echo $CUDA_VISIBLE_DEVICES

### 2025-04-10 job.sh
job machine multithread

@@ -1,0 +1,17 @@
+#!/bin/bash
+#SBATCH --job-name=visibilityTest
+#SBATCH --partition=weekend
+#SBATCH --nodes=1
+#SBATCH --ntasks=1
+#SBATCH --cpus-per-task=128
+## SBATCH --gres=gpu:1
+#SBATCH --mem=200GB
+#SBATCH --time=10:00:00
+
+# export CUDA_VISIBLE_DEVICES=0
+# echo $CUDA_VISIBLE_DEVICES
+
+export OMP_NUM_THREADS=128
+echo $OMP_NUM_THREADS
+
+/home/negror/VisibilityLattices/build/visibilityLattices -i /home/negror/VolGallery/Stanford-bunny/bunny-1024.vol --noInterface -r 60

### 2025-04-10 main.cpp

@@ -660,6 +660,7 @@ int main(int argc, char *argv[]) {
 
   // Initialize polyscope
   if (noInterface) {
+    checkParallelism();
     trace.beginBlock("Compute visibilities");
     computeVisibilityOmp(VisibilityRadius);
     Time = trace.endBlock();

### 2025-04-10 DGMM2025/paper.tex
fixing intersection algorithm
Add abstract

@@
 %
-    \title{Fast and exact visibility on digitized shapes and application to feature-aware normal estimation}
+    \title{Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation}
 %
@@
     \begin{abstract}
-        Our abstract
+      Computing visibility on a geometric object requires heavy
+      computations since it requires to identify pair of points that
+      are visible to each other, i.e. there is a straight segment
+      joining them that stays in the close vicinity of the object
+      boundary. We propose to exploit a specific representation of
+      digital sets based on lists of integral intervals in order to
+      compute efficiently the complete visibility graph between
+      lattice points of the digital shape. As a quite direct
+      application, we show then how we can use visibility to estimate
+      the normal vector field of a digital shape in an accurate and
+      convergent manner while staying aware of the salient and sharp features of
+      the shape.
+
       \keywords{Visibility \and Geometric inference \and Digital normal estimation \and Digital geometry}
@@
                     \State $f \gets \min(b, d)$
-                    \If{$e < f$}
-                        \State $R.append([e, f])$
+                    \If{$e \leq f$}\State $R.append([e, f])$
                     \EndIf
-                    \If{$b \leq d$}
-                        \State $k \gets k+1$
+                    \If{$b \leq d$}\State $k \gets k+1$
                     \EndIf
-                    \If{$d \leq b$}
-                        \State $l \gets l+1$
+                    \If{$d \leq b$}\State $l \gets l+1$
                     \EndIf

### 2025-04-11 main.cpp
normal computation and move old normal computation to sharp feature direction

@@ -49,7 +49,7 @@ CountedPtr<SH3::DigitalSurface> digital_surface(nullptr);
 CountedPtr<SH3::SurfaceMesh> primal_surface(nullptr);
 
 std::vector<RealPoint> visibility_normals;
-std::vector<double> visibility_H;
+std::vector<RealPoint> visibility_sharps;
 
 // Parameters
 int VisibilityRadius = 10;
@@ -509,9 +509,8 @@ void computeMeanDistanceVisibility() {
   std::cout << "Mean distance between visible points = " << meanDistance / nbVisiblePairs << std::endl;
 }
 
-void computeVisibilityNormals() {
-  visibility_normals.resize(pointels.size());
-  visibility_H.resize(pointels.size());
+void computeVisibilityDirectionToSharpFeatures() {
+  visibility_sharps.resize(pointels.size());
   auto kdTree = LinearKDTree<Point, 3>(pointels);
 #pragma omp for schedule(dynamic)
   for (int i = 0; i < pointels.size(); ++i) {
@@ -524,12 +523,60 @@ void computeVisibilityNormals() {
         count++;
       }
     }
-    visibility_normals[i] = -tmpSum/count;
-    visibility_H[i] = visibility_normals[i].norm();
+    visibility_sharps[i] = -tmpSum/count;
+  }
+  if (!noInterface) {
+    psPrimalMesh->addVertexVectorQuantity("Pointel visibility sharp direction", visibility_sharps);
+  }
+}
+
+void computeVisibilityNormals() {
+  visibility_normals.clear();
+  visibility_normals.reserve(pointels.size());
+  auto kdTree = LinearKDTree<Point, 3>(pointels);
+#pragma omp for schedule(dynamic)
+  for (const auto & pointel : pointels) {
+    std::vector<Point> visibles;
+    RealPoint centroid(0,0,0);
+    for (auto point_idx: kdTree.pointsInBall(pointel, VisibilityRadius)) {
+      auto tmp = kdTree.position(point_idx);
+      if (visibility.isVisible(pointel, tmp) && tmp != pointel) {
+        visibles.push_back(tmp);
+        centroid += tmp;
+      }
+    }
+    centroid /= (double)visibles.size();
+    Eigen::Matrix3d cov = Eigen::Matrix3d::Zero();
+    for (const auto& pt: visibles) {
+      auto diff = pt - centroid;
+      for (int i = 0; i < 3; ++i) {
+        for (int j = 0; j < 3; ++j) {
[…]

### 2025-04-12 main.cpp
Small fixes

@@ -262,7 +262,7 @@ Intervals
 checkInterval(const Interval toCheck, const Intervals &figIntervals) {
   Intervals result;
   result.reserve(figIntervals.size());
-  auto toCheckSize = toCheck.second - toCheck.first;
+  const auto toCheckSize = toCheck.second - toCheck.first;
   for (auto interval: figIntervals) {
     if (interval.second - interval.first >= toCheckSize) {
       result.emplace_back(interval.first - toCheck.first, interval.second - toCheck.second);
@@ -273,13 +273,14 @@ checkInterval(const Interval toCheck, const Intervals &figIntervals) {
 
 Intervals intersect(const Intervals &l1, const Intervals &l2) {
   Intervals result;
-  result.reserve(l1.size() + l2.size() - 1);
+  // result.reserve( l1.size() + l2.size() - 1);
+  result.reserve( std::max( l1.size(), l2.size() ) );
   int k1 = 0, k2 = 0;
   while (k1 < l1.size() && k2 < l2.size()) {
-    auto interval1 = l1[k1];
-    auto interval2 = l2[k2];
-    auto i = std::max(interval1.first, interval2.first);
-    auto j = std::min(interval1.second, interval2.second);
+    const auto interval1 = l1[k1];
+    const auto interval2 = l2[k2];
+    const auto i = std::max(interval1.first, interval2.first);
+    const auto j = std::min(interval1.second, interval2.second);
     if (i <= j) result.emplace_back(i, j);
     if (interval1.second <= interval2.second) k1++;
     if (interval1.second >= interval2.second) k2++;
@@ -294,10 +295,10 @@ Intervals intersect(const Intervals &l1, const Intervals &l2) {
  * @param figLattices
  * @return
  */
-Intervals matchVector(Intervals &toCheck,
-                                       const Intervals &vectorIntervals,
-                                       const Intervals &figIntervals) {
-  for (auto vInterval: vectorIntervals) {
+Intervals matchVector( Intervals &toCheck,
+		       const Intervals &vectorIntervals,
+		       const Intervals &figIntervals ) {
+  for (const auto& vInterval: vectorIntervals) {
     toCheck = intersect(toCheck, checkInterval(vInterval, figIntervals));
     if (toCheck.empty()) break;
   }
[…]

### 2025-04-15 main.cpp
fix reserve size you can have # of intersected intervals -1 amount of intervals after intersection

@@ -273,8 +273,9 @@ checkInterval(const Interval toCheck, const Intervals &figIntervals) {
 
 Intervals intersect(const Intervals &l1, const Intervals &l2) {
   Intervals result;
-  // result.reserve( l1.size() + l2.size() - 1);
-  result.reserve( std::max( l1.size(), l2.size() ) );
+    // check 3rd example of testIntersection to see that you need at most this amount
+   result.reserve( l1.size() + l2.size() - 1);
+//  result.reserve( std::max( l1.size(), l2.size() ) );
   int k1 = 0, k2 = 0;
   while (k1 < l1.size() && k2 < l2.size()) {
     const auto interval1 = l1[k1];
@@ -496,7 +497,7 @@ void computeMeanDistanceVisibility() {
 
   unsigned seed = std::chrono::system_clock::now().time_since_epoch().count();
   std::mt19937 gen(seed);
-  auto pointelsSample = pickSet(pointels.size(), pointels.size()/10, gen);
+  auto pointelsSample = pickSet(pointels.size(), pointels.size(), gen);
   auto kdTree = LinearKDTree<Point, 3>(pointels);
 
   for (auto i: pointelsSample) {
@@ -514,7 +515,6 @@ void computeMeanDistanceVisibility() {
 void computeVisibilityDirectionToSharpFeatures() {
   visibility_sharps.resize(pointels.size());
   auto kdTree = LinearKDTree<Point, 3>(pointels);
-#pragma omp for schedule(dynamic)
   for (int i = 0; i < pointels.size(); ++i) {
     RealVector tmpSum(0,0,0);
     size_t count = 0;
@@ -536,7 +536,6 @@ void computeVisibilityNormals() {
   visibility_normals.clear();
   visibility_normals.reserve(pointels.size());
   auto kdTree = LinearKDTree<Point, 3>(pointels);
-#pragma omp for schedule(dynamic)
   for (const auto & pointel : pointels) {
     std::vector<Point> visibles;
     RealPoint centroid(0,0,0);

### 2025-04-15 DGMM2025/paper.tex
added gridstep vs mean visibility distance plot

@@
 \usepackage{mathtools}
+\usepackage{pgfplots}
 \setauthormarkup{}
@@
         \centering
-        \caption{Representation of a 2d cell complex (here the star of a given curve) as lattices}
         \label{fig:lattice-representation}
@@
         \end{tabular}
-
+        \caption{Representation of a 2d cell complex (here the star of a given curve) as lattices. From X cells from the star on the left, we get Y intervals on the right}
     \end{figure}
@@
 
+    \pgfplotsset{width=13cm}
+    \begin{tikzpicture}
+        \centering
+        \begin{axis}[
+            xlabel={Gridstep},
+            x dir=reverse,
+            ylabel={Mean distance},
+            legend pos=north west,
+            ymajorgrids=true,
+            grid style=dashed,
+            ymode=log,
+            log ticks with fixed point,
+        ]
+
+            \addplot[
+                color=cyan,
+                mark=square,
+            ]
+            coordinates {
+                (1,5.76973)(0.875,6.03836)(0.75,6.22426)(0.625,6.39012)(0.5,6.51014)(0.375,6.63571)(0.25, 6.68132)
+            };
+            \addlegendentry{sphere9 radius 10}
+            \addplot[
+                color=red,
+                mark=square,
+            ]
+            coordinates {
+                (1,5.91022)(0.875,6.10641)(0.75,6.14175)(0.625,6.20202)(0.5,6.28637)(0.375,6.44418)(0.25, 6.56938)
+            };
+            \addlegendentry{goursat radius 10}
+            \addplot[
+                color=red,
+                mark=triangle,
+            ]
+            coordinates {
+                (1,9.04228)(0.875,10.1319)(0.75,10.2837)(0.625,10.6125)(0.5,10.8969)(0.375,11.3186)(0.25, 11.8382)
+            };
+            \addlegendentry{radius 20}
+            \addplot[
+                color=red,
+                mark=halfcircle,
+            ]
+            coordinates {
+                (1,9.22083)(0.875,10.6476)(0.75,11.5976)(0.625,12.7428)(0.5,13.9534)(0.375,14.73)(0.25,15.8425)
+            };
+            \addlegendentry{radius 30}
+            \addplot[
+                color=violet,
+                mark=square,
+            ]
+            coordinates {
+                (1,5.36873)(0.875,5.43148)(0.75,5.47206)(0.625,5.67227)(0.5,5.81554)(0.375,6.03961)(0.25,6.31671)
+            };
+            \addlegendentry{torus}
+            \addplot[
+                color=violet,
+                mark=triangle,
+            ]
+            coordinates {
+                (1,6.42158)(0.875,6.36929)(0.75,6.94675)(0.625,7.65529)(0.5,8.65652)(0.375,9.05402)(0.25,10.0784)
+            };
+            \addplot[
+                color=violet,
+                mark=halfcircle,
+            ]
+            coordinates {
+                (1,6.44119)(0.875,6.43563)(0.75,7.00852)(0.625,7.71613)(0.5,9.1544)(0.375,9.84299)(0.25,12.241)
+            };
+        \end{axis}
+    \end{tikzpicture}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2025-04-15 main.cpp
trivial normals

@@ -9,6 +9,7 @@
 #include <DGtal/arithmetic/IntegerComputer.h>
 #include <DGtal/base/Common.h>
 #include <DGtal/geometry/volumes/DigitalConvexity.h>
+#include <DGtal/geometry/volumes/TangencyComputer.h>
 #include <DGtal/helpers/StdDefs.h>
 #include <DGtal/helpers/Shortcuts.h>
 #include <DGtal/helpers/ShortcutsGeometry.h>
@@ -565,19 +566,26 @@ void computeVisibilityNormals() {
   }
 }
 
+RealVector getTrivNormal(size_t idx) {
+  return primal_surface->vertexNormal(idx);
+}
+
 void reorientVisibilityNormals() {
   if (visibility_normals.empty()) {
     computeVisibilityNormals();
   }
-  if (visibility_sharps.empty()) {
-    computeVisibilityDirectionToSharpFeatures();
-  }
+//  if (visibility_sharps.empty()) {
+//    computeVisibilityDirectionToSharpFeatures();
+//  }
   for (int i = 0; i < visibility_normals.size(); ++i) {
-    if (visibility_normals[i].dot(visibility_sharps[i]) < 0)
+    const auto triv_normal = getTrivNormal(i);
+    if (visibility_normals[i].dot(triv_normal) < 0)
       visibility_normals[i] = -visibility_normals[i];
   }
   if (!noInterface) {
     psPrimalMesh->addVertexVectorQuantity("Pointel visibility normals", visibility_normals);
+    psPrimalMesh->addVertexVectorQuantity("Pointel trivial normal", primal_surface->vertexNormals());
+    psPrimalMesh->addFaceVectorQuantity("Face trivial normal", primal_surface->faceNormals());
   }
 }
 
@@ -747,6 +755,35 @@ int main(int argc, char *argv[]) {
   digital_dimensions = getFigSizes();
   trace.info() << "Surface has " << pointels.size() << " pointels." << std::endl;
   trace.endBlock();
+
+  // Compute trivial normals
+
+  auto pTC = new TangencyComputer<KSpace>(K);
+  pTC->init(pointels.cbegin(), pointels.cend(), true);
+  int t_ring = int(round(params["t-ring"].as<double>()));
+  auto surfel_trivial_normals = SHG3::getTrivialNormalVectors(K, surfels);
+  primal_surface->faceNormals() = surfel_trivial_normals;
+  for (auto i = 1; i < t_ring+3; i++) {
[…]

### 2025-04-15 DGMM2025/paper.tex
graphs and visibility test 2d example

@@
 \usepackage{pgfplots}
+\usetikzlibrary {arrows.meta,decorations.shapes}
 \setauthormarkup{}
@@
         \label{fig:lattice-representation}
-        \usetikzlibrary {arrows.meta,decorations.shapes}
+        % \usetikzlibrary {arrows.meta,decorations.shapes}
         \begin{tabular}{c c}
@@
 
+    \begin{figure}
+        \centering
+        \begin{tabular}{c c}
+            \begin{tikzpicture}[scale=0.75]
+                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.75,-0.25) grid (12.25,3.25);
+                \draw[-{Stealth[length=3mm]}=black] (-1.5,-1) -- (-1.5,2.5);
+                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=21.5pt}] {(-1.5,-1) -- (-1.5,2)};
+                \filldraw[black] (0,0) circle (0.05);
+                \filldraw[black] (1,0) circle (0.05);
+                \filldraw[black] (2,0) circle (0.05);
+                \filldraw[black] (2,1) circle (0.05);
+                \filldraw[black] (3,1) circle (0.05);
+                \filldraw[black] (4,1) circle (0.05);
+                \filldraw[black] (5,1) circle (0.05);
+                \filldraw[black] (5,0) circle (0.05);
+                \filldraw[black] (6,0) circle (0.05);
+                \filldraw[black] (7,0) circle (0.05);
+                \filldraw[black] (7,1) circle (0.05);
+                \filldraw[black] (8,1) circle (0.05);
+                \filldraw[black] (8,0) circle (0.05);
+                \filldraw[black] (9,0) circle (0.05);
+                \filldraw[black] (10,0) circle (0.05);
+                \filldraw[black] (10,1) circle (0.05);
+                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,-0.5)--(2.6,-0.5);
+                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,-0.5)--(10.6,-0.5);
+                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0)--(2.6,0);
+                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,0)--(10.6,0);
+                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(10.6,0.5);
+                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1)--(5.6,1);
+                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1)--(8.6,1);
+                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1)--(10.6,1);
+                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(5.6,1.5);
+                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1.5)--(8.6,1.5);
+                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1.5)--(10.6,1.5);
+                \draw[thick, black] (0,0) -- (2,0) -- (2,1) -- (5,1) -- (5,0) -- (7,0) -- (7,1) -- (8,1) -- (8,0) -- (10,0) -- (10,1);
+                \draw[thick,dashed] (6,1) -- (6,2);
+                \draw[thick,dashed] (9,1) -- (9,2);
+                \draw[thick,dashed] (-1,-1) -- (-1,1) -- (1,1) -- (1,2) -- (11,2) -- (11,-1) -- (4,-1) -- (4,0) -- (3,0) -- (3,-1) -- (-1,-1);
+
+            \end{tikzpicture} &
+            \begin{tikzpicture}[scale=0.75]
+                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.75,-0.25) grid (4.25,3.25);
+                \draw[-{Stealth[length=3mm]}=black] (-1.5,-1) -- (-1.5,2.5);
+                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=21.5pt}] {(-1.5,-1) -- (-1.5,2)};
+                \filldraw[black] (0,0) circle (0.05);
+                \filldraw[black] (2,1) circle (0.05);
+                \draw[thick, black] (0,0) -- (2,1);
+                \draw[thick,dashed] (-1,-1) -- (-1,1) -- (1,1) -- (1,2) -- (3,2) -- (3,0) -- (1,0) --  (1,-1) -- (-1,-1);
+                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,-0.5)--(0.6,-0.5);
+                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0)--(0.6,0);
+                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(2.6,0.5);
+                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1)--(2.6,1);
+                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(2.6,1.5);
+            \end{tikzpicture}\\
+            \hline
+            \multicolumn{2}{c}{
+                \begin{tikzpicture}[scale=0.75]
+                    \foreach \y in {0,0.5,...,10.5} {
+                        \draw[thin, lightgray] (-1.25,\y) -- (11.25,\y);
+                    }
+                    \foreach \y in {0,2,...,10} {
+                        \draw[blue] (-1.25,\y) -- (11.25,\y);
+                    }
+
+                    \draw[thick,green, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9.5)--(0.6,9.5);
+                    \draw[thick,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9)--(2.6,9);
+                    \draw[thick,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,9)--(10.6,9);
+                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,8.5)--(1.6,8.5);
+                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,8.5)--(9.6,8.5);
+
+                    \draw[thick,green, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,7.5)--(0.6,7.5);
+                    \draw[thick,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,7)--(2.6,7);
+                    \draw[thick,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,7)--(10.6,7);
+                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,6.5)--(1.6,6.5);
+                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,6.5)--(9.6,6.5);
+
+                    \draw[thick,green, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,5.5)--(2.6,5.5);
+                    \draw[thick,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,5)--(10.6,5);
+                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,4.5)--(1.6,4.5);
+                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,4.5)--(7.6,4.5);
+
+                    \draw[thick,green, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,3.5)--(2.6,3.5);
+                    \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,3)--(5.6,3);
+                    \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,3)--(8.6,3);
+                    \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,3)--(10.6,3);
+                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,2.5)--(1.6,2.5);
+                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,2.5)--(5.6,2.5);
+                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,2.5)--(7.6,2.5);
+
+                    \draw[thick,green, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(2.6,1.5);
+                    \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1)--(5.6,1);
+                    \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1)--(8.6,1);
+                    \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1)--(10.6,1);
+                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(1.6,0.5);
+                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,0.5)--(5.6,0.5);
+                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,0.5)--(7.6,0.5);
+
+                \end{tikzpicture}}
+        \end{tabular}
+        \caption{Evolution of the visibility check algorithm for a 2,1 vector.
+Green are the vector lattices, black are the figure lattices, red are the current intervals of positions where the visibility is still possible.
+The last red intervals are the visible positions.
+We travel the lattices from bottom-up.
+}
+        \label{fig:enter-label}
+    \end{figure}
+
     \begin{algorithm}
@@
                     \State $f \gets \min(b, d)$
-                    \If{$e \leq f$}\State $R.append([e, f])$
+                    \If{$e \leq f$}
+                        \State $R.append([e, f])$
                     \EndIf
-                    \If{$b \leq d$}\State $k \gets k+1$
+                    \If{$b \leq d$}
+                        \State $k \gets k+1$
                     \EndIf
-                    \If{$d \leq b$}\State $l \gets l+1$
+                    \If{$d \leq b$}
+                        \State $l \gets l+1$
                     \EndIf
@@
     \pgfplotsset{width=13cm}
+    \begin{figure}
         \begin{tikzpicture}
@@
                 coordinates {
-                (1,5.76973)(0.875,6.03836)(0.75,6.22426)(0.625,6.39012)(0.5,6.51014)(0.375,6.63571)(0.25, 6.68132)
+                    (1,5.76973)(0.875,6.03836)(0.75,6.22426)(0.625,6.39012)(0.5,6.51014)(0.375,6.63571)(0.25,6.68132)
                 };
@@
                 coordinates {
-                (1,5.91022)(0.875,6.10641)(0.75,6.14175)(0.625,6.20202)(0.5,6.28637)(0.375,6.44418)(0.25, 6.56938)
+                    (1,5.91022)(0.875,6.10641)(0.75,6.14175)(0.625,6.20202)(0.5,6.28637)(0.375,6.44418)(0.25,6.56938)
                 };
@@
                 coordinates {
-                (1,9.04228)(0.875,10.1319)(0.75,10.2837)(0.625,10.6125)(0.5,10.8969)(0.375,11.3186)(0.25, 11.8382)
+                    (1,9.04228)(0.875,10.1319)(0.75,10.2837)(0.625,10.6125)(0.5,10.8969)(0.375,11.3186)(0.25,11.8382)
                 };
@@
         \end{tikzpicture}
+        \caption{Mean Visibility Distance as a Function of Grid Resolution}
+    \end{figure}
+    \begin{figure}
+        \begin{tikzpicture}
+            \centering
+            \begin{axis}[
+                xlabel={Gridstep},
+                x dir=reverse,
+                ylabel={Duration (s)},
+                legend pos=north west,
+                ymajorgrids=true,
+                grid style=dashed,
+                ymode=log,
+                log ticks with fixed point,
+            ]
+
+                \addplot[
+                    color=cyan,
+                    mark=square,
+                ]
+                coordinates {
+                    (1,0.513)(0.875,0.585)(0.75,0.897)(0.625,1.401)(0.5,2.441)(0.375,4.664)(0.25,11.420)
+                };
+                \addlegendentry{sphere9 radius 10}
+                \addplot[
+                    color=red,
+                    mark=square,
+                ]
+                coordinates {
+                    (1,0.440)(0.875,0.665)(0.75,0.823)(0.625,1.428)(0.5,2.463)(0.375,4.697)(0.25,11.766)
+                };
+                \addlegendentry{goursat radius 10}
+                \addplot[
+                    color=red,
+                    mark=triangle,
+                ]
+                coordinates {
+                    (1,1.389)(0.875,2.567)(0.75,3.661)(0.625,7.123)(0.5,13.881)(0.375,28.913)(0.25,77.360)
+                };
+                \addlegendentry{radius 20}
+                \addplot[
+                    color=red,
+                    mark=halfcircle,
+                ]
+                coordinates {
+                    (1,2.172)(0.875,3.747)(0.75,5.565)(0.625,13.180)(0.5,33.088)(0.375,80.584)(0.25,240.546)
+                };
+                \addlegendentry{radius 30}
+                \addplot[
+                    color=violet,
+                    mark=square,
+                ]
+                coordinates {
+                    (1,0.057)(0.875,0.081)(0.75,0.097)(0.625,0.197)(0.5,0.330)(0.375,0.800)(0.25,2.253)
+                };
+                \addlegendentry{torus}
+                \addplot[
+                    color=violet,
+                    mark=triangle,
+                ]
+                coordinates {
+                    (1,0.248)(0.875,0.294)(0.75,0.339)(0.625,0.620)(0.5,1.110)(0.375,2.643)(0.25,9.369)
+                };
+                \addplot[
+                    color=violet,
+                    mark=halfcircle,
+                ]
+                coordinates {
+                    (1,0.837)(0.875,0.880)(0.75,0.942)(0.625,1.316)(0.5,2.142)(0.375,5.046)(0.25,20.418)
+                };
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Computation Time of Visibility as a Function of Grid Resolution}
+    \end{figure}
 

### 2025-04-16 DGMM2025/paper.tex
upgrade 2d example visib test

@@
 \usepackage{pgfplots}
+\usepackage[dvipsnames]{xcolor}
 \usetikzlibrary {arrows.meta,decorations.shapes}
@@
 
+    \colorlet{MyGreen}{green!80!gray}
     \begin{figure}
@@
             \begin{tikzpicture}[scale=0.75]
+                \foreach[count=\i] \y in {-0.5,0,...,1.5} {
+                    \draw (0,0) node at (-1.25,\y) {\i};
+                }
                 \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.75,-0.25) grid (12.25,3.25);
                 \draw[-{Stealth[length=3mm]}=black] (-1.5,-1) -- (-1.5,2.5);
-                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=21.5pt}] {(-1.5,-1) -- (-1.5,2)};
                 \filldraw[black] (0,0) circle (0.05);
@@
 
+                \draw (0,0) node at (-0.25,1.75) {F};
+
             \end{tikzpicture} &
@@
                 \draw[-{Stealth[length=3mm]}=black] (-1.5,-1) -- (-1.5,2.5);
-                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=21.5pt}] {(-1.5,-1) -- (-1.5,2)};
+                \foreach[count=\i] \y in {-0.5,0,...,1.5} {
+                    \draw (0,0) node at (-1.25,\y) {\i};
+                }
                 \filldraw[black] (0,0) circle (0.05);
@@
                 \draw[thick,dashed] (-1,-1) -- (-1,1) -- (1,1) -- (1,2) -- (3,2) -- (3,0) -- (1,0) --  (1,-1) -- (-1,-1);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,-0.5)--(0.6,-0.5);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0)--(0.6,0);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(2.6,0.5);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1)--(2.6,1);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(2.6,1.5);
+                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,-0.5)--(0.6,-0.5);
+                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0)--(0.6,0);
+                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(2.6,0.5);
+                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1)--(2.6,1);
+                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(2.6,1.5);
+
+                \draw (0,0) node at (-0.25,1.75) {V};
             \end{tikzpicture}\\
@@
                 \begin{tikzpicture}[scale=0.75]
-                    \foreach \y in {0,0.5,...,10.5} {
+                    \foreach \y in {0,0.5,...,12.5} {
                         \draw[thin, lightgray] (-1.25,\y) -- (11.25,\y);
                     }
-                    \foreach \y in {0,2,...,10} {
-                        \draw[blue] (-1.25,\y) -- (11.25,\y);
+                    \foreach \y in {0,2.5,...,12.5} {
+                        \draw[blue] (-7,\y) -- (11.25,\y);
                     }
 
-                    \draw[thick,green, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9.5)--(0.6,9.5);
-                    \draw[thick,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9)--(2.6,9);
-                    \draw[thick,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,9)--(10.6,9);
-                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,8.5)--(1.6,8.5);
-                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,8.5)--(9.6,8.5);
+                    \foreach[count=\i] \y in {12,9.5,...,2} {
+                        \draw (0,0) node at (-4,\y) {$V_{\i}$};
+                    }
+                    \foreach[count=\i] \y in {11.5,9,...,1.5} {
+                        \draw (0,0) node at (-4,\y) {$F_{\i}$};
+                    }
+                    \foreach[count=\i] \y in {11,8.5,...,1} {
+                        \draw (0,0) node at (-4,\y) {$T_{\i} = \text{Translations}(V_{\i},F_{\i})$};
+                    }
+                    \draw (0,0) node at (-4,10.5) {$R_1 = T_1$};
 
-                    \draw[thick,green, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,7.5)--(0.6,7.5);
-                    \draw[thick,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,7)--(2.6,7);
-                    \draw[thick,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,7)--(10.6,7);
-                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,6.5)--(1.6,6.5);
-                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,6.5)--(9.6,6.5);
+                    \foreach[count=\i] \y in {8,5.5,...,0.5} {
 
-                    \draw[thick,green, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,5.5)--(2.6,5.5);
-                    \draw[thick,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,5)--(10.6,5);
-                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,4.5)--(1.6,4.5);
-                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,4.5)--(7.6,4.5);
+                        \draw (0,0) node at (-4,\y) {$R_{\the\numexpr\i+1\relax} = T_{\the\numexpr\i+1\relax} \cap R_{\i}$};
+                    }
 
-                    \draw[thick,green, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,3.5)--(2.6,3.5);
-                    \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,3)--(5.6,3);
-                    \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,3)--(8.6,3);
-                    \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,3)--(10.6,3);
-                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,2.5)--(1.6,2.5);
-                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,2.5)--(5.6,2.5);
-                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,2.5)--(7.6,2.5);
+                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,12)--(0.6,12);
+                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,11.5)--(2.6,11.5);
+                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,11.5)--(10.6,11.5);
+                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,11)--(1.6,11);
+                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,11)--(9.6,11);
+                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,10.5)--(1.6,10.5);
+                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,10.5)--(9.6,10.5);
 
-                    \draw[thick,green, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(2.6,1.5);
-                    \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1)--(5.6,1);
-                    \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1)--(8.6,1);
-                    \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1)--(10.6,1);
-                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(1.6,0.5);
-                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,0.5)--(5.6,0.5);
-                    \draw[thick,red, arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,0.5)--(7.6,0.5);
+                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9.5)--(0.6,9.5);
+                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9)--(2.6,9);
+                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,9)--(10.6,9);
+                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,8.5)--(1.6,8.5);
+                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,8.5)--(9.6,8.5);
+                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,8)--(1.6,8);
+                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,8)--(9.6,8);
+
+                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,7)--(2.6,7);
+                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,6.5)--(10.6,6.5);
+                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,6)--(7.6,6);
+                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,5.5)--(1.6,5.5);
+                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,5.5)--(7.6,5.5);
+
+                    \draw[thick,black,arrows = {-Stealth[]}] (-0.6,4.5)--(1.4,4.5);
+                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,4.5)--(2.6,4.5);
+                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,4)--(5.6,4);
+                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,4)--(8.6,4);
+                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,4)--(10.6,4);
+                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,3.5)--(2.6,3.5);
+                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,3.5)--(5.6,3.5);
+                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,3.5)--(7.6,3.5);
+                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,3)--(1.6,3);
+                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,3)--(5.6,3);
+                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,3)--(7.6,3);
+
+                    \draw[thick,black,arrows = {-Stealth[]}] (-0.6,2)--(1.4,2);
+                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2)--(2.6,2);
+                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(5.6,1.5);
+                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1.5)--(8.6,1.5);
+                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1.5)--(10.6,1.5);
+                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,1)--(2.6,1);
+                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,1)--(5.6,1);
+                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,1)--(7.6,1);
+                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(1.6,0.5);
+                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,0.5)--(5.6,0.5);
+                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,0.5)--(7.6,0.5);
 

### 2025-04-16 main.cpp
fix trivial normals

@@ -707,7 +707,7 @@ int main(int argc, char *argv[]) {
                 | SHG3::defaultParameters()
                 | SHG3::parametersGeometryEstimation();
   params("surfaceComponents", "All")("surfelAdjacency", 0); //exterior adjacency
-  params("surfaceTraversal", "DepthFirst");
+  params("surfaceTraversal", "default");
   bool is_polynomial = !polynomial.empty();
   if (is_polynomial) {
     trace.beginBlock("Build polynomial surface");

### 2025-04-16 DGMM2025/paper.tex
some fixes

@@
 \usepackage[dvipsnames]{xcolor}
+\pgfplotsset{compat=1.18}
 \usetikzlibrary {arrows.meta,decorations.shapes}
@@
         \end{tikzpicture}
-        \caption{Example of non connex visibility in 2D, q is visible from p while the visibility points are not 26-connected.}
+        \caption{Example of non-connex visibility in 2D, q is visible from p while the visibility points are not 26-connected.}
         \label{fig:visibility-2d-not-connected}
@@
 
-    To improve computation time, we will use lattice sets of integer intervals.
+    To improve computation time, we will use lattice maps of integer intervals.
 
@@
     \begin{definition}
-        All translations $T$ of an interval or a sequence of intervals $A$ in a sequence of intervals $L$ are defined as $ T \coloneqq t, st. A+t \subset L\}$
+        All translations $T$ of an interval or a sequence of intervals $A$ in a sequence of intervals $L$ are defined as $ T \coloneqq \{ t, st. A+t \subset L\}$
     \end{definition}
 
-    We will consider the lattices as a map from points $p \in \R^{d-1}$ to a sequence of intervals, where all coordinates are doubled, so that the represented cell $\forall c \in \R^d$ will have a dimension equal to $\sum_{i=1}^d \left(c[i]\mod2\right)$.
+    We will consider lattice maps as pairs of (shift, intervals), where shifts are points $p \in \R^{d-1}$.
+All coordinates are doubled, so that the represented cell $\forall c \in \R^d$ will have a dimension equal to $\sum_{i=1}^d \left(c[i]\mod d\right)$.
+Note that all examples are in 2-d while the shown algorithm is in n-d.
 
@@
         \end{tabular}
-        \caption{Representation of a 2d cell complex (here the star of a given curve) as lattices. From X cells from the star on the left, we get Y intervals on the right}
+        \caption{Representation of a 2d cell complex (here the star of a given curve) as a lattice map. From 31 cells from the star on the left, we get 15 intervals on the right}
     \end{figure}
@@
                     }
-                    \foreach[count=\i] \y in {11,8.5,...,1} {
-                        \draw (0,0) node at (-4,\y) {$T_{\i} = \text{Translations}(V_{\i},F_{\i})$};
+                    \draw (0,0) node at (-4,11) {$T_{1} = \text{Translations}(V_{1},F_{1})$};
+                    \foreach[count=\i] \y in {8.5,6,...,1} {
+                        \draw (0,0) node at (-4,\y) {$T_{\the\numexpr\i+1\relax}$};
                     }
@@
         \caption{Evolution of the visibility check algorithm for a 2,1 vector.
-Green are the vector lattices, black are the figure lattices, red are the current intervals of positions where the visibility is still possible.
+Green is the vector lattice map, black is the figure lattice map, red are the current intervals of positions where the visibility is still possible.
 The last red intervals are the visible positions.
-We travel the lattices from bottom-up.
+We travel the lattice maps from bottom-up.
 }
@@
     \begin{algorithm}
-        \caption{Given a cell complex C and a radius $r$, compute the visibility at every point of C up to distance $r$. We assume z being the lattice main axis, x and y being the auxiliary axises}
+        \caption{Given a cell complex C and a radius $r$, compute the visibility at every point of C up to distance $r$.
+We assume z being the main axis of the lattice maps, x and y being the auxiliary axises}
         \label{alg:visibility}
         \begin{algorithmic}
-            \Function{Visibility}{\text{C}: Cell complex, \text{r}: Integer}
-                \State $\Omega \gets \Call{Star}{C}$ \Comment{Lattices of the star of the studied cell complex}
-                \State $Vectors \gets \Call{GetAllPrimalVectors}{r}$
-                \State $V: \text{vector of boolean} \gets [0, \ldots, 0]$ \Comment{length $Size(Vectors) * PointelsAmount$}
+            \Function{Visibility}{C: Cell complex, r: Integer}
+                \State $\Omega \gets \Call{Star}{C}$ \Comment{Lattice map of the star of the studied cell complex}
+                \State $Directions \gets \Call{GetAllPrimalDirections}{r}$
+                \State $V: \text{vector of boolean} \gets [0, \ldots, 0]$ \Comment{length $Size(Directions) \times \#C.pointels$}
                 \State $low, high \gets \Call{BoundingBoxZ}{\Omega}$
-                \ForAll{$v$ in $Vectors$}
-                    \State $VStar \gets \Call{Star}{\text{v}}$
-                    \ForAll{shift $tx, ty$ in $\Omega$}
+                \ForAll{$d$ in $Directions$}
+                    \ForAll{shift $S$ in $\Omega$}
                         \State $R \gets [low, high]$
-                        \State $S: \R^3 \gets [2tx, 2ty,0]$
-                        \ForAll{lattice $L$ in $VStar$}
-                            \State $\text{R} \gets \text{R} \cap \Call{Translations}{L.intervals,\Omega[S + L.position]}$
+                        \ForAll{pair $P$ in $\Call{Star}{\text{d}}$}
+                            \State $R \gets R \cap \Call{Translations}{P.intervals,\Omega[S + P.shift]}$
                         \EndFor
@@
             \Function{Intersection ($\cap$)}{\text{K, L}: Intervals}
-                \State $R \gets \emptyset$
-                \State $k, l \gets 0$
+                \State $R \gets \emptyset$; $k, l \gets 0$
                 \While{$k < K.nbIntervals \And l < L.nbIntervals$}
-                    \State $[a,b] \gets K[k]$
-                    \State $[c,d] \gets L[l]$
-                    \State $e \gets \max(a, c)$
-                    \State $f \gets \min(b, d)$
+                    \State $[a,b] \gets K[k]$; $[c,d] \gets L[l]$
+                    \State $e \gets \max(a, c)$; $f \gets \min(b, d)$
                     \If{$e \leq f$}
@@
                 ymode=log,
+                xmode=log,
                 log ticks with fixed point,

### 2025-04-19 DGMM2025/paper.tex
Update biblio
Working on intro

@@
 
-    Visibility is a fundamental concept in computational geometry and digital topology, with applications ranging from computer vision to geometric modeling.
+    Visibility is a fundamental concept in computational geometry and
+    digital topology, with applications ranging from computer vision
+    (identifying occlusions) to geometric modeling (feature detection, geodesics)
+    and computer graphics (path tracing, shadowmap). Visibility within
+    polygons in the plane has been extensively studied in the
+    litterature \cite{ghosh:2007-book} and is still studied in higher
+    dimensional spaces \cite{orourke:2017-book}. The general problem
+    has a high complexity. For instance, the 3d visibility complex
+    between $n$ spheres and occluding spheres has a complexity
+    $O(n^4)$ \cite{durand:2002-tog}. Exact 3d visibility between
+    polygons and occluding polygons is often casted into 5d Euclidean
+    space derived from Plücker space \cite{nirenstein:2002-ewr}, which
+    nicely represents 3d lines and their respective positions. The
+    computational cost remains high even with decomposition into
+    coarse cells for speed up (several days of computation for a
+    million triangles at the time).
+
+    To increase efficiency, several authors have proposed to cast the
+    visibility problem into a digital space, generally $\Z^3$ or its
+    decomposition into cubical cells. Visibility is simplified as the
+    problem if there is a connected digital straight line joining a
+    pair of cells without occluding cell(s) (e.g. Soille
+    \cite{soille:1994-prl} uses Bresenham line segments). Coeurjolly
+    \emph{et al.} \cite{coeurjolly:2004-prl} uses a non-symmetric
+    visibility definition and preimage computations to speed up that
+    kind of algorithms. Chica \cite{chica:2008-spm} uses a half-cell
+    erosion of the complementary space and Bresenham straight lines to
+    decide visibility.
+
+    We propose an algorithm that solves the following visibility
+    problem: given a digital set $X \subset \Z^d$, two points $p,q$ of
+    $X$ are \emph{visible} whenever the Euclidean straight line
+    segment $\lbrack p,q \rbrack$ is never at $\infty$-distance
+    greater or equal to $1$ from $X$.
+
+    (Work in progress)
+
+    Visibility is a fundamental concept in computational geometry and digital topology, with applications ranging from computer vision to geometric modeling and computer graphics.
     In this work, we explore visibility through the lens of chord tangency, introducing a novel approach that builds on discrete geometric structures.

### 2025-04-19 DGMM2025/paper.tex
Working on intro

@@
     $X$ are \emph{visible} whenever the Euclidean straight line
-    segment $\lbrack p,q \rbrack$ is never at $\infty$-distance
-    greater or equal to $1$ from $X$.
+    segment $\lbrack p,q \rbrack$ is never at chessboard distance
+    ($\infty$-distance) greater or equal to $1$ from $X$.
+
+    We focus on solving efficiently this problem because it is crucial
+    in computing geometric normals along digital surfaces that are
+    aware of salient features.
 

### 2025-04-19 DGMM2025/paper.tex
Working on intro

@@
     segment $\lbrack p,q \rbrack$ is never at chessboard distance
-    ($\infty$-distance) greater or equal to $1$ from $X$.
+    ($\infty$-distance) greater or equal to $1$ from $X$. It is
+    equivalent to the \emph{cotangency} of $p$ and $q$ in $X$, as
+    formalized in \cite{lachaud:2021-dgmm,lachaud:2022-jmiv}, and can
+    be viewed as an inclusion problem between sets of lattice points
+    in this form. Indeed cells surounding $X$ can be encoded as
+    lattice points (Khalimsky coding), as well as the cells covering
+    lattice directions. The originality of our method is to encode
+    subsets of lattice points as sets of integer intervals and to
+    reduce all the inclusion problems as intersections and
+    translations of integer intervals.
 

### 2025-04-19 DGMM2025/paper.tex
Working on intro

@@
     reduce all the inclusion problems as intersections and
-    translations of integer intervals.
+    translations of integer intervals. For a given lattice vector
+    $\mathbf{t}$, we solve the visibility of every pair of points
+    $(p,p+\mathbf{t})$ of $X$. Global visibility is achieved by
+    testing all sought directions within a given range, and is
+    parallelized straightforwardly.
 
@@
     in computing geometric normals along digital surfaces that are
-    aware of salient features.
+    aware of salient features. Indeed, 2d discrete tangent estimators
+    based on tangency or discrete line segments have proven to be both
+    sensitive to sharp corners while multigrid convergent along the
+    boundary of digitized smooth shapes
+    \cite{feschet:1999-dgci,lachaud:2007-ivc,nguyen:2011-pr}.
+
+    or
+    normal estimators along digital surfaces have been shown to be
+    multigrid convergent on digitization of shapes with smooth
+    boundary \cite{Cuel:2014-dgci,Lachaud:2017-lnm}
 

### 2025-04-19 DGMM2025/paper.tex
Working on intro

@@
 \setauthormarkup{}
-\definechangesauthor[name=jo, color=magenta]{JO}
+\definechangesauthor[name=jo, color=blue]{JO}
 \definechangesauthor[name=rom, color=teal]{ROM}
@@
     boundary of digitized smooth shapes
-    \cite{feschet:1999-dgci,lachaud:2007-ivc,nguyen:2011-pr}.
+    \cite{feschet:1999-dgci,lachaud:2007-ivc,nguyen:2011-pr}. Many ad
+    hoc methods have been proposed for tangent plane or normal
+    estimation on 3d digital surfaces
+    (e.g. \cite{fourey:2009-cg,charrier:2011-iwcia,Cuel:2014-dgci,Lachaud:2017-lnm,mareche:2024-ispr}).
+    If two of these methods \cite{Cuel:2014-dgci,Lachaud:2017-lnm}
+    have been shown to be multigrid convergent on digitization of
+    shapes with smooth boundary, their formulation intrinsically
+    smoothes features, e.g. in contrast with the method of
+    Mar{\^e}ch{\'e} \emph{et al.}  \cite{mareche:2024-ispr}, whose
+    convergence is not established. We propose here a normal estimator
+    defined as the most orthogonal vector to the cone of visibility at
+    the point of interest. Visibility is high in smooth regions and
+    the induced visibility vectors are good approximations of tangent
+    vectors. On the contrary the visibility is blocked at sharp
+    features, so the normal vector is then not influenced by the
+    geometry on the other side of the features. We demonstrate the
+    superiority of this normal estimator for estimating curvatures
+    along digital surfaces with sharp features.
 
-    or
-    normal estimators along digital surfaces have been shown to be
-    multigrid convergent on digitization of shapes with smooth
-    boundary \cite{Cuel:2014-dgci,Lachaud:2017-lnm}
+    Note that our algorithm for computing visibility is in fact much
+    more general. The same algorithm could be used to recognize if any
+    pattern of lattice points is present on a shape. It is similar to
+    an erosion algorithm where the structuring element is the chosen
+    pattern, and could also be used for morphological operations
+    \cite{soille1999morphological}.  The paper outline is as
+    follows. In Section~2, we recall some definitions and present
+    tangency of chords and its equivalence to visibility.  Section~3
+    describes the specific data structure for encoding set of grid
+    cells, and the main algorithm that exploits this encoding to
+    compute visibility exactly.  Section~4 presents experimental
+    results on visibility, its usage as a discrete normal estimator,
+    and how it improves curvature estimates on digital surfaces.
+    Finally, Section 5 concludes and gives some perspectives to this
+    work, notably other usages of this algorithm in the field.
 
-    (Work in progress)
-
+    \deleted[id=JO]{
     Visibility is a fundamental concept in computational geometry and digital topology, with applications ranging from computer vision to geometric modeling and computer graphics.
@@
     Our framework leverages the discrete setting of and cell complexes, providing a rigorous foundation for analyzing visibility properties in digital spaces.
+    }
 
+    \deleted[id=JO]{
     We recall essential definitions from previous works, particularly the notions of cell complexes and the star operator as formalized in~\cite{lachaud:2021-dgmm} and~\cite{lachaud:2022-jmiv}.
@@
     The star of a cell, as defined in these works, consists of all higher-dimensional cells that contain it, a crucial concept for analyzing local neighborhoods and connectivity.
+    }
 
+    \deleted[id=JO]{
       Building on these foundations, our study focuses on visibility as determined by the tangency of chords in discrete geometry.
@@
     This approach provides a new perspective on discrete visibility, offering potential applications in digital imaging, surface reconstruction, and computational topology.
+    }
 
+    \deleted[id=JO]{
       The remainder of this paper is structured as follows.
@@
     Finally, Section 5 concludes with some other applications of integer intervals intersections in the field.
+    }
 

### 2025-04-22 DGMM2025/paper.tex
accept introduction and rework graph of mean distance as of gridstep

@@
 
-    \deleted[id=JO]{
-    Visibility is a fundamental concept in computational geometry and digital topology, with applications ranging from computer vision to geometric modeling and computer graphics.
-    In this work, we explore visibility through the lens of chord tangency, introducing a novel approach that builds on discrete geometric structures.
-    Our framework leverages the discrete setting of and cell complexes, providing a rigorous foundation for analyzing visibility properties in digital spaces.
-    }
-
-    \deleted[id=JO]{
-    We recall essential definitions from previous works, particularly the notions of cell complexes and the star operator as formalized in~\cite{lachaud:2021-dgmm} and~\cite{lachaud:2022-jmiv}.
-    The integer grid serves as our primary space of study, where geometric structures are discretized using cell complexes.
-    A cell complex is a decomposition of space into elementary units (vertices, edges, faces, and higher-dimensional counterparts) forming a combinatorial representation of geometric objects.
-    The star of a cell, as defined in these works, consists of all higher-dimensional cells that contain it, a crucial concept for analyzing local neighborhoods and connectivity.
-    }
-
-    \deleted[id=JO]{
-      Building on these foundations, our study focuses on visibility as determined by the tangency of chords in discrete geometry.
-    We define and analyze how visibility relationships emerge in this context and investigate their combinatorial and topological implications.
-    This approach provides a new perspective on discrete visibility, offering potential applications in digital imaging, surface reconstruction, and computational topology.
-    }
-
-    \deleted[id=JO]{
-      The remainder of this paper is structured as follows.
-    In Section 2, we formalize the concept of chord tangency and its role in visibility analysis.
-    Section 3 enters into the usage of integer intervals intersections to quickly scan the figure in order to recover this visibiltiy.
-    Section 4 presents our main results, using this visibility to compute normals using the CNC estimator~\cite{lachaud:2022-dcg}.
-    Finally, Section 5 concludes with some other applications of integer intervals intersections in the field.
-    }
+%    \deleted[id=JO]{
+%    Visibility is a fundamental concept in computational geometry and digital topology, with applications ranging from computer vision to geometric modeling and computer graphics.
+%    In this work, we explore visibility through the lens of chord tangency, introducing a novel approach that builds on discrete geometric structures.
+%    Our framework leverages the discrete setting of and cell complexes, providing a rigorous foundation for analyzing visibility properties in digital spaces.
+%    }
+%
+%
+%    \deleted[id=JO]{
+%    We recall essential definitions from previous works, particularly the notions of cell complexes and the star operator as formalized in~\cite{lachaud:2021-dgmm} and~\cite{lachaud:2022-jmiv}.
+%    The integer grid serves as our primary space of study, where geometric structures are discretized using cell complexes.
+%    A cell complex is a decomposition of space into elementary units (vertices, edges, faces, and higher-dimensional counterparts) forming a combinatorial representation of geometric objects.
+%    The star of a cell, as defined in these works, consists of all higher-dimensional cells that contain it, a crucial concept for analyzing local neighborhoods and connectivity.
+%    }
+%
+%    \deleted[id=JO]{
+%      Building on these foundations, our study focuses on visibility as determined by the tangency of chords in discrete geometry.
+%    We define and analyze how visibility relationships emerge in this context and investigate their combinatorial and topological implications.
+%    This approach provides a new perspective on discrete visibility, offering potential applications in digital imaging, surface reconstruction, and computational topology.
+%    }
+%
+%    \deleted[id=JO]{
+%      The remainder of this paper is structured as follows.
+%    In Section 2, we formalize the concept of chord tangency and its role in visibility analysis.
+%    Section 3 enters into the usage of integer intervals intersections to quickly scan the figure in order to recover this visibiltiy.
+%    Section 4 presents our main results, using this visibility to compute normals using the CNC estimator~\cite{lachaud:2022-dcg}.
+%    Finally, Section 5 concludes with some other applications of integer intervals intersections in the field.
+%    }
 
@@
                 \draw (0,0) node at (-0.25,1.75) {V};
-            \end{tikzpicture}\\
+            \end{tikzpicture} \\
             \hline
@@
                 grid style=dashed,
+                ymax=50,
                 ymode=log,
@@
                     color=cyan,
-                    mark=square,
-                ]
-                coordinates {
-                    (1,5.76973)(0.875,6.03836)(0.75,6.22426)(0.625,6.39012)(0.5,6.51014)(0.375,6.63571)(0.25,6.68132)
+                ] coordinates {
+                    (0.25,3.97418)(0.375,3.00921)(0.5,2.85702)(0.625,2.34448)(0.75,1.85023)(0.875,2.16868)(1.0,1.85023)
                 };
-                \addlegendentry{sphere9 radius 10}
+                \addlegendentry{sphere1}
                 \addplot[
                     color=red,
-                    mark=square,
-                ]
-                coordinates {
-                    (1,5.91022)(0.875,6.10641)(0.75,6.14175)(0.625,6.20202)(0.5,6.28637)(0.375,6.44418)(0.25,6.56938)
+                ] coordinates {
+                    (1,8.90781)(0.875,10.2845)(0.75,11.3734)(0.625,12.5062)(0.5,14.0867)(0.375,16.6192)(0.25,19.6747)
                 };
-                \addlegendentry{goursat radius 10}
-                \addplot[
-                    color=red,
-                    mark=triangle,
-                ]
-                coordinates {
-                    (1,9.04228)(0.875,10.1319)(0.75,10.2837)(0.625,10.6125)(0.5,10.8969)(0.375,11.3186)(0.25,11.8382)
-                };
-                \addlegendentry{radius 20}
-                \addplot[
-                    color=red,
-                    mark=halfcircle,
-                ]
-                coordinates {
-                    (1,9.22083)(0.875,10.6476)(0.75,11.5976)(0.625,12.7428)(0.5,13.9534)(0.375,14.73)(0.25,15.8425)
-                };
-                \addlegendentry{radius 30}
+                \addlegendentry{goursat}
                 \addplot[
                     color=violet,
-                    mark=square,
-                ]
-                coordinates {
-                    (1,5.36873)(0.875,5.43148)(0.75,5.47206)(0.625,5.67227)(0.5,5.81554)(0.375,6.03961)(0.25,6.31671)
+                ] coordinates {
+                    (0.25,12.3975)(0.375,9.41303)(0.5,8.69558)(0.625,7.37667)(0.75,6.82131)(0.875,6.05735)(1,6.33877)
                 };
@@
                 \addplot[
-                    color=violet,
-                    mark=triangle,
-                ]
-                coordinates {
-                    (1,6.42158)(0.875,6.36929)(0.75,6.94675)(0.625,7.65529)(0.5,8.65652)(0.375,9.05402)(0.25,10.0784)
+                    color=MyGreen,
+                ] coordinates {
+                    (0.25,10.8007)(0.375,8.69514)(0.5,7.26074)(0.625,6.2309)(0.75,5.6897)(0.875,5.28197)(1,4.96098)
                 };
+                \addlegendentry{leopold}
                 \addplot[
-                    color=violet,
-                    mark=halfcircle,
-                ]
-                coordinates {
-                    (1,6.44119)(0.875,6.43563)(0.75,7.00852)(0.625,7.71613)(0.5,9.1544)(0.375,9.84299)(0.25,12.241)
+                    color=yellow!80!black,
+                ] coordinates {
+                    (0.25,18.2339)(0.375,14.6475)(0.5,12.3618)(0.625,9.55647)(0.75,9.83208)(0.875,7.51861)(1,7.99732)
                 };
+                \addlegendentry{rcube}
+                \addplot [
+                    color=black,
+                    thick,
+                    domain=0.25:1,
+                    samples=100,
+                ] {x^(-0.5)};
+                \addlegendentry{$\sqrt{h}=\sqrt{\frac{1}{x}}$}
             \end{axis}
@@
         \caption{Mean Visibility Distance as a Function of Grid Resolution}
+        \label{fig:meanvisibility-gridstep}
     \end{figure}
@@
         \caption{Computation Time of Visibility as a Function of Grid Resolution}
+        \label{fig:meanvisibility-computationComplexity}
     \end{figure}

### 2025-04-22 DGMM2025/paper.tex
fixing some typographic issues

@@
         Computing visibility on a geometric object requires heavy
-        computations since it requires to identify pair of points that
-        are visible to each other, i.e. there is a straight segment
+        computations since it requires to identify pairs of points that
+        are visible to each other, i.e.\ there is a straight segment
         joining them that stays in the close vicinity of the object
@@
     polygons in the plane has been extensively studied in the
-    litterature \cite{ghosh:2007-book} and is still studied in higher
-    dimensional spaces \cite{orourke:2017-book}. The general problem
+    litterature~\cite{ghosh:2007-book} and is still studied in higher
+    dimensional spaces~\cite{orourke:2017-book}. The general problem
     has a high complexity. For instance, the 3d visibility complex
     between $n$ spheres and occluding spheres has a complexity
-    $O(n^4)$ \cite{durand:2002-tog}. Exact 3d visibility between
+    $O(n^4)$~\cite{durand:2002-tog}. Exact 3d visibility between
     polygons and occluding polygons is often casted into 5d Euclidean
-    space derived from Plücker space \cite{nirenstein:2002-ewr}, which
+    space derived from Plücker space~\cite{nirenstein:2002-ewr}, which
     nicely represents 3d lines and their respective positions. The
@@
     problem if there is a connected digital straight line joining a
-    pair of cells without occluding cell(s) (e.g. Soille
-    \cite{soille:1994-prl} uses Bresenham line segments). Coeurjolly
-    \emph{et al.} \cite{coeurjolly:2004-prl} uses a non-symmetric
-    visibility definition and preimage computations to speed up that
-    kind of algorithms. Chica \cite{chica:2008-spm} uses a half-cell
-    erosion of the complementary space and Bresenham straight lines to
-    decide visibility.
+    pair of cells without occluding cell(s) (e.g.\ Soille~\cite{soille:1994-prl}
+    uses Bresenham line segments). Coeurjolly \emph{et al.}~\cite{coeurjolly:2004-prl}
+    uses a non-symmetric visibility definition and preimage computations
+    to speed up that kind of algorithms. Chica~\cite{chica:2008-spm}
+    uses a half-cell erosion of the complementary space and Bresenham
+    straight lines to decide visibility.
 
@@
     equivalent to the \emph{cotangency} of $p$ and $q$ in $X$, as
-    formalized in \cite{lachaud:2021-dgmm,lachaud:2022-jmiv}, and can
+    formalized in~\cite{lachaud:2021-dgmm,lachaud:2022-jmiv}, and can
     be viewed as an inclusion problem between sets of lattice points
@@
     sensitive to sharp corners while multigrid convergent along the
-    boundary of digitized smooth shapes
-    \cite{feschet:1999-dgci,lachaud:2007-ivc,nguyen:2011-pr}. Many ad
-    hoc methods have been proposed for tangent plane or normal
+    boundary of digitized smooth shapes~\cite{feschet:1999-dgci,lachaud:2007-ivc,nguyen:2011-pr}.
+    Many ad hoc methods have been proposed for tangent plane or normal
     estimation on 3d digital surfaces
     (e.g. \cite{fourey:2009-cg,charrier:2011-iwcia,Cuel:2014-dgci,Lachaud:2017-lnm,mareche:2024-ispr}).
-    If two of these methods \cite{Cuel:2014-dgci,Lachaud:2017-lnm}
+    If two of these methods~\cite{Cuel:2014-dgci,Lachaud:2017-lnm}
     have been shown to be multigrid convergent on digitization of
     shapes with smooth boundary, their formulation intrinsically
-    smoothes features, e.g. in contrast with the method of
-    Mar{\^e}ch{\'e} \emph{et al.}  \cite{mareche:2024-ispr}, whose
+    smoothes features, e.g.\ in contrast with the method of
+    Mar{ê}ch{é} \emph{et al.}~\cite{mareche:2024-ispr}, whose
     convergence is not established. We propose here a normal estimator
@@
     an erosion algorithm where the structuring element is the chosen
-    pattern, and could also be used for morphological operations
-    \cite{soille1999morphological}.  The paper outline is as
-    follows. In Section~2, we recall some definitions and present
-    tangency of chords and its equivalence to visibility.  Section~3
-    describes the specific data structure for encoding set of grid
-    cells, and the main algorithm that exploits this encoding to
-    compute visibility exactly.  Section~4 presents experimental
-    results on visibility, its usage as a discrete normal estimator,
-    and how it improves curvature estimates on digital surfaces.
-    Finally, Section 5 concludes and gives some perspectives to this
-    work, notably other usages of this algorithm in the field.
+    pattern, and could also be used for morphological operations~\cite{soille1999morphological}.
+    The paper outline is as follows. In Section~2, we recall some
+    definitions and present tangency of chords and its equivalence
+    to visibility. Section~3 describes the specific data structure
+    for encoding set of grid cells, and the main algorithm that
+    exploits this encoding to compute visibility exactly. Section~4
+    presents experimental results on visibility, its usage as a
+    discrete normal estimator, and how it improves curvature estimates
+    on digital surfaces. Finally, Section 5 concludes and gives some
+    perspectives to this work, notably other usages of this algorithm
+    in the field.
 

### 2025-04-22 DGMM2025/paper.tex
rework time complexity graph (wip)

@@
                 xlabel={Gridstep},
-                x dir=reverse,
                 ylabel={Mean distance},
@@
             \begin{axis}[
-                xlabel={Gridstep},
-                x dir=reverse,
-                ylabel={Duration (s)},
+                xlabel={\#Pointels},
+                ylabel={Computation Time},
                 legend pos=north west,
@@
                 \addplot[
-                    color=cyan,
-                    mark=square,
-                ]
-                coordinates {
-                    (1,0.513)(0.875,0.585)(0.75,0.897)(0.625,1.401)(0.5,2.441)(0.375,4.664)(0.25,11.420)
+                    red,
+                    only marks,
+                    mark=halfcircle,
+                    mark options={solid}
+                ] table[row sep=crcr] {
+                    10624 2246.69\\
+                    4968 793.426\\
+                    2584 328.535\\
+                    1840 190.401\\
+                    1176 93.2502\\
+                    912 78.7981\\
+                    624 56.3769\\
+                    28568 10193.5\\
+                    12632 4004.92\\
+                    7088 2010.63\\
+                    4664 1188.73\\
+                    3080 755.754\\
+                    2408 545.347\\
+                    1736 366.541\\
+                    24320 11169.1\\
+                    10760 4720.44\\
+                    6056 2397.79\\
+                    3944 1380.38\\
+                    2648 874.979\\
+                    2000 580.0\\
+                    1520 415.373\\
+                    8336 3196.55\\
+                    3720 1268.46\\
+                    2104 639.305\\
+                    1336 342.873\\
+                    928 177.54\\
+                    680 112.142\\
+                    520 87.0747\\
+                    37592 12335.6\\
+                    16712 5582.38\\
+                    9512 2976.21\\
+                    6056 1731.32\\
+                    4088 990.78\\
+                    3032 788.507\\
+                    2456 548.66\\
                 };
-                \addlegendentry{sphere9 radius 10}
+                \addlegendentry{radius 10};
                 \addplot[
-                    color=red,
-                    mark=square,
-                ]
-                coordinates {
-                    (1,0.440)(0.875,0.665)(0.75,0.823)(0.625,1.428)(0.5,2.463)(0.375,4.697)(0.25,11.766)
+                    MyGreen,
+                    only marks,
+                    mark=halfcircle,
+                    mark options={solid}
+                ] table[row sep=crcr] {
+                    1000 1000\\
                 };
-                \addlegendentry{goursat radius 10}
+                \addlegendentry{radius 20};
                 \addplot[
-                    color=red,
-                    mark=triangle,
-                ]
-                coordinates {
-                    (1,1.389)(0.875,2.567)(0.75,3.661)(0.625,7.123)(0.5,13.881)(0.375,28.913)(0.25,77.360)
+                    blue,
+                    only marks,
+                    mark=halfcircle,
+                    mark options={solid}
+                ] table[row sep=crcr] {
+                    10624 18283.5\\
+                    4968 4957.93\\
+                    2584 2133.36\\
+                    1840 1292.53\\
+                    1176 922.51\\
+                    912 863.731\\
+                    624 813.638\\
+                    28568 188784.0\\
+                    12632 62237.1\\
+                    7088 24874.9\\
+                    4664 9043.39\\
+                    3080 4407.09\\
+                    2408 2641.04\\
+                    1736 1820.31\\
+                    24320 227432.0\\
+                    10760 69706.8\\
+                    6056 25408.9\\
+                    3944 10094.7\\
+                    2648 5269.56\\
+                    2000 2948.16\\
+                    1520 2082.02\\
+                    8336 45045.4\\
+                    3720 8638.42\\
+                    2104 3238.48\\
+                    1336 1731.9\\
+                    928 1122.69\\
+                    680 928.084\\
+                    520 890.592\\
+                    37592 257981.0\\
+                    16712 84729.7\\
+                    9512 36298.8\\
+                    6056 15640.2\\
+                    4088 6662.17\\
+                    3032 4431.71\\
+                    2456 2621.98\\
                 };
-                \addlegendentry{radius 20}
-                \addplot[
-                    color=red,
-                    mark=halfcircle,
-                ]
-                coordinates {
-                    (1,2.172)(0.875,3.747)(0.75,5.565)(0.625,13.180)(0.5,33.088)(0.375,80.584)(0.25,240.546)
-                };
-                \addlegendentry{radius 30}
-                \addplot[
-                    color=violet,
-                    mark=square,
-                ]
-                coordinates {
-                    (1,0.057)(0.875,0.081)(0.75,0.097)(0.625,0.197)(0.5,0.330)(0.375,0.800)(0.25,2.253)
-                };
-                \addlegendentry{torus}
-                \addplot[
-                    color=violet,
-                    mark=triangle,
-                ]
-                coordinates {
-                    (1,0.248)(0.875,0.294)(0.75,0.339)(0.625,0.620)(0.5,1.110)(0.375,2.643)(0.25,9.369)
-                };
-                \addplot[
-                    color=violet,
-                    mark=halfcircle,
-                ]
-                coordinates {
-                    (1,0.837)(0.875,0.880)(0.75,0.942)(0.625,1.316)(0.5,2.142)(0.375,5.046)(0.25,20.418)
-                };
+                \addlegendentry{radius 30};
             \end{axis}

### 2025-04-22 DGMM2025/paper.tex
Add figure

@@
 
+    \begin{figure}
+      \begin{center}
+        \begin{tabular}{|c||c|c|c|} \hline
+          Curvature & II normals & CTriv normals & Our normals \\ \hline \hline
+          $\kappa_1$&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-k1-II.png}&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-k1-CTriv.png}&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-k1-NV.png}\\ \hline
+          $\kappa_2$&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-k2-II.png}&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-k2-CTriv.png}&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-k2-NV.png}\\ \hline
+          $H$&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-H-II.png}&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-H-CTriv.png}&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-H-NV.png}\\ \hline
+          $G$&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-G-II.png}&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-G-CTriv.png}&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-G-NV.png}\\ \hline
+        \end{tabular}
+      \end{center}
+      \caption{Estimation of curvatures using Corrected Normal Current
+        estimators \cite{} for the shape ``Dice-20'' of Thingi10K
+        database at resolution $256^3$. This estimator is
+        parameterized by an input normal estimator: first column by
+        ``Integral Invariant normals'' (radius $r=4.77$, second column
+        by ``Convolved Trivial normals'' (radius $k=3$), third column
+        by our presented normal estimator (radius $r=8.5$). Per row are displayed the
+        estimated curvatures in order: first and second principal
+        curvatures $\kappa_1$ and $\kappa_2$, mean curvature $H$,
+        Gaussian curvature $G$. The range of curvature between deep
+        blue and deep red is $\lbrack -0.1, 0.1 \rbrack$ with white
+        color equal to $0$.}
+    \end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2025-04-22 DGMM2025/paper.tex
fix graph presentations

@@
                 ylabel={Mean distance},
+                x dir=reverse,
                 legend pos=north west,
@@
                 xlabel={\#Pointels},
-                ylabel={Computation Time},
+                ylabel={Computation Time (ms)},
                 legend pos=north west,

### 2025-04-22 DGMM2025/paper.tex
added 20 radius complexities + higher pointel examples

@@
             ]
-
                 \addplot[
@@
                     2456 548.66\\
+                    97844 49226.3\\
+                    390235 181322\\
                 };
@@
                 ] table[row sep=crcr] {
-                    1000 1000\\
+                    10624 9522.43\\
+                    4968 2876.81\\
+                    2584 1152.25\\
+                    1840 635.332\\
+                    1176 347.973\\
+                    912 304.801\\
+                    624 250.126\\
+                    28568 70137.9\\
+                    12632 26063.0\\
+                    7088 11985.8\\
+                    4664 6239.51\\
+                    3080 3468.31\\
+                    2408 2059.84\\
+                    1736 1254.2\\
+                    24320 86616.9\\
+                    10760 26605.7\\
+                    6056 11813.5\\
+                    3944 6516.92\\
+                    2648 3564.03\\
+                    2000 1949.32\\
+                    1520 1244.89\\
+                    8336 18125.5\\
+                    3720 5157.11\\
+                    2104 2029.09\\
+                    1336 896.186\\
+                    928 446.136\\
+                    680 306.651\\
+                    520 259.078\\
+                    37592 76316.3\\
+                    16712 27747.3\\
+                    9512 13608.6\\
+                    6056 7140.03\\
+                    4088 3704.52\\
+                    3032 2624.2\\
+                    2456 1422.6\\
+                    97844 378906\\
+                    390235 1747780\\
                 };
@@
                     2456 2621.98\\
+                    97844 1157400\\
+                    390235 10000000\\ % TODO récup le temps demain (en ~10e4s)
                 };
                 \addlegendentry{radius 30};
+                \addplot [
+                    color=black,
+                    thick,
+                    domain=500:60000,
+                    samples=100,
+                ] {0.01*x^(1.5)};
+                \addlegendentry{$0.01\times x\sqrt{x}$}
             \end{axis}
@@
           $\kappa_1$&
-          \includegraphics[width=0.3\textwidth]{pictures/d20-k1-II.png}&
-          \includegraphics[width=0.3\textwidth]{pictures/d20-k1-CTriv.png}&
-          \includegraphics[width=0.3\textwidth]{pictures/d20-k1-NV.png}\\ \hline
+          \includegraphics[width=0.3\textwidth]{pictures/d20-k1-II}&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-k1-CTriv}&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-k1-NV}\\ \hline
           $\kappa_2$&
-          \includegraphics[width=0.3\textwidth]{pictures/d20-k2-II.png}&
-          \includegraphics[width=0.3\textwidth]{pictures/d20-k2-CTriv.png}&
-          \includegraphics[width=0.3\textwidth]{pictures/d20-k2-NV.png}\\ \hline
+          \includegraphics[width=0.3\textwidth]{pictures/d20-k2-II}&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-k2-CTriv}&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-k2-NV}\\ \hline
           $H$&
-          \includegraphics[width=0.3\textwidth]{pictures/d20-H-II.png}&
-          \includegraphics[width=0.3\textwidth]{pictures/d20-H-CTriv.png}&
-          \includegraphics[width=0.3\textwidth]{pictures/d20-H-NV.png}\\ \hline
+          \includegraphics[width=0.3\textwidth]{pictures/d20-H-II}&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-H-CTriv}&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-H-NV}\\ \hline
           $G$&
-          \includegraphics[width=0.3\textwidth]{pictures/d20-G-II.png}&
-          \includegraphics[width=0.3\textwidth]{pictures/d20-G-CTriv.png}&
-          \includegraphics[width=0.3\textwidth]{pictures/d20-G-NV.png}\\ \hline
+          \includegraphics[width=0.3\textwidth]{pictures/d20-G-II}&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-G-CTriv}&
+          \includegraphics[width=0.3\textwidth]{pictures/d20-G-NV}\\ \hline
         \end{tabular}
@@
       \caption{Estimation of curvatures using Corrected Normal Current
-        estimators \cite{} for the shape ``Dice-20'' of Thingi10K
+        estimators \cite{lachaud:2022-dcg} for the shape ``Dice-20'' of Thingi10K
         database at resolution $256^3$. This estimator is

### 2025-04-23 main.cpp
added curvature computation on figure

@@ -8,6 +8,7 @@
 #include <polyscope/surface_mesh.h>
 #include <DGtal/arithmetic/IntegerComputer.h>
 #include <DGtal/base/Common.h>
+#include <DGtal/geometry/meshes/CorrectedNormalCurrentComputer.h>
 #include <DGtal/geometry/volumes/DigitalConvexity.h>
 #include <DGtal/geometry/volumes/TangencyComputer.h>
 #include <DGtal/helpers/StdDefs.h>
@@ -27,6 +28,7 @@ typedef Shortcuts<KSpace> SH3;
 typedef ShortcutsGeometry<KSpace> SHG3;
 typedef DigitalConvexity<KSpace> Convexity;
 typedef typename Convexity::LatticeSet LatticeSet;
+typedef CorrectedNormalCurrentComputer<RealPoint, RealVector> CNC;
 
 typedef std::pair<Integer, Integer> Interval;
 typedef std::vector<Interval> Intervals;
@@ -51,6 +53,20 @@ CountedPtr<SH3::SurfaceMesh> primal_surface(nullptr);
 
 std::vector<RealPoint> visibility_normals;
 std::vector<RealPoint> visibility_sharps;
+
+// Curvature variables
+CountedPtr<CNC> pCNC;
+CNC::ScalarMeasure mu0;
+CNC::ScalarMeasure mu1;
+CNC::ScalarMeasure mu2;
+CNC::TensorMeasure muXY;
+std::vector<double> H;
+std::vector<double> G;
+std::vector<double> K1;
+std::vector<double> K2;
+std::vector<RealVector> D1;
+std::vector<RealVector> D2;
+float MaxCurv = 0.2;
 
 // Parameters
 int VisibilityRadius = 10;
@@ -274,8 +290,8 @@ checkInterval(const Interval toCheck, const Intervals &figIntervals) {
 
 Intervals intersect(const Intervals &l1, const Intervals &l2) {
   Intervals result;
-    // check 3rd example of testIntersection to see that you need at most this amount
-   result.reserve( l1.size() + l2.size() - 1);
+  // check 3rd example of testIntersection to see that you need at most this amount
+  result.reserve(l1.size() + l2.size() - 1);
 //  result.reserve( std::max( l1.size(), l2.size() ) );
   int k1 = 0, k2 = 0;
   while (k1 < l1.size() && k2 < l2.size()) {
[…]

### 2025-04-23 DGMM2025/paper.tex
rearrangement + adding missing data
added pictures to show visibility

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    % Insert visibility results images
 
-    \section{Feature-aware normal estimation on digital surfaces}
+    \begin{figure}
+        \begin{center}
+            \includegraphics[width=0.8\textwidth]{pictures/visibility_from_given_point_r_10}
+            \caption{Visibility of a point on an edge of a fandisk}
+            \label{fig:visibility-fandisk}
+        \end{center}
+    \end{figure}
+    \begin{figure}
+        \begin{center}
+            \includegraphics[width=0.8\textwidth]{pictures/visibility_aware_of_features}
+            \caption{Visibility of a point on a torus knot (the visibility is feature-aware)}
+            \label{fig:visibility-torus-knot}
+        \end{center}
+    \end{figure}
+
+    % Quantitative results
 
@@
                     97844 1157400\\
-                    390235 10000000\\ % TODO récup le temps demain (en ~10e4s)
+                    390235 10493200\\
                 };
@@
     \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+    \section{Feature-aware normal estimation and curvature estimation on digital surfaces}
+
+    % Explain how i use the resulting visibility to compute the normals
+
+    % Then same with curvatures
+
+    % Graphical result comparison of curvatures
 

### 2025-04-23 DGMM2025/paper.tex
added text for section 4

@@
 
-    % Explain how i use the resulting visibility to compute the normals
+    Let $V$ the visibility around the point $p$, let $c$ be the centroid of the
+    visible points around p. The normal $\vec{n}$ is defined as the first
+    eigenvector of the covariance matrix \Nu of the visible points:
+    \begin{equation}
+        \Nu = \frac{1}{\#V} \sum_{i=1}^{\#V} (p_i - c)(p_i - c)^T
+    \end{equation}
+    In order to reorient the normal, we use the trivial normal of the
+    surface as a reference.
 
-    % Then same with curvatures
-
-    % Graphical result comparison of curvatures
+    Then, to compute the curvatures, we use the Corrected Normal Current
+    estimator~\cite{lachaud:2022-dcg} which are based on the normals computed
+    above.
 

### 2025-04-23 main.cpp
bugfix crash parallel computation
Crash occured because operator[] isn't read only : if the value doesn't exist (which sometimes it does when reading an empty lattice line) it creates the value in the lmap. So sometimes you may by inadvertance write on the same memory zone the same empty data...

@@ -366,7 +366,12 @@ void computeVisibilityOmp(int radius) {
           const Point pInterest(axis == 0 ? 0 : 2 * tx, axis == 1 ? 0 : 2 * (axis == 0 ? tx : ty),
                                 axis == 2 ? 0 : 2 * ty);
           for (const auto &cInfo: latticeVector) {
-            eligibles = matchVector(eligibles, cInfo.second, figLattices[pInterest + cInfo.first]);
+            const auto it = figLattices.find(pInterest + cInfo.first);
+            if (it == figLattices.end()) {
+              eligibles.clear();
+              break;
+            }
+            eligibles = matchVector(eligibles, cInfo.second, it->second);
             if (eligibles.empty()) break;
           }
           if (!eligibles.empty()) {

### 2025-04-23 main.cpp
bugfix pointel selection issue

@@ -656,7 +656,7 @@ void myCallback() {
   // Select a vertex with the mouse
   if (polyscope::pick::haveSelection()) {
     auto selection = polyscope::pick::getSelection();
-    auto selectedSurface = dynamic_cast<polyscope::SurfaceMesh *>(selection.first);
+    auto selectedSurface = static_cast<polyscope::SurfaceMesh *>(selection.first);
     auto idx = selection.second;
 
     // Only authorize selection on the input surface and the reconstruction

### 2025-04-23 DGMM2025/paper.tex
adding visuals for visibility example

@@
 
+                \draw[red,arrows = {-Stealth[]}] (0,0)--(2,1);
+                \draw[red,arrows = {-Stealth[]}] (1,0)--(3,1);
+                \draw[red,arrows = {-Stealth[]}] (2,0)--(4,1);
+                \draw[red,arrows = {-Stealth[]}] (5,0)--(7,1);
+                \draw[red,arrows = {-Stealth[]}] (6,0)--(8,1);
+                \draw[red,arrows = {-Stealth[]}] (8,0)--(10,1);
+
             \end{tikzpicture} &
@@
                     \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,10.5)--(9.6,10.5);
+                    \filldraw[black] (-0.5,10.5) circle (0.05);
+                    \filldraw[black] (0.5,10.5) circle (0.05);
+                    \filldraw[black] (1.5,10.5) circle (0.05);
+                    \filldraw[black] (4.5,10.5) circle (0.05);
+                    \filldraw[black] (5.5,10.5) circle (0.05);
+                    \filldraw[black] (6.5,10.5) circle (0.05);
+                    \filldraw[black] (7.5,10.5) circle (0.05);
+                    \filldraw[black] (8.5,10.5) circle (0.05);
+                    \filldraw[black] (9.5,10.5) circle (0.05);
 
@@
                     \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,8)--(9.6,8);
+                    \filldraw[black] (-0.5,8) circle (0.05);
+                    \filldraw[black] (0.5,8) circle (0.05);
+                    \filldraw[black] (1.5,8) circle (0.05);
+                    \filldraw[black] (4.5,8) circle (0.05);
+                    \filldraw[black] (5.5,8) circle (0.05);
+                    \filldraw[black] (6.5,8) circle (0.05);
+                    \filldraw[black] (7.5,8) circle (0.05);
+                    \filldraw[black] (8.5,8) circle (0.05);
+                    \filldraw[black] (9.5,8) circle (0.05);
 
@@
                     \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,5.5)--(7.6,5.5);
+                    \filldraw[black] (-0.5,5.5) circle (0.05);
+                    \filldraw[black] (0.5,5.5) circle (0.05);
+                    \filldraw[black] (1.5,5.5) circle (0.05);
+                    \filldraw[black] (4.5,5.5) circle (0.05);
+                    \filldraw[black] (5.5,5.5) circle (0.05);
+                    \filldraw[black] (6.5,5.5) circle (0.05);
+                    \filldraw[black] (7.5,5.5) circle (0.05);
 
@@
                     \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,3)--(7.6,3);
+                    \filldraw[black] (-0.5,3) circle (0.05);
+                    \filldraw[black] (0.5,3) circle (0.05);
+                    \filldraw[black] (1.5,3) circle (0.05);
+                    \filldraw[black] (4.5,3) circle (0.05);
+                    \filldraw[black] (5.5,3) circle (0.05);
+                    \filldraw[black] (7.5,3) circle (0.05);
 
@@
                     \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,0.5)--(7.6,0.5);
+                    \filldraw[black] (-0.5,0.5) circle (0.05);
+                    \filldraw[black] (0.5,0.5) circle (0.05);
+                    \filldraw[black] (1.5,0.5) circle (0.05);
+                    \filldraw[black] (4.5,0.5) circle (0.05);
+                    \filldraw[black] (5.5,0.5) circle (0.05);
+                    \filldraw[black] (7.5,0.5) circle (0.05);
 
@@
 We travel the lattice maps from bottom-up.
-}
+The found possible visibilities are shown on the original figure}
         \label{fig:enter-label}
@@
 
+    In order to compute the visibility, we first compute $\Omega = \text{Star}(C)$. Then for each primal direction of
+    coordinates at most $r$, we look at all the possible positions this specific direction does link 2 visible points
+    of the cell complex. In order to do so, for each shift in $\Omega$, we compute the positions where points are
+    visible using the same method as presented in \ref{fig:enter-label}.
+
     \begin{algorithm}
@@
     \end{algorithm}
+
+    To efficiently compute the intersection of 2 lists of intervals $K$ and $L$, we go through the first 2 unvisited
+    elements of the 2 lists. If they don't overlap (i.e. the start and end of the 1st interval are both smaller than
+    the start of the other), then we can discard the smaller interval. Else, we construct the intersection of these
+    2 intervals as one of the resulting intervals. We then can skip the interval with the smallest end. If both
+    intervals have the same end, then both intervals can be skipped. Doing this computation until one of the lists
+    is empty returns the intersection of both lists of intervals.
 
@@
         \begin{center}
-        \begin{tabular}{|c||c|c|c|} \hline
+            \begin{tabular}{|c||c|c|c|}
+                \hline
                 Curvature & II normals & CTriv normals & Our normals \\ \hline \hline
-          $\kappa_1$&
-          \includegraphics[width=0.3\textwidth]{pictures/d20-k1-II}&
+                $\kappa_1$ &
+                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-II} &
                 \includegraphics[width=0.3\textwidth]{pictures/d20-k1-CTriv}&
                 \includegraphics[width=0.3\textwidth]{pictures/d20-k1-NV}\\ \hline
-          $\kappa_2$&
-          \includegraphics[width=0.3\textwidth]{pictures/d20-k2-II}&
+                $\kappa_2$ &
+                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-II} &
                 \includegraphics[width=0.3\textwidth]{pictures/d20-k2-CTriv}&
                 \includegraphics[width=0.3\textwidth]{pictures/d20-k2-NV}\\ \hline
-          $H$&
-          \includegraphics[width=0.3\textwidth]{pictures/d20-H-II}&
+                $H$ &
+                \includegraphics[width=0.3\textwidth]{pictures/d20-H-II} &
                 \includegraphics[width=0.3\textwidth]{pictures/d20-H-CTriv}&
                 \includegraphics[width=0.3\textwidth]{pictures/d20-H-NV}\\ \hline
-          $G$&
-          \includegraphics[width=0.3\textwidth]{pictures/d20-G-II}&
+                $G$ &
+                \includegraphics[width=0.3\textwidth]{pictures/d20-G-II} &
                 \includegraphics[width=0.3\textwidth]{pictures/d20-G-CTriv}&

### 2025-04-23 DGMM2025/paper.tex
adding visuals for visibility example and one example on the paper

@@
 \usepackage{environ}
+\usepackage{bbm}
 
@@
     of the cell complex. In order to do so, for each shift in $\Omega$, we compute the positions where points are
-    visible using the same method as presented in \ref{fig:enter-label}.
+    visible using the same method as presented in~\ref{fig:enter-label}.
 
@@
     visible points around p. The normal $\vec{n}$ is defined as the first
-    eigenvector of the covariance matrix \Nu of the visible points:
+    eigenvector of the covariance matrix $\mathcal{V}$ of the visible points:
     \begin{equation}
-        \Nu = \frac{1}{\#V} \sum_{i=1}^{\#V} (p_i - c)(p_i - c)^T
+        \mathcal{V} = \frac{1}{\#V} \sum_{i=1}^{\#V} (p_i - c)(p_i - c)^T
     \end{equation}
@@
     surface as a reference.
+
+    \begin{figure}
+        \begin{center}
+            \includegraphics[width=0.8\textwidth]{pictures/torus-knot-normal-estimation}
+            \caption{Normal estimation on a torus knot using the visibility
+            algorithm. The normals are colored according to their orientation as $0.5 \cdot (n_i + \mathbbm{1})$
+                .}
+            \label{fig:normal-estimation}
+        \end{center}
+    \end{figure}
 

### 2025-04-23 main.cpp

@@ -52,6 +52,7 @@ CountedPtr<SH3::DigitalSurface> digital_surface(nullptr);
 CountedPtr<SH3::SurfaceMesh> primal_surface(nullptr);
 
 std::vector<RealPoint> visibility_normals;
+std::vector<RealPoint> normal_colors;
 std::vector<RealPoint> visibility_sharps;
 
 // Curvature variables
@@ -90,10 +91,10 @@ bool isPointLowerThan(const Point &p1, const Point &p2) {
 
 class Visibility {
 public:
-  Dimension mainAxis;
+  Dimension mainAxis{};
   std::vector<bool> visibles;
-  size_t vectorsSize;
-  size_t pointsSize;
+  size_t vectorsSize{};
+  size_t pointsSize{};
   std::map<Point, size_t> pointIdxs;
   std::map<IntegerVector, size_t> vectorIdxs;
 
@@ -652,6 +653,15 @@ void doRedisplayCurvatures() {
   psPrimalMesh->addFaceVectorQuantity("D2 (2nd princ. direction)", D2);
 }
 
+void doRedisplayNormalAsColors() {
+  normal_colors.clear();
+  normal_colors.reserve(visibility_normals.size());
+  for (const auto& n : visibility_normals) {
+    normal_colors.push_back(0.5f * (n + 1.0f));
+  }
+  psPrimalMesh->addVertexColorQuantity("Normals as colors", normal_colors);
+}
+
 void myCallback() {
   // Select a vertex with the mouse
   if (polyscope::pick::haveSelection()) {
@@ -700,12 +710,9 @@ void myCallback() {
   if (ImGui::Button("Compute Normals")) {
     trace.beginBlock("Compute visibilities Normals");
     computeVisibilityNormals();
-    Time = trace.endBlock();
-  }
-  if (ImGui::Button("Reorient Normals")) {
-    trace.beginBlock("Reorient visibility normals");
     reorientVisibilityNormals();
     Time = trace.endBlock();
+    doRedisplayNormalAsColors();
   }
   if (ImGui::Button("Compute Curvatures")) {
     trace.beginBlock("Compute visibilities Curvatures");

### 2025-04-24 DGMM2025/paper.tex
Update figure 10

@@
 \usepackage{bbm}
+%\usepackage{array}
+%\usepackage{multirow}
 
@@
                 Curvature & II normals & CTriv normals & Our normals \\ \hline \hline
-                $\kappa_1$ &
-                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-II} &
-                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-CTriv}&
-                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-NV}\\ \hline
-                $\kappa_2$ &
-                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-II} &
-                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-CTriv}&
-                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-NV}\\ \hline
-                $H$ &
-                \includegraphics[width=0.3\textwidth]{pictures/d20-H-II} &
-                \includegraphics[width=0.3\textwidth]{pictures/d20-H-CTriv}&
-                \includegraphics[width=0.3\textwidth]{pictures/d20-H-NV}\\ \hline
-                $G$ &
-                \includegraphics[width=0.3\textwidth]{pictures/d20-G-II} &
-                \includegraphics[width=0.3\textwidth]{pictures/d20-G-CTriv}&
-                \includegraphics[width=0.3\textwidth]{pictures/d20-G-NV}\\ \hline
+                \raisebox{18mm}{$\kappa_1$} &
+                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-II.jpg} &
+                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-CTriv.jpg}&
+                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-VN.jpg}\\ \hline
+                \raisebox{18mm}{$\kappa_2$} &
+                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-II.jpg} &
+                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-CTriv.jpg}&
+                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-VN.jpg}\\ \hline
+                \raisebox{18mm}{$H$} &
+                \includegraphics[width=0.3\textwidth]{pictures/d20-H-II.jpg} &
+                \includegraphics[width=0.3\textwidth]{pictures/d20-H-CTriv.jpg}&
+                \includegraphics[width=0.3\textwidth]{pictures/d20-H-VN.jpg}\\ \hline
+                \raisebox{18mm}{$G$} &
+                \includegraphics[width=0.3\textwidth]{pictures/d20-G-II.jpg} &
+                \includegraphics[width=0.3\textwidth]{pictures/d20-G-CTriv.jpg}&
+                \includegraphics[width=0.3\textwidth]{pictures/d20-G-VN.jpg}\\ \hline
             \end{tabular}
         \end{center}
-        \caption{Estimation of curvatures using Corrected Normal Current
-        estimators \cite{lachaud:2022-dcg} for the shape ``Dice-20'' of Thingi10K
-        database at resolution $256^3$. This estimator is
-        parameterized by an input normal estimator: first column by
-        ``Integral Invariant normals'' (radius $r=4.77$, second column
-        by ``Convolved Trivial normals'' (radius $k=3$), third column
-        by our presented normal estimator (radius $r=8.5$). Per row are displayed the
-        estimated curvatures in order: first and second principal
-        curvatures $\kappa_1$ and $\kappa_2$, mean curvature $H$,
-            Gaussian curvature $G$. The range of curvature between deep
-            blue and deep red is $\lbrack -0.1, 0.1 \rbrack$ with white
-            color equal to $0$.}
+        \caption{Estimation of curvatures using Corrected Normal
+          Current estimators \cite{lachaud:2022-dcg} with a measure of
+          radius $2$ for the shape ``Dice-20'' of Thingi10K database
+          at resolution $256^3$. This estimator is parameterized by an
+          input normal estimator: first column by ``Integral Invariant
+          normals'' (radius $r=6$, second column by ``Convolved
+          Trivial normals'' (radius $k=6$), third column by our
+          presented normal estimator (deviation $\sigma=4$, radius
+          $r=2\sigma=8$). Per row are displayed the estimated
+          curvatures in order: first and second principal curvatures
+          $\kappa_1$ and $\kappa_2$, mean curvature $H$, Gaussian
+          curvature $G$. The range of curvature between deep blue and
+          deep red is $\lbrack -0.1, 0.1 \rbrack$ with white color
+          equal to $0$.}
     \end{figure}

### 2025-04-24 DGMM2025/paper.tex
Update figure 10
Reduce intro

@@
 \pgfplotsset{compat=1.18}
-\usetikzlibrary {arrows.meta,decorations.shapes}
+\usetikzlibrary {spy,arrows.meta,decorations.shapes}
 \setauthormarkup{}
@@
     digital topology, with applications ranging from computer vision
-    (identifying occlusions) to geometric modeling (feature detection, geodesics)
-    and computer graphics (path tracing, shadowmap). Visibility within
-    polygons in the plane has been extensively studied in the
-    litterature~\cite{ghosh:2007-book} and is still studied in higher
-    dimensional spaces~\cite{orourke:2017-book}. The general problem
-    has a high complexity. For instance, the 3d visibility complex
-    between $n$ spheres and occluding spheres has a complexity
+    (occlusions), geometric modeling (feature detection,
+    geodesics) to computer graphics (path tracing,
+    shadowmap). Visibility within polygons in the plane has been
+    extensively studied in the litterature~\cite{ghosh:2007-book} and
+    is still studied in higher dimensional
+    spaces~\cite{orourke:2017-book}. The general problem has a high
+    complexity. For instance, the 3d visibility complex between $n$
+    spheres and occluding spheres has a complexity
     $O(n^4)$~\cite{durand:2002-tog}. Exact 3d visibility between
-    polygons and occluding polygons is often casted into 5d Euclidean
-    space derived from Plücker space~\cite{nirenstein:2002-ewr}, which
-    nicely represents 3d lines and their respective positions. The
-    computational cost remains high even with decomposition into
-    coarse cells for speed up (several days of computation for a
-    million triangles at the time).
+    polygons and occluding polygons is often casted into 5d Plücker
+    space~\cite{nirenstein:2002-ewr}, which nicely represents 3d lines
+    and their respective positions. The computational cost remains
+    high even with decomposition into coarse cells for speed up
+    (several days of computation for 1M triangles at the time).
 
@@
     vectors. On the contrary the visibility is blocked at sharp
-    features, so the normal vector is then not influenced by the
+    features, so the normal vector is not influenced by the
     geometry on the other side of the features. We demonstrate the
@@
 
+    \newcommand{\MyZoom}[1]{%
+      \begin{tikzpicture}[spy using outlines={circle,magnification=1.8,size=2cm,connect spies}]
+        \node[inner sep=0pt] {\pgfimage[width=0.3\textwidth]{#1}};
+        \spy[overlay,blue] on (0.4,0.2) in node at (-0.8,0.8);
+      \end{tikzpicture}}
+    % \newcommand{\MyZoom}[1]{\includegraphics[width=0.3\textwidth]{#1}}
+
     \begin{figure}
@@
                 \hline
-                Curvature & II normals & CTriv normals & Our normals \\ \hline \hline
+                Curv. & II normals & CTriv normals & Our normals \\ \hline \hline
                 \raisebox{18mm}{$\kappa_1$} &
-                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-II.jpg} &
-                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-CTriv.jpg}&
-                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-VN.jpg}\\ \hline
+                \MyZoom{pictures/d20-k1-II.jpg} &
+                \MyZoom{pictures/d20-k1-CTriv.jpg}&
+                \MyZoom{pictures/d20-k1-VN.jpg}\\ \hline
                 \raisebox{18mm}{$\kappa_2$} &
-                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-II.jpg} &
-                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-CTriv.jpg}&
-                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-VN.jpg}\\ \hline
+                \MyZoom{pictures/d20-k2-II.jpg} &
+                \MyZoom{pictures/d20-k2-CTriv.jpg}&
+                \MyZoom{pictures/d20-k2-VN.jpg}\\ \hline
                 \raisebox{18mm}{$H$} &
-                \includegraphics[width=0.3\textwidth]{pictures/d20-H-II.jpg} &
-                \includegraphics[width=0.3\textwidth]{pictures/d20-H-CTriv.jpg}&
-                \includegraphics[width=0.3\textwidth]{pictures/d20-H-VN.jpg}\\ \hline
+                \MyZoom{pictures/d20-H-II.jpg} &
+                \MyZoom{pictures/d20-H-CTriv.jpg}&
+                \MyZoom{pictures/d20-H-VN.jpg}\\ \hline
                 \raisebox{18mm}{$G$} &
-                \includegraphics[width=0.3\textwidth]{pictures/d20-G-II.jpg} &
-                \includegraphics[width=0.3\textwidth]{pictures/d20-G-CTriv.jpg}&
-                \includegraphics[width=0.3\textwidth]{pictures/d20-G-VN.jpg}\\ \hline
+                \MyZoom{pictures/d20-G-II.jpg} &
+                \MyZoom{pictures/d20-G-CTriv.jpg}&
+                \MyZoom{pictures/d20-G-VN.jpg}\\ \hline
             \end{tabular}

### 2025-04-24 DGMM2025/paper.tex
Working on 4

@@
 
-    Let $V$ the visibility around the point $p$, let $c$ be the centroid of the
-    visible points around p. The normal $\vec{n}$ is defined as the first
-    eigenvector of the covariance matrix $\mathcal{V}$ of the visible points:
+    \newcommand{\Kernel}[1]{\ensuremath{w_{\sigma}(#1)}}
+    We propose a new normal estimator on digital surfaces, which uses
+    the visibility of the point of interest while taking into account
+    a user-given scale $\sigma$. If $\sigma$ is proportionnal to the
+    average length between visible points (so some $c\sqrt{h}$ for $c$
+    some constant), then this estimator is observed to be multigrid
+    convergent along digitization of smooth shapes. However, since the
+    computation window is limited by the visibility, it better
+    approximates the geometry near sharp or salient features.
+
+    More precisely, we choose a Gaussian function
+    $\Kernel{x}:=e^{-\frac{x^2}{2\sigma^2}}$ as a weight kernel. Let
+    $V_p$ be the set of visible points from the point $p$.  Let $c_p$
+    be the weighted centroid of the visible points around $p$,
+    i.e. $c_p := \frac{\sum_{q \in V_p} \Kernel{\|q-p\|}q}{\sum_{q \in
+        V_p} \Kernel{\|q-p\|}}$.  We form the weighted covariance matrix
+    $\mathcal{V}_p$ of the points $V_p$ as:
     \begin{equation}
-        \mathcal{V} = \frac{1}{\#V} \sum_{i=1}^{\#V} (p_i - c)(p_i - c)^T
+        \mathcal{V}_p = \sum_{q \in V_p} \Kernel{\|q-p\|}(q - c_p)(q - c_p)^T.
     \end{equation}
-    In order to reorient the normal, we use the trivial normal of the
-    surface as a reference.
+    The \emph{visibility normal} $\vec{n}_p$ of point $p$ is defined
+    as the first eigenvector of the covariance matrix $\mathcal{V}_p$
+    of the visible points, corresponding to its smallest
+    eigenvalue. Its orientation is chosen so as to point in the same
+    direction as the average of the trivial normals to the surfels
+    touching the point $p$.
+
+    %% Let $V_p$ be the set of visible points from the point $p$. Let
+    %% $c_p$ be the weighted centroid of the visible points around $p$.
+    %% The normal $\vec{n}$ is defined as the first eigenvector of the
+    %% covariance matrix $\mathcal{V}$ of the visible points:
+    %% \begin{equation}
+    %%     \mathcal{V} = \frac{1}{\#V} \sum_{i=1}^{\#V} (p_i - c)(p_i - c)^T
+    %% \end{equation}
+    %% In order to reorient the normal, we use the trivial normal of the
+    %% surface as a reference.
 

### 2025-04-24 DGMM2025/paper.tex
Working on 4

@@
 
-    \section{Feature-aware normal estimation and curvature estimation on digital surfaces}
+    \section{Saliency-aware normal and curvature estimation}
 
     \newcommand{\Kernel}[1]{\ensuremath{w_{\sigma}(#1)}}
+    \paragraph*{Saliency-aware normal estimator.}
     We propose a new normal estimator on digital surfaces, which uses
@@
     a user-given scale $\sigma$. If $\sigma$ is proportionnal to the
-    average length between visible points (so some $c\sqrt{h}$ for $c$
-    some constant), then this estimator is observed to be multigrid
-    convergent along digitization of smooth shapes. However, since the
-    computation window is limited by the visibility, it better
-    approximates the geometry near sharp or salient features.
+    average length between visible points (so some
+    $\Theta(\sqrt{h})$), then this estimator is observed to be
+    multigrid convergent along digitization of smooth shapes. However,
+    since the computation window is limited by the visibility, it
+    better approximates the geometry near sharp or salient features.
 
@@
 
-    Then, to compute the curvatures, we use the Corrected Normal Current
-    estimator~\cite{lachaud:2022-dcg} which are based on the normals computed
-    above.
+    \paragraph*{Experimental convergence of normal estimation.}
+    [TODO] Show normal estimations along smooth shapes and compare with Integral Invariant.
+
+    \paragraph*{Application to curvature estimation.}
+    Then, to compute the curvatures, we use the Corrected Normal
+    Current estimator~\cite{lachaud:2022-dcg} which are based on the
+    normals computed above.
 

### 2025-04-24 DGMM2025/paper.tex
ii visibility + merging with what i have in local

@@
 \usepackage{bbm}
-%\usepackage{array}
-%\usepackage{multirow}
 
@@
     \begin{figure}
-        \begin{center}
-            \includegraphics[width=0.8\textwidth]{pictures/visibility_from_given_point_r_10}
-            \caption{Visibility of a point on an edge of a fandisk}
-            \label{fig:visibility-fandisk}
-        \end{center}
+        \centering
+        \begin{tabular}{c c}
+            \includegraphics[width=0.4\textwidth]{pictures/visibility_from_given_point_r_10} &
+            \includegraphics[width=0.4\textwidth]{pictures/visibility_aware_of_features}
+        \end{tabular}
+        \caption{Examples of visibility on a fandisk and a torus knot. First one is on the edge
+        of a fandisk, where the visibility stops at the edges. The other one is in the interior
+        of a torus knot, where we can see that the visibility is feature-aware and doesn't see
+        the other side of the torus' branch.}
+        \label{fig:visibility-examples}
     \end{figure}
-    \begin{figure}
-        \begin{center}
-            \includegraphics[width=0.8\textwidth]{pictures/visibility_aware_of_features}
-            \caption{Visibility of a point on a torus knot (the visibility is feature-aware)}
-            \label{fig:visibility-torus-knot}
-        \end{center}
-    \end{figure}
+%
+%    \begin{figure}
+%        \begin{center}
+%            \includegraphics[width=0.8\textwidth]{pictures/visibility_from_given_point_r_10}
+%            \caption{Visibility of a point on an edge of a fandisk}
+%            \label{fig:visibility-fandisk}
+%        \end{center}
+%    \end{figure}
+%    \begin{figure}
+%        \begin{center}
+%            \includegraphics[width=0.8\textwidth]{pictures/visibility_aware_of_features}
+%            \caption{Visibility of a point on a torus knot (the visibility is feature-aware)}
+%            \label{fig:visibility-torus-knot}
+%        \end{center}
+%    \end{figure}
 
@@
 
-    \pgfplotsset{width=13cm}
     \begin{figure}
@@
             \begin{axis}[
+                width=0.8\textwidth,
+                legend columns=3,
                 xlabel={Gridstep},
@@
             \begin{axis}[
+                width=0.8\textwidth,
                 xlabel={\#Pointels},
@@
     More precisely, we choose a Gaussian function
-    $\Kernel{x}:=e^{-\frac{x^2}{2\sigma^2}}$ as a weight kernel. Let
+    $\Kernel{x}\coloneqq e^{-\frac{x^2}{2\sigma^2}}$ as a weight kernel. Let
     $V_p$ be the set of visible points from the point $p$.  Let $c_p$
     be the weighted centroid of the visible points around $p$,
-    i.e. $c_p := \frac{\sum_{q \in V_p} \Kernel{\|q-p\|}q}{\sum_{q \in
+    i.e. $c_p \coloneqq \frac{\sum_{q \in V_p} \Kernel{\|q-p\|}q}{\sum_{q \in
         V_p} \Kernel{\|q-p\|}}$.  We form the weighted covariance matrix
@@
     direction as the average of the trivial normals to the surfels
-    touching the point $p$.
-
-    %% Let $V_p$ be the set of visible points from the point $p$. Let
-    %% $c_p$ be the weighted centroid of the visible points around $p$.
-    %% The normal $\vec{n}$ is defined as the first eigenvector of the
-    %% covariance matrix $\mathcal{V}$ of the visible points:
-    %% \begin{equation}
-    %%     \mathcal{V} = \frac{1}{\#V} \sum_{i=1}^{\#V} (p_i - c)(p_i - c)^T
-    %% \end{equation}
-    %% In order to reorient the normal, we use the trivial normal of the
-    %% surface as a reference.
+    touching the point $p$. \ref{fig:normals-estimation} shows an example
+    of our normals compared to normals computed with II
 
     \begin{figure}
-        \begin{center}
-            \includegraphics[width=0.8\textwidth]{pictures/torus-knot-normal-estimation}
-            \caption{Normal estimation on a torus knot using the visibility
-            algorithm. The normals are colored according to their orientation as $0.5 \cdot (n_i + \mathbbm{1})$
-                .}
-            \label{fig:normal-estimation}
-        \end{center}
+        \centering
+        \begin{tabular}{|c||c|c|}
+            \hline
+            II normals &
+            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
+            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} \\
+            \hline
+            Visibility normals &
+            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
+            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} \\
+            \hline
+        \end{tabular}
+        \caption{Examples of normals computed on a chinese dragon as a color map. First set displays II normals, second set uses the visibility
+        algorithm to compute them. The normals are colored according to their orientation as $0.5 \cdot (n_i + \mathbbm{1})$
+            . The right images are the smooth version of the left images}
+        \label{fig:normals-estimation}
     \end{figure}
 
-    \paragraph*{Experimental convergence of normal estimation.}
-    [TODO] Show normal estimations along smooth shapes and compare with Integral Invariant.
+    Then, to compute the curvatures, we use the Corrected Normal Current
+    estimator~\cite{lachaud:2022-dcg} which are based on the normals computed
+    above.
 

### 2025-04-24 DGMM2025/paper.tex
Working on 4

--- 2025-04-24 DGMM2025/paper.tex
@@
     \paragraph*{Application to curvature estimation.}
-    Then, to compute the curvatures, we use the Corrected Normal
-    Current estimator~\cite{lachaud:2022-dcg} which are based on the
-    normals computed above.
+    In order to illustrate better that the visibility normals better
+    take into account the sharp features of a digital surface while
+    staying meaningfull in digitization of smooth parts, we compare
+    the curvature estimates induced by different discrete normal
+    estimators. We exploit the \emph{Corrected Normal Current (CNC)
+    estimator}, whose theory is detailed in \cite{lachaud:2022-dcg}
+    and which can estimate all kinds of curvatures given positions and
+    normals. It produces state-of-the-art curvature estimates on
+    polygonal surfaces \cite{lachaud:2020-cgf}, point clouds
+    \cite{lachaud:2023-cgf}, and even outperforms Integral Invariant
+    curvature estimates \cite{coeurjolly:2014-cviu} on digital
+    surfaces \cite{lachaud:2022-dcg}. Its implementation is also
+    available in
+    \href{https://dgtal-team.github.io/doc-nightly/moduleCurvatureMeasures.html}{\textsc{DGtal}}.
+
+    Then,
+    to compute the curvatures, we use the Corrected Normal Current
+    estimator~\cite{lachaud:2022-dcg} which are based on the normals
+    computed above.
 

### 2025-04-24 DGMM2025/paper.tex
quick ref adding
Working on 4

@@
 
-    Then,
-    to compute the curvatures, we use the Corrected Normal Current
-    estimator~\cite{lachaud:2022-dcg} which are based on the normals
-    computed above.
+    \RefFigure{fig-curvatures} displays the results of CNC curvature
+    estimations on the digitization of a piecewise smooth shape
+    ``Talking D20'', taken from
+    \href{https://ten-thousand-models.appspot.com/detail.html?file_id=1533028}{Thingi10K}.
+    We compare the differences obtained by just changing the discrete
+    normal estimator (available in the \textsc{DGtal} library):
+    (column II normals) Integral Invariant normals with $r=6$, (column
+    CTriv normals) convolved trivial normals with $r=6$, (column
+    Visibility normals) our proposed estimator (VN) with $\sigma=4$ and
+    maximal visibility distance $2\sigma$. These parameters were
+    chosen so that the respective computation windows of the different
+    estimators are approximately the same.
+
+    II estimator is good along digitization of smooth or flat parts of
+    the dice, but presents curious artefacts near sharp features
+    induced by the hollowed out numbers: this is due to the nature of
+    II normal estimates, which computes a PCA of a ball centered on
+    the point of interest and may include points on the other side of
+    the saliencies.
+
+    CTriv estimator only performs averaging of trivial normal
+    directions along the surface. It behaves much better than II near
+    features (although it tends to smooth curvatures) since it does
+    not use information from across the gap. However some oscillations
+    of the curvatures are distinguishable especially along the flat
+    parts, and some curvature estimates are erroneous on smoother
+    parts (like the edge above 6 for $\kappa_2$ or several dice
+    vertices).
+
+    VN estimator takes the best of the two previous approaches. It
+    remains precise and stable on smooth and flat regions, while
+    perfectly delineating sharp features and holes, whatever the kind
+    of estimated curvatures. Its only drawback is the computation
+    time, which is [TO COMPLETE], compared to $2.3$s for II and $0.1s$
+    for CTriv.
 
@@
         \end{center}
-        \caption{Estimation of curvatures using Corrected Normal
-          Current estimators \cite{lachaud:2022-dcg} with a measure of
-          radius $2$ for the shape ``Dice-20'' of Thingi10K database
-          at resolution $256^3$. This estimator is parameterized by an
-          input normal estimator: first column by ``Integral Invariant
-          normals'' (radius $r=6$, second column by ``Convolved
-          Trivial normals'' (radius $k=6$), third column by our
-          presented normal estimator (deviation $\sigma=4$, radius
-          $r=2\sigma=8$). Per row are displayed the estimated
-          curvatures in order: first and second principal curvatures
-          $\kappa_1$ and $\kappa_2$, mean curvature $H$, Gaussian
-          curvature $G$. The range of curvature between deep blue and
-          deep red is $\lbrack -0.1, 0.1 \rbrack$ with white color
-          equal to $0$.}
+        \caption{\label{fig-curvatures}Estimation of curvatures using
+          Corrected Normal Current estimators \cite{lachaud:2022-dcg}
+          with a measure of radius $2$ for the shape ``Dice-20'' of
+          Thingi10K database at resolution $256^3$. This estimator is
+          parameterized by an input normal estimator: first column by
+          ``Integral Invariant normals'' (radius $r=6$, second column
+          by ``Convolved Trivial normals'' (radius $k=6$), third
+          column by our presented normal estimator (deviation
+          $\sigma=4$, radius $r=2\sigma=8$). Per row are displayed the
+          estimated curvatures in order: first and second principal
+          curvatures $\kappa_1$ and $\kappa_2$, mean curvature $H$,
+          Gaussian curvature $G$. The range of curvature between deep
+          blue and deep red is $\lbrack -0.1, 0.1 \rbrack$ with white
+          color equal to $0$.}
     \end{figure}

### 2025-04-24 DGMM2025/paper.tex
Working on 4

@@
     direction as the average of the trivial normals to the surfels
-    touching the point $p$. \ref{fig:normals-estimation} shows an example
-    of our normals compared to normals computed with II
+    touching the point $p$. Figure~\ref{fig:normals-estimation} shows an example
+    of our normals compared to normals computed with the integral invariant (II) estimator~\cite{Lachaud:2017-lnm}.
 
@@
     surfaces \cite{lachaud:2022-dcg}. Its implementation is also
-    available in
-    \href{https://dgtal-team.github.io/doc-nightly/moduleCurvatureMeasures.html}{\textsc{DGtal}}.
+    available in    \href{https://dgtal-team.github.io/doc-nightly/moduleCurvatureMeasures.html}{\textsc{DGtal}}.
 

### 2025-04-24 DGMM2025/paper.tex
Working on 4

@@
     \newcommand{\Kernel}[1]{\ensuremath{w_{\sigma}(#1)}}
-    \paragraph*{Saliency-aware normal estimator.}
+    \paragraph{Saliency-aware normal estimator.}
     We propose a new normal estimator on digital surfaces, which uses
@@
     \end{equation}
-    The \emph{visibility normal} $\vec{n}_p$ of point $p$ is defined
+    The \emph{visibility normal} $\vec{n}(p)$ of point $p$ at scale $\sigma$ is defined
     as the first eigenvector of the covariance matrix $\mathcal{V}_p$
@@
         \end{tabular}
-        \caption{Examples of normals computed on a chinese dragon as a color map. First set displays II normals, second set uses the visibility
-        algorithm to compute them. The normals are colored according to their orientation as $0.5 \cdot (n_i + \mathbbm{1})$
-            . The right images are the smooth version of the left images}
+        \caption{Examples of normals computed on a chinese dragon as a
+          color map. First set displays II normals, second set uses
+          the visibility algorithm to compute them. The normals are
+          colored according to their orientation as $0.5 \cdot (n_i +
+          \mathbbm{1})$. The right images are the smooth version of
+          the left images}
         \label{fig:normals-estimation}
@@
 
-    Then, to compute the curvatures, we use the Corrected Normal Current
-    estimator~\cite{lachaud:2022-dcg} which are based on the normals computed
-    above.
-
-    \paragraph*{Application to curvature estimation.}
+    %% Then, to compute the curvatures, we use the Corrected Normal Current
+    %% estimator~\cite{lachaud:2022-dcg} which are based on the normals computed
+    %% above.
+
+    \paragraph{Application to curvature estimation.}
     In order to illustrate better that the visibility normals better

### 2025-04-24 DGMM2025/paper.tex
refs

@@
 
+    Figure~\ref{fig:visibility-2d} shows what is considered visible or not.
 We note that one particular aspect of this visibility definition is that all visible points from a given point taken as a separate complex are not necessarily 26-connected~\ref{fig:visibility-2d-not-connected}.
@@
 All coordinates are doubled, so that the represented cell $\forall c \in \R^d$ will have a dimension equal to $\sum_{i=1}^d \left(c[i]\mod d\right)$.
-Note that all examples are in 2-d while the shown algorithm is in n-d.
+    In figure~\ref{fig:lattice-representation}, we display a representation of lattice maps applied to a 2-d cell complex where all coordinates are already doubled.
+Note that the examples are in 2-d, the shown results are in 3-d and the algorithm is for n-d.
 
@@
 The found possible visibilities are shown on the original figure}
-        \label{fig:enter-label}
+        \label{fig:visibility-algorithm-evolution}
     \end{figure}
@@
     of the cell complex. In order to do so, for each shift in $\Omega$, we compute the positions where points are
-    visible using the same method as presented in~\ref{fig:enter-label}.
+    visible using the same method as presented in~\ref{fig:visibility-algorithm-evolution}.
 
@@
     estimators. We exploit the \emph{Corrected Normal Current (CNC)
-    estimator}, whose theory is detailed in \cite{lachaud:2022-dcg}
+    estimator}, whose theory is detailed in~\cite{lachaud:2022-dcg}
     and which can estimate all kinds of curvatures given positions and
     normals. It produces state-of-the-art curvature estimates on
-    polygonal surfaces \cite{lachaud:2020-cgf}, point clouds
-    \cite{lachaud:2023-cgf}, and even outperforms Integral Invariant
-    curvature estimates \cite{coeurjolly:2014-cviu} on digital
-    surfaces \cite{lachaud:2022-dcg}. Its implementation is also
+    polygonal surfaces~\cite{lachaud:2020-cgf}, point clouds~\cite{lachaud:2023-cgf}, and even outperforms Integral Invariant
+    curvature estimates~\cite{coeurjolly:2014-cviu} on digital
+    surfaces~\cite{lachaud:2022-dcg}. Its implementation is also
     available in    \href{https://dgtal-team.github.io/doc-nightly/moduleCurvatureMeasures.html}{\textsc{DGtal}}.

### 2025-04-24 DGMM2025/paper.tex
refs
added octaflower images and kernel specifications for normals

@@
 \usepackage[dvipsnames]{xcolor}
+\usepackage[utf8]{inputenc}
 \pgfplotsset{compat=1.18}
@@
     of the cell complex. In order to do so, for each shift in $\Omega$, we compute the positions where points are
-    visible using the same method as presented in~\ref{fig:visibility-algorithm-evolution}.
+    visible using the same method as presented in~\ref{fig:visibility-algorithm-evolution}. Some results of visible
+    points are present in figure~\ref{fig:visibility-results}.
 
@@
         the other side of the torus' branch.}
-        \label{fig:visibility-examples}
+        \label{fig:visibility-results}
     \end{figure}
@@
     \newcommand{\Kernel}[1]{\ensuremath{w_{\sigma}(#1)}}
+
     \paragraph{Saliency-aware normal estimator.}
@@
         \centering
-        \begin{tabular}{|c||c|c|}
+        \begin{tabular}{|c||c|c||c|c|}
             \hline
@@
             \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
-            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} \\
+            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} &
+            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-II} &
+            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-II} \\
             \hline
@@
             \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
-            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} \\
+            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} &
+            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-NV} &
+            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-NV} \\
             \hline
         \end{tabular}
-        \caption{Examples of normals computed on a chinese dragon as a
-          color map. First set displays II normals, second set uses
-          the visibility algorithm to compute them. The normals are
-          colored according to their orientation as $0.5 \cdot (n_i +
-          \mathbbm{1})$. The right images are the smooth version of
-          the left images}
+        \caption{Examples of normals computed on a chinese dragon, then on an
+        octaflower as a color map. First set displays II normals, second set
+        uses the visibility algorithm to compute them. The normals are colored
+        according to their orientation as $0.5 \cdot (n_i + \mathbbm{1})$. The
+        right images are the smooth version of the left images. ``Integral
+        Invariant normals'' are computed using a radius of $r=3$, while
+        our normal estimator are computed using a deviation of $\sigma=3$, and so
+        a radius of $r=2\sigma=6$}
         \label{fig:normals-estimation}
@@
           parameterized by an input normal estimator: first column by
-          ``Integral Invariant normals'' (radius $r=6$, second column
+          ``Integral Invariant normals'' (radius $r=6$), second column
           by ``Convolved Trivial normals'' (radius $k=6$), third

### 2025-04-24 DGMM2025/paper.tex
fix overflow

@@
         \centering
-        \begin{tabular}{|c||c|c||c|c|}
+        \begin{tabular}{|c||c|c|}
             \hline
@@
             \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
-            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} &
+            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} \\
+            \hline
+            Visibility normals &
+            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
+            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} \\
+            \hline
+            II normals &
             \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-II} &
@@
             Visibility normals &
-            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
-            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} &
             \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-NV} &

### 2025-04-25 DGMM2025/paper.tex
tabular improvement
Working on 1

@@
 
-    To increase efficiency, several authors have proposed to cast the
+    To increase efficiency, several authors have casted the
     visibility problem into a digital space, generally $\Z^3$ or its
     decomposition into cubical cells. Visibility is simplified as the
-    problem if there is a connected digital straight line joining a
-    pair of cells without occluding cell(s) (e.g.\ Soille~\cite{soille:1994-prl}
-    uses Bresenham line segments). Coeurjolly \emph{et al.}~\cite{coeurjolly:2004-prl}
-    uses a non-symmetric visibility definition and preimage computations
-    to speed up that kind of algorithms. Chica~\cite{chica:2008-spm}
-    uses a half-cell erosion of the complementary space and Bresenham
-    straight lines to decide visibility.
+    question whether there is a connected digital straight line
+    joining a pair of cells without occluding cell(s)
+    (e.g. Soille~\cite{soille:1994-prl} uses Bresenham
+    segments). Coeurjolly \emph{et al.}~\cite{coeurjolly:2004-prl}
+    uses a non-symmetric visibility definition and preimage
+    computations to speed up these
+    algorithms. Chica~\cite{chica:2008-spm} uses a half-cell erosion
+    of the complementary space and Bresenham lines to decide
+    visibility.
 
@@
     based on tangency or discrete line segments have proven to be both
-    sensitive to sharp corners while multigrid convergent along the
+    sensitive to sharp corners and multigrid convergent on the
     boundary of digitized smooth shapes~\cite{feschet:1999-dgci,lachaud:2007-ivc,nguyen:2011-pr}.
@@
     on digital surfaces. Finally, Section 5 concludes and gives some
-    perspectives to this work, notably other usages of this algorithm
-    in the field.
+    perspectives to this work.
+    %% , notably other usages of this algorithm in the field.
 
@@
     direction as the average of the trivial normals to the surfels
-    touching the point $p$. Figure~\ref{fig:normals-estimation} shows an example
+    touching the point $p$.
+
+    \paragraph{Experimental validation.} [TO COMPLETE]
+    Figure~\ref{fig:normals-estimation} shows an example
     of our normals compared to normals computed with the integral invariant (II) estimator~\cite{Lachaud:2017-lnm}.
@@
             \hline
-            II normals &
+            Normals & Cubes & Smooth \\
+            \hline
+            \hline
+            \raisebox{18mm}{II} &
             \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
@@
             \hline
-            Visibility normals &
+            \raisebox{18mm}{Ours} &
             \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
@@
             \hline
-            II normals &
+            \raisebox{18mm}{II} &
             \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-II} &
@@
             \hline
-            Visibility normals &
+            \raisebox{18mm}{Ours} &
             \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-NV} &

### 2025-04-25 DGMM2025/introduction.tex
Working on 1

--- 2025-04-25 DGMM2025/paper.tex
@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.21 of 2022/01/12
-%
-\documentclass[runningheads]{llncs}
-%
-\usepackage[T1]{fontenc}
-% T1 fonts will be used to generate the final print and online PDFs,
-% so please use T1 fonts in your manuscript whenever possible.
-% Other font encondings may result in incorrect characters.
-%
-\usepackage{graphicx}
-\usepackage{hyperref}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following two lines
-% to display URLs in blue roman font according to Springer's eBook style:
-\usepackage{color}
-\renewcommand\UrlFont{\color{blue}\rmfamily}
-\urlstyle{rm}
-
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{tikz}
-\usepackage{wrapfig}
-\usepackage{environ}
-\usepackage{bbm}
-
-\usepackage{changes}
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-\usepackage{varwidth}
-\usepackage{mathtools}
-\usepackage{pgfplots}
-\usepackage[dvipsnames]{xcolor}
-\usepackage[utf8]{inputenc}
-\pgfplotsset{compat=1.18}
-\usetikzlibrary {spy,arrows.meta,decorations.shapes}
-\setauthormarkup{}
-\definechangesauthor[name=jo, color=blue]{JO}
-\definechangesauthor[name=rom, color=teal]{ROM}
-
-\input{./macros}
-
-%
-\begin{document}
-%
-    \title{Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation}
-%
-    \titlerunning{Fast and exact visibility on digitized shapes}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-    \author{Romain Negro\inst{1}\orcidID{0000-XXXX-YYYY-ZZZZ} \and
-    Jacques-Olivier Lachaud\inst{1}\orcidID{0000-0003-4236-2133}}
-%
-    \authorrunning{R. Negro and J.-O. Lachaud}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-    \institute{Universit\'e Savoie Mont Blanc, CNRS, LAMA, F-73000 Chambéry, France\\
-    \email{\{romain.negro|jacques-olivier.lachaud\}@univ-smb.fr}}
-%
-    \maketitle              % typeset the header of the contribution
-%
-    \begin{abstract}
-        Computing visibility on a geometric object requires heavy
-        computations since it requires to identify pairs of points that
-        are visible to each other, i.e.\ there is a straight segment
-        joining them that stays in the close vicinity of the object
-        boundary. We propose to exploit a specific representation of
-        digital sets based on lists of integral intervals in order to
-        compute efficiently the complete visibility graph between
-        lattice points of the digital shape. As a quite direct
-        application, we show then how we can use visibility to estimate
-        the normal vector field of a digital shape in an accurate and
-        convergent manner while staying aware of the salient and sharp features of
-        the shape.
-
-        \keywords{Visibility \and Geometric inference \and Digital normal estimation \and Digital geometry}
-    \end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-    \section{Introduction}
-
     Visibility is a fundamental concept in computational geometry and
@@
 %    }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-    \section{Visibility through tangency of chords}
-
-    Let $\Z^d$ be the d-dimensional digital space, $d$ > 0.
-    Let $\mathcal{C}^d$ be the (cubical) cell complex induced by the lattice $\Z^d$ : its 0-cells are the points of $\Z^d$, its 1-cells are the open unit segments joining two 0-cells at distance 1, its 2-cells are the open unit squares, etc., and its d-cells are the d-dimensional open unit hypercubes with vertices in $\Z^d$.
-    We denote $\mathcal{C}^d_k$ the set of its k-cells.
-    In the following, a cell will always designate an element of $\mathcal{C}^d$, and the term subcomplex always designates a subset of $\mathcal{C}^d$.
-
-    A cell $\sigma$ is a face of another cell $\tau$ whenever $\sigma$ is a subset of the topological closure $\bar{\tau}$ of $\tau$, written $\sigma \preccurlyeq \tau$.
-    Given any subcomplex K of $\mathcal{C}^d$, the star $Star(K)$ of K is $\{\tau \in \mathcal{C}^d, s.t.\ \exists\sigma \in K,\sigma \preccurlyeq \tau\}$
-
-    \begin{definition}
-        Two points \( p \) and \( q \) on \( K \) are visible if and only if the segment \([p, q]\) is included in \(\text{Star}(K)\), i.e., \( [p, q] \subseteq \text{Star}(K)\)
-    \end{definition}
-
-    % Examples of visibility in 2D
-    \begin{figure}
-        \centering
-        \begin{tabular}{cc|cc}
-            \begin{tikzpicture}
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.75,2.75);
-                \draw[dashed] (0,0) -- (2,1);
-                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p1};
-                \filldraw[black] (2,1) circle (0.05) node[anchor=north] {q1};
-                \draw [thick] (0,0) -- (0.5,0) -- (1,0) -- (1,0.5) -- (1.5,0.5) -- (1.5,1) -- (2,1);
-                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,0.5) -- (0.5,0.5) -- (0.5,1) -- (1,1) -- (1,1.5) -- (2.5,1.5) -- (2.5,0.5) -- (2,0.5) -- (2,0) -- (1.5,0) -- (1.5,-0.5) -- (-0.5,-0.5);
-            \end{tikzpicture} & & &
-            \begin{tikzpicture}
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.25,3.25);
-                \draw[red,dashed,thick] (0,0) -- (1.5,1);
-                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p2};
-                \filldraw[black] (1.5,1) circle (0.05) node[anchor=north] {q2};
-                \draw [thick] (0,0) -- (0,1) -- (0.5,1) -- (0.5,1.5) -- (1,1.5) -- (1,1) -- (1.5,1);
-                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (0,1.5) -- (0,2) -- (1.5,2) -- (1.5,1.5) -- (2,1.5)  -- (2,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
-            \end{tikzpicture} \\
-            Visible                       & & & Non Visible                   \\\\
-            \hline\\
-            \begin{tikzpicture}
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
-                \draw[red,dashed,thick] (0,0) -- (1,0);
-                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p3};
-                \filldraw[black] (1,0) circle (0.05) node[anchor=north] {q3};
-                \draw [thick] (0,0) -- (0,1) -- (1,1) -- (1,0);
-                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,-0.5) -- (-0.5,-0.5) -- (0.5,-0.5) -- (0.5,0.5);
-            \end{tikzpicture} & & &
-            \begin{tikzpicture}
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
-                \draw[red,dashed,thick] (0,0) -- (1,1);
-                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p4};
-                \filldraw[black] (1,1) circle (0.05) node[anchor=north] {q4};
-                \draw [thick] (0,0) -- (0,1) -- (1,1);
-                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
-            \end{tikzpicture}\\
-            Non Visible (from a 1-d cell) & & & Non Visible (from a 0-d cell)
-        \end{tabular}
-        \caption{Examples of visibility in 2D.}
-        \label{fig:visibility-2d}
-    \end{figure}
-
-    Figure~\ref{fig:visibility-2d} shows what is considered visible or not.
-We note that one particular aspect of this visibility definition is that all visible points from a given point taken as a separate complex are not necessarily 26-connected~\ref{fig:visibility-2d-not-connected}.
-    Furthermore, we conjecture that they even may not be $n$-connected for $n$ arbitrarily large.
-    This characteristic has implications for the applicability of Algorithm 3 from~\cite{lachaud:2022-jmiv}, as the algorithm assumes that visited points are 26-connected, potentially leading to incomplete collection of visible points.
-
-    % Example of visibility not necessarily connected
-    % Path from p to q : r u r u r r r r r u r
-    \begin{figure}
-        \centering
-        \begin{tikzpicture}
-            \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (5.25,3.25);
-            \draw[thick] (0,0) -- (0.5,0) -- (0.5,0.5) -- (1,0.5) -- (1,1) -- (3.5,1) -- (3.5,1.5);
-            \draw [black, dashed] (0,0) -- (3.5,1.5);
-            \draw [red, dashed] (0,0) -- (3.5,1);
-            \draw [red, dashed] (0,0) -- (3,1);
-            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p};
-            \filldraw[gray] (0.5,0) circle (0.05);
-            \filldraw[gray] (0.5,0.5) circle (0.05);
-            \filldraw[gray] (1,0.5) circle (0.05);
-            \filldraw[gray] (1,1) circle (0.05);
-            \filldraw[gray] (1.5,1) circle (0.05);
-            \filldraw[gray] (2,1) circle (0.05);
-            \filldraw[gray] (2.5,1) circle (0.05);
-            \filldraw[red] (3,1) circle (0.05);
-            \filldraw[red] (3.5,1) circle (0.05);
-            \filldraw[black] (3.5,1.5) circle (0.05) node[anchor=west] {q};
-            \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,0.5) -- (0,0.5) -- (0,1) -- (0.5,1) -- (0.5,1.5) -- (3,1.5) -- (3,2) -- (4,2) -- (4,0.5) -- (1.5,0.5) -- (1.5,0) -- (1,0) -- (1,-0.5) -- (-0.5,-0.5);
-        \end{tikzpicture}
-        \caption{Example of non-connex visibility in 2D, q is visible from p while the visibility points are not 26-connected.}
-        \label{fig:visibility-2d-not-connected}
-    \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-    \section{Fast computation using integer intervals intersections}
-
-    To improve computation time, we will use lattice maps of integer intervals.
-
-    \begin{definition}
-        A sequence of intervals is an ordered list of intervals $L = ([a_i,b_i])_{i=1,\ldots,n}$ such that $b_i + 1 < a_{i+1}$, i.e., disjoint intervals with at least a missing integer.
-    \end{definition}
-
-    \begin{definition}
-        A translation of an interval $A$ is defined as $A+t \coloneqq [a+t, b+t]$
-    \end{definition}
-
-    \begin{definition}
-        A translation of a sequence of intervals $L$ is the sequence defined as $L+t \coloneqq \{L_1+t,\ldots,L_n+t\}$
-    \end{definition}
-
-    \begin{definition}
-        All translations $T$ of an interval or a sequence of intervals $A$ in a sequence of intervals $L$ are defined as $ T \coloneqq \{ t, st. A+t \subset L\}$
-    \end{definition}
-
-    We will consider lattice maps as pairs of (shift, intervals), where shifts are points $p \in \R^{d-1}$.
-All coordinates are doubled, so that the represented cell $\forall c \in \R^d$ will have a dimension equal to $\sum_{i=1}^d \left(c[i]\mod d\right)$.
-    In figure~\ref{fig:lattice-representation}, we display a representation of lattice maps applied to a 2-d cell complex where all coordinates are already doubled.
-Note that the examples are in 2-d, the shown results are in 3-d and the algorithm is for n-d.
-
-    \begin{figure}
-        \centering
-        \label{fig:lattice-representation}
-        % \usetikzlibrary {arrows.meta,decorations.shapes}
-        \begin{tabular}{c c}
-            \begin{tikzpicture}[scale=0.75]
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.25,-0.25) grid (7.25,7.25);
-                \filldraw[black] (1,4) circle (0.05);
-                \filldraw[black] (1,5) circle (0.05);
-                \filldraw[black] (2,5) circle (0.05);
-                \filldraw[black] (3,5) circle (0.05);
-                \filldraw[black] (3,4) circle (0.05);
-                \filldraw[black] (3,3) circle (0.05);
-                \filldraw[black] (3,2) circle (0.05);
-                \filldraw[black] (2,2) circle (0.05);
-                \filldraw[black] (2,1) circle (0.05);
-                \filldraw[black] (1,1) circle (0.05);
-                \filldraw[black] (1,0) circle (0.05);
-                \filldraw[black] (2,0) circle (0.05);
-                \filldraw[black] (3,0) circle (0.05);
-                \filldraw[black] (3,1) circle (0.05);
-                \filldraw[black] (4,1) circle (0.05);
-                \filldraw[black] (5,1) circle (0.05);
-                \draw[-{Stealth[length=3mm]}=black] (-1,-1) -- (-1,6.5);
-                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=21.5pt}] {(-1,-1) -- (-1,7)};
-                \draw[black] (1,4) -- (1,5) -- (3,5) -- (3,2) -- (2,2) -- (2,1) -- (1,1) -- (1,0) -- (3,0) -- (3,1) -- (5,1);
-                \draw[thick,dashed] (1,3) -- (1,2) -- (0,2) -- (0,-1) -- (4,-1) -- (4,0) -- (6,0) -- (6,2) -- (4,2) -- (4,6) -- (0,6) -- (0,3) -- (2,3) -- (2,4);
-            \end{tikzpicture} &
-            %      \begin{tikzpicture}
-            %     \foreach \y in {1,1.5,...,6} {
-            %       \draw[thin, lightgray,xshift=-1cm,yshift=-1cm] (0.75,\y) -- (6.25,\y);
-            %     }
-            %     \draw[-{Stealth[length=3mm]}=black] (0,0) -- (0,5.5);
-            %     \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=10mm}] {(0,0) -- (0,5)};
-            %     \draw[black] (1,4) -- (1,5) -- (3,5) -- (3,2) -- (2,2) -- (2,1) -- (1,1) -- (1,0) -- (3,0) -- (3,1) -- (5,1);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,5)--(3.1,5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,4.5)--(1.1,4.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,4.5)--(3.1,4.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,4)--(1.1,4);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,4)--(3.1,4);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,3.5)--(3.1,3.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,3)--(3.1,3);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,2.5)--(3.1,2.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.9,2)--(3.1,2);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.9,1.5)--(2.1,1.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,1)--(2.1,1);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,1)--(5.1,1);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,0.5)--(1.1,0.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,0.5)--(3.1,0.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,0)--(3.1,0);
-            %     \filldraw[white,yshift=-1cm] (0,0) circle (0.01); % readjust the height to match the original path
-            % \end{tikzpicture} &
-            \begin{tikzpicture}[scale=0.75]
-                \foreach \y in {0,0.5,...,7} {
-                    \draw[thin, lightgray,xshift=-1cm,yshift=-1cm] (-0.25,\y) -- (7.25,\y);
-                }
-                \draw[-{Stealth[length=3mm]}=black] (-1,-1) -- (-1,6.5);
-                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=21.5pt}] {(-1,-1) -- (-1,6.5)};
-                \draw[thick,dashed] (1,3) -- (1,2) -- (0,2) -- (0,-1) -- (4,-1) -- (4,0) -- (6,0) -- (6,2) -- (4,2) -- (4,6) -- (0,6) -- (0,3) -- (2,3) -- (2,4);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,5.5)--(3.6,5.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,5)--(3.6,5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,4.5)--(3.6,4.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,4)--(1.6,4);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,4)--(3.6,4);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,3.5)--(1.6,3.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,3.5)--(3.6,3.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,3)--(3.6,3);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2.5)--(3.6,2.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2)--(3.6,2);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,1.5)--(5.6,1.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,1)--(5.6,1);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,0.5)--(5.6,0.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,0)--(3.6,0);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,-0.5)--(3.6,-0.5);
-                \filldraw[white,yshift=-1.25cm] (0,0) circle (0.01); % readjust the height to match the original path
-            \end{tikzpicture}
-        \end{tabular}
-        \caption{Representation of a 2d cell complex (here the star of a given curve) as a lattice map. From 31 cells from the star on the left, we get 15 intervals on the right}
-    \end{figure}
-
-    \colorlet{MyGreen}{green!80!gray}
-    \begin{figure}
-        \centering
-        \begin{tabular}{c c}
-            \begin{tikzpicture}[scale=0.75]
-                \foreach[count=\i] \y in {-0.5,0,...,1.5} {
-                    \draw (0,0) node at (-1.25,\y) {\i};
-                }
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.75,-0.25) grid (12.25,3.25);
-                \draw[-{Stealth[length=3mm]}=black] (-1.5,-1) -- (-1.5,2.5);
-                \filldraw[black] (0,0) circle (0.05);
-                \filldraw[black] (1,0) circle (0.05);
-                \filldraw[black] (2,0) circle (0.05);
-                \filldraw[black] (2,1) circle (0.05);
-                \filldraw[black] (3,1) circle (0.05);
-                \filldraw[black] (4,1) circle (0.05);
-                \filldraw[black] (5,1) circle (0.05);
-                \filldraw[black] (5,0) circle (0.05);
-                \filldraw[black] (6,0) circle (0.05);
-                \filldraw[black] (7,0) circle (0.05);
-                \filldraw[black] (7,1) circle (0.05);
-                \filldraw[black] (8,1) circle (0.05);
-                \filldraw[black] (8,0) circle (0.05);
-                \filldraw[black] (9,0) circle (0.05);
-                \filldraw[black] (10,0) circle (0.05);
-                \filldraw[black] (10,1) circle (0.05);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,-0.5)--(2.6,-0.5);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,-0.5)--(10.6,-0.5);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0)--(2.6,0);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,0)--(10.6,0);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(10.6,0.5);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1)--(5.6,1);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1)--(8.6,1);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1)--(10.6,1);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(5.6,1.5);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1.5)--(8.6,1.5);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1.5)--(10.6,1.5);
-                \draw[thick, black] (0,0) -- (2,0) -- (2,1) -- (5,1) -- (5,0) -- (7,0) -- (7,1) -- (8,1) -- (8,0) -- (10,0) -- (10,1);
-                \draw[thick,dashed] (6,1) -- (6,2);
-                \draw[thick,dashed] (9,1) -- (9,2);
-                \draw[thick,dashed] (-1,-1) -- (-1,1) -- (1,1) -- (1,2) -- (11,2) -- (11,-1) -- (4,-1) -- (4,0) -- (3,0) -- (3,-1) -- (-1,-1);
-
-                \draw (0,0) node at (-0.25,1.75) {F};
-
-                \draw[red,arrows = {-Stealth[]}] (0,0)--(2,1);
-                \draw[red,arrows = {-Stealth[]}] (1,0)--(3,1);
-                \draw[red,arrows = {-Stealth[]}] (2,0)--(4,1);
-                \draw[red,arrows = {-Stealth[]}] (5,0)--(7,1);
-                \draw[red,arrows = {-Stealth[]}] (6,0)--(8,1);
-                \draw[red,arrows = {-Stealth[]}] (8,0)--(10,1);
-
-            \end{tikzpicture} &
-            \begin{tikzpicture}[scale=0.75]
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.75,-0.25) grid (4.25,3.25);
-                \draw[-{Stealth[length=3mm]}=black] (-1.5,-1) -- (-1.5,2.5);
-                \foreach[count=\i] \y in {-0.5,0,...,1.5} {
-                    \draw (0,0) node at (-1.25,\y) {\i};
-                }
-                \filldraw[black] (0,0) circle (0.05);
-                \filldraw[black] (2,1) circle (0.05);
-                \draw[thick, black] (0,0) -- (2,1);
-                \draw[thick,dashed] (-1,-1) -- (-1,1) -- (1,1) -- (1,2) -- (3,2) -- (3,0) -- (1,0) --  (1,-1) -- (-1,-1);
-                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,-0.5)--(0.6,-0.5);
-                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0)--(0.6,0);
-                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(2.6,0.5);
-                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1)--(2.6,1);
-                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(2.6,1.5);
-
-                \draw (0,0) node at (-0.25,1.75) {V};
-            \end{tikzpicture} \\
-            \hline
-            \multicolumn{2}{c}{
-                \begin{tikzpicture}[scale=0.75]
-                    \foreach \y in {0,0.5,...,12.5} {
-                        \draw[thin, lightgray] (-1.25,\y) -- (11.25,\y);
-                    }
-                    \foreach \y in {0,2.5,...,12.5} {
-                        \draw[blue] (-7,\y) -- (11.25,\y);
-                    }
-
-                    \foreach[count=\i] \y in {12,9.5,...,2} {
-                        \draw (0,0) node at (-4,\y) {$V_{\i}$};
-                    }
-                    \foreach[count=\i] \y in {11.5,9,...,1.5} {
-                        \draw (0,0) node at (-4,\y) {$F_{\i}$};
-                    }
-                    \draw (0,0) node at (-4,11) {$T_{1} = \text{Translations}(V_{1},F_{1})$};
-                    \foreach[count=\i] \y in {8.5,6,...,1} {
-                        \draw (0,0) node at (-4,\y) {$T_{\the\numexpr\i+1\relax}$};
-                    }
-                    \draw (0,0) node at (-4,10.5) {$R_1 = T_1$};
-
-                    \foreach[count=\i] \y in {8,5.5,...,0.5} {
-
-                        \draw (0,0) node at (-4,\y) {$R_{\the\numexpr\i+1\relax} = T_{\the\numexpr\i+1\relax} \cap R_{\i}$};
-                    }
-
-                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,12)--(0.6,12);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,11.5)--(2.6,11.5);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,11.5)--(10.6,11.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,11)--(1.6,11);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,11)--(9.6,11);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,10.5)--(1.6,10.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,10.5)--(9.6,10.5);
-                    \filldraw[black] (-0.5,10.5) circle (0.05);
-                    \filldraw[black] (0.5,10.5) circle (0.05);
-                    \filldraw[black] (1.5,10.5) circle (0.05);
-                    \filldraw[black] (4.5,10.5) circle (0.05);
-                    \filldraw[black] (5.5,10.5) circle (0.05);
-                    \filldraw[black] (6.5,10.5) circle (0.05);
-                    \filldraw[black] (7.5,10.5) circle (0.05);
-                    \filldraw[black] (8.5,10.5) circle (0.05);
-                    \filldraw[black] (9.5,10.5) circle (0.05);
-
-                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9.5)--(0.6,9.5);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9)--(2.6,9);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,9)--(10.6,9);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,8.5)--(1.6,8.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,8.5)--(9.6,8.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,8)--(1.6,8);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,8)--(9.6,8);
-                    \filldraw[black] (-0.5,8) circle (0.05);
-                    \filldraw[black] (0.5,8) circle (0.05);
-                    \filldraw[black] (1.5,8) circle (0.05);
-                    \filldraw[black] (4.5,8) circle (0.05);
-                    \filldraw[black] (5.5,8) circle (0.05);
-                    \filldraw[black] (6.5,8) circle (0.05);
-                    \filldraw[black] (7.5,8) circle (0.05);
-                    \filldraw[black] (8.5,8) circle (0.05);
-                    \filldraw[black] (9.5,8) circle (0.05);
-
-                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,7)--(2.6,7);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,6.5)--(10.6,6.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,6)--(7.6,6);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,5.5)--(1.6,5.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,5.5)--(7.6,5.5);
-                    \filldraw[black] (-0.5,5.5) circle (0.05);
-                    \filldraw[black] (0.5,5.5) circle (0.05);
-                    \filldraw[black] (1.5,5.5) circle (0.05);
-                    \filldraw[black] (4.5,5.5) circle (0.05);
-                    \filldraw[black] (5.5,5.5) circle (0.05);
-                    \filldraw[black] (6.5,5.5) circle (0.05);
-                    \filldraw[black] (7.5,5.5) circle (0.05);
-
-                    \draw[thick,black,arrows = {-Stealth[]}] (-0.6,4.5)--(1.4,4.5);
-                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,4.5)--(2.6,4.5);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,4)--(5.6,4);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,4)--(8.6,4);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,4)--(10.6,4);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,3.5)--(2.6,3.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,3.5)--(5.6,3.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,3.5)--(7.6,3.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,3)--(1.6,3);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,3)--(5.6,3);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,3)--(7.6,3);
-                    \filldraw[black] (-0.5,3) circle (0.05);
-                    \filldraw[black] (0.5,3) circle (0.05);
-                    \filldraw[black] (1.5,3) circle (0.05);
-                    \filldraw[black] (4.5,3) circle (0.05);
-                    \filldraw[black] (5.5,3) circle (0.05);
-                    \filldraw[black] (7.5,3) circle (0.05);
-
-                    \draw[thick,black,arrows = {-Stealth[]}] (-0.6,2)--(1.4,2);
-                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2)--(2.6,2);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(5.6,1.5);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1.5)--(8.6,1.5);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1.5)--(10.6,1.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,1)--(2.6,1);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,1)--(5.6,1);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,1)--(7.6,1);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(1.6,0.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,0.5)--(5.6,0.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,0.5)--(7.6,0.5);
-                    \filldraw[black] (-0.5,0.5) circle (0.05);
-                    \filldraw[black] (0.5,0.5) circle (0.05);
-                    \filldraw[black] (1.5,0.5) circle (0.05);
-                    \filldraw[black] (4.5,0.5) circle (0.05);
-                    \filldraw[black] (5.5,0.5) circle (0.05);
-                    \filldraw[black] (7.5,0.5) circle (0.05);
-
-                \end{tikzpicture}}
-        \end{tabular}
-        \caption{Evolution of the visibility check algorithm for a 2,1 vector.
-Green is the vector lattice map, black is the figure lattice map, red are the current intervals of positions where the visibility is still possible.
-The last red intervals are the visible positions.
-We travel the lattice maps from bottom-up.
-The found possible visibilities are shown on the original figure}
-        \label{fig:visibility-algorithm-evolution}
-    \end{figure}
-
-    \begin{algorithm}
-        \caption{Given a cell complex C and a radius $r$, compute the visibility at every point of C up to distance $r$.
-We assume z being the main axis of the lattice maps, x and y being the auxiliary axises}
-        \label{alg:visibility}
-        \begin{algorithmic}
-            \Function{Visibility}{C: Cell complex, r: Integer}
-                \State $\Omega \gets \Call{Star}{C}$ \Comment{Lattice map of the star of the studied cell complex}
-                \State $Directions \gets \Call{GetAllPrimalDirections}{r}$
-                \State $V: \text{vector of boolean} \gets [0, \ldots, 0]$ \Comment{length $Size(Directions) \times \#C.pointels$}
-                \State $low, high \gets \Call{BoundingBoxZ}{\Omega}$
-                \ForAll{$d$ in $Directions$}
-                    \ForAll{shift $S$ in $\Omega$}
-                        \State $R \gets [low, high]$
-                        \ForAll{pair $P$ in $\Call{Star}{\text{d}}$}
-                            \State $R \gets R \cap \Call{Translations}{P.intervals,\Omega[S + P.shift]}$
-                        \EndFor
-                        \State \Call{UpdateVisibility}{$V$, $R$}
-                    \EndFor
-                \EndFor
-                \State \Return $V$
-            \EndFunction
-        \end{algorithmic}
-    \end{algorithm}
-
-    In order to compute the visibility, we first compute $\Omega = \text{Star}(C)$. Then for each primal direction of
-    coordinates at most $r$, we look at all the possible positions this specific direction does link 2 visible points
-    of the cell complex. In order to do so, for each shift in $\Omega$, we compute the positions where points are
-    visible using the same method as presented in~\ref{fig:visibility-algorithm-evolution}. Some results of visible
-    points are present in figure~\ref{fig:visibility-results}.
-
-    \begin{algorithm}
-        \caption{Given 2 lists of intervals $K$ and $L$, find $K \cap L$, the intersection of those 2 lists}
-        \label{alg:intersection}
-        \begin{algorithmic}
-            \Function{Intersection ($\cap$)}{\text{K, L}: Intervals}
-                \State $R \gets \emptyset$; $k, l \gets 0$
-                \While{$k < K.nbIntervals \And l < L.nbIntervals$}
-                    \State $[a,b] \gets K[k]$; $[c,d] \gets L[l]$
-                    \State $e \gets \max(a, c)$; $f \gets \min(b, d)$
-                    \If{$e \leq f$}
-                        \State $R.append([e, f])$
-                    \EndIf
-                    \If{$b \leq d$}
-                        \State $k \gets k+1$
-                    \EndIf
-                    \If{$d \leq b$}
-                        \State $l \gets l+1$
-                    \EndIf
-                \EndWhile
-                \State \Return $R$
-            \EndFunction
-        \end{algorithmic}
-    \end{algorithm}
-
-    To efficiently compute the intersection of 2 lists of intervals $K$ and $L$, we go through the first 2 unvisited
-    elements of the 2 lists. If they don't overlap (i.e. the start and end of the 1st interval are both smaller than
-    the start of the other), then we can discard the smaller interval. Else, we construct the intersection of these
-    2 intervals as one of the resulting intervals. We then can skip the interval with the smallest end. If both
-    intervals have the same end, then both intervals can be skipped. Doing this computation until one of the lists
-    is empty returns the intersection of both lists of intervals.
-
-    % Insert visibility results images
-
-    \begin{figure}
-        \centering
-        \begin{tabular}{c c}
-            \includegraphics[width=0.4\textwidth]{pictures/visibility_from_given_point_r_10} &
-            \includegraphics[width=0.4\textwidth]{pictures/visibility_aware_of_features}
-        \end{tabular}
-        \caption{Examples of visibility on a fandisk and a torus knot. First one is on the edge
-        of a fandisk, where the visibility stops at the edges. The other one is in the interior
-        of a torus knot, where we can see that the visibility is feature-aware and doesn't see
-        the other side of the torus' branch.}
-        \label{fig:visibility-results}
-    \end{figure}
-%
-%    \begin{figure}
-%        \begin{center}
-%            \includegraphics[width=0.8\textwidth]{pictures/visibility_from_given_point_r_10}
-%            \caption{Visibility of a point on an edge of a fandisk}
-%            \label{fig:visibility-fandisk}
-%        \end{center}
-%    \end{figure}
-%    \begin{figure}
-%        \begin{center}
-%            \includegraphics[width=0.8\textwidth]{pictures/visibility_aware_of_features}
-%            \caption{Visibility of a point on a torus knot (the visibility is feature-aware)}
-%            \label{fig:visibility-torus-knot}
-%        \end{center}
-%    \end{figure}
-
-    % Quantitative results
-
-    \begin{figure}
-        \begin{tikzpicture}
-            \centering
-            \begin{axis}[
-                width=0.8\textwidth,
-                legend columns=3,
-                xlabel={Gridstep},
-                ylabel={Mean distance},
-                x dir=reverse,
-                legend pos=north west,
-                ymajorgrids=true,
-                grid style=dashed,
-                ymax=50,
-                ymode=log,
-                xmode=log,
-                log ticks with fixed point,
-            ]
-
-                \addplot[
-                    color=cyan,
-                ] coordinates {
-                    (0.25,3.97418)(0.375,3.00921)(0.5,2.85702)(0.625,2.34448)(0.75,1.85023)(0.875,2.16868)(1.0,1.85023)
-                };
-                \addlegendentry{sphere1}
-                \addplot[
-                    color=red,
-                ] coordinates {
-                    (1,8.90781)(0.875,10.2845)(0.75,11.3734)(0.625,12.5062)(0.5,14.0867)(0.375,16.6192)(0.25,19.6747)
-                };
-                \addlegendentry{goursat}
-                \addplot[
-                    color=violet,
-                ] coordinates {
-                    (0.25,12.3975)(0.375,9.41303)(0.5,8.69558)(0.625,7.37667)(0.75,6.82131)(0.875,6.05735)(1,6.33877)
-                };
-                \addlegendentry{torus}
-                \addplot[
-                    color=MyGreen,
-                ] coordinates {
-                    (0.25,10.8007)(0.375,8.69514)(0.5,7.26074)(0.625,6.2309)(0.75,5.6897)(0.875,5.28197)(1,4.96098)
-                };
-                \addlegendentry{leopold}
-                \addplot[
-                    color=yellow!80!black,
-                ] coordinates {
-                    (0.25,18.2339)(0.375,14.6475)(0.5,12.3618)(0.625,9.55647)(0.75,9.83208)(0.875,7.51861)(1,7.99732)
-                };
-                \addlegendentry{rcube}
-                \addplot [
-                    color=black,
-                    thick,
-                    domain=0.25:1,
-                    samples=100,
-                ] {x^(-0.5)};
-                \addlegendentry{$\sqrt{h}=\sqrt{\frac{1}{x}}$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Mean Visibility Distance as a Function of Grid Resolution}
-        \label{fig:meanvisibility-gridstep}
-    \end{figure}
-    \begin{figure}
-        \begin{tikzpicture}
-            \centering
-            \begin{axis}[
-                width=0.8\textwidth,
-                xlabel={\#Pointels},
-                ylabel={Computation Time (ms)},
-                legend pos=north west,
-                ymajorgrids=true,
-                grid style=dashed,
-                ymode=log,
-                xmode=log,
-                log ticks with fixed point,
-            ]
-                \addplot[
-                    red,
-                    only marks,
-                    mark=halfcircle,
-                    mark options={solid}
-                ] table[row sep=crcr] {
-                    10624 2246.69\\
-                    4968 793.426\\
-                    2584 328.535\\
-                    1840 190.401\\
-                    1176 93.2502\\
-                    912 78.7981\\
-                    624 56.3769\\
-                    28568 10193.5\\
-                    12632 4004.92\\
-                    7088 2010.63\\
-                    4664 1188.73\\
-                    3080 755.754\\
-                    2408 545.347\\
-                    1736 366.541\\
-                    24320 11169.1\\
-                    10760 4720.44\\
-                    6056 2397.79\\
-                    3944 1380.38\\
-                    2648 874.979\\
-                    2000 580.0\\
-                    1520 415.373\\
-                    8336 3196.55\\
-                    3720 1268.46\\
-                    2104 639.305\\
-                    1336 342.873\\
-                    928 177.54\\
-                    680 112.142\\
-                    520 87.0747\\
-                    37592 12335.6\\
-                    16712 5582.38\\
-                    9512 2976.21\\
-                    6056 1731.32\\
-                    4088 990.78\\
-                    3032 788.507\\
-                    2456 548.66\\
-                    97844 49226.3\\
-                    390235 181322\\
-                };
-                \addlegendentry{radius 10};
-                \addplot[
-                    MyGreen,
-                    only marks,
-                    mark=halfcircle,
-                    mark options={solid}
-                ] table[row sep=crcr] {
-                    10624 9522.43\\
-                    4968 2876.81\\
-                    2584 1152.25\\
-                    1840 635.332\\
-                    1176 347.973\\
-                    912 304.801\\
-                    624 250.126\\
-                    28568 70137.9\\
-                    12632 26063.0\\
-                    7088 11985.8\\
-                    4664 6239.51\\
-                    3080 3468.31\\
-                    2408 2059.84\\
-                    1736 1254.2\\
-                    24320 86616.9\\
-                    10760 26605.7\\
-                    6056 11813.5\\
-                    3944 6516.92\\
-                    2648 3564.03\\
-                    2000 1949.32\\
-                    1520 1244.89\\
-                    8336 18125.5\\
-                    3720 5157.11\\
-                    2104 2029.09\\
-                    1336 896.186\\
-                    928 446.136\\
-                    680 306.651\\
-                    520 259.078\\
-                    37592 76316.3\\
-                    16712 27747.3\\
-                    9512 13608.6\\
-                    6056 7140.03\\
-                    4088 3704.52\\
-                    3032 2624.2\\
-                    2456 1422.6\\
-                    97844 378906\\
-                    390235 1747780\\
-                };
-                \addlegendentry{radius 20};
-                \addplot[
-                    blue,
-                    only marks,
-                    mark=halfcircle,
-                    mark options={solid}
-                ] table[row sep=crcr] {
-                    10624 18283.5\\
-                    4968 4957.93\\
-                    2584 2133.36\\
-                    1840 1292.53\\
-                    1176 922.51\\
-                    912 863.731\\
-                    624 813.638\\
-                    28568 188784.0\\
-                    12632 62237.1\\
-                    7088 24874.9\\
-                    4664 9043.39\\
-                    3080 4407.09\\
-                    2408 2641.04\\
-                    1736 1820.31\\
-                    24320 227432.0\\
-                    10760 69706.8\\
-                    6056 25408.9\\
-                    3944 10094.7\\
-                    2648 5269.56\\
-                    2000 2948.16\\
-                    1520 2082.02\\
-                    8336 45045.4\\
-                    3720 8638.42\\
-                    2104 3238.48\\
-                    1336 1731.9\\
-                    928 1122.69\\
-                    680 928.084\\
-                    520 890.592\\
-                    37592 257981.0\\
-                    16712 84729.7\\
-                    9512 36298.8\\
-                    6056 15640.2\\
-                    4088 6662.17\\
-                    3032 4431.71\\
-                    2456 2621.98\\
-                    97844 1157400\\
-                    390235 10493200\\
-                };
-                \addlegendentry{radius 30};
-                \addplot [
-                    color=black,
-                    thick,
-                    domain=500:60000,
-                    samples=100,
-                ] {0.01*x^(1.5)};
-                \addlegendentry{$0.01\times x\sqrt{x}$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Computation Time of Visibility as a Function of Grid Resolution}
-        \label{fig:meanvisibility-computationComplexity}
-    \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-    \section{Saliency-aware normal and curvature estimation}
-
-    \newcommand{\Kernel}[1]{\ensuremath{w_{\sigma}(#1)}}
-
-    \paragraph{Saliency-aware normal estimator.}
-    We propose a new normal estimator on digital surfaces, which uses
-    the visibility of the point of interest while taking into account
-    a user-given scale $\sigma$. If $\sigma$ is proportionnal to the
-    average length between visible points (so some
-    $\Theta(\sqrt{h})$), then this estimator is observed to be
-    multigrid convergent along digitization of smooth shapes. However,
-    since the computation window is limited by the visibility, it
-    better approximates the geometry near sharp or salient features.
-
-    More precisely, we choose a Gaussian function
-    $\Kernel{x}\coloneqq e^{-\frac{x^2}{2\sigma^2}}$ as a weight kernel. Let
-    $V_p$ be the set of visible points from the point $p$. Let $c_p$
-    be the weighted centroid of the visible points around $p$,
-    i.e. $c_p \coloneqq \frac{\sum_{q \in V_p} \Kernel{\|q-p\|}q}{\sum_{q \in
-    V_p} \Kernel{\|q-p\|}}$. We form the weighted covariance matrix
-    $\mathcal{V}_p$ of the points $V_p$ as:
-    \begin{equation}
-        \mathcal{V}_p = \sum_{q \in V_p} \Kernel{\|q-p\|}(q - c_p)(q - c_p)^T.
-    \end{equation}
-    The \emph{visibility normal} $\vec{n}(p)$ of point $p$ at scale $\sigma$ is defined
-    as the first eigenvector of the covariance matrix $\mathcal{V}_p$
-    of the visible points, corresponding to its smallest
-    eigenvalue. Its orientation is chosen so as to point in the same
-    direction as the average of the trivial normals to the surfels
-    touching the point $p$.
-
-    \paragraph{Experimental validation.} [TO COMPLETE]
-    Figure~\ref{fig:normals-estimation} shows an example
-    of our normals compared to normals computed with the integral invariant (II) estimator~\cite{Lachaud:2017-lnm}.
-
-    \begin{figure}
-        \centering
-        \begin{tabular}{|c||c|c|}
-            \hline
-            Normals & Cubes & Smooth \\
-            \hline
-            \hline
-            \raisebox{18mm}{II} &
-            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
-            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} \\
-            \hline
-            \raisebox{18mm}{Ours} &
-            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
-            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} \\
-            \hline
-            \raisebox{18mm}{II} &
-            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-II} &
-            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-II} \\
-            \hline
-            \raisebox{18mm}{Ours} &
-            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-NV} &
-            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-NV} \\
-            \hline
-        \end{tabular}
-        \caption{Examples of normals computed on a chinese dragon, then on an
-        octaflower as a color map. First set displays II normals, second set
-        uses the visibility algorithm to compute them. The normals are colored
-        according to their orientation as $0.5 \cdot (n_i + \mathbbm{1})$. The
-        right images are the smooth version of the left images. ``Integral
-        Invariant normals'' are computed using a radius of $r=3$, while
-        our normal estimator are computed using a deviation of $\sigma=3$, and so
-        a radius of $r=2\sigma=6$}
-        \label{fig:normals-estimation}
-    \end{figure}
-
-    %% Then, to compute the curvatures, we use the Corrected Normal Current
-    %% estimator~\cite{lachaud:2022-dcg} which are based on the normals computed
-    %% above.
-
-    \paragraph{Application to curvature estimation.}
-    In order to illustrate better that the visibility normals better
-    take into account the sharp features of a digital surface while
-    staying meaningfull in digitization of smooth parts, we compare
-    the curvature estimates induced by different discrete normal
-    estimators. We exploit the \emph{Corrected Normal Current (CNC)
-        estimator}, whose theory is detailed in~\cite{lachaud:2022-dcg}
-    and which can estimate all kinds of curvatures given positions and
-    normals. It produces state-of-the-art curvature estimates on
-    polygonal surfaces~\cite{lachaud:2020-cgf}, point clouds~\cite{lachaud:2023-cgf}, and even outperforms Integral Invariant
-    curvature estimates~\cite{coeurjolly:2014-cviu} on digital
-    surfaces~\cite{lachaud:2022-dcg}. Its implementation is also
-    available in    \href{https://dgtal-team.github.io/doc-nightly/moduleCurvatureMeasures.html}{\textsc{DGtal}}.
-
-    \RefFigure{fig-curvatures} displays the results of CNC curvature
-    estimations on the digitization of a piecewise smooth shape
-    ``Talking D20'', taken from
-    \href{https://ten-thousand-models.appspot.com/detail.html?file_id=1533028}{Thingi10K}.
-    We compare the differences obtained by just changing the discrete
-    normal estimator (available in the \textsc{DGtal} library):
-    (column II normals) Integral Invariant normals with $r=6$, (column
-    CTriv normals) convolved trivial normals with $r=6$, (column
-    Visibility normals) our proposed estimator (VN) with $\sigma=4$ and
-    maximal visibility distance $2\sigma$. These parameters were
-    chosen so that the respective computation windows of the different
-    estimators are approximately the same.
-
-    II estimator is good along digitization of smooth or flat parts of
-    the dice, but presents curious artefacts near sharp features
-    induced by the hollowed out numbers: this is due to the nature of
-    II normal estimates, which computes a PCA of a ball centered on
-    the point of interest and may include points on the other side of
-    the saliencies.
-
-    CTriv estimator only performs averaging of trivial normal
-    directions along the surface. It behaves much better than II near
-    features (although it tends to smooth curvatures) since it does
-    not use information from across the gap. However some oscillations
-    of the curvatures are distinguishable especially along the flat
-    parts, and some curvature estimates are erroneous on smoother
-    parts (like the edge above 6 for $\kappa_2$ or several dice
-    vertices).
-
-    VN estimator takes the best of the two previous approaches. It
-    remains precise and stable on smooth and flat regions, while
-    perfectly delineating sharp features and holes, whatever the kind
-    of estimated curvatures. Its only drawback is the computation
-    time, which is [TO COMPLETE], compared to $2.3$s for II and $0.1s$
-    for CTriv.
-
-    \newcommand{\MyZoom}[1]{%
-        \begin{tikzpicture}[spy using outlines={circle,magnification=1.8,size=2cm,connect spies}]
-        \node[inner sep=0pt] {\pgfimage[width=0.3\textwidth]{#1}};
-        \spy[overlay,blue] on (0.4,0.2) in node at (-0.8,0.8);
-        \end{tikzpicture}}
-    % \newcommand{\MyZoom}[1]{\includegraphics[width=0.3\textwidth]{#1}}
-
-    \begin{figure}
-        \begin{center}
-            \begin{tabular}{|c||c|c|c|}
-                \hline
-                Curv. & II normals & CTriv normals & Our normals \\ \hline \hline
-                \raisebox{18mm}{$\kappa_1$} &
-                \MyZoom{pictures/d20-k1-II.jpg} &
-                \MyZoom{pictures/d20-k1-CTriv.jpg}&
-                \MyZoom{pictures/d20-k1-VN.jpg}\\ \hline
-                \raisebox{18mm}{$\kappa_2$} &
-                \MyZoom{pictures/d20-k2-II.jpg} &
-                \MyZoom{pictures/d20-k2-CTriv.jpg}&
-                \MyZoom{pictures/d20-k2-VN.jpg}\\ \hline
-                \raisebox{18mm}{$H$} &
-                \MyZoom{pictures/d20-H-II.jpg} &
-                \MyZoom{pictures/d20-H-CTriv.jpg}&
-                \MyZoom{pictures/d20-H-VN.jpg}\\ \hline
-                \raisebox{18mm}{$G$} &
-                \MyZoom{pictures/d20-G-II.jpg} &
-                \MyZoom{pictures/d20-G-CTriv.jpg}&
-                \MyZoom{pictures/d20-G-VN.jpg}\\ \hline
-            \end{tabular}
-        \end{center}
-        \caption{\label{fig-curvatures}Estimation of curvatures using
-          Corrected Normal Current estimators \cite{lachaud:2022-dcg}
-          with a measure of radius $2$ for the shape ``Dice-20'' of
-          Thingi10K database at resolution $256^3$. This estimator is
-          parameterized by an input normal estimator: first column by
-          ``Integral Invariant normals'' (radius $r=6$), second column
-          by ``Convolved Trivial normals'' (radius $k=6$), third
-          column by our presented normal estimator (deviation
-          $\sigma=4$, radius $r=2\sigma=8$). Per row are displayed the
-          estimated curvatures in order: first and second principal
-          curvatures $\kappa_1$ and $\kappa_2$, mean curvature $H$,
-          Gaussian curvature $G$. The range of curvature between deep
-          blue and deep red is $\lbrack -0.1, 0.1 \rbrack$ with white
-          color equal to $0$.}
-    \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-    \section{Conclusion}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \begin{credits}
-        \subsubsection{\ackname}
-        This work is partially supported by the French National Research Agency
-        within the StableProxies project (ANR-22-CE46-0006).
-%% \subsubsection{\discintname}
-%% It is now necessary to declare any competing interests or to specifically
-%% state that the authors have no competing interests. Please place the
-%% statement with a bold run-in heading in small font size beneath the
-%% (optional) acknowledgments\footnote{If EquinOCS, our proceedings submission
-%% system, is used, then the disclaimer can be provided directly in the system.},
-%% for example: The authors have no competing interests to declare that are
-%% relevant to the content of this article. Or: Author A has received research
-%% grants from Company W. Author B has received a speaker honorarium from
-%% Company X and owns stock in Company Y. Author C is a member of committee Z.
-    \end{credits}
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-    \bibliographystyle{splncs04}
-    \bibliography{biblio}
-
-\end{document}

### 2025-04-25 DGMM2025/paper.tex
Working on 1

@@
     \section{Introduction}
-
-    Visibility is a fundamental concept in computational geometry and
-    digital topology, with applications ranging from computer vision
-    (occlusions), geometric modeling (feature detection,
-    geodesics) to computer graphics (path tracing,
-    shadowmap). Visibility within polygons in the plane has been
-    extensively studied in the litterature~\cite{ghosh:2007-book} and
-    is still studied in higher dimensional
-    spaces~\cite{orourke:2017-book}. The general problem has a high
-    complexity. For instance, the 3d visibility complex between $n$
-    spheres and occluding spheres has a complexity
-    $O(n^4)$~\cite{durand:2002-tog}. Exact 3d visibility between
-    polygons and occluding polygons is often casted into 5d Plücker
-    space~\cite{nirenstein:2002-ewr}, which nicely represents 3d lines
-    and their respective positions. The computational cost remains
-    high even with decomposition into coarse cells for speed up
-    (several days of computation for 1M triangles at the time).
-
-    To increase efficiency, several authors have casted the
-    visibility problem into a digital space, generally $\Z^3$ or its
-    decomposition into cubical cells. Visibility is simplified as the
-    question whether there is a connected digital straight line
-    joining a pair of cells without occluding cell(s)
-    (e.g. Soille~\cite{soille:1994-prl} uses Bresenham
-    segments). Coeurjolly \emph{et al.}~\cite{coeurjolly:2004-prl}
-    uses a non-symmetric visibility definition and preimage
-    computations to speed up these
-    algorithms. Chica~\cite{chica:2008-spm} uses a half-cell erosion
-    of the complementary space and Bresenham lines to decide
-    visibility.
-
-    We propose an algorithm that solves the following visibility
-    problem: given a digital set $X \subset \Z^d$, two points $p,q$ of
-    $X$ are \emph{visible} whenever the Euclidean straight line
-    segment $\lbrack p,q \rbrack$ is never at chessboard distance
-    ($\infty$-distance) greater or equal to $1$ from $X$. It is
-    equivalent to the \emph{cotangency} of $p$ and $q$ in $X$, as
-    formalized in~\cite{lachaud:2021-dgmm,lachaud:2022-jmiv}, and can
-    be viewed as an inclusion problem between sets of lattice points
-    in this form. Indeed cells surounding $X$ can be encoded as
-    lattice points (Khalimsky coding), as well as the cells covering
-    lattice directions. The originality of our method is to encode
-    subsets of lattice points as sets of integer intervals and to
-    reduce all the inclusion problems as intersections and
-    translations of integer intervals. For a given lattice vector
-    $\mathbf{t}$, we solve the visibility of every pair of points
-    $(p,p+\mathbf{t})$ of $X$. Global visibility is achieved by
-    testing all sought directions within a given range, and is
-    parallelized straightforwardly.
-
-    We focus on solving efficiently this problem because it is crucial
-    in computing geometric normals along digital surfaces that are
-    aware of salient features. Indeed, 2d discrete tangent estimators
-    based on tangency or discrete line segments have proven to be both
-    sensitive to sharp corners and multigrid convergent on the
-    boundary of digitized smooth shapes~\cite{feschet:1999-dgci,lachaud:2007-ivc,nguyen:2011-pr}.
-    Many ad hoc methods have been proposed for tangent plane or normal
-    estimation on 3d digital surfaces
-    (e.g. \cite{fourey:2009-cg,charrier:2011-iwcia,Cuel:2014-dgci,Lachaud:2017-lnm,mareche:2024-ispr}).
-    If two of these methods~\cite{Cuel:2014-dgci,Lachaud:2017-lnm}
-    have been shown to be multigrid convergent on digitization of
-    shapes with smooth boundary, their formulation intrinsically
-    smoothes features, e.g.\ in contrast with the method of
-    Mar{ê}ch{é} \emph{et al.}~\cite{mareche:2024-ispr}, whose
-    convergence is not established. We propose here a normal estimator
-    defined as the most orthogonal vector to the cone of visibility at
-    the point of interest. Visibility is high in smooth regions and
-    the induced visibility vectors are good approximations of tangent
-    vectors. On the contrary the visibility is blocked at sharp
-    features, so the normal vector is not influenced by the
-    geometry on the other side of the features. We demonstrate the
-    superiority of this normal estimator for estimating curvatures
-    along digital surfaces with sharp features.
-
-    Note that our algorithm for computing visibility is in fact much
-    more general. The same algorithm could be used to recognize if any
-    pattern of lattice points is present on a shape. It is similar to
-    an erosion algorithm where the structuring element is the chosen
-    pattern, and could also be used for morphological operations~\cite{soille1999morphological}.
-    The paper outline is as follows. In Section~2, we recall some
-    definitions and present tangency of chords and its equivalence
-    to visibility. Section~3 describes the specific data structure
-    for encoding set of grid cells, and the main algorithm that
-    exploits this encoding to compute visibility exactly. Section~4
-    presents experimental results on visibility, its usage as a
-    discrete normal estimator, and how it improves curvature estimates
-    on digital surfaces. Finally, Section 5 concludes and gives some
-    perspectives to this work.
-    %% , notably other usages of this algorithm in the field.
-
-%    \deleted[id=JO]{
-%    Visibility is a fundamental concept in computational geometry and digital topology, with applications ranging from computer vision to geometric modeling and computer graphics.
-%    In this work, we explore visibility through the lens of chord tangency, introducing a novel approach that builds on discrete geometric structures.
-%    Our framework leverages the discrete setting of and cell complexes, providing a rigorous foundation for analyzing visibility properties in digital spaces.
-%    }
-%
-%
-%    \deleted[id=JO]{
-%    We recall essential definitions from previous works, particularly the notions of cell complexes and the star operator as formalized in~\cite{lachaud:2021-dgmm} and~\cite{lachaud:2022-jmiv}.
-%    The integer grid serves as our primary space of study, where geometric structures are discretized using cell complexes.
-%    A cell complex is a decomposition of space into elementary units (vertices, edges, faces, and higher-dimensional counterparts) forming a combinatorial representation of geometric objects.
-%    The star of a cell, as defined in these works, consists of all higher-dimensional cells that contain it, a crucial concept for analyzing local neighborhoods and connectivity.
-%    }
-%
-%    \deleted[id=JO]{
-%      Building on these foundations, our study focuses on visibility as determined by the tangency of chords in discrete geometry.
-%    We define and analyze how visibility relationships emerge in this context and investigate their combinatorial and topological implications.
-%    This approach provides a new perspective on discrete visibility, offering potential applications in digital imaging, surface reconstruction, and computational topology.
-%    }
-%
-%    \deleted[id=JO]{
-%      The remainder of this paper is structured as follows.
-%    In Section 2, we formalize the concept of chord tangency and its role in visibility analysis.
-%    Section 3 enters into the usage of integer intervals intersections to quickly scan the figure in order to recover this visibiltiy.
-%    Section 4 presents our main results, using this visibility to compute normals using the CNC estimator~\cite{lachaud:2022-dcg}.
-%    Finally, Section 5 concludes with some other applications of integer intervals intersections in the field.
-%    }
+    \input{introduction.tex}
 

### 2025-04-25 batch.sh
added modular ii and sigma

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+BASE_COMMAND="$1 --noInterface -r $2 -p $3 -g"
+
+for count in $(LANG=fr_FR seq 0.25 0.125 1); do
+  $BASE_COMMAND $count
+done

### 2025-04-25 main.cpp

@@ -75,6 +75,7 @@ float MaxCurv = 0.2;
 
 // Parameters
 int VisibilityRadius = 10;
+double iiRadius = 3;
 double gridstep = 1.0;
 int OMP_max_nb_threads = 1;
 double Time = 0.0;
@@ -559,6 +560,13 @@ void computeVisibilityDirectionToSharpFeatures() {
   }
 }
 
+double sigma = 5;
+double minus2SigmaSquare = -2*sigma*sigma;
+
+double wSig(double d) {
+  return exp(d/minus2SigmaSquare);
+}
+
 void computeVisibilityNormals() {
   visibility_normals.clear();
   visibility_normals.reserve(pointels.size());
@@ -566,11 +574,12 @@ void computeVisibilityNormals() {
   for (const auto &pointel: pointels) {
     std::vector<Point> visibles;
     RealPoint centroid(0, 0, 0);
-    for (auto point_idx: kdTree.pointsInBall(pointel, VisibilityRadius)) {
+    for (auto point_idx: kdTree.pointsInBall(pointel, 2*sigma)) {
       auto tmp = kdTree.position(point_idx);
       if (visibility.isVisible(pointel, tmp) && tmp != pointel) {
         visibles.push_back(tmp);
-        centroid += tmp;
+//        centroid += tmp;
+        centroid += wSig((pointel-tmp).squaredNorm())*tmp;
       }
     }
     centroid /= (double) visibles.size();
@@ -579,7 +588,8 @@ void computeVisibilityNormals() {
       auto diff = pt - centroid;
       for (int i = 0; i < 3; ++i) {
         for (int j = 0; j < 3; ++j) {
-          cov(i, j) += diff[i] * diff[j];
+//          cov(i, j) += diff[i] * diff[j];
+          cov(i, j) += diff[i] * diff[j] * wSig(diff.squaredNorm());
         }
       }
     }
@@ -781,6 +791,7 @@ int main(int argc, char *argv[]) {
   app.add_option("-r,--radius", VisibilityRadius, "the radius of the visibility sphere");
   app.add_flag("-l", listP, "lists the known named polynomials.");
   app.add_flag("--noInterface", noInterface, "desactivate the interface and use the visibility OMP algorithm");
+  app.add_option("--IIradius", iiRadius, "the radius of the visibility sphere");
   // -p "x^2+y^2+2*z^2-x*y*z+z^3-100" -g 0.5
[…]

### 2025-04-25 main.cpp
fix prog + params

@@ -589,7 +589,7 @@ void computeVisibilityNormals() {
       for (int i = 0; i < 3; ++i) {
         for (int j = 0; j < 3; ++j) {
 //          cov(i, j) += diff[i] * diff[j];
-          cov(i, j) += diff[i] * diff[j] * wSig(diff.squaredNorm());
+          cov(i, j) += diff[i] * diff[j] * wSig((pt-pointel).squaredNorm());
         }
       }
     }
@@ -791,7 +791,9 @@ int main(int argc, char *argv[]) {
   app.add_option("-r,--radius", VisibilityRadius, "the radius of the visibility sphere");
   app.add_flag("-l", listP, "lists the known named polynomials.");
   app.add_flag("--noInterface", noInterface, "desactivate the interface and use the visibility OMP algorithm");
-  app.add_option("--IIradius", iiRadius, "the radius of the visibility sphere");
+  app.add_option("--IIradius", iiRadius, "radius used for ii normal computation");
+  double sigmaTmp;
+  app.add_option("-s,--sigma", sigmaTmp, "sigma used for visib normal computation");
   // -p "x^2+y^2+2*z^2-x*y*z+z^3-100" -g 0.5
   // Parse command line options. Exit on error.
   CLI11_PARSE(app, argc, argv)
@@ -889,7 +891,11 @@ int main(int argc, char *argv[]) {
 
   primal_surface->vertexNormals() = trivial_normals;
 
-  sigma = 5*pow(gridstep,-0.5);
+  if (sigmaTmp) {
+    sigma = sigmaTmp;
+  } else {
+    sigma = 5*pow(gridstep,-0.5);
+  }
   minus2SigmaSquare = -2*sigma*sigma;
 
   std::cout << "sigma = " << sigma << std::endl;

### 2025-04-25 DGMM2025/paper.tex
Working on 2

@@
 
-    Let $\Z^d$ be the d-dimensional digital space, $d$ > 0.
-    Let $\mathcal{C}^d$ be the (cubical) cell complex induced by the lattice $\Z^d$ : its 0-cells are the points of $\Z^d$, its 1-cells are the open unit segments joining two 0-cells at distance 1, its 2-cells are the open unit squares, etc., and its d-cells are the d-dimensional open unit hypercubes with vertices in $\Z^d$.
-    We denote $\mathcal{C}^d_k$ the set of its k-cells.
-    In the following, a cell will always designate an element of $\mathcal{C}^d$, and the term subcomplex always designates a subset of $\mathcal{C}^d$.
-
-    A cell $\sigma$ is a face of another cell $\tau$ whenever $\sigma$ is a subset of the topological closure $\bar{\tau}$ of $\tau$, written $\sigma \preccurlyeq \tau$.
-    Given any subcomplex K of $\mathcal{C}^d$, the star $Star(K)$ of K is $\{\tau \in \mathcal{C}^d, s.t.\ \exists\sigma \in K,\sigma \preccurlyeq \tau\}$
-
-    \begin{definition}
-        Two points \( p \) and \( q \) on \( K \) are visible if and only if the segment \([p, q]\) is included in \(\text{Star}(K)\), i.e., \( [p, q] \subseteq \text{Star}(K)\)
+    All the theory and algorithms presented in this section are
+    defined and valid in arbitrary dimension $d$. They will however be
+    illustrated in 2d for clarity, while experiments willl be
+    performed on 3d digital shapes.  Let $\Z^d$ be the $d$-dimensional
+    digital space.  Let $\mathcal{C}^d$ be the (cubical) cell complex
+    induced by the lattice $\Z^d$ : its 0-cells are the points of
+    $\Z^d$, its 1-cells are the open unit segments joining two 0-cells
+    at distance 1, its 2-cells are the open unit squares, \ldots, and
+    its $d$-cells are the $d$-dimensional open unit hypercubes with
+    vertices in $\Z^d$.  We denote by $\mathcal{C}^d_k$ the set of its
+    $k$-cells, for $0 \Le k \Le d$.  In the following, a cell always
+    designates an element of $\mathcal{C}^d$, and the term subcomplex
+    always indicates a subset of $\mathcal{C}^d$.
+
+    The \emph{topological closure} of a cell $\tau$ is denoted by
+    $\bar{\tau}$. The \emph{star} of a cell $\sigma$ is the subcomplex
+    $\Star{\sigma}:=\{\tau \in \mathcal{C}, \sigma \subset \bar{\tau}
+    \}$. It is naturally extended to any subcomplex $K$ by union,
+    i.e. $\Star{K} := \cup_{\sigma \in K} \Star{\sigma}$, and more
+    generally to any subset $Y$ of $\R^d$ as $\Star{Y}:=\{ c \in \C,
+    \bar{c} \cap Y \neq \emptyset \}$. The \emph{body} $\|K\|$ of $K$
+    is its realization in $\R^d$, i.e. $\|K\|:=\cup_{c \in K} c$. One
+    can check that $\Star{K}=\Star{\|K\|}$, so these definitions are
+    sound.
+
+    %% A cell $\sigma$ is a face of another cell $\tau$ whenever $\sigma$
+    %% is a subset of the topological closure $\bar{\tau}$ of $\tau$,
+    %% written $\sigma \preccurlyeq \tau$.  Given any subcomplex K of
+    %% $\mathcal{C}^d$, the star $Star(K)$ of K is $\{\tau \in
+    %% \mathcal{C}^d, s.t.\ \exists\sigma \in K,\sigma \preccurlyeq
+    %% \tau\}$.
+    \begin{definition}[Visibility]
+      Let $Z \subset \Z^d$ be a digital set. Two digital points $p$
+      and $q$ are \emph{visible in $Z$} if and only if the straight
+      segment $[p, q]$ is included in $\Star{Z}$, i.e., $\Star{[p, q]}
+      \subseteq \Star{Z}$.
     \end{definition}
+    This definition corresponds to the concept of tangency presented
+    in \cite{lachaud:2022-jmiv}, limited to pair of points. One can
+    check that $p$ and $q$ must belong to $Z$ to be visible.
 

### 2025-04-25 DGMM2025/paper.tex
Working on 2

--- 2025-04-25 DGMM2025/paper.tex
@@
     \section{Visibility through tangency of chords}
-
-    Let $\Z^d$ be the d-dimensional digital space, $d$ > 0.
-    Let $\mathcal{C}^d$ be the (cubical) cell complex induced by the lattice $\Z^d$ : its 0-cells are the points of $\Z^d$, its 1-cells are the open unit segments joining two 0-cells at distance 1, its 2-cells are the open unit squares, etc., and its d-cells are the d-dimensional open unit hypercubes with vertices in $\Z^d$.
-    We denote $\mathcal{C}^d_k$ the set of its k-cells.
-    In the following, a cell will always designate an element of $\mathcal{C}^d$, and the term subcomplex always designates a subset of $\mathcal{C}^d$.
-
-    A cell $\sigma$ is a face of another cell $\tau$ whenever $\sigma$ is a subset of the topological closure $\bar{\tau}$ of $\tau$, written $\sigma \preccurlyeq \tau$.
-    Given any subcomplex K of $\mathcal{C}^d$, the star $Star(K)$ of K is $\{\tau \in \mathcal{C}^d, s.t.\ \exists\sigma \in K,\sigma \preccurlyeq \tau\}$
-
-    \begin{definition}
-        Two points \( p \) and \( q \) on \( K \) are visible if and only if the segment \([p, q]\) is included in \(\text{Star}(K)\), i.e., \( [p, q] \subseteq \text{Star}(K)\)
-    \end{definition}
-
-    % Examples of visibility in 2D
-    \begin{figure}
-        \centering
-        \begin{tabular}{cc|cc}
-            \begin{tikzpicture}
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.75,2.75);
-                \draw[dashed] (0,0) -- (2,1);
-                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p1};
-                \filldraw[black] (2,1) circle (0.05) node[anchor=north] {q1};
-                \draw [thick] (0,0) -- (0.5,0) -- (1,0) -- (1,0.5) -- (1.5,0.5) -- (1.5,1) -- (2,1);
-                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,0.5) -- (0.5,0.5) -- (0.5,1) -- (1,1) -- (1,1.5) -- (2.5,1.5) -- (2.5,0.5) -- (2,0.5) -- (2,0) -- (1.5,0) -- (1.5,-0.5) -- (-0.5,-0.5);
-            \end{tikzpicture} & & &
-            \begin{tikzpicture}
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.25,3.25);
-                \draw[red,dashed,thick] (0,0) -- (1.5,1);
-                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p2};
-                \filldraw[black] (1.5,1) circle (0.05) node[anchor=north] {q2};
-                \draw [thick] (0,0) -- (0,1) -- (0.5,1) -- (0.5,1.5) -- (1,1.5) -- (1,1) -- (1.5,1);
-                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (0,1.5) -- (0,2) -- (1.5,2) -- (1.5,1.5) -- (2,1.5)  -- (2,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
-            \end{tikzpicture} \\
-            Visible                       & & & Non Visible                   \\\\
-            \hline\\
-            \begin{tikzpicture}
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
-                \draw[red,dashed,thick] (0,0) -- (1,0);
-                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p3};
-                \filldraw[black] (1,0) circle (0.05) node[anchor=north] {q3};
-                \draw [thick] (0,0) -- (0,1) -- (1,1) -- (1,0);
-                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,-0.5) -- (-0.5,-0.5) -- (0.5,-0.5) -- (0.5,0.5);
-            \end{tikzpicture} & & &
-            \begin{tikzpicture}
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
-                \draw[red,dashed,thick] (0,0) -- (1,1);
-                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p4};
-                \filldraw[black] (1,1) circle (0.05) node[anchor=north] {q4};
-                \draw [thick] (0,0) -- (0,1) -- (1,1);
-                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
-            \end{tikzpicture}\\
-            Non Visible (from a 1-d cell) & & & Non Visible (from a 0-d cell)
-        \end{tabular}
-        \caption{Examples of visibility in 2D.}
-        \label{fig:visibility-2d}
-    \end{figure}
-
-    Figure~\ref{fig:visibility-2d} shows what is considered visible or not.
-We note that one particular aspect of this visibility definition is that all visible points from a given point taken as a separate complex are not necessarily 26-connected~\ref{fig:visibility-2d-not-connected}.
-    Furthermore, we conjecture that they even may not be $n$-connected for $n$ arbitrarily large.
-    This characteristic has implications for the applicability of Algorithm 3 from~\cite{lachaud:2022-jmiv}, as the algorithm assumes that visited points are 26-connected, potentially leading to incomplete collection of visible points.
-
-    % Example of visibility not necessarily connected
-    % Path from p to q : r u r u r r r r r u r
-    \begin{figure}
-        \centering
-        \begin{tikzpicture}
-            \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (5.25,3.25);
-            \draw[thick] (0,0) -- (0.5,0) -- (0.5,0.5) -- (1,0.5) -- (1,1) -- (3.5,1) -- (3.5,1.5);
-            \draw [black, dashed] (0,0) -- (3.5,1.5);
-            \draw [red, dashed] (0,0) -- (3.5,1);
-            \draw [red, dashed] (0,0) -- (3,1);
-            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p};
-            \filldraw[gray] (0.5,0) circle (0.05);
-            \filldraw[gray] (0.5,0.5) circle (0.05);
-            \filldraw[gray] (1,0.5) circle (0.05);
-            \filldraw[gray] (1,1) circle (0.05);
-            \filldraw[gray] (1.5,1) circle (0.05);
-            \filldraw[gray] (2,1) circle (0.05);
-            \filldraw[gray] (2.5,1) circle (0.05);
-            \filldraw[red] (3,1) circle (0.05);
-            \filldraw[red] (3.5,1) circle (0.05);
-            \filldraw[black] (3.5,1.5) circle (0.05) node[anchor=west] {q};
-            \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,0.5) -- (0,0.5) -- (0,1) -- (0.5,1) -- (0.5,1.5) -- (3,1.5) -- (3,2) -- (4,2) -- (4,0.5) -- (1.5,0.5) -- (1.5,0) -- (1,0) -- (1,-0.5) -- (-0.5,-0.5);
-        \end{tikzpicture}
-        \caption{Example of non-connex visibility in 2D, q is visible from p while the visibility points are not 26-connected.}
-        \label{fig:visibility-2d-not-connected}
-    \end{figure}
+    \input{visibility.tex}
 

### 2025-04-25 DGMM2025/visibility.tex
Working on 2

    All the theory and algorithms presented in this section are
    defined and valid in arbitrary dimension $d$. They will however be
    illustrated in 2d for clarity, while experiments willl be
    performed on 3d digital shapes.  Let $\Z^d$ be the $d$-dimensional
    digital space.  Let $\mathcal{C}^d$ be the (cubical) cell complex
    induced by the lattice $\Z^d$ : its 0-cells are the points of
    $\Z^d$, its 1-cells are the open unit segments joining two 0-cells
    at distance 1, its 2-cells are the open unit squares, \ldots, and
    its $d$-cells are the $d$-dimensional open unit hypercubes with
    vertices in $\Z^d$.  We denote by $\mathcal{C}^d_k$ the set of its
    $k$-cells, for $0 \Le k \Le d$.  In the following, a cell always
    designates an element of $\mathcal{C}^d$, and the term subcomplex
    always indicates a subset of $\mathcal{C}^d$.

    The \emph{topological closure} of a cell $\tau$ is denoted by
    $\bar{\tau}$. The \emph{star} of a cell $\sigma$ is the subcomplex
    $\Star{\sigma}:=\{\tau \in \mathcal{C}, \sigma \subset \bar{\tau}
    \}$. It is naturally extended to any subcomplex $K$ by union,
    i.e. $\Star{K} := \cup_{\sigma \in K} \Star{\sigma}$, and more
    generally to any subset $Y$ of $\R^d$ as $\Star{Y}:=\{ c \in \C,
    \bar{c} \cap Y \neq \emptyset \}$. The \emph{body} $\|K\|$ of $K$
    is its realization in $\R^d$, i.e. $\|K\|:=\cup_{c \in K} c$. One
    can check that $\Star{K}=\Star{\|K\|}$, so these definitions are
    sound.

    %% A cell $\sigma$ is a face of another cell $\tau$ whenever $\sigma$
    %% is a subset of the topological closure $\bar{\tau}$ of $\tau$,
    %% written $\sigma \preccurlyeq \tau$.  Given any subcomplex K of
    %% $\mathcal{C}^d$, the star $Star(K)$ of K is $\{\tau \in
    %% \mathcal{C}^d, s.t.\ \exists\sigma \in K,\sigma \preccurlyeq
    %% \tau\}$.
    \begin{definition}[Visibility]
      Let $Z \subset \Z^d$ be a digital set. Two digital points $p$
      and $q$ are \emph{visible in $Z$} if and only if the straight
      segment $[p, q]$ is included in $\Star{Z}$, i.e., $\Star{[p, q]}
      \subseteq \Star{Z}$.
    \end{definition}
    This definition corresponds to the concept of tangency presented
    in \cite{lachaud:2022-jmiv}, limited to pair of points. One can
    check that $p$ and $q$ must belong to $Z$ to be visible.

    % Examples of visibility in 2D
    \begin{figure}
        \centering
        \begin{tabular}{cc|cc}
            \begin{tikzpicture}
                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.75,2.75);
                \draw[dashed] (0,0) -- (2,1);
                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p1};
                \filldraw[black] (2,1) circle (0.05) node[anchor=north] {q1};
                \draw [thick] (0,0) -- (0.5,0) -- (1,0) -- (1,0.5) -- (1.5,0.5) -- (1.5,1) -- (2,1);
                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,0.5) -- (0.5,0.5) -- (0.5,1) -- (1,1) -- (1,1.5) -- (2.5,1.5) -- (2.5,0.5) -- (2,0.5) -- (2,0) -- (1.5,0) -- (1.5,-0.5) -- (-0.5,-0.5);
            \end{tikzpicture} & & &
            \begin{tikzpicture}
                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.25,3.25);
                \draw[red,dashed,thick] (0,0) -- (1.5,1);
                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p2};
                \filldraw[black] (1.5,1) circle (0.05) node[anchor=north] {q2};
                \draw [thick] (0,0) -- (0,1) -- (0.5,1) -- (0.5,1.5) -- (1,1.5) -- (1,1) -- (1.5,1);
                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (0,1.5) -- (0,2) -- (1.5,2) -- (1.5,1.5) -- (2,1.5)  -- (2,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
            \end{tikzpicture} \\
            Visible                       & & & Non Visible                   \\\\
            \hline\\
            \begin{tikzpicture}
                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
                \draw[red,dashed,thick] (0,0) -- (1,0);
                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p3};
                \filldraw[black] (1,0) circle (0.05) node[anchor=north] {q3};
                \draw [thick] (0,0) -- (0,1) -- (1,1) -- (1,0);
                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,-0.5) -- (-0.5,-0.5) -- (0.5,-0.5) -- (0.5,0.5);
            \end{tikzpicture} & & &
            \begin{tikzpicture}
                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
                \draw[red,dashed,thick] (0,0) -- (1,1);
                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p4};
                \filldraw[black] (1,1) circle (0.05) node[anchor=north] {q4};
                \draw [thick] (0,0) -- (0,1) -- (1,1);
                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
            \end{tikzpicture}\\
            Non Visible (from a 1-d cell) & & & Non Visible (from a 0-d cell)
        \end{tabular}
        \caption{Examples of visibility in 2D.}
        \label{fig:visibility-2d}
    \end{figure}

    Figure~\ref{fig:visibility-2d} shows what is considered visible or not. We note that one particular aspect of this visibility definition is that all visible points from a given point taken as a separate complex are not necessarily 26-connected~\ref{fig:visibility-2d-not-connected}.
    Furthermore, we conjecture that they even may not be $n$-connected for $n$ arbitrarily large.
    This characteristic has implications for the applicability of Algorithm 3 from~\cite{lachaud:2022-jmiv}, as the algorithm assumes that visited points are 26-connected, potentially leading to incomplete collection of visible points.

    % Example of visibility not necessarily connected
    % Path from p to q : r u r u r r r r r u r
    \begin{figure}
        \centering
        \begin{tikzpicture}
            \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (5.25,3.25);
            \draw[thick] (0,0) -- (0.5,0) -- (0.5,0.5) -- (1,0.5) -- (1,1) -- (3.5,1) -- (3.5,1.5);
            \draw [black, dashed] (0,0) -- (3.5,1.5);
            \draw [red, dashed] (0,0) -- (3.5,1);
            \draw [red, dashed] (0,0) -- (3,1);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p};
            \filldraw[gray] (0.5,0) circle (0.05);
            \filldraw[gray] (0.5,0.5) circle (0.05);
            \filldraw[gray] (1,0.5) circle (0.05);
            \filldraw[gray] (1,1) circle (0.05);
            \filldraw[gray] (1.5,1) circle (0.05);
            \filldraw[gray] (2,1) circle (0.05);
            \filldraw[gray] (2.5,1) circle (0.05);
            \filldraw[red] (3,1) circle (0.05);
            \filldraw[red] (3.5,1) circle (0.05);
            \filldraw[black] (3.5,1.5) circle (0.05) node[anchor=west] {q};
            \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,0.5) -- (0,0.5) -- (0,1) -- (0.5,1) -- (0.5,1.5) -- (3,1.5) -- (3,2) -- (4,2) -- (4,0.5) -- (1.5,0.5) -- (1.5,0) -- (1,0) -- (1,-0.5) -- (-0.5,-0.5);
        \end{tikzpicture}
        \caption{Example of non-connex visibility in 2D, q is visible from p while the visibility points are not 26-connected.}
        \label{fig:visibility-2d-not-connected}
    \end{figure}

### 2025-04-25 DGMM2025/visibility.tex
Working on 2

@@
       \centering
-        \begin{tabular}{cc|cc}
-            \begin{tikzpicture}
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.75,2.75);
-                \draw[dashed] (0,0) -- (2,1);
-                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p1};
-                \filldraw[black] (2,1) circle (0.05) node[anchor=north] {q1};
-                \draw [thick] (0,0) -- (0.5,0) -- (1,0) -- (1,0.5) -- (1.5,0.5) -- (1.5,1) -- (2,1);
-                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,0.5) -- (0.5,0.5) -- (0.5,1) -- (1,1) -- (1,1.5) -- (2.5,1.5) -- (2.5,0.5) -- (2,0.5) -- (2,0) -- (1.5,0) -- (1.5,-0.5) -- (-0.5,-0.5);
-            \end{tikzpicture} & & &
-            \begin{tikzpicture}
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.25,3.25);
-                \draw[red,dashed,thick] (0,0) -- (1.5,1);
-                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p2};
-                \filldraw[black] (1.5,1) circle (0.05) node[anchor=north] {q2};
-                \draw [thick] (0,0) -- (0,1) -- (0.5,1) -- (0.5,1.5) -- (1,1.5) -- (1,1) -- (1.5,1);
-                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (0,1.5) -- (0,2) -- (1.5,2) -- (1.5,1.5) -- (2,1.5)  -- (2,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
-            \end{tikzpicture} \\
-            Visible                       & & & Non Visible                   \\\\
-            \hline\\
-            \begin{tikzpicture}
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
-                \draw[red,dashed,thick] (0,0) -- (1,0);
-                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p3};
-                \filldraw[black] (1,0) circle (0.05) node[anchor=north] {q3};
-                \draw [thick] (0,0) -- (0,1) -- (1,1) -- (1,0);
-                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,-0.5) -- (-0.5,-0.5) -- (0.5,-0.5) -- (0.5,0.5);
-            \end{tikzpicture} & & &
-            \begin{tikzpicture}
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
-                \draw[red,dashed,thick] (0,0) -- (1,1);
-                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p4};
-                \filldraw[black] (1,1) circle (0.05) node[anchor=north] {q4};
-                \draw [thick] (0,0) -- (0,1) -- (1,1);
-                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
-            \end{tikzpicture}\\
-            Non Visible (from a 1-d cell) & & & Non Visible (from a 0-d cell)
-        \end{tabular}
+      \input{visibility.tikz}
       \caption{Examples of visibility in 2D.}

### 2025-04-25 DGMM2025/visibility.tex
Working on 2

@@
     check that $p$ and $q$ must belong to $Z$ to be visible.
+    Figure~\ref{fig:visibility-2d} illustrates what is considered
+    visible or not on some examples.
 
     % Examples of visibility in 2D
-    \begin{figure}
+    \begin{figure}[t]
       \centering
       \input{visibility.tikz}
-      \caption{Examples of visibility in 2D.}
+      \caption{Examples of visibility and non visibility in 2D within
+        the set $X$ (represented with black disks $\bullet$).}
       \label{fig:visibility-2d}
@@
 
-    Figure~\ref{fig:visibility-2d} shows what is considered visible or not.
-We note that one particular aspect of this visibility definition is that all visible points from a given point taken as a separate complex are not necessarily 26-connected~\ref{fig:visibility-2d-not-connected}.
-    Furthermore, we conjecture that they even may not be $n$-connected for $n$ arbitrarily large.
-    This characteristic has implications for the applicability of Algorithm 3 from~\cite{lachaud:2022-jmiv}, as the algorithm assumes that visited points are 26-connected, potentially leading to incomplete collection of visible points.
+    A quite unexpected fact about visibility it that the set of
+    visible points from a source $p$ is not necessarily digitally
+    connected in $X$. Indeed, for $n \in \Z, n \Ge 1$, we say that
+    $p,q$ are \emph{$n$-neighbors} when $\|q-p\|_\infty \Le n$, and
+    this induces the $n$-adjacency and $n$-connectedness relation in
+    $X$. As illustrated on
+    Figure~\ref{fig:visibility-2d-not-connected}, the set of points
+    visible from $p$ is clearly not $1$-connected. As our experiments
+    have shown, we even conjecture that it may not be $n$-connected
+    for $n$ arbitrarily large.
+
+    This characteristic has implications for the applicability of
+    \cite[Algorithm 3]{lachaud:2022-jmiv}, which is a breadth-first
+    like algorithm for computing all the points of $X$ visible in $X$
+    to a source point $p$. This algorithm sometimes outputs an
+    incomplete collection of visible points. This is why in the next
+    section we present an algorithm that computes the exact visibility
+    pairs within $X$, without recourse to connectedness in its formulation.
+
+    %% We note that one particular
+    %% aspect of this visibility definition is that all visible points
+    %% from a given point taken as a separate complex are not necessarily
+    %% 26-connected~\ref{fig:visibility-2d-not-connected}.  Furthermore,
+    %% we conjecture that they even may not be $n$-connected for $n$
+    %% arbitrarily large.  This characteristic has implications for the
+    %% applicability of Algorithm 3 from~\cite{lachaud:2022-jmiv}, as the
+    %% algorithm assumes that visited points are 26-connected,
+    %% potentially leading to incomplete collection of visible points.
 
@@
     % Path from p to q : r u r u r r r r r u r
-    \begin{figure}
+    \begin{figure}[t]
         \centering
@@
         \end{tikzpicture}
-        \caption{Example of non-connex visibility in 2D, q is visible from p while the visibility points are not 26-connected.}
+        \caption{The set of visible points in $X$ from source $p$ is not $1$-connected.}
         \label{fig:visibility-2d-not-connected}

### 2025-04-25 DGMM2025/paper.tex
smaller gridsteps
naive breadth first timings

@@
                 ] coordinates {
-                    (0.25,3.97418)(0.375,3.00921)(0.5,2.85702)(0.625,2.34448)(0.75,1.85023)(0.875,2.16868)(1.0,1.85023)
+                    (0.0625,7.61948)(0.125,5.49755)(0.25,3.97418)(0.375,3.00921)(0.5,2.85702)(0.625,2.34448)(0.75,1.85023)(0.875,2.16868)(1.0,1.85023)
                 };
@@
                 ] coordinates {
-                    (1,8.90781)(0.875,10.2845)(0.75,11.3734)(0.625,12.5062)(0.5,14.0867)(0.375,16.6192)(0.25,19.6747)
+                    (0.0625,38.1045)(0.125,26.8765)(0.25,19.6747)(0.375,16.6192)(0.5,14.0867)(0.625,12.5062)(0.75,11.3734)(0.875,10.2845)(1,8.90781)
                 };
@@
                 ] coordinates {
-                    (0.25,12.3975)(0.375,9.41303)(0.5,8.69558)(0.625,7.37667)(0.75,6.82131)(0.875,6.05735)(1,6.33877)
+                    (0.0625,25.5024)(0.125,18.2364)(0.25,12.3975)(0.375,9.41303)(0.5,8.69558)(0.625,7.37667)(0.75,6.82131)(0.875,6.05735)(1,6.33877)
                 };
@@
                 ] coordinates {
-                    (0.25,10.8007)(0.375,8.69514)(0.5,7.26074)(0.625,6.2309)(0.75,5.6897)(0.875,5.28197)(1,4.96098)
+                    (0.0625,27.9287)(0.125,17.5104)(0.25,10.8007)(0.375,8.69514)(0.5,7.26074)(0.625,6.2309)(0.75,5.6897)(0.875,5.28197)(1,4.96098)
                 };
@@
                 ] coordinates {
-                    (0.25,18.2339)(0.375,14.6475)(0.5,12.3618)(0.625,9.55647)(0.75,9.83208)(0.875,7.51861)(1,7.99732)
+                    (0.0625,41.9816)(0.125,27.7104)(0.25,18.2339)(0.375,14.6475)(0.5,12.3618)(0.625,9.55647)(0.75,9.83208)(0.875,7.51861)(1,7.99732)
                 };
@@
                 \addlegendentry{radius 30};
+                \addplot[
+                    orange,
+                    only marks,
+                    mark=square,
+                    mark options={solid}
+                ] table[row sep=crcr] {
+                    % torus
+                    10624 7172.49\\
+                    4968 2330.69\\
+                    2584 883.559\\
+                    1840 568.776\\
+                    1176 278.712\\
+                    912 212.285\\
+                    624 122.615\\
+                    % rcube
+                    28568 20358.9\\
+                    12632 5964.1\\
+                    7088 2631.15\\
+                    4664 1394.49\\
+                    3080 742.638\\
+                    2408 554.389\\
+                    1736 334.654\\
+                    % sphere9
+                    24320 21263.4\\
+                    10760 6225.27\\
+                    6056 2829.2\\
+                    3944 1494.98\\
+                    2648 833.047\\
+                    2000 579.561\\
+                    1520 394.169\\
+                    % leopold
+                    8336 6866.82\\
+                    3720 2232.34\\
+                    2104 1050.28\\
+                    1336 576.853\\
+                    928 354.691\\
+                    680 243.249\\
+                    520 174.452\\
+                    % goursat
+                    37592 26954.6\\
+                    16712 8358.2\\
+                    9512 3748.3\\
+                    6056 1921.43\\
+                    4088 1088.38\\
+                    3032 706.378\\
+                    2456 531.932\\
+                    % d20
+                    97844 26392.3\\
+                    390235 110416.0\\
+                };
+                \addlegendentry{naive breadth first};
                 \addplot [
@@
         right images are the smooth version of the left images. ``Integral
-        Invariant normals'' are computed using a radius of $r=3$, while
-        our normal estimator are computed using a deviation of $\sigma=3$, and so
-        a radius of $r=2\sigma=6$}
+        Invariant normals'' are computed using a radius of $r=4.5$, while
+        our normal estimator are computed using a deviation of $\sigma=4$, and so
+        a radius of $r=2\sigma=8$}
         \label{fig:normals-estimation}

### 2025-04-25 main.cpp
Correct normals

@@ -563,8 +563,8 @@ void computeVisibilityDirectionToSharpFeatures() {
 double sigma = 5;
 double minus2SigmaSquare = -2*sigma*sigma;
 
-double wSig(double d) {
-  return exp(d/minus2SigmaSquare);
+double wSig( double d2) {
+  return exp(d2 / minus2SigmaSquare);
 }
 
 void computeVisibilityNormals() {
@@ -574,15 +574,18 @@ void computeVisibilityNormals() {
   for (const auto &pointel: pointels) {
     std::vector<Point> visibles;
     RealPoint centroid(0, 0, 0);
+    double total_w = 0.0;
     for (auto point_idx: kdTree.pointsInBall(pointel, 2*sigma)) {
       auto tmp = kdTree.position(point_idx);
-      if (visibility.isVisible(pointel, tmp) && tmp != pointel) {
+      if (visibility.isVisible(pointel, tmp) ) { //  && tmp != pointel) {
         visibles.push_back(tmp);
 //        centroid += tmp;
-        centroid += wSig((pointel-tmp).squaredNorm())*tmp;
+	const double w = wSig((pointel-tmp).squaredNorm());
+        centroid += w * tmp;
+	total_w  += w;
       }
     }
-    centroid /= (double) visibles.size();
+    centroid /= total_w; // (double) visibles.size();
     Eigen::Matrix3d cov = Eigen::Matrix3d::Zero();
     for (const auto &pt: visibles) {
       auto diff = pt - centroid;
@@ -599,6 +602,7 @@ void computeVisibilityNormals() {
   }
   if (!noInterface) {
     psPrimalMesh->addVertexVectorQuantity("Pointel visibility normals", visibility_normals);
+    //psPrimalMesh->addVertexVectorQuantity("Pointel visibility normals", visibility_normals);
   }
 }
 
@@ -792,7 +796,7 @@ int main(int argc, char *argv[]) {
   app.add_flag("-l", listP, "lists the known named polynomials.");
   app.add_flag("--noInterface", noInterface, "desactivate the interface and use the visibility OMP algorithm");
   app.add_option("--IIradius", iiRadius, "radius used for ii normal computation");
-  double sigmaTmp;
+  double sigmaTmp = 3.0;
   app.add_option("-s,--sigma", sigmaTmp, "sigma used for visib normal computation");
[…]

### 2025-04-25 DGMM2025/paper.tex
extensions removal
draft compilation in comment
some small fixes

@@
 \documentclass[runningheads]{llncs}
+%\documentclass[draft]{llncs}
 %
@@
     \section{Introduction}
-    \input{introduction.tex}
+    \input{introduction}
 
@@
     \section{Visibility through tangency of chords}
-    \input{visibility.tex}
+    \input{visibility}
 
@@
     To efficiently compute the intersection of 2 lists of intervals $K$ and $L$, we go through the first 2 unvisited
-    elements of the 2 lists. If they don't overlap (i.e. the start and end of the 1st interval are both smaller than
+    elements of the 2 lists. If they don't overlap (i.e.\ the start and end of the 1st interval are both smaller than
     the start of the other), then we can discard the smaller interval. Else, we construct the intersection of these
@@
     average length between visible points (so some
-    $\Theta(\sqrt{h})$), then this estimator is observed to be
+    $\Theta\left(\sqrt{h}\right)$), then this estimator is observed to be
     multigrid convergent along digitization of smooth shapes. However,
@@
         \end{center}
-        \caption{\label{fig-curvatures}Estimation of curvatures using
+        \caption{\label{fig:fig-curvatures}Estimation of curvatures using
           Corrected Normal Current estimators \cite{lachaud:2022-dcg}

### 2025-04-25 DGMM2025/paper.tex
Change figures

--- 2025-04-25 DGMM2025/paper.tex
@@
             \hline
-            Normals & Cubes & Smooth \\
+            Normals & With cube edges & Flat (no shading) \\
             \hline
@@
             \raisebox{18mm}{II} &
-            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
-            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} \\
+            \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat-edge.jpg} &
+            \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat.jpg} \\
+            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
+            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} \\
             \hline
             \raisebox{18mm}{Ours} &
-            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
-            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} \\
+            \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat-edge.jpg} &
+            \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat.jpg} \\
+            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
+            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} \\
             \hline
             \raisebox{18mm}{II} &
-            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-II} &
-            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-II} \\
+            \includegraphics[width=0.4\textwidth]{pictures/tie256-IIN-flat-edge.jpg} &
+            \includegraphics[width=0.4\textwidth]{pictures/tie256-IIN-flat.jpg} \\
+            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-II} &
+            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-II} \\
             \hline
             \raisebox{18mm}{Ours} &
-            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-NV} &
-            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-NV} \\
+            \includegraphics[width=0.4\textwidth]{pictures/tie256-VN-flat-edge.jpg} &
+            \includegraphics[width=0.4\textwidth]{pictures/tie256-VN-flat.jpg} \\
+            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-NV} &
+            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-NV} \\
             \hline

### 2025-04-25 DGMM2025/paper.tex
fix fig exts & figref

@@
             \raisebox{18mm}{II} &
-            \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat-edge.jpg} &
-            \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat.jpg} \\
+            \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat-edge} &
+            \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat} \\
             %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
@@
             \raisebox{18mm}{Ours} &
-            \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat-edge.jpg} &
-            \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat.jpg} \\
+            \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat-edge} &
+            \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat} \\
             %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
@@
             \raisebox{18mm}{II} &
-            \includegraphics[width=0.4\textwidth]{pictures/tie256-IIN-flat-edge.jpg} &
-            \includegraphics[width=0.4\textwidth]{pictures/tie256-IIN-flat.jpg} \\
+            \includegraphics[width=0.4\textwidth]{pictures/tie256-IIN-flat-edge} &
+            \includegraphics[width=0.4\textwidth]{pictures/tie256-IIN-flat} \\
             %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-II} &
@@
             \raisebox{18mm}{Ours} &
-            \includegraphics[width=0.4\textwidth]{pictures/tie256-VN-flat-edge.jpg} &
-            \includegraphics[width=0.4\textwidth]{pictures/tie256-VN-flat.jpg} \\
+            \includegraphics[width=0.4\textwidth]{pictures/tie256-VN-flat-edge} &
+            \includegraphics[width=0.4\textwidth]{pictures/tie256-VN-flat} \\
             %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-NV} &
@@
 
-    \RefFigure{fig-curvatures} displays the results of CNC curvature
+    Figure~\ref{fig:fig-curvatures} displays the results of CNC curvature
     estimations on the digitization of a piecewise smooth shape

### 2025-04-25 DGMM2025/paper.tex
Fix size
breadth with max radii (wip for radius 30)

@@
                 grid style=dashed,
-                ymax=50,
+                ymax=70,
                 ymode=log,
@@
                     thick,
-                    domain=0.25:1,
+                    domain=0.0625:1,
                     samples=100,
@@
     \end{figure}
-    \begin{figure}
-        \begin{tikzpicture}
-            \centering
-            \begin{axis}[
-                width=0.8\textwidth,
-                xlabel={\#Pointels},
-                ylabel={Computation Time (ms)},
-                legend pos=north west,
-                ymajorgrids=true,
-                grid style=dashed,
-                ymode=log,
-                xmode=log,
-                log ticks with fixed point,
-            ]
-                \addplot[
-                    red,
-                    only marks,
-                    mark=halfcircle,
-                    mark options={solid}
-                ] table[row sep=crcr] {
-                    10624 2246.69\\
-                    4968 793.426\\
-                    2584 328.535\\
-                    1840 190.401\\
-                    1176 93.2502\\
-                    912 78.7981\\
-                    624 56.3769\\
-                    28568 10193.5\\
-                    12632 4004.92\\
-                    7088 2010.63\\
-                    4664 1188.73\\
-                    3080 755.754\\
-                    2408 545.347\\
-                    1736 366.541\\
-                    24320 11169.1\\
-                    10760 4720.44\\
-                    6056 2397.79\\
-                    3944 1380.38\\
-                    2648 874.979\\
-                    2000 580.0\\
-                    1520 415.373\\
-                    8336 3196.55\\
-                    3720 1268.46\\
-                    2104 639.305\\
-                    1336 342.873\\
-                    928 177.54\\
-                    680 112.142\\
-                    520 87.0747\\
-                    37592 12335.6\\
-                    16712 5582.38\\
-                    9512 2976.21\\
-                    6056 1731.32\\
-                    4088 990.78\\
-                    3032 788.507\\
-                    2456 548.66\\
-                    97844 49226.3\\
-                    390235 181322\\
-                };
-                \addlegendentry{radius 10};
-                \addplot[
-                    MyGreen,
-                    only marks,
-                    mark=halfcircle,
-                    mark options={solid}
-                ] table[row sep=crcr] {
-                    10624 9522.43\\
-                    4968 2876.81\\
-                    2584 1152.25\\
-                    1840 635.332\\
-                    1176 347.973\\
-                    912 304.801\\
-                    624 250.126\\
-                    28568 70137.9\\
-                    12632 26063.0\\
-                    7088 11985.8\\
-                    4664 6239.51\\
-                    3080 3468.31\\
-                    2408 2059.84\\
-                    1736 1254.2\\
-                    24320 86616.9\\
-                    10760 26605.7\\
-                    6056 11813.5\\
-                    3944 6516.92\\
-                    2648 3564.03\\
-                    2000 1949.32\\
-                    1520 1244.89\\
-                    8336 18125.5\\
-                    3720 5157.11\\
-                    2104 2029.09\\
-                    1336 896.186\\
-                    928 446.136\\
-                    680 306.651\\
-                    520 259.078\\
-                    37592 76316.3\\
-                    16712 27747.3\\
-                    9512 13608.6\\
-                    6056 7140.03\\
-                    4088 3704.52\\
-                    3032 2624.2\\
-                    2456 1422.6\\
-                    97844 378906\\
-                    390235 1747780\\
-                };
-                \addlegendentry{radius 20};
-                \addplot[
-                    blue,
-                    only marks,
-                    mark=halfcircle,
-                    mark options={solid}
-                ] table[row sep=crcr] {
-                    10624 18283.5\\
-                    4968 4957.93\\
-                    2584 2133.36\\
-                    1840 1292.53\\
-                    1176 922.51\\
-                    912 863.731\\
-                    624 813.638\\
-                    28568 188784.0\\
-                    12632 62237.1\\
-                    7088 24874.9\\
-                    4664 9043.39\\
-                    3080 4407.09\\
-                    2408 2641.04\\
-                    1736 1820.31\\
-                    24320 227432.0\\
-                    10760 69706.8\\
-                    6056 25408.9\\
-                    3944 10094.7\\
-                    2648 5269.56\\
-                    2000 2948.16\\
-                    1520 2082.02\\
-                    8336 45045.4\\
-                    3720 8638.42\\
-                    2104 3238.48\\
-                    1336 1731.9\\
-                    928 1122.69\\
-                    680 928.084\\
-                    520 890.592\\
-                    37592 257981.0\\
-                    16712 84729.7\\
-                    9512 36298.8\\
-                    6056 15640.2\\
-                    4088 6662.17\\
-                    3032 4431.71\\
-                    2456 2621.98\\
-                    97844 1157400\\
-                    390235 10493200\\
-                };
-                \addlegendentry{radius 30};
-                \addplot[
-                    orange,
-                    only marks,
-                    mark=square,
-                    mark options={solid}
-                ] table[row sep=crcr] {
-                    % torus
-                    10624 7172.49\\
-                    4968 2330.69\\
-                    2584 883.559\\
-                    1840 568.776\\
-                    1176 278.712\\
-                    912 212.285\\
-                    624 122.615\\
-                    % rcube
-                    28568 20358.9\\
-                    12632 5964.1\\
-                    7088 2631.15\\
-                    4664 1394.49\\
-                    3080 742.638\\
-                    2408 554.389\\
-                    1736 334.654\\
-                    % sphere9
-                    24320 21263.4\\
-                    10760 6225.27\\
-                    6056 2829.2\\
-                    3944 1494.98\\
-                    2648 833.047\\
-                    2000 579.561\\
-                    1520 394.169\\
-                    % leopold
-                    8336 6866.82\\
-                    3720 2232.34\\
-                    2104 1050.28\\
-                    1336 576.853\\
-                    928 354.691\\
-                    680 243.249\\
-                    520 174.452\\
-                    % goursat
-                    37592 26954.6\\
-                    16712 8358.2\\
-                    9512 3748.3\\
-                    6056 1921.43\\
-                    4088 1088.38\\
-                    3032 706.378\\
-                    2456 531.932\\
-                    % d20
-                    97844 26392.3\\
-                    390235 110416.0\\
-                };
-                \addlegendentry{naive breadth first};
-                \addplot [
-                    color=black,
-                    thick,
-                    domain=500:60000,
-                    samples=100,
-                ] {0.01*x^(1.5)};
-                \addlegendentry{$0.01\times x\sqrt{x}$}
-            \end{axis}
-        \end{tikzpicture}
+
+    \begin{figure}[t]
+        \input{pointelscomptime.tikz}
         \caption{Computation Time of Visibility as a Function of Grid Resolution}
@@
             \raisebox{18mm}{II} &
-            \includegraphics[width=0.4\textwidth]{pictures/tie256-IIN-flat-edge} &
-            \includegraphics[width=0.4\textwidth]{pictures/tie256-IIN-flat} \\
+            \includegraphics[width=0.43\textwidth]{pictures/tie256-IIN-flat-edge} &
+            \includegraphics[width=0.43\textwidth]{pictures/tie256-IIN-flat} \\
             %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-II} &
@@
             \raisebox{18mm}{Ours} &
-            \includegraphics[width=0.4\textwidth]{pictures/tie256-VN-flat-edge} &
-            \includegraphics[width=0.4\textwidth]{pictures/tie256-VN-flat} \\
+            \includegraphics[width=0.43\textwidth]{pictures/tie256-VN-flat-edge} &
+            \includegraphics[width=0.43\textwidth]{pictures/tie256-VN-flat} \\
             %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-NV} &

### 2025-04-25 DGMM2025/paper.tex
fix caption normals colormap

@@
         \input{pointelscomptime.tikz}
-        \caption{Computation Time of Visibility as a Function of Grid Resolution}
+        \caption{Computation Time of Visibility as a Function of pointels amount. We compare the computation time of
+        the naive breadth first visibility algorithm against our version using intervals. We input the same radius to
+        both versions (10, 20, 30) and test it on 6 different figures (goursat, torus, rcube, sphere9, leopold, d20)
+        with various gridsteps, giving us figures with pointel amounts ranging from 520 to 390235.}
         \label{fig:meanvisibility-computationComplexity}
@@
         \end{tabular}
-        \caption{Examples of normals computed on a chinese dragon, then on an
-        octaflower as a color map. First set displays II normals, second set
+        \caption{Examples of normals computed on a cps, then on an
+        tie as a color map. First set displays II normals, second set
         uses the visibility algorithm to compute them. The normals are colored

### 2025-04-25 DGMM2025/paper.tex
fix caption normals colormap
Update text in 4

@@
         \end{tabular}
-        \caption{Examples of normals computed on a cps, then on an
+        \caption{Examples of normals computed on a cps, then on a
         tie as a color map. First set displays II normals, second set
@@
 
-    II estimator is good along digitization of smooth or flat parts of
+    The II estimator is good along digitization of smooth or flat parts of
     the dice, but presents curious artefacts near sharp features
@@
 
-    CTriv estimator only performs averaging of trivial normal
+    The CTriv estimator only performs averaging of trivial normal
     directions along the surface. It behaves much better than II near
@@
 
-    VN estimator takes the best of the two previous approaches. It
+    The VN estimator takes the best of the two previous approaches. It
     remains precise and stable on smooth and flat regions, while
     perfectly delineating sharp features and holes, whatever the kind
-    of estimated curvatures. Its only drawback is the computation
-    time, which is [TO COMPLETE], compared to $2.3$s for II and $0.1s$
-    for CTriv.
+    of estimated curvatures. Its drawback is the computation time,
+    which is $52s$ for a maximal visibility distance $8$, compared to
+    $2.3$s for II and $0.1s$ for CTriv. Note that the computation time
+    falls back to $33s$ for a maximal distance of $6$ (and same
+    $\sigma=4$) while the result is visually indistinguishable.
 

### 2025-04-25 DGMM2025/conclusion.tex
Add conclusion

We have proposed a new algorithm that computes the visibility between
all pairs of points on a digital surface. It uses the specificity of a
structure to represent sets of lattice points or cells, a mapping from
projected coordinates to list of integer intervals. Compared to a
classical breadth-first approach to compute visibility, it provides
the exact visibility result, even when when the set of visible points
from a source is disconnected. As shown by experiments the running
times are comparable with the breadth-first algorithm, and even faster
for small maximal visibility distance, which are typical when
processing standard 3d images up to $512^3$. We have used visibility
to define a discrete tangent estimator that respects salient features
while giving good approximations on digitization of smooth parts. The
obtained normal field is more suitable to curvature estimation than
the classical Integral Invariant normal estimator.

We have several ideas for possible future works. First, it is possible
to speed-up the identification of non visibility by a coarse-to-fine
approach and a precomputation of a pyramid of covering cells. We would
like to explore if we can build such a pyramid variant of our
algorithm, considering the primitive vectors as a hierarchy. Second we
would like to prove the muligrid convergence of our normal estimator,
which is observable on experiments. Last, our algorithm is not limited
to pairwise visibility, but is more an algorithm of exact pattern
matching. We would like to explore new applications of pattern
identification along digital surfaces (like corner detection, locally
convex zones identification, etc).

### 2025-04-25 DGMM2025/paper.tex
Add conclusion
error computation

@@
     \section{Fast computation using integer intervals intersections}
-
-    To improve computation time, we will use lattice maps of integer intervals.
-
-    \begin{definition}
-        A sequence of intervals is an ordered list of intervals $L = ([a_i,b_i])_{i=1,\ldots,n}$ such that $b_i + 1 < a_{i+1}$, i.e., disjoint intervals with at least a missing integer.
-    \end{definition}
-
-    \begin{definition}
-        A translation of an interval $A$ is defined as $A+t \coloneqq [a+t, b+t]$
-    \end{definition}
-
-    \begin{definition}
-        A translation of a sequence of intervals $L$ is the sequence defined as $L+t \coloneqq \{L_1+t,\ldots,L_n+t\}$
-    \end{definition}
-
-    \begin{definition}
-        All translations $T$ of an interval or a sequence of intervals $A$ in a sequence of intervals $L$ are defined as $ T \coloneqq \{ t, st. A+t \subset L\}$
-    \end{definition}
-
-    We will consider lattice maps as pairs of (shift, intervals), where shifts are points $p \in \R^{d-1}$.
-All coordinates are doubled, so that the represented cell $\forall c \in \R^d$ will have a dimension equal to $\sum_{i=1}^d \left(c[i]\mod d\right)$.
-    In figure~\ref{fig:lattice-representation}, we display a representation of lattice maps applied to a 2-d cell complex where all coordinates are already doubled.
-Note that the examples are in 2-d, the shown results are in 3-d and the algorithm is for n-d.
-
-    \begin{figure}
-        \centering
-        \label{fig:lattice-representation}
-        % \usetikzlibrary {arrows.meta,decorations.shapes}
-        \begin{tabular}{c c}
-            \begin{tikzpicture}[scale=0.75]
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.25,-0.25) grid (7.25,7.25);
-                \filldraw[black] (1,4) circle (0.05);
-                \filldraw[black] (1,5) circle (0.05);
-                \filldraw[black] (2,5) circle (0.05);
-                \filldraw[black] (3,5) circle (0.05);
-                \filldraw[black] (3,4) circle (0.05);
-                \filldraw[black] (3,3) circle (0.05);
-                \filldraw[black] (3,2) circle (0.05);
-                \filldraw[black] (2,2) circle (0.05);
-                \filldraw[black] (2,1) circle (0.05);
-                \filldraw[black] (1,1) circle (0.05);
-                \filldraw[black] (1,0) circle (0.05);
-                \filldraw[black] (2,0) circle (0.05);
-                \filldraw[black] (3,0) circle (0.05);
-                \filldraw[black] (3,1) circle (0.05);
-                \filldraw[black] (4,1) circle (0.05);
-                \filldraw[black] (5,1) circle (0.05);
-                \draw[-{Stealth[length=3mm]}=black] (-1,-1) -- (-1,6.5);
-                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=21.5pt}] {(-1,-1) -- (-1,7)};
-                \draw[black] (1,4) -- (1,5) -- (3,5) -- (3,2) -- (2,2) -- (2,1) -- (1,1) -- (1,0) -- (3,0) -- (3,1) -- (5,1);
-                \draw[thick,dashed] (1,3) -- (1,2) -- (0,2) -- (0,-1) -- (4,-1) -- (4,0) -- (6,0) -- (6,2) -- (4,2) -- (4,6) -- (0,6) -- (0,3) -- (2,3) -- (2,4);
-            \end{tikzpicture} &
-            %      \begin{tikzpicture}
-            %     \foreach \y in {1,1.5,...,6} {
-            %       \draw[thin, lightgray,xshift=-1cm,yshift=-1cm] (0.75,\y) -- (6.25,\y);
-            %     }
-            %     \draw[-{Stealth[length=3mm]}=black] (0,0) -- (0,5.5);
-            %     \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=10mm}] {(0,0) -- (0,5)};
-            %     \draw[black] (1,4) -- (1,5) -- (3,5) -- (3,2) -- (2,2) -- (2,1) -- (1,1) -- (1,0) -- (3,0) -- (3,1) -- (5,1);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,5)--(3.1,5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,4.5)--(1.1,4.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,4.5)--(3.1,4.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,4)--(1.1,4);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,4)--(3.1,4);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,3.5)--(3.1,3.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,3)--(3.1,3);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,2.5)--(3.1,2.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.9,2)--(3.1,2);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.9,1.5)--(2.1,1.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,1)--(2.1,1);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,1)--(5.1,1);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,0.5)--(1.1,0.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,0.5)--(3.1,0.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,0)--(3.1,0);
-            %     \filldraw[white,yshift=-1cm] (0,0) circle (0.01); % readjust the height to match the original path
-            % \end{tikzpicture} &
-            \begin{tikzpicture}[scale=0.75]
-                \foreach \y in {0,0.5,...,7} {
-                    \draw[thin, lightgray,xshift=-1cm,yshift=-1cm] (-0.25,\y) -- (7.25,\y);
-                }
-                \draw[-{Stealth[length=3mm]}=black] (-1,-1) -- (-1,6.5);
-                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=21.5pt}] {(-1,-1) -- (-1,6.5)};
-                \draw[thick,dashed] (1,3) -- (1,2) -- (0,2) -- (0,-1) -- (4,-1) -- (4,0) -- (6,0) -- (6,2) -- (4,2) -- (4,6) -- (0,6) -- (0,3) -- (2,3) -- (2,4);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,5.5)--(3.6,5.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,5)--(3.6,5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,4.5)--(3.6,4.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,4)--(1.6,4);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,4)--(3.6,4);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,3.5)--(1.6,3.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,3.5)--(3.6,3.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,3)--(3.6,3);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2.5)--(3.6,2.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2)--(3.6,2);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,1.5)--(5.6,1.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,1)--(5.6,1);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,0.5)--(5.6,0.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,0)--(3.6,0);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,-0.5)--(3.6,-0.5);
-                \filldraw[white,yshift=-1.25cm] (0,0) circle (0.01); % readjust the height to match the original path
-            \end{tikzpicture}
-        \end{tabular}
-        \caption{Representation of a 2d cell complex (here the star of a given curve) as a lattice map. From 31 cells from the star on the left, we get 15 intervals on the right}
-    \end{figure}
-
-    \colorlet{MyGreen}{green!80!gray}
-    \begin{figure}
-        \centering
-        \begin{tabular}{c c}
-            \begin{tikzpicture}[scale=0.75]
-                \foreach[count=\i] \y in {-0.5,0,...,1.5} {
-                    \draw (0,0) node at (-1.25,\y) {\i};
-                }
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.75,-0.25) grid (12.25,3.25);
-                \draw[-{Stealth[length=3mm]}=black] (-1.5,-1) -- (-1.5,2.5);
-                \filldraw[black] (0,0) circle (0.05);
-                \filldraw[black] (1,0) circle (0.05);
-                \filldraw[black] (2,0) circle (0.05);
-                \filldraw[black] (2,1) circle (0.05);
-                \filldraw[black] (3,1) circle (0.05);
-                \filldraw[black] (4,1) circle (0.05);
-                \filldraw[black] (5,1) circle (0.05);
-                \filldraw[black] (5,0) circle (0.05);
-                \filldraw[black] (6,0) circle (0.05);
-                \filldraw[black] (7,0) circle (0.05);
-                \filldraw[black] (7,1) circle (0.05);
-                \filldraw[black] (8,1) circle (0.05);
-                \filldraw[black] (8,0) circle (0.05);
-                \filldraw[black] (9,0) circle (0.05);
-                \filldraw[black] (10,0) circle (0.05);
-                \filldraw[black] (10,1) circle (0.05);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,-0.5)--(2.6,-0.5);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,-0.5)--(10.6,-0.5);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0)--(2.6,0);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,0)--(10.6,0);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(10.6,0.5);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1)--(5.6,1);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1)--(8.6,1);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1)--(10.6,1);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(5.6,1.5);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1.5)--(8.6,1.5);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1.5)--(10.6,1.5);
-                \draw[thick, black] (0,0) -- (2,0) -- (2,1) -- (5,1) -- (5,0) -- (7,0) -- (7,1) -- (8,1) -- (8,0) -- (10,0) -- (10,1);
-                \draw[thick,dashed] (6,1) -- (6,2);
-                \draw[thick,dashed] (9,1) -- (9,2);
-                \draw[thick,dashed] (-1,-1) -- (-1,1) -- (1,1) -- (1,2) -- (11,2) -- (11,-1) -- (4,-1) -- (4,0) -- (3,0) -- (3,-1) -- (-1,-1);
-
-                \draw (0,0) node at (-0.25,1.75) {F};
-
-                \draw[red,arrows = {-Stealth[]}] (0,0)--(2,1);
-                \draw[red,arrows = {-Stealth[]}] (1,0)--(3,1);
-                \draw[red,arrows = {-Stealth[]}] (2,0)--(4,1);
-                \draw[red,arrows = {-Stealth[]}] (5,0)--(7,1);
-                \draw[red,arrows = {-Stealth[]}] (6,0)--(8,1);
-                \draw[red,arrows = {-Stealth[]}] (8,0)--(10,1);
-
-            \end{tikzpicture} &
-            \begin{tikzpicture}[scale=0.75]
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.75,-0.25) grid (4.25,3.25);
-                \draw[-{Stealth[length=3mm]}=black] (-1.5,-1) -- (-1.5,2.5);
-                \foreach[count=\i] \y in {-0.5,0,...,1.5} {
-                    \draw (0,0) node at (-1.25,\y) {\i};
-                }
-                \filldraw[black] (0,0) circle (0.05);
-                \filldraw[black] (2,1) circle (0.05);
-                \draw[thick, black] (0,0) -- (2,1);
-                \draw[thick,dashed] (-1,-1) -- (-1,1) -- (1,1) -- (1,2) -- (3,2) -- (3,0) -- (1,0) --  (1,-1) -- (-1,-1);
-                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,-0.5)--(0.6,-0.5);
-                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0)--(0.6,0);
-                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(2.6,0.5);
-                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1)--(2.6,1);
-                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(2.6,1.5);
-
-                \draw (0,0) node at (-0.25,1.75) {V};
-            \end{tikzpicture} \\
-            \hline
-            \multicolumn{2}{c}{
-                \begin{tikzpicture}[scale=0.75]
-                    \foreach \y in {0,0.5,...,12.5} {
-                        \draw[thin, lightgray] (-1.25,\y) -- (11.25,\y);
-                    }
-                    \foreach \y in {0,2.5,...,12.5} {
-                        \draw[blue] (-7,\y) -- (11.25,\y);
-                    }
-
-                    \foreach[count=\i] \y in {12,9.5,...,2} {
-                        \draw (0,0) node at (-4,\y) {$V_{\i}$};
-                    }
-                    \foreach[count=\i] \y in {11.5,9,...,1.5} {
-                        \draw (0,0) node at (-4,\y) {$F_{\i}$};
-                    }
-                    \draw (0,0) node at (-4,11) {$T_{1} = \text{Translations}(V_{1},F_{1})$};
-                    \foreach[count=\i] \y in {8.5,6,...,1} {
-                        \draw (0,0) node at (-4,\y) {$T_{\the\numexpr\i+1\relax}$};
-                    }
-                    \draw (0,0) node at (-4,10.5) {$R_1 = T_1$};
-
-                    \foreach[count=\i] \y in {8,5.5,...,0.5} {
-
-                        \draw (0,0) node at (-4,\y) {$R_{\the\numexpr\i+1\relax} = T_{\the\numexpr\i+1\relax} \cap R_{\i}$};
-                    }
-
-                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,12)--(0.6,12);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,11.5)--(2.6,11.5);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,11.5)--(10.6,11.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,11)--(1.6,11);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,11)--(9.6,11);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,10.5)--(1.6,10.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,10.5)--(9.6,10.5);
-                    \filldraw[black] (-0.5,10.5) circle (0.05);
-                    \filldraw[black] (0.5,10.5) circle (0.05);
-                    \filldraw[black] (1.5,10.5) circle (0.05);
-                    \filldraw[black] (4.5,10.5) circle (0.05);
-                    \filldraw[black] (5.5,10.5) circle (0.05);
-                    \filldraw[black] (6.5,10.5) circle (0.05);
-                    \filldraw[black] (7.5,10.5) circle (0.05);
-                    \filldraw[black] (8.5,10.5) circle (0.05);
-                    \filldraw[black] (9.5,10.5) circle (0.05);
-
-                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9.5)--(0.6,9.5);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9)--(2.6,9);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,9)--(10.6,9);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,8.5)--(1.6,8.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,8.5)--(9.6,8.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,8)--(1.6,8);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,8)--(9.6,8);
-                    \filldraw[black] (-0.5,8) circle (0.05);
-                    \filldraw[black] (0.5,8) circle (0.05);
-                    \filldraw[black] (1.5,8) circle (0.05);
-                    \filldraw[black] (4.5,8) circle (0.05);
-                    \filldraw[black] (5.5,8) circle (0.05);
-                    \filldraw[black] (6.5,8) circle (0.05);
-                    \filldraw[black] (7.5,8) circle (0.05);
-                    \filldraw[black] (8.5,8) circle (0.05);
-                    \filldraw[black] (9.5,8) circle (0.05);
-
-                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,7)--(2.6,7);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,6.5)--(10.6,6.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,6)--(7.6,6);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,5.5)--(1.6,5.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,5.5)--(7.6,5.5);
-                    \filldraw[black] (-0.5,5.5) circle (0.05);
-                    \filldraw[black] (0.5,5.5) circle (0.05);
-                    \filldraw[black] (1.5,5.5) circle (0.05);
-                    \filldraw[black] (4.5,5.5) circle (0.05);
-                    \filldraw[black] (5.5,5.5) circle (0.05);
-                    \filldraw[black] (6.5,5.5) circle (0.05);
-                    \filldraw[black] (7.5,5.5) circle (0.05);
-
-                    \draw[thick,black,arrows = {-Stealth[]}] (-0.6,4.5)--(1.4,4.5);
-                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,4.5)--(2.6,4.5);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,4)--(5.6,4);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,4)--(8.6,4);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,4)--(10.6,4);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,3.5)--(2.6,3.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,3.5)--(5.6,3.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,3.5)--(7.6,3.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,3)--(1.6,3);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,3)--(5.6,3);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,3)--(7.6,3);
-                    \filldraw[black] (-0.5,3) circle (0.05);
-                    \filldraw[black] (0.5,3) circle (0.05);
-                    \filldraw[black] (1.5,3) circle (0.05);
-                    \filldraw[black] (4.5,3) circle (0.05);
-                    \filldraw[black] (5.5,3) circle (0.05);
-                    \filldraw[black] (7.5,3) circle (0.05);
-
-                    \draw[thick,black,arrows = {-Stealth[]}] (-0.6,2)--(1.4,2);
-                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2)--(2.6,2);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(5.6,1.5);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1.5)--(8.6,1.5);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1.5)--(10.6,1.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,1)--(2.6,1);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,1)--(5.6,1);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,1)--(7.6,1);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(1.6,0.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,0.5)--(5.6,0.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,0.5)--(7.6,0.5);
-                    \filldraw[black] (-0.5,0.5) circle (0.05);
-                    \filldraw[black] (0.5,0.5) circle (0.05);
-                    \filldraw[black] (1.5,0.5) circle (0.05);
-                    \filldraw[black] (4.5,0.5) circle (0.05);
-                    \filldraw[black] (5.5,0.5) circle (0.05);
-                    \filldraw[black] (7.5,0.5) circle (0.05);
-
-                \end{tikzpicture}}
-        \end{tabular}
-        \caption{Evolution of the visibility check algorithm for a 2,1 vector.
-Green is the vector lattice map, black is the figure lattice map, red are the current intervals of positions where the visibility is still possible.
-The last red intervals are the visible positions.
-We travel the lattice maps from bottom-up.
-The found possible visibilities are shown on the original figure}
-        \label{fig:visibility-algorithm-evolution}
-    \end{figure}
-
-    \begin{algorithm}
-        \caption{Given a cell complex C and a radius $r$, compute the visibility at every point of C up to distance $r$.
-We assume z being the main axis of the lattice maps, x and y being the auxiliary axises}
-        \label{alg:visibility}
-        \begin{algorithmic}
-            \Function{Visibility}{C: Cell complex, r: Integer}
-                \State $\Omega \gets \Call{Star}{C}$ \Comment{Lattice map of the star of the studied cell complex}
-                \State $Directions \gets \Call{GetAllPrimalDirections}{r}$
-                \State $V: \text{vector of boolean} \gets [0, \ldots, 0]$ \Comment{length $Size(Directions) \times \#C.pointels$}
-                \State $low, high \gets \Call{BoundingBoxZ}{\Omega}$
-                \ForAll{$d$ in $Directions$}
-                    \ForAll{shift $S$ in $\Omega$}
-                        \State $R \gets [low, high]$
-                        \ForAll{pair $P$ in $\Call{Star}{\text{d}}$}
-                            \State $R \gets R \cap \Call{Translations}{P.intervals,\Omega[S + P.shift]}$
-                        \EndFor
-                        \State \Call{UpdateVisibility}{$V$, $R$}
-                    \EndFor
-                \EndFor
-                \State \Return $V$
-            \EndFunction
-        \end{algorithmic}
-    \end{algorithm}
-
-    In order to compute the visibility, we first compute $\Omega = \text{Star}(C)$. Then for each primal direction of
-    coordinates at most $r$, we look at all the possible positions this specific direction does link 2 visible points
-    of the cell complex. In order to do so, for each shift in $\Omega$, we compute the positions where points are
-    visible using the same method as presented in~\ref{fig:visibility-algorithm-evolution}. Some results of visible
-    points are present in figure~\ref{fig:visibility-results}.
-
-    \begin{algorithm}
-        \caption{Given 2 lists of intervals $K$ and $L$, find $K \cap L$, the intersection of those 2 lists}
-        \label{alg:intersection}
-        \begin{algorithmic}
-            \Function{Intersection ($\cap$)}{\text{K, L}: Intervals}
-                \State $R \gets \emptyset$; $k, l \gets 0$
-                \While{$k < K.nbIntervals \And l < L.nbIntervals$}
-                    \State $[a,b] \gets K[k]$; $[c,d] \gets L[l]$
-                    \State $e \gets \max(a, c)$; $f \gets \min(b, d)$
-                    \If{$e \leq f$}
-                        \State $R.append([e, f])$
-                    \EndIf
-                    \If{$b \leq d$}
-                        \State $k \gets k+1$
-                    \EndIf
-                    \If{$d \leq b$}
-                        \State $l \gets l+1$
-                    \EndIf
-                \EndWhile
-                \State \Return $R$
-            \EndFunction
-        \end{algorithmic}
-    \end{algorithm}
-
-    To efficiently compute the intersection of 2 lists of intervals $K$ and $L$, we go through the first 2 unvisited
-    elements of the 2 lists. If they don't overlap (i.e.\ the start and end of the 1st interval are both smaller than
-    the start of the other), then we can discard the smaller interval. Else, we construct the intersection of these
-    2 intervals as one of the resulting intervals. We then can skip the interval with the smallest end. If both
-    intervals have the same end, then both intervals can be skipped. Doing this computation until one of the lists
-    is empty returns the intersection of both lists of intervals.
-
-    % Insert visibility results images
-
-    \begin{figure}
-        \centering
-        \begin{tabular}{c c}
-            \includegraphics[width=0.4\textwidth]{pictures/visibility_from_given_point_r_10} &
-            \includegraphics[width=0.4\textwidth]{pictures/visibility_aware_of_features}
-        \end{tabular}
-        \caption{Examples of visibility on a fandisk and a torus knot. First one is on the edge
-        of a fandisk, where the visibility stops at the edges. The other one is in the interior
-        of a torus knot, where we can see that the visibility is feature-aware and doesn't see
-        the other side of the torus' branch.}
-        \label{fig:visibility-results}
-    \end{figure}
-%
-%    \begin{figure}
-%        \begin{center}
-%            \includegraphics[width=0.8\textwidth]{pictures/visibility_from_given_point_r_10}
-%            \caption{Visibility of a point on an edge of a fandisk}
-%            \label{fig:visibility-fandisk}
-%        \end{center}
-%    \end{figure}
-%    \begin{figure}
-%        \begin{center}
-%            \includegraphics[width=0.8\textwidth]{pictures/visibility_aware_of_features}
-%            \caption{Visibility of a point on a torus knot (the visibility is feature-aware)}
-%            \label{fig:visibility-torus-knot}
-%        \end{center}
-%    \end{figure}
-
-    % Quantitative results
-
-    \begin{figure}
-        \begin{tikzpicture}
-            \centering
-            \begin{axis}[
-                width=0.8\textwidth,
-                legend columns=3,
-                xlabel={Gridstep},
-                ylabel={Mean distance},
-                x dir=reverse,
-                legend pos=north west,
-                ymajorgrids=true,
-                grid style=dashed,
-                ymax=70,
-                ymode=log,
-                xmode=log,
-                log ticks with fixed point,
-            ]
-
-                \addplot[
-                    color=cyan,
-                ] coordinates {
-                    (0.0625,7.61948)(0.125,5.49755)(0.25,3.97418)(0.375,3.00921)(0.5,2.85702)(0.625,2.34448)(0.75,1.85023)(0.875,2.16868)(1.0,1.85023)
-                };
-                \addlegendentry{sphere1}
-                \addplot[
-                    color=red,
-                ] coordinates {
-                    (0.0625,38.1045)(0.125,26.8765)(0.25,19.6747)(0.375,16.6192)(0.5,14.0867)(0.625,12.5062)(0.75,11.3734)(0.875,10.2845)(1,8.90781)
-                };
-                \addlegendentry{goursat}
-                \addplot[
-                    color=violet,
-                ] coordinates {
-                    (0.0625,25.5024)(0.125,18.2364)(0.25,12.3975)(0.375,9.41303)(0.5,8.69558)(0.625,7.37667)(0.75,6.82131)(0.875,6.05735)(1,6.33877)
-                };
-                \addlegendentry{torus}
-                \addplot[
-                    color=MyGreen,
-                ] coordinates {
-                    (0.0625,27.9287)(0.125,17.5104)(0.25,10.8007)(0.375,8.69514)(0.5,7.26074)(0.625,6.2309)(0.75,5.6897)(0.875,5.28197)(1,4.96098)
-                };
-                \addlegendentry{leopold}
-                \addplot[
-                    color=yellow!80!black,
-                ] coordinates {
-                    (0.0625,41.9816)(0.125,27.7104)(0.25,18.2339)(0.375,14.6475)(0.5,12.3618)(0.625,9.55647)(0.75,9.83208)(0.875,7.51861)(1,7.99732)
-                };
-                \addlegendentry{rcube}
-                \addplot [
-                    color=black,
-                    thick,
-                    domain=0.0625:1,
-                    samples=100,
-                ] {x^(-0.5)};
-                \addlegendentry{$\sqrt{h}=\sqrt{\frac{1}{x}}$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Mean Visibility Distance as a Function of Grid Resolution}
-        \label{fig:meanvisibility-gridstep}
-    \end{figure}
-
-    \begin{figure}[t]
-        \input{pointelscomptime.tikz}
-        \caption{Computation Time of Visibility as a Function of pointels amount. We compare the computation time of
-        the naive breadth first visibility algorithm against our version using intervals. We input the same radius to
-        both versions (10, 20, 30) and test it on 6 different figures (goursat, torus, rcube, sphere9, leopold, d20)
-        with various gridsteps, giving us figures with pointel amounts ranging from 520 to 390235.}
-        \label{fig:meanvisibility-computationComplexity}
-    \end{figure}
+    \input{computation}
 
@@
     of the visible points, corresponding to its smallest
-    eigenvalue. Its orientation is chosen so as to point in the same
+    eigenvalue. Its orientation is chosen to point in the same
     direction as the average of the trivial normals to the surfels
@@
     \section{Conclusion}
+    \input{conclusion.tex}
 

### 2025-04-25 DGMM2025/computation.tex
Split into files

    To improve computation time, we will use lattice maps of integer intervals.

    \begin{definition}
        A sequence of intervals is an ordered list of intervals $L = ([a_i,b_i])_{i=1,\ldots,n}$ such that $b_i + 1 < a_{i+1}$, i.e., disjoint intervals with at least a missing integer.
    \end{definition}

    \begin{definition}
        A translation of an interval $A$ is defined as $A+t \coloneqq [a+t, b+t]$
    \end{definition}

    \begin{definition}
        A translation of a sequence of intervals $L$ is the sequence defined as $L+t \coloneqq \{L_1+t,\ldots,L_n+t\}$
    \end{definition}

    \begin{definition}
        All translations $T$ of an interval or a sequence of intervals $A$ in a sequence of intervals $L$ are defined as $ T \coloneqq \{ t, st. A+t \subset L\}$
    \end{definition}

    We will consider lattice maps as pairs of (shift, intervals), where shifts are points $p \in \R^{d-1}$. All coordinates are doubled, so that the represented cell $\forall c \in \R^d$ will have a dimension equal to $\sum_{i=1}^d \left(c[i]\mod d\right)$.
    In figure~\ref{fig:lattice-representation}, we display a representation of lattice maps applied to a 2-d cell complex where all coordinates are already doubled. Note that the examples are in 2-d, the shown results are in 3-d and the algorithm is for n-d.

    \begin{figure}
        \centering
        \label{fig:lattice-representation}
        % \usetikzlibrary {arrows.meta,decorations.shapes}
        \begin{tabular}{c c}
            \begin{tikzpicture}[scale=0.75]
                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.25,-0.25) grid (7.25,7.25);
                \filldraw[black] (1,4) circle (0.05);
                \filldraw[black] (1,5) circle (0.05);
                \filldraw[black] (2,5) circle (0.05);
                \filldraw[black] (3,5) circle (0.05);
                \filldraw[black] (3,4) circle (0.05);
                \filldraw[black] (3,3) circle (0.05);
                \filldraw[black] (3,2) circle (0.05);
                \filldraw[black] (2,2) circle (0.05);
                \filldraw[black] (2,1) circle (0.05);
                \filldraw[black] (1,1) circle (0.05);
                \filldraw[black] (1,0) circle (0.05);
                \filldraw[black] (2,0) circle (0.05);
                \filldraw[black] (3,0) circle (0.05);
                \filldraw[black] (3,1) circle (0.05);
                \filldraw[black] (4,1) circle (0.05);
                \filldraw[black] (5,1) circle (0.05);
                \draw[-{Stealth[length=3mm]}=black] (-1,-1) -- (-1,6.5);
                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=21.5pt}] {(-1,-1) -- (-1,7)};
                \draw[black] (1,4) -- (1,5) -- (3,5) -- (3,2) -- (2,2) -- (2,1) -- (1,1) -- (1,0) -- (3,0) -- (3,1) -- (5,1);
                \draw[thick,dashed] (1,3) -- (1,2) -- (0,2) -- (0,-1) -- (4,-1) -- (4,0) -- (6,0) -- (6,2) -- (4,2) -- (4,6) -- (0,6) -- (0,3) -- (2,3) -- (2,4);
            \end{tikzpicture} &
            %      \begin{tikzpicture}
            %     \foreach \y in {1,1.5,...,6} {
            %       \draw[thin, lightgray,xshift=-1cm,yshift=-1cm] (0.75,\y) -- (6.25,\y);
            %     }
            %     \draw[-{Stealth[length=3mm]}=black] (0,0) -- (0,5.5);
            %     \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=10mm}] {(0,0) -- (0,5)};
            %     \draw[black] (1,4) -- (1,5) -- (3,5) -- (3,2) -- (2,2) -- (2,1) -- (1,1) -- (1,0) -- (3,0) -- (3,1) -- (5,1);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,5)--(3.1,5);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,4.5)--(1.1,4.5);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,4.5)--(3.1,4.5);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,4)--(1.1,4);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,4)--(3.1,4);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,3.5)--(3.1,3.5);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,3)--(3.1,3);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,2.5)--(3.1,2.5);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.9,2)--(3.1,2);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.9,1.5)--(2.1,1.5);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,1)--(2.1,1);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,1)--(5.1,1);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,0.5)--(1.1,0.5);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,0.5)--(3.1,0.5);
            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,0)--(3.1,0);
            %     \filldraw[white,yshift=-1cm] (0,0) circle (0.01); % readjust the height to match the original path
            % \end{tikzpicture} &
            \begin{tikzpicture}[scale=0.75]
                \foreach \y in {0,0.5,...,7} {
                    \draw[thin, lightgray,xshift=-1cm,yshift=-1cm] (-0.25,\y) -- (7.25,\y);
                }
                \draw[-{Stealth[length=3mm]}=black] (-1,-1) -- (-1,6.5);
                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=21.5pt}] {(-1,-1) -- (-1,6.5)};
                \draw[thick,dashed] (1,3) -- (1,2) -- (0,2) -- (0,-1) -- (4,-1) -- (4,0) -- (6,0) -- (6,2) -- (4,2) -- (4,6) -- (0,6) -- (0,3) -- (2,3) -- (2,4);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,5.5)--(3.6,5.5);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,5)--(3.6,5);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,4.5)--(3.6,4.5);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,4)--(1.6,4);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,4)--(3.6,4);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,3.5)--(1.6,3.5);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,3.5)--(3.6,3.5);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,3)--(3.6,3);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2.5)--(3.6,2.5);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2)--(3.6,2);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,1.5)--(5.6,1.5);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,1)--(5.6,1);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,0.5)--(5.6,0.5);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,0)--(3.6,0);
                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,-0.5)--(3.6,-0.5);
                \filldraw[white,yshift=-1.25cm] (0,0) circle (0.01); % readjust the height to match the original path
            \end{tikzpicture}
        \end{tabular}
        \caption{Representation of a 2d cell complex (here the star of a given curve) as a lattice map. From 31 cells from the star on the left, we get 15 intervals on the right}
    \end{figure}

    \colorlet{MyGreen}{green!80!gray}
    \begin{figure}
        \centering
        \begin{tabular}{c c}
            \begin{tikzpicture}[scale=0.75]
                \foreach[count=\i] \y in {-0.5,0,...,1.5} {
                    \draw (0,0) node at (-1.25,\y) {\i};
                }
                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.75,-0.25) grid (12.25,3.25);
                \draw[-{Stealth[length=3mm]}=black] (-1.5,-1) -- (-1.5,2.5);
                \filldraw[black] (0,0) circle (0.05);
                \filldraw[black] (1,0) circle (0.05);
                \filldraw[black] (2,0) circle (0.05);
                \filldraw[black] (2,1) circle (0.05);
                \filldraw[black] (3,1) circle (0.05);
                \filldraw[black] (4,1) circle (0.05);
                \filldraw[black] (5,1) circle (0.05);
                \filldraw[black] (5,0) circle (0.05);
                \filldraw[black] (6,0) circle (0.05);
                \filldraw[black] (7,0) circle (0.05);
                \filldraw[black] (7,1) circle (0.05);
                \filldraw[black] (8,1) circle (0.05);
                \filldraw[black] (8,0) circle (0.05);
                \filldraw[black] (9,0) circle (0.05);
                \filldraw[black] (10,0) circle (0.05);
                \filldraw[black] (10,1) circle (0.05);
                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,-0.5)--(2.6,-0.5);
                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,-0.5)--(10.6,-0.5);
                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0)--(2.6,0);
                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,0)--(10.6,0);
                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(10.6,0.5);
                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1)--(5.6,1);
                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1)--(8.6,1);
                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1)--(10.6,1);
                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(5.6,1.5);
                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1.5)--(8.6,1.5);
                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1.5)--(10.6,1.5);
                \draw[thick, black] (0,0) -- (2,0) -- (2,1) -- (5,1) -- (5,0) -- (7,0) -- (7,1) -- (8,1) -- (8,0) -- (10,0) -- (10,1);
                \draw[thick,dashed] (6,1) -- (6,2);
                \draw[thick,dashed] (9,1) -- (9,2);
                \draw[thick,dashed] (-1,-1) -- (-1,1) -- (1,1) -- (1,2) -- (11,2) -- (11,-1) -- (4,-1) -- (4,0) -- (3,0) -- (3,-1) -- (-1,-1);

                \draw (0,0) node at (-0.25,1.75) {F};

                \draw[red,arrows = {-Stealth[]}] (0,0)--(2,1);
                \draw[red,arrows = {-Stealth[]}] (1,0)--(3,1);
                \draw[red,arrows = {-Stealth[]}] (2,0)--(4,1);
                \draw[red,arrows = {-Stealth[]}] (5,0)--(7,1);
                \draw[red,arrows = {-Stealth[]}] (6,0)--(8,1);
                \draw[red,arrows = {-Stealth[]}] (8,0)--(10,1);

            \end{tikzpicture} &
            \begin{tikzpicture}[scale=0.75]
                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.75,-0.25) grid (4.25,3.25);
                \draw[-{Stealth[length=3mm]}=black] (-1.5,-1) -- (-1.5,2.5);
                \foreach[count=\i] \y in {-0.5,0,...,1.5} {
                    \draw (0,0) node at (-1.25,\y) {\i};
                }
                \filldraw[black] (0,0) circle (0.05);
                \filldraw[black] (2,1) circle (0.05);
                \draw[thick, black] (0,0) -- (2,1);
                \draw[thick,dashed] (-1,-1) -- (-1,1) -- (1,1) -- (1,2) -- (3,2) -- (3,0) -- (1,0) --  (1,-1) -- (-1,-1);
                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,-0.5)--(0.6,-0.5);
                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0)--(0.6,0);
                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(2.6,0.5);
                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1)--(2.6,1);
                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(2.6,1.5);

                \draw (0,0) node at (-0.25,1.75) {V};
            \end{tikzpicture} \\
            \hline
            \multicolumn{2}{c}{
                \begin{tikzpicture}[scale=0.75]
                    \foreach \y in {0,0.5,...,12.5} {
                        \draw[thin, lightgray] (-1.25,\y) -- (11.25,\y);
                    }
                    \foreach \y in {0,2.5,...,12.5} {
                        \draw[blue] (-7,\y) -- (11.25,\y);
                    }

                    \foreach[count=\i] \y in {12,9.5,...,2} {
                        \draw (0,0) node at (-4,\y) {$V_{\i}$};
                    }
                    \foreach[count=\i] \y in {11.5,9,...,1.5} {
                        \draw (0,0) node at (-4,\y) {$F_{\i}$};
                    }
                    \draw (0,0) node at (-4,11) {$T_{1} = \text{Translations}(V_{1},F_{1})$};
                    \foreach[count=\i] \y in {8.5,6,...,1} {
                        \draw (0,0) node at (-4,\y) {$T_{\the\numexpr\i+1\relax}$};
                    }
                    \draw (0,0) node at (-4,10.5) {$R_1 = T_1$};

                    \foreach[count=\i] \y in {8,5.5,...,0.5} {

                        \draw (0,0) node at (-4,\y) {$R_{\the\numexpr\i+1\relax} = T_{\the\numexpr\i+1\relax} \cap R_{\i}$};
                    }

                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,12)--(0.6,12);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,11.5)--(2.6,11.5);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,11.5)--(10.6,11.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,11)--(1.6,11);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,11)--(9.6,11);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,10.5)--(1.6,10.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,10.5)--(9.6,10.5);
                    \filldraw[black] (-0.5,10.5) circle (0.05);
                    \filldraw[black] (0.5,10.5) circle (0.05);
                    \filldraw[black] (1.5,10.5) circle (0.05);
                    \filldraw[black] (4.5,10.5) circle (0.05);
                    \filldraw[black] (5.5,10.5) circle (0.05);
                    \filldraw[black] (6.5,10.5) circle (0.05);
                    \filldraw[black] (7.5,10.5) circle (0.05);
                    \filldraw[black] (8.5,10.5) circle (0.05);
                    \filldraw[black] (9.5,10.5) circle (0.05);

                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9.5)--(0.6,9.5);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9)--(2.6,9);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,9)--(10.6,9);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,8.5)--(1.6,8.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,8.5)--(9.6,8.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,8)--(1.6,8);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,8)--(9.6,8);
                    \filldraw[black] (-0.5,8) circle (0.05);
                    \filldraw[black] (0.5,8) circle (0.05);
                    \filldraw[black] (1.5,8) circle (0.05);
                    \filldraw[black] (4.5,8) circle (0.05);
                    \filldraw[black] (5.5,8) circle (0.05);
                    \filldraw[black] (6.5,8) circle (0.05);
                    \filldraw[black] (7.5,8) circle (0.05);
                    \filldraw[black] (8.5,8) circle (0.05);
                    \filldraw[black] (9.5,8) circle (0.05);

                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,7)--(2.6,7);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,6.5)--(10.6,6.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,6)--(7.6,6);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,5.5)--(1.6,5.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,5.5)--(7.6,5.5);
                    \filldraw[black] (-0.5,5.5) circle (0.05);
                    \filldraw[black] (0.5,5.5) circle (0.05);
                    \filldraw[black] (1.5,5.5) circle (0.05);
                    \filldraw[black] (4.5,5.5) circle (0.05);
                    \filldraw[black] (5.5,5.5) circle (0.05);
                    \filldraw[black] (6.5,5.5) circle (0.05);
                    \filldraw[black] (7.5,5.5) circle (0.05);

                    \draw[thick,black,arrows = {-Stealth[]}] (-0.6,4.5)--(1.4,4.5);
                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,4.5)--(2.6,4.5);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,4)--(5.6,4);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,4)--(8.6,4);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,4)--(10.6,4);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,3.5)--(2.6,3.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,3.5)--(5.6,3.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,3.5)--(7.6,3.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,3)--(1.6,3);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,3)--(5.6,3);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,3)--(7.6,3);
                    \filldraw[black] (-0.5,3) circle (0.05);
                    \filldraw[black] (0.5,3) circle (0.05);
                    \filldraw[black] (1.5,3) circle (0.05);
                    \filldraw[black] (4.5,3) circle (0.05);
                    \filldraw[black] (5.5,3) circle (0.05);
                    \filldraw[black] (7.5,3) circle (0.05);

                    \draw[thick,black,arrows = {-Stealth[]}] (-0.6,2)--(1.4,2);
                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2)--(2.6,2);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(5.6,1.5);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1.5)--(8.6,1.5);
                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1.5)--(10.6,1.5);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,1)--(2.6,1);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,1)--(5.6,1);
                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,1)--(7.6,1);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(1.6,0.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,0.5)--(5.6,0.5);
                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,0.5)--(7.6,0.5);
                    \filldraw[black] (-0.5,0.5) circle (0.05);
                    \filldraw[black] (0.5,0.5) circle (0.05);
                    \filldraw[black] (1.5,0.5) circle (0.05);
                    \filldraw[black] (4.5,0.5) circle (0.05);
                    \filldraw[black] (5.5,0.5) circle (0.05);
                    \filldraw[black] (7.5,0.5) circle (0.05);

                \end{tikzpicture}}
        \end{tabular}
        \caption{Evolution of the visibility check algorithm for a 2,1 vector. Green is the vector lattice map, black is the figure lattice map, red are the current intervals of positions where the visibility is still possible. The last red intervals are the visible positions. We travel the lattice maps from bottom-up. The found possible visibilities are shown on the original figure}
        \label{fig:visibility-algorithm-evolution}
    \end{figure}

    \begin{algorithm}
        \caption{Given a cell complex C and a radius $r$, compute the visibility at every point of C up to distance $r$. We assume z being the main axis of the lattice maps, x and y being the auxiliary axises}
        \label{alg:visibility}
        \begin{algorithmic}
            \Function{Visibility}{C: Cell complex, r: Integer}
                \State $\Omega \gets \Call{Star}{C}$ \Comment{Lattice map of the star of the studied cell complex}
                \State $Directions \gets \Call{GetAllPrimalDirections}{r}$
                \State $V: \text{vector of boolean} \gets [0, \ldots, 0]$ \Comment{length $Size(Directions) \times \#C.pointels$}
                \State $low, high \gets \Call{BoundingBoxZ}{\Omega}$
                \ForAll{$d$ in $Directions$}
                    \ForAll{shift $S$ in $\Omega$}
                        \State $R \gets [low, high]$
                        \ForAll{pair $P$ in $\Call{Star}{\text{d}}$}
                            \State $R \gets R \cap \Call{Translations}{P.intervals,\Omega[S + P.shift]}$
                        \EndFor
                        \State \Call{UpdateVisibility}{$V$, $R$}
                    \EndFor
                \EndFor
                \State \Return $V$
            \EndFunction
        \end{algorithmic}
    \end{algorithm}

    In order to compute the visibility, we first compute $\Omega = \text{Star}(C)$. Then for each primal direction of
    coordinates at most $r$, we look at all the possible positions this specific direction does link 2 visible points
    of the cell complex. In order to do so, for each shift in $\Omega$, we compute the positions where points are
    visible using the same method as presented in~\ref{fig:visibility-algorithm-evolution}. Some results of visible
    points are present in figure~\ref{fig:visibility-results}.

    \begin{algorithm}
        \caption{Given 2 lists of intervals $K$ and $L$, find $K \cap L$, the intersection of those 2 lists}
        \label{alg:intersection}
        \begin{algorithmic}
            \Function{Intersection ($\cap$)}{\text{K, L}: Intervals}
                \State $R \gets \emptyset$; $k, l \gets 0$
                \While{$k < K.nbIntervals \And l < L.nbIntervals$}
                    \State $[a,b] \gets K[k]$; $[c,d] \gets L[l]$
                    \State $e \gets \max(a, c)$; $f \gets \min(b, d)$
                    \If{$e \leq f$}
                        \State $R.append([e, f])$
                    \EndIf
                    \If{$b \leq d$}
                        \State $k \gets k+1$
                    \EndIf
                    \If{$d \leq b$}
                        \State $l \gets l+1$
                    \EndIf
                \EndWhile
                \State \Return $R$
            \EndFunction
        \end{algorithmic}
    \end{algorithm}

    To efficiently compute the intersection of 2 lists of intervals $K$ and $L$, we go through the first 2 unvisited
    elements of the 2 lists. If they don't overlap (i.e.\ the start and end of the 1st interval are both smaller than
    the start of the other), then we can discard the smaller interval. Else, we construct the intersection of these
    2 intervals as one of the resulting intervals. We then can skip the interval with the smallest end. If both
    intervals have the same end, then both intervals can be skipped. Doing this computation until one of the lists
    is empty returns the intersection of both lists of intervals.

    % Insert visibility results images

    \begin{figure}
        \centering
        \begin{tabular}{c c}
            \includegraphics[width=0.4\textwidth]{pictures/visibility_from_given_point_r_10} &
            \includegraphics[width=0.4\textwidth]{pictures/visibility_aware_of_features}
        \end{tabular}
        \caption{Examples of visibility on a fandisk and a torus knot. First one is on the edge
        of a fandisk, where the visibility stops at the edges. The other one is in the interior
        of a torus knot, where we can see that the visibility is feature-aware and doesn't see
        the other side of the torus' branch.}
        \label{fig:visibility-results}
    \end{figure}
%
%    \begin{figure}
%        \begin{center}
%            \includegraphics[width=0.8\textwidth]{pictures/visibility_from_given_point_r_10}
%            \caption{Visibility of a point on an edge of a fandisk}
%            \label{fig:visibility-fandisk}
%        \end{center}
%    \end{figure}
%    \begin{figure}
%        \begin{center}
%            \includegraphics[width=0.8\textwidth]{pictures/visibility_aware_of_features}
%            \caption{Visibility of a point on a torus knot (the visibility is feature-aware)}
%            \label{fig:visibility-torus-knot}
%        \end{center}
%    \end{figure}

    % Quantitative results

    \begin{figure}
        \begin{tikzpicture}
            \centering
            \begin{axis}[
                width=0.8\textwidth,
                legend columns=3,
                xlabel={Gridstep},
                ylabel={Mean distance},
                x dir=reverse,
                legend pos=north west,
                ymajorgrids=true,
                grid style=dashed,
                ymax=70,
                ymode=log,
                xmode=log,
                log ticks with fixed point,
            ]

                \addplot[
                    color=cyan,
                ] coordinates {
                    (0.0625,7.61948)(0.125,5.49755)(0.25,3.97418)(0.375,3.00921)(0.5,2.85702)(0.625,2.34448)(0.75,1.85023)(0.875,2.16868)(1.0,1.85023)
                };
                \addlegendentry{sphere1}
                \addplot[
                    color=red,
                ] coordinates {
                    (0.0625,38.1045)(0.125,26.8765)(0.25,19.6747)(0.375,16.6192)(0.5,14.0867)(0.625,12.5062)(0.75,11.3734)(0.875,10.2845)(1,8.90781)
                };
                \addlegendentry{goursat}
                \addplot[
                    color=violet,
                ] coordinates {
                    (0.0625,25.5024)(0.125,18.2364)(0.25,12.3975)(0.375,9.41303)(0.5,8.69558)(0.625,7.37667)(0.75,6.82131)(0.875,6.05735)(1,6.33877)
                };
                \addlegendentry{torus}
                \addplot[
                    color=MyGreen,
                ] coordinates {
                    (0.0625,27.9287)(0.125,17.5104)(0.25,10.8007)(0.375,8.69514)(0.5,7.26074)(0.625,6.2309)(0.75,5.6897)(0.875,5.28197)(1,4.96098)
                };
                \addlegendentry{leopold}
                \addplot[
                    color=yellow!80!black,
                ] coordinates {
                    (0.0625,41.9816)(0.125,27.7104)(0.25,18.2339)(0.375,14.6475)(0.5,12.3618)(0.625,9.55647)(0.75,9.83208)(0.875,7.51861)(1,7.99732)
                };
                \addlegendentry{rcube}
                \addplot [
                    color=black,
                    thick,
                    domain=0.0625:1,
                    samples=100,
                ] {x^(-0.5)};
                \addlegendentry{$\sqrt{h}=\sqrt{\frac{1}{x}}$}
            \end{axis}
        \end{tikzpicture}
        \caption{Mean Visibility Distance as a Function of Grid Resolution}
        \label{fig:meanvisibility-gridstep}
    \end{figure}

    \begin{figure}[t]
        \input{pointelscomptime.tikz}
        \caption{Computation Time of Visibility as a Function of pointels amount. We compare the computation time of
        the naive breadth first visibility algorithm against our version using intervals. We input the same radius to
        both versions (10, 20, 30) and test it on 6 different figures (goursat, torus, rcube, sphere9, leopold, d20)
        with various gridsteps, giving us figures with pointel amounts ranging from 520 to 390235.}
        \label{fig:meanvisibility-computationComplexity}
    \end{figure}

### 2025-04-25 DGMM2025/normalsandcurvature.tex
split into file section 4

--- 2025-04-25 DGMM2025/paper.tex
@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.21 of 2022/01/12
-%
-\documentclass[runningheads]{llncs}
-%\documentclass[draft]{llncs}
-%
-\usepackage[T1]{fontenc}
-% T1 fonts will be used to generate the final print and online PDFs,
-% so please use T1 fonts in your manuscript whenever possible.
-% Other font encondings may result in incorrect characters.
-%
-\usepackage{graphicx}
-\usepackage{hyperref}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following two lines
-% to display URLs in blue roman font according to Springer's eBook style:
-\usepackage{color}
-\renewcommand\UrlFont{\color{blue}\rmfamily}
-\urlstyle{rm}
-
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{tikz}
-\usepackage{wrapfig}
-\usepackage{environ}
-\usepackage{bbm}
-
-\usepackage{changes}
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-\usepackage{varwidth}
-\usepackage{mathtools}
-\usepackage{pgfplots}
-\usepackage[dvipsnames]{xcolor}
-\usepackage[utf8]{inputenc}
-\pgfplotsset{compat=1.18}
-\usetikzlibrary {spy,arrows.meta,decorations.shapes}
-\setauthormarkup{}
-\definechangesauthor[name=jo, color=blue]{JO}
-\definechangesauthor[name=rom, color=teal]{ROM}
-
-\input{./macros}
-
-%
-\begin{document}
-%
-    \title{Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation}
-%
-    \titlerunning{Fast and exact visibility on digitized shapes}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-    \author{Romain Negro\inst{1}\orcidID{0000-XXXX-YYYY-ZZZZ} \and
-    Jacques-Olivier Lachaud\inst{1}\orcidID{0000-0003-4236-2133}}
-%
-    \authorrunning{R. Negro and J.-O. Lachaud}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-    \institute{Universit\'e Savoie Mont Blanc, CNRS, LAMA, F-73000 Chambéry, France\\
-    \email{\{romain.negro|jacques-olivier.lachaud\}@univ-smb.fr}}
-%
-    \maketitle              % typeset the header of the contribution
-%
-    \begin{abstract}
-        Computing visibility on a geometric object requires heavy
-        computations since it requires to identify pairs of points that
-        are visible to each other, i.e.\ there is a straight segment
-        joining them that stays in the close vicinity of the object
-        boundary. We propose to exploit a specific representation of
-        digital sets based on lists of integral intervals in order to
-        compute efficiently the complete visibility graph between
-        lattice points of the digital shape. As a quite direct
-        application, we show then how we can use visibility to estimate
-        the normal vector field of a digital shape in an accurate and
-        convergent manner while staying aware of the salient and sharp features of
-        the shape.
-
-        \keywords{Visibility \and Geometric inference \and Digital normal estimation \and Digital geometry}
-    \end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-    \section{Introduction}
-    \input{introduction}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-    \section{Visibility through tangency of chords}
-    \input{visibility}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-    \section{Fast computation using integer intervals intersections}
-    \input{computation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-    \section{Saliency-aware normal and curvature estimation}
-
 \newcommand{\Kernel}[1]{\ensuremath{w_{\sigma}(#1)}}
@@
 of our normals compared to normals computed with the integral invariant (II) estimator~\cite{Lachaud:2017-lnm}.
+
+\begin{figure}
+
+\end{figure}
 
@@
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-    \section{Conclusion}
-    \input{conclusion.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \begin{credits}
-        \subsubsection{\ackname}
-        This work is partially supported by the French National Research Agency
-        within the StableProxies project (ANR-22-CE46-0006).
-%% \subsubsection{\discintname}
-%% It is now necessary to declare any competing interests or to specifically
-%% state that the authors have no competing interests. Please place the
-%% statement with a bold run-in heading in small font size beneath the
-%% (optional) acknowledgments\footnote{If EquinOCS, our proceedings submission
-%% system, is used, then the disclaimer can be provided directly in the system.},
-%% for example: The authors have no competing interests to declare that are
-%% relevant to the content of this article. Or: Author A has received research
-%% grants from Company W. Author B has received a speaker honorarium from
-%% Company X and owns stock in Company Y. Author C is a member of committee Z.
-    \end{credits}
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-    \bibliographystyle{splncs04}
-    \bibliography{biblio}
-
-\end{document}

### 2025-04-25 DGMM2025/paper.tex
Split into files
split into file section 4

@@
     \section{Saliency-aware normal and curvature estimation}
-
-    \newcommand{\Kernel}[1]{\ensuremath{w_{\sigma}(#1)}}
-
-    \paragraph{Saliency-aware normal estimator.}
-    We propose a new normal estimator on digital surfaces, which uses
-    the visibility of the point of interest while taking into account
-    a user-given scale $\sigma$. If $\sigma$ is proportionnal to the
-    average length between visible points (so some
-    $\Theta\left(\sqrt{h}\right)$), then this estimator is observed to be
-    multigrid convergent along digitization of smooth shapes. However,
-    since the computation window is limited by the visibility, it
-    better approximates the geometry near sharp or salient features.
-
-    More precisely, we choose a Gaussian function
-    $\Kernel{x}\coloneqq e^{-\frac{x^2}{2\sigma^2}}$ as a weight kernel. Let
-    $V_p$ be the set of visible points from the point $p$. Let $c_p$
-    be the weighted centroid of the visible points around $p$,
-    i.e. $c_p \coloneqq \frac{\sum_{q \in V_p} \Kernel{\|q-p\|}q}{\sum_{q \in
-    V_p} \Kernel{\|q-p\|}}$. We form the weighted covariance matrix
-    $\mathcal{V}_p$ of the points $V_p$ as:
-    \begin{equation}
-        \mathcal{V}_p = \sum_{q \in V_p} \Kernel{\|q-p\|}(q - c_p)(q - c_p)^T.
-    \end{equation}
-    The \emph{visibility normal} $\vec{n}(p)$ of point $p$ at scale $\sigma$ is defined
-    as the first eigenvector of the covariance matrix $\mathcal{V}_p$
-    of the visible points, corresponding to its smallest
-    eigenvalue. Its orientation is chosen to point in the same
-    direction as the average of the trivial normals to the surfels
-    touching the point $p$.
-
-    \paragraph{Experimental validation.} [TO COMPLETE]
-    Figure~\ref{fig:normals-estimation} shows an example
-    of our normals compared to normals computed with the integral invariant (II) estimator~\cite{Lachaud:2017-lnm}.
-
-    \begin{figure}
-        \centering
-        \begin{tabular}{|c||c|c|}
-            \hline
-            Normals & With cube edges & Flat (no shading) \\
-            \hline
-            \hline
-            \raisebox{18mm}{II} &
-            \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat-edge} &
-            \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat} \\
-            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
-            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} \\
-            \hline
-            \raisebox{18mm}{Ours} &
-            \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat-edge} &
-            \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat} \\
-            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
-            %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} \\
-            \hline
-            \raisebox{18mm}{II} &
-            \includegraphics[width=0.43\textwidth]{pictures/tie256-IIN-flat-edge} &
-            \includegraphics[width=0.43\textwidth]{pictures/tie256-IIN-flat} \\
-            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-II} &
-            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-II} \\
-            \hline
-            \raisebox{18mm}{Ours} &
-            \includegraphics[width=0.43\textwidth]{pictures/tie256-VN-flat-edge} &
-            \includegraphics[width=0.43\textwidth]{pictures/tie256-VN-flat} \\
-            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-NV} &
-            %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-NV} \\
-            \hline
-        \end{tabular}
-        \caption{Examples of normals computed on a cps, then on a
-        tie as a color map. First set displays II normals, second set
-        uses the visibility algorithm to compute them. The normals are colored
-        according to their orientation as $0.5 \cdot (n_i + \mathbbm{1})$. The
-        right images are the smooth version of the left images. ``Integral
-        Invariant normals'' are computed using a radius of $r=4.5$, while
-        our normal estimator are computed using a deviation of $\sigma=4$, and so
-        a radius of $r=2\sigma=8$}
-        \label{fig:normals-estimation}
-    \end{figure}
-
-    %% Then, to compute the curvatures, we use the Corrected Normal Current
-    %% estimator~\cite{lachaud:2022-dcg} which are based on the normals computed
-    %% above.
-
-    \paragraph{Application to curvature estimation.}
-    In order to illustrate better that the visibility normals better
-    take into account the sharp features of a digital surface while
-    staying meaningfull in digitization of smooth parts, we compare
-    the curvature estimates induced by different discrete normal
-    estimators. We exploit the \emph{Corrected Normal Current (CNC)
-        estimator}, whose theory is detailed in~\cite{lachaud:2022-dcg}
-    and which can estimate all kinds of curvatures given positions and
-    normals. It produces state-of-the-art curvature estimates on
-    polygonal surfaces~\cite{lachaud:2020-cgf}, point clouds~\cite{lachaud:2023-cgf}, and even outperforms Integral Invariant
-    curvature estimates~\cite{coeurjolly:2014-cviu} on digital
-    surfaces~\cite{lachaud:2022-dcg}. Its implementation is also
-    available in    \href{https://dgtal-team.github.io/doc-nightly/moduleCurvatureMeasures.html}{\textsc{DGtal}}.
-
-    Figure~\ref{fig:fig-curvatures} displays the results of CNC curvature
-    estimations on the digitization of a piecewise smooth shape
-    ``Talking D20'', taken from
-    \href{https://ten-thousand-models.appspot.com/detail.html?file_id=1533028}{Thingi10K}.
-    We compare the differences obtained by just changing the discrete
-    normal estimator (available in the \textsc{DGtal} library):
-    (column II normals) Integral Invariant normals with $r=6$, (column
-    CTriv normals) convolved trivial normals with $r=6$, (column
-    Visibility normals) our proposed estimator (VN) with $\sigma=4$ and
-    maximal visibility distance $2\sigma$. These parameters were
-    chosen so that the respective computation windows of the different
-    estimators are approximately the same.
-
-    The II estimator is good along digitization of smooth or flat parts of
-    the dice, but presents curious artefacts near sharp features
-    induced by the hollowed out numbers: this is due to the nature of
-    II normal estimates, which computes a PCA of a ball centered on
-    the point of interest and may include points on the other side of
-    the saliencies.
-
-    The CTriv estimator only performs averaging of trivial normal
-    directions along the surface. It behaves much better than II near
-    features (although it tends to smooth curvatures) since it does
-    not use information from across the gap. However some oscillations
-    of the curvatures are distinguishable especially along the flat
-    parts, and some curvature estimates are erroneous on smoother
-    parts (like the edge above 6 for $\kappa_2$ or several dice
-    vertices).
-
-    The VN estimator takes the best of the two previous approaches. It
-    remains precise and stable on smooth and flat regions, while
-    perfectly delineating sharp features and holes, whatever the kind
-    of estimated curvatures. Its drawback is the computation time,
-    which is $52s$ for a maximal visibility distance $8$, compared to
-    $2.3$s for II and $0.1s$ for CTriv. Note that the computation time
-    falls back to $33s$ for a maximal distance of $6$ (and same
-    $\sigma=4$) while the result is visually indistinguishable.
-
-    \newcommand{\MyZoom}[1]{%
-        \begin{tikzpicture}[spy using outlines={circle,magnification=1.8,size=2cm,connect spies}]
-        \node[inner sep=0pt] {\pgfimage[width=0.3\textwidth]{#1}};
-        \spy[overlay,blue] on (0.4,0.2) in node at (-0.8,0.8);
-        \end{tikzpicture}}
-    % \newcommand{\MyZoom}[1]{\includegraphics[width=0.3\textwidth]{#1}}
-
-    \begin{figure}
-        \begin{center}
-            \begin{tabular}{|c||c|c|c|}
-                \hline
-                Curv. & II normals & CTriv normals & Our normals \\ \hline \hline
-                \raisebox{18mm}{$\kappa_1$} &
-                \MyZoom{pictures/d20-k1-II.jpg} &
-                \MyZoom{pictures/d20-k1-CTriv.jpg}&
-                \MyZoom{pictures/d20-k1-VN.jpg}\\ \hline
-                \raisebox{18mm}{$\kappa_2$} &
-                \MyZoom{pictures/d20-k2-II.jpg} &
-                \MyZoom{pictures/d20-k2-CTriv.jpg}&
-                \MyZoom{pictures/d20-k2-VN.jpg}\\ \hline
-                \raisebox{18mm}{$H$} &
-                \MyZoom{pictures/d20-H-II.jpg} &
-                \MyZoom{pictures/d20-H-CTriv.jpg}&
-                \MyZoom{pictures/d20-H-VN.jpg}\\ \hline
-                \raisebox{18mm}{$G$} &
-                \MyZoom{pictures/d20-G-II.jpg} &
-                \MyZoom{pictures/d20-G-CTriv.jpg}&
-                \MyZoom{pictures/d20-G-VN.jpg}\\ \hline
-            \end{tabular}
-        \end{center}
-        \caption{\label{fig:fig-curvatures}Estimation of curvatures using
-          Corrected Normal Current estimators \cite{lachaud:2022-dcg}
-          with a measure of radius $2$ for the shape ``Dice-20'' of
-          Thingi10K database at resolution $256^3$. This estimator is
-          parameterized by an input normal estimator: first column by
-          ``Integral Invariant normals'' (radius $r=6$), second column
-          by ``Convolved Trivial normals'' (radius $k=6$), third
-          column by our presented normal estimator (deviation
-          $\sigma=4$, radius $r=2\sigma=8$). Per row are displayed the
-          estimated curvatures in order: first and second principal
-          curvatures $\kappa_1$ and $\kappa_2$, mean curvature $H$,
-          Gaussian curvature $G$. The range of curvature between deep
-          blue and deep red is $\lbrack -0.1, 0.1 \rbrack$ with white
-          color equal to $0$.}
-    \end{figure}
+    \input{normalsandcurvature}
 
@@
     \section{Conclusion}
-    \input{conclusion.tex}
+    \input{conclusion}
 

### 2025-04-25 DGMM2025/computation.tex
Split 3

@@
 
-    \colorlet{MyGreen}{green!80!gray}
     \begin{figure}
       \centering
-        \begin{tabular}{c c}
-            \begin{tikzpicture}[scale=0.75]
-                \foreach[count=\i] \y in {-0.5,0,...,1.5} {
-                    \draw (0,0) node at (-1.25,\y) {\i};
-                }
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.75,-0.25) grid (12.25,3.25);
-                \draw[-{Stealth[length=3mm]}=black] (-1.5,-1) -- (-1.5,2.5);
-                \filldraw[black] (0,0) circle (0.05);
-                \filldraw[black] (1,0) circle (0.05);
-                \filldraw[black] (2,0) circle (0.05);
-                \filldraw[black] (2,1) circle (0.05);
-                \filldraw[black] (3,1) circle (0.05);
-                \filldraw[black] (4,1) circle (0.05);
-                \filldraw[black] (5,1) circle (0.05);
-                \filldraw[black] (5,0) circle (0.05);
-                \filldraw[black] (6,0) circle (0.05);
-                \filldraw[black] (7,0) circle (0.05);
-                \filldraw[black] (7,1) circle (0.05);
-                \filldraw[black] (8,1) circle (0.05);
-                \filldraw[black] (8,0) circle (0.05);
-                \filldraw[black] (9,0) circle (0.05);
-                \filldraw[black] (10,0) circle (0.05);
-                \filldraw[black] (10,1) circle (0.05);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,-0.5)--(2.6,-0.5);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,-0.5)--(10.6,-0.5);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0)--(2.6,0);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,0)--(10.6,0);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(10.6,0.5);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1)--(5.6,1);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1)--(8.6,1);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1)--(10.6,1);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(5.6,1.5);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1.5)--(8.6,1.5);
-                \draw[thick,gray, arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1.5)--(10.6,1.5);
-                \draw[thick, black] (0,0) -- (2,0) -- (2,1) -- (5,1) -- (5,0) -- (7,0) -- (7,1) -- (8,1) -- (8,0) -- (10,0) -- (10,1);
-                \draw[thick,dashed] (6,1) -- (6,2);
-                \draw[thick,dashed] (9,1) -- (9,2);
-                \draw[thick,dashed] (-1,-1) -- (-1,1) -- (1,1) -- (1,2) -- (11,2) -- (11,-1) -- (4,-1) -- (4,0) -- (3,0) -- (3,-1) -- (-1,-1);
+      \input{algorithm.tikz}
 
-                \draw (0,0) node at (-0.25,1.75) {F};
-
-                \draw[red,arrows = {-Stealth[]}] (0,0)--(2,1);
-                \draw[red,arrows = {-Stealth[]}] (1,0)--(3,1);
-                \draw[red,arrows = {-Stealth[]}] (2,0)--(4,1);
-                \draw[red,arrows = {-Stealth[]}] (5,0)--(7,1);
-                \draw[red,arrows = {-Stealth[]}] (6,0)--(8,1);
-                \draw[red,arrows = {-Stealth[]}] (8,0)--(10,1);
-
-            \end{tikzpicture} &
-            \begin{tikzpicture}[scale=0.75]
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.75,-0.25) grid (4.25,3.25);
-                \draw[-{Stealth[length=3mm]}=black] (-1.5,-1) -- (-1.5,2.5);
-                \foreach[count=\i] \y in {-0.5,0,...,1.5} {
-                    \draw (0,0) node at (-1.25,\y) {\i};
-                }
-                \filldraw[black] (0,0) circle (0.05);
-                \filldraw[black] (2,1) circle (0.05);
-                \draw[thick, black] (0,0) -- (2,1);
-                \draw[thick,dashed] (-1,-1) -- (-1,1) -- (1,1) -- (1,2) -- (3,2) -- (3,0) -- (1,0) --  (1,-1) -- (-1,-1);
-                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,-0.5)--(0.6,-0.5);
-                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0)--(0.6,0);
-                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(2.6,0.5);
-                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1)--(2.6,1);
-                \draw[thick,MyGreen, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(2.6,1.5);
-
-                \draw (0,0) node at (-0.25,1.75) {V};
-            \end{tikzpicture} \\
-            \hline
-            \multicolumn{2}{c}{
-                \begin{tikzpicture}[scale=0.75]
-                    \foreach \y in {0,0.5,...,12.5} {
-                        \draw[thin, lightgray] (-1.25,\y) -- (11.25,\y);
-                    }
-                    \foreach \y in {0,2.5,...,12.5} {
-                        \draw[blue] (-7,\y) -- (11.25,\y);
-                    }
-
-                    \foreach[count=\i] \y in {12,9.5,...,2} {
-                        \draw (0,0) node at (-4,\y) {$V_{\i}$};
-                    }
-                    \foreach[count=\i] \y in {11.5,9,...,1.5} {
-                        \draw (0,0) node at (-4,\y) {$F_{\i}$};
-                    }
-                    \draw (0,0) node at (-4,11) {$T_{1} = \text{Translations}(V_{1},F_{1})$};
-                    \foreach[count=\i] \y in {8.5,6,...,1} {
-                        \draw (0,0) node at (-4,\y) {$T_{\the\numexpr\i+1\relax}$};
-                    }
-                    \draw (0,0) node at (-4,10.5) {$R_1 = T_1$};
-
-                    \foreach[count=\i] \y in {8,5.5,...,0.5} {
-
-                        \draw (0,0) node at (-4,\y) {$R_{\the\numexpr\i+1\relax} = T_{\the\numexpr\i+1\relax} \cap R_{\i}$};
-                    }
-
-                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,12)--(0.6,12);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,11.5)--(2.6,11.5);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,11.5)--(10.6,11.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,11)--(1.6,11);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,11)--(9.6,11);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,10.5)--(1.6,10.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,10.5)--(9.6,10.5);
-                    \filldraw[black] (-0.5,10.5) circle (0.05);
-                    \filldraw[black] (0.5,10.5) circle (0.05);
-                    \filldraw[black] (1.5,10.5) circle (0.05);
-                    \filldraw[black] (4.5,10.5) circle (0.05);
-                    \filldraw[black] (5.5,10.5) circle (0.05);
-                    \filldraw[black] (6.5,10.5) circle (0.05);
-                    \filldraw[black] (7.5,10.5) circle (0.05);
-                    \filldraw[black] (8.5,10.5) circle (0.05);
-                    \filldraw[black] (9.5,10.5) circle (0.05);
-
-                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9.5)--(0.6,9.5);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,9)--(2.6,9);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,9)--(10.6,9);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,8.5)--(1.6,8.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,8.5)--(9.6,8.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,8)--(1.6,8);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,8)--(9.6,8);
-                    \filldraw[black] (-0.5,8) circle (0.05);
-                    \filldraw[black] (0.5,8) circle (0.05);
-                    \filldraw[black] (1.5,8) circle (0.05);
-                    \filldraw[black] (4.5,8) circle (0.05);
-                    \filldraw[black] (5.5,8) circle (0.05);
-                    \filldraw[black] (6.5,8) circle (0.05);
-                    \filldraw[black] (7.5,8) circle (0.05);
-                    \filldraw[black] (8.5,8) circle (0.05);
-                    \filldraw[black] (9.5,8) circle (0.05);
-
-                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,7)--(2.6,7);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,6.5)--(10.6,6.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,6)--(7.6,6);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,5.5)--(1.6,5.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,5.5)--(7.6,5.5);
-                    \filldraw[black] (-0.5,5.5) circle (0.05);
-                    \filldraw[black] (0.5,5.5) circle (0.05);
-                    \filldraw[black] (1.5,5.5) circle (0.05);
-                    \filldraw[black] (4.5,5.5) circle (0.05);
-                    \filldraw[black] (5.5,5.5) circle (0.05);
-                    \filldraw[black] (6.5,5.5) circle (0.05);
-                    \filldraw[black] (7.5,5.5) circle (0.05);
-
-                    \draw[thick,black,arrows = {-Stealth[]}] (-0.6,4.5)--(1.4,4.5);
-                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,4.5)--(2.6,4.5);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,4)--(5.6,4);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,4)--(8.6,4);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,4)--(10.6,4);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,3.5)--(2.6,3.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,3.5)--(5.6,3.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,3.5)--(7.6,3.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,3)--(1.6,3);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,3)--(5.6,3);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,3)--(7.6,3);
-                    \filldraw[black] (-0.5,3) circle (0.05);
-                    \filldraw[black] (0.5,3) circle (0.05);
-                    \filldraw[black] (1.5,3) circle (0.05);
-                    \filldraw[black] (4.5,3) circle (0.05);
-                    \filldraw[black] (5.5,3) circle (0.05);
-                    \filldraw[black] (7.5,3) circle (0.05);
-
-                    \draw[thick,black,arrows = {-Stealth[]}] (-0.6,2)--(1.4,2);
-                    \draw[thick,MyGreen,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2)--(2.6,2);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,1.5)--(5.6,1.5);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (6.4,1.5)--(8.6,1.5);
-                    \draw[thick,gray,arrows = {Bracket[sharp]-Bracket[sharp]}] (9.4,1.5)--(10.6,1.5);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,1)--(2.6,1);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,1)--(5.6,1);
-                    \draw[thick,violet,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,1)--(7.6,1);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (-0.6,0.5)--(1.6,0.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (4.4,0.5)--(5.6,0.5);
-                    \draw[thick,red,arrows = {Bracket[sharp]-Bracket[sharp]}] (7.4,0.5)--(7.6,0.5);
-                    \filldraw[black] (-0.5,0.5) circle (0.05);
-                    \filldraw[black] (0.5,0.5) circle (0.05);
-                    \filldraw[black] (1.5,0.5) circle (0.05);
-                    \filldraw[black] (4.5,0.5) circle (0.05);
-                    \filldraw[black] (5.5,0.5) circle (0.05);
-                    \filldraw[black] (7.5,0.5) circle (0.05);
-
-                \end{tikzpicture}}
-        \end{tabular}
       \caption{Evolution of the visibility check algorithm for a 2,1 vector.

### 2025-04-25 DGMM2025/normalsandcurvature.tex
true normals and error graphs

@@
 \begin{figure}
+    \begin{tikzpicture}
+        \centering
+        \begin{axis}[
+            width=0.8\textwidth,
+            xlabel={Gridstep},
+            ylabel={RMSE error},
+            x dir=reverse,
+            legend pos=north east,
+            ymajorgrids=true,
+            grid style=dashed,
+            ymode=log,
+            xmode=log,
+            log ticks with fixed point,
+        ]
+            \addplot[
+                color=cyan,
+            ] coordinates {
+                (0.125,0.0133408)(0.250,0.0146335)(0.375,0.0178744)(0.500,0.0236486)(0.625,0.0337591)(0.750,0.0408107)(0.875,0.0461201)(1.000,0.0561247)
+            };
+            \addlegendentry{ellipsoid};
+            \addplot[
+                color=red,
+            ] coordinates {
+                (0.125,0.0230513)(0.250,0.0221659)(0.375,0.0396149)(0.500,0.0588389)(0.625,0.0738491)(0.750,0.0919486)(0.875,0.105444)(1.000,0.103468)
+            };
+            \addlegendentry{goursat};
+        \end{axis}
+    \end{tikzpicture}
+    \caption{RMSE error as a function of Grid Resolution}
+    \label{fig:errorl2-gridstep}
+\end{figure}
 
+\begin{figure}
+    \begin{tikzpicture}
+        \centering
+        \begin{axis}
+            [
+            width=0.8\textwidth,
+            xlabel={Gridstep},
+            ylabel={$E_{\max}$ error},
+            x dir=reverse,
+            legend pos=north east,
+            ymajorgrids=true,
+            grid style=dashed,
+            ymode=log,
+            xmode=log,
+            log ticks with fixed point,
+            ]
+            \addplot[
+                color=cyan,
+            ] coordinates {
+                (0.125,0.0688766)(0.250,0.0581494)(0.375,0.0503613)(0.500,0.0501076)(0.625,0.085362)(0.750,0.0821788)(0.875,0.120426)(1.000,0.102295)
+            };
+            \addlegendentry{ellipsoid}
+            \addplot[
+                color=red,
+            ] coordinates {
+                (0.125,0.116514)(0.250,0.0554448)(0.375,0.111164)(0.500,0.144318)(0.625,0.186091)(0.750,0.151117)(0.875,0.213926)(1.000,0.197462)
+            };
+            \addlegendentry{goursat}
+        \end{axis}
+    \end{tikzpicture}
+    \caption{$E_{\max}$ error as a function of Grid Resolution}
+    \label{fig:errorloo-gridstep}
 \end{figure}

### 2025-04-25 main.cpp

@@ -56,6 +56,8 @@ std::vector<RealPoint> normalVisibilityColors;
 std::vector<RealPoint> normalIIColors;
 std::vector<RealPoint> visibility_sharps;
 
+std::vector<RealPoint> true_normals;
+std::vector<RealPoint> surfel_true_normals;
 std::vector<RealPoint> ii_normals;
 std::vector<RealPoint> surfel_ii_normals;
 
@@ -870,6 +872,9 @@ int main(int argc, char *argv[]) {
   digital_surface = SH3::makeDigitalSurface(binary_image, K, params);
   primal_surface = SH3::makePrimalSurfaceMesh(digital_surface);
   surfels = SH3::getSurfelRange(digital_surface, params);
+  if (is_polynomial) {
+    surfel_true_normals = SHG3::getNormalVectors(implicit_shape, K, surfels, params);
+  }
   // Need to convert the faces
   for (auto face = 0; face < primal_surface->nbFaces(); ++face)
     primal_faces.push_back(primal_surface->incidentVertices(face));

### 2025-04-25 DGMM2025/computation.tex
Working on 3

@@
       \centering
-        \label{fig:lattice-representation}
-        % \usetikzlibrary {arrows.meta,decorations.shapes}
-        \begin{tabular}{c c}
-            \begin{tikzpicture}[scale=0.75]
-                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (-0.25,-0.25) grid (7.25,7.25);
-                \filldraw[black] (1,4) circle (0.05);
-                \filldraw[black] (1,5) circle (0.05);
-                \filldraw[black] (2,5) circle (0.05);
-                \filldraw[black] (3,5) circle (0.05);
-                \filldraw[black] (3,4) circle (0.05);
-                \filldraw[black] (3,3) circle (0.05);
-                \filldraw[black] (3,2) circle (0.05);
-                \filldraw[black] (2,2) circle (0.05);
-                \filldraw[black] (2,1) circle (0.05);
-                \filldraw[black] (1,1) circle (0.05);
-                \filldraw[black] (1,0) circle (0.05);
-                \filldraw[black] (2,0) circle (0.05);
-                \filldraw[black] (3,0) circle (0.05);
-                \filldraw[black] (3,1) circle (0.05);
-                \filldraw[black] (4,1) circle (0.05);
-                \filldraw[black] (5,1) circle (0.05);
-                \draw[-{Stealth[length=3mm]}=black] (-1,-1) -- (-1,6.5);
-                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=21.5pt}] {(-1,-1) -- (-1,7)};
-                \draw[black] (1,4) -- (1,5) -- (3,5) -- (3,2) -- (2,2) -- (2,1) -- (1,1) -- (1,0) -- (3,0) -- (3,1) -- (5,1);
-                \draw[thick,dashed] (1,3) -- (1,2) -- (0,2) -- (0,-1) -- (4,-1) -- (4,0) -- (6,0) -- (6,2) -- (4,2) -- (4,6) -- (0,6) -- (0,3) -- (2,3) -- (2,4);
-            \end{tikzpicture} &
-            %      \begin{tikzpicture}
-            %     \foreach \y in {1,1.5,...,6} {
-            %       \draw[thin, lightgray,xshift=-1cm,yshift=-1cm] (0.75,\y) -- (6.25,\y);
-            %     }
-            %     \draw[-{Stealth[length=3mm]}=black] (0,0) -- (0,5.5);
-            %     \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=10mm}] {(0,0) -- (0,5)};
-            %     \draw[black] (1,4) -- (1,5) -- (3,5) -- (3,2) -- (2,2) -- (2,1) -- (1,1) -- (1,0) -- (3,0) -- (3,1) -- (5,1);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,5)--(3.1,5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,4.5)--(1.1,4.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,4.5)--(3.1,4.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,4)--(1.1,4);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,4)--(3.1,4);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,3.5)--(3.1,3.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,3)--(3.1,3);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,2.5)--(3.1,2.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.9,2)--(3.1,2);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.9,1.5)--(2.1,1.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,1)--(2.1,1);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,1)--(5.1,1);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,0.5)--(1.1,0.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.9,0.5)--(3.1,0.5);
-            %     \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.9,0)--(3.1,0);
-            %     \filldraw[white,yshift=-1cm] (0,0) circle (0.01); % readjust the height to match the original path
-            % \end{tikzpicture} &
-            \begin{tikzpicture}[scale=0.75]
-                \foreach \y in {0,0.5,...,7} {
-                    \draw[thin, lightgray,xshift=-1cm,yshift=-1cm] (-0.25,\y) -- (7.25,\y);
-                }
-                \draw[-{Stealth[length=3mm]}=black] (-1,-1) -- (-1,6.5);
-                \draw decorate [decoration={crosses,transform={rotate=45},shape size=1.5mm,segment length=21.5pt}] {(-1,-1) -- (-1,6.5)};
-                \draw[thick,dashed] (1,3) -- (1,2) -- (0,2) -- (0,-1) -- (4,-1) -- (4,0) -- (6,0) -- (6,2) -- (4,2) -- (4,6) -- (0,6) -- (0,3) -- (2,3) -- (2,4);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,5.5)--(3.6,5.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,5)--(3.6,5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,4.5)--(3.6,4.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,4)--(1.6,4);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,4)--(3.6,4);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,3.5)--(1.6,3.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,3.5)--(3.6,3.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (2.4,3)--(3.6,3);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2.5)--(3.6,2.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (1.4,2)--(3.6,2);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,1.5)--(5.6,1.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,1)--(5.6,1);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,0.5)--(5.6,0.5);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,0)--(3.6,0);
-                \draw[thick, arrows = {Bracket[sharp]-Bracket[sharp]}] (0.4,-0.5)--(3.6,-0.5);
-                \filldraw[white,yshift=-1.25cm] (0,0) circle (0.01); % readjust the height to match the original path
-            \end{tikzpicture}
-        \end{tabular}
-        \caption{Representation of a 2d cell complex (here the star of a given curve) as a lattice map. From 31 cells from the star on the left, we get 15 intervals on the right}
+      \input{lattice.tikz}
+      \caption{\label{fig:lattice-representation} Representation of a
+        2d cell complex (here the star of a given curve) as a lattice
+        map. From 65 cells (with two coordinates) on the left, we get 11
+        intervals on the right.}
     \end{figure}
@@
       \input{algorithm.tikz}
-
-      \caption{Evolution of the visibility check algorithm for a 2,1 vector.
-Green is the vector lattice map, black is the figure lattice map, red are the current intervals of positions where the visibility is still possible.
-The last red intervals are the visible positions.
-We travel the lattice maps from bottom-up.
-The found possible visibilities are shown on the original figure}
+      \caption{Evolution of the visibility check algorithm for a $(2,1)$
+        vector. Green is the vector lattice map, black is the figure
+        lattice map, red are the current intervals of positions where
+        the visibility is still possible. The last red intervals are
+        the visible positions. We travel the lattice maps from
+        bottom-up and the found visibilities are drawn on the
+        uppest figure.}
         \label{fig:visibility-algorithm-evolution}
@@
     \begin{algorithm}
-        \caption{Given a cell complex C and a radius $r$, compute the visibility at every point of C up to distance $r$.
-We assume z being the main axis of the lattice maps, x and y being the auxiliary axises}
+      \caption{Given a subcomplex $C$ and an integer $r$, returns the visibility from every point of $C$ up to distance $r$. The main axis is supposed to be $z$, while $x,y$ are the auxiliary axes.}
         \label{alg:visibility}
         \begin{algorithmic}
-            \Function{Visibility}{C: Cell complex, r: Integer}
+            \Function{Visibility}{$C$: Subcomplex, $r$: Integer}
                 \State $\Omega \gets \Call{Star}{C}$ \Comment{Lattice map of the star of the studied cell complex}
@@
     \begin{algorithm}
-        \caption{Given 2 lists of intervals $K$ and $L$, find $K \cap L$, the intersection of those 2 lists}
+        \caption{Given 2 lists of integer intervals $K$ and $L$, returns $K \cap L$}
         \label{alg:intersection}
@@
             \Function{Intersection ($\cap$)}{\text{K, L}: Intervals}
-                \State $R \gets \emptyset$; $k, l \gets 0$
+                \State $R \gets \emptyset$; $k \gets 0$; $l \gets 0$;
                 \While{$k < K.nbIntervals \And l < L.nbIntervals$}
                     \State $[a,b] \gets K[k]$; $[c,d] \gets L[l]$
-                    \State $e \gets \max(a, c)$; $f \gets \min(b, d)$
+                    \State $e \gets \max(a, c)$; $f \gets \min(b, d)$;
                     \If{$e \leq f$}
-                        \State $R.append([e, f])$
+                         $R.append([e, f])$;
                     \EndIf
                     \If{$b \leq d$}
-                        \State $k \gets k+1$
+                        $k \gets k+1$;
                     \EndIf
                     \If{$d \leq b$}
-                        \State $l \gets l+1$
+                        $l \gets l+1$;
                     \EndIf

### 2025-04-25 DGMM2025/computation.tex
Working on 3

@@
-    To improve computation time, we will use lattice maps of integer intervals.
+As said in the introduction, any cell of $\mathcal{C}$ can be
+characterized as a point with integer coordinates, aka \emph{lattice
+point}. For instance, a standard way is to double the coordinates of
+the centroid of the cell (often called its Khalimsky code). Now we
+have to represent an arbitrary set $K$ of lattice points.
+
+We may choose an arbitrary projection \emph{axis} $a \in
+\{1,\ldots,d\}$. Letting $\pi_a$ be the projector along this axis, we
+can collect all the cells of $K$ that projects onto the same
+points. Let $p \in K$. Then $\pi^{-1}_a(p)$ is a set of cells having
+all the same coordinates except along coordinate $a$. This set can be ordered increasingly
+
+To improve computation time, we will use lattice maps of integer
+intervals.
 

### 2025-04-25 DGMM2025/normalsandcurvature.tex
added sphere9 & rcube
reformat error plots

--- 2025-04-25 DGMM2025/normalsandcurvature.tex
@@
 
-\begin{figure}
-
-\end{figure}
+\begin{tabular}{|c|c|}
+    \hline
+    \begin{tikzpicture}
+        \centering
+        \begin{axis}[
+            width=0.8\textwidth,
+            xlabel={Gridstep},
+            ylabel={RMSE error},
+            x dir=reverse,
+            legend pos=north east,
+            ymajorgrids=true,
+            grid style=dashed,
+            ymode=log,
+            xmode=log,
+            log ticks with fixed point,
+        ]
+            \addplot[
+                color=cyan,
+            ] coordinates {
+                (0.125,0.0156736)(0.250,0.031503)(0.375,0.0384303)(0.500,0.0441086)(0.625,0.0418896)(0.750,0.0584604)(0.875,0.065503)(1.000,0.0729735)
+            };
+            \addlegendentry{ellipsoid};
+            \addplot[
+                color=red,
+            ] coordinates {
+                (0.125,0.0221236)(0.250,0.0317159)(0.375,0.0542242)(0.500,0.0706101)(0.625,0.09481)(0.750,0.134544)(0.875,0.130578)(1.000,0.127371)
+            };
+            \addlegendentry{goursat};
+            \addplot[
+                color=MyGreen,
+            ] coordinates {
+                (0.125,0.0203851)(0.250,0.032289)(0.375,0.0353311)(0.500,0.0568694)(0.625,0.0665957)(0.750,0.106711)(0.875,0.0817172)(1.000,0.104688)
+            };
+            \addlegendentry{rcube}
+            \addplot[
+                color=orange,
+            ] coordinates {
+                (0.125,0.0106125)(0.250,0.0223176)(0.375,0.032738)(0.500,0.0365776)(0.625,0.0362568)(0.750,0.0181232)(0.875,0.0303189)(1.000,0.0263066)
+            };
+            \addlegendentry{sphere9}
+        \end{axis}
+    \end{tikzpicture} &
+    \begin{tikzpicture}
+        \centering
+        \begin{axis}
+            [
+            width=0.8\textwidth,
+            xlabel={Gridstep},
+            ylabel={$E_{\max}$ error},
+            x dir=reverse,
+            legend pos=north east,
+            ymajorgrids=true,
+            grid style=dashed,
+            ymode=log,
+            xmode=log,
+            log ticks with fixed point,
+            ]
+            \addplot[
+                color=cyan,
+            ] coordinates {
+                (0.125,0.0586128)(0.250,0.0736204)(0.375,0.114564)(0.500,0.114592)(0.625,0.136021)(0.750,0.152418)(0.875,0.139939)(1.000,0.234379)
+            };
+            \addlegendentry{ellipsoid}
+            \addplot[
+                color=red,
+            ] coordinates {
+                (0.125,0.0743185)(0.250,0.0810657)(0.375,0.113504)(0.500,0.145859)(0.625,0.256274)(0.750,0.266855)(0.875,0.259101)(1.000,0.274269)
+            };
+            \addlegendentry{goursat}
+            \addplot[
+                color=MyGreen,
+            ] coordinates {
+                (0.125,0.0670488)(0.250,0.0926269)(0.375,0.0973621)(0.500,0.137059)(0.625,0.155913)(0.750,0.290065)(0.875,0.164799)(1.000,0.317625)
+            };
+            \addlegendentry{rcube}
+            \addplot[
+                color=orange,
+            ] coordinates {
+                (0.125,0.0313599)(0.250,0.044124)(0.375,0.0643389)(0.500,0.0684951)(0.625,0.0853552)(0.750,0.0532733)(0.875,0.064386)(1.000,0.0873334)
+            };
+            \addlegendentry{sphere9}
+        \end{axis}
+    \end{tikzpicture} \\
+    \hline
+    \caption{Error RMSE and $E_{\max}$ as a function of grid resolution}
+    \label{fig:errors-normals}
+\end{tabular}
 

### 2025-04-25 DGMM2025/normalsandcurvature.tex
fix figure
fix figs size

@@
 
+\begin{figure}
     \begin{tabular}{|c|c|}
@@
             \begin{axis}[
-            width=0.8\textwidth,
+                width=0.4\textwidth,
                 xlabel={Gridstep},
@@
                 [
-            width=0.8\textwidth,
+                width=0.4\textwidth,
                 xlabel={Gridstep},
@@
         \hline
+    \end{tabular}
     \caption{Error RMSE and $E_{\max}$ as a function of grid resolution}
     \label{fig:errors-normals}
-\end{tabular}
+\end{figure}
 

### 2025-04-25 DGMM2025/normalsandcurvature.tex
fix figs size

@@
 \begin{figure}
-    \begin{tabular}{|c|c|}
-        \hline
+    \begin{tabular}{c c}
         \begin{tikzpicture}
@@
                 [
-                width=0.4\textwidth,
+                width=0.5\textwidth,
                 xlabel={Gridstep},
@@
         \end{tikzpicture} \\
-        \hline
     \end{tabular}

### 2025-04-25 DGMM2025/normalsandcurvature.tex
fix figs size

@@
             \begin{axis}[
-                width=0.4\textwidth,
+                width=0.55\textwidth,
                 xlabel={Gridstep},
@@
                 [
-                width=0.5\textwidth,
+                width=0.55\textwidth,
                 xlabel={Gridstep},

### 2025-04-25 DGMM2025/computation.tex
Working on 3

@@
 
-We may choose an arbitrary projection \emph{axis} $a \in
-\{1,\ldots,d\}$. Letting $\pi_a$ be the projector along this axis, we
+Let $(\ve_j)_{j=1,\dots}$ be the canonical basis of $\Z^d$.  We may
+choose an arbitrary projection \emph{axis} $j \in
+\{1,\ldots,d\}$. Letting $\pi_j$ be the projector along this axis, we
 can collect all the cells of $K$ that projects onto the same
-points. Let $p \in K$. Then $\pi^{-1}_a(p)$ is a set of cells having
-all the same coordinates except along coordinate $a$. This set can be ordered increasingly
+points. Let $p \in K$. Then $\pi^{-1}_j(p)$ is a set of cells having
+all the same coordinates except along coordinate $j$. This set can be
+ordered increasingly and stored as a list of integer intervals (see
+Fig.~\ref{fig:lattice-representation} for an illustration).
+
+A \emph{sequence of intervals} is an ordered list of intervals $L =
+([a_i,b_i])_{i=1,\ldots,n}$ such that $a_i \in \Z, b_i \in \Z, b_i + 1
+< a_{i+1}$, i.e., disjoint intervals with at least a missing
+integer. We denote by $\mathbb{L}$ the set of sequences of
+intervals. An integer $k$ belongs to $L$ iff $\exists i$ such that
+$a_i \Le k \Le b_i$. For a finite set of integers, there is a unique
+sequence of intervals representing it.
+
+A \emph{lattice map along axis $j$} is a set of pairs $(q,L_q)$, with
+$q \in \Z^{d-1}$ and $L_q \in \mathbb{L}$. The lattice map $M_K$
+\emph{represents} $K$ when, for any point $p \in K$, the pair
+$(\pi_j(p), L_{\pi_j(p)})$ exists in $M_K$ and $p_j \in L_{\pi_j(p)}$,
+with $p_j$ the $j$-th coordinate of $p$, and reciprocally, $\forall
+(q,L_q) \in M_K, \forall i \in L_q, q+i\ve_j \in K$.
 

### 2025-04-25 DGMM2025/computation.tex
Working on 3

@@
 
+\begin{figure}[t]
+  \centering
+  \input{lattice.tikz}
+  \caption{\label{fig:lattice-representation} Representation of a
+    2d cell complex (here the star of a given curve) as a lattice
+    map. From 65 cells (with two coordinates) on the left, we get 11
+    intervals on the right.}
+\end{figure}
+
 A \emph{sequence of intervals} is an ordered list of intervals $L =
@@
 with $p_j$ the $j$-th coordinate of $p$, and reciprocally, $\forall
-(q,L_q) \in M_K, \forall i \in L_q, q+i\ve_j \in K$.
+(q,L_q) \in M_K, \forall i \in L_q, q+i\ve_j \in K$. A lattice map is
+thus made of pairs $(q,L_q)$, where $q$ is the \emph{shift} while
+$L_q$ is the \emph{intervals}. For a point $q$ which is a shift of
+$M_K$, we write $M_K[q]$ for the corresponding intervals $L_q$.
 
-To improve computation time, we will use lattice maps of integer
-intervals.
+The global algorithm for computing visibility is given in
+Algorithm~\ref{alg:visibility}.  Given a digital input surface $C$ (a
+subcomplex), we compute the lattice map $\Omega$ of $\Star{C}$ once,
+generally along the axis where $C$ is the most elongated. In order to
+compute visibility up to a given distance $r$, we consider all non
+null primitive vectors $D$ with infinity norm no greater than $r$.
+For each vector $\vv$, we compute the lattice map $M_\vv$ of its
+intersected cells (as a vector from $\mathbf{0}$ to $\vv$ in
+$\R^d$). The visibility along the direction $\vv$ reduces to computing
+for each pair of $M_\vv$ the possible translations of intervals in
+$\Omega$, and then intersecting all the translations.
 
-\begin{definition}
-  A sequence of intervals is an ordered list of intervals $L = ([a_i,b_i])_{i=1,\ldots,n}$ such that $b_i + 1 < a_{i+1}$, i.e., disjoint intervals with at least a missing integer.
-\end{definition}
+%% \begin{definition}
+%%   A sequence of intervals is an ordered list of intervals $L = ([a_i,b_i])_{i=1,\ldots,n}$ such that $b_i + 1 < a_{i+1}$, i.e., disjoint intervals with at least a missing integer.
+%% \end{definition}
 
-\begin{definition}
-  A translation of an interval $A$ is defined as $A+t \coloneqq [a+t, b+t]$
-\end{definition}
+%% \begin{definition}
+%%   A translation of an interval $A$ is defined as $A+t \coloneqq [a+t, b+t]$
+%% \end{definition}
 
-\begin{definition}
-  A translation of a sequence of intervals $L$ is the sequence defined as $L+t \coloneqq \{L_1+t,\ldots,L_n+t\}$
-\end{definition}
+%% \begin{definition}
+%%   A translation of a sequence of intervals $L$ is the sequence defined as $L+t \coloneqq \{L_1+t,\ldots,L_n+t\}$
+%% \end{definition}
 
-\begin{definition}
-  All translations $T$ of an interval or a sequence of intervals $A$ in a sequence of intervals $L$ are defined as $ T \coloneqq \{ t, st. A+t \subset L\}$
-\end{definition}
+%% \begin{definition}
+%%   All translations $T$ of an interval or a sequence of intervals $A$ in a sequence of intervals $L$ are defined as $ T \coloneqq \{ t, st. A+t \subset L\}$
+%% \end{definition}
 
-We will consider lattice maps as pairs of (shift, intervals), where shifts are points $p \in \R^{d-1}$.
+%% We will consider lattice maps as pairs of (shift, intervals), where shifts are points $p \in \R^{d-1}$.
 All coordinates are doubled, so that the represented cell $\forall c \in \R^d$ will have a dimension equal to $\sum_{i=1}^d \left(c[i]\mod d\right)$.
-In figure~\ref{fig:lattice-representation}, we display a representation of lattice maps applied to a 2-d cell complex where all coordinates are already doubled.
+%% In figure~\ref{fig:lattice-representation}, we display a representation of lattice maps applied to a 2-d cell complex where all coordinates are already doubled.
 Note that the examples are in 2-d, the shown results are in 3-d and the algorithm is for n-d.
 
-\begin{figure}
-  \centering
-  \input{lattice.tikz}
-  \caption{\label{fig:lattice-representation} Representation of a
-    2d cell complex (here the star of a given curve) as a lattice
-    map. From 65 cells (with two coordinates) on the left, we get 11
-    intervals on the right.}
-\end{figure}
+\begin{algorithm}
+  \caption{Given a subcomplex $C$ and an integer $r$, returns the visibility from every point of $C$ up to distance $r$. The main axis is supposed to be $z$, while $x,y$ are the auxiliary axes.}
+  \label{alg:visibility}
+  \begin{algorithmic}
+    \Function{Visibility}{$C$: Subcomplex, $r$: Integer}
+    \State $\Omega \gets M_{\Call{Star}{C}}$ \Comment{Lattice map of the star of input subcomplex}
+    \State $Directions \gets \Call{GetAllPrimalDirections}{r}$
+    \State $V: \text{vector of boolean} \gets [0, \ldots, 0]$ \Comment{length $Size(Directions) \times \#C.pointels$}
+    \State $low, high \gets \Call{BoundingBoxZ}{\Omega}$
+    \ForAll{$\vv$ in $Directions$}
+    \ForAll{shift $S$ in $\Omega$}
+    \State $R \gets [low, high]$
+    \ForAll{pair $P$ in $M_{\Call{Star}{[\mathbf{0},\mathbf{v}]}}$}
+    \State $R \gets R \cap \Call{Translations}{P.intervals,\Omega[S + P.shift]}$
+    \EndFor
+    \State \Call{UpdateVisibility}{$V$, $R$}
+    \EndFor
+    \EndFor
+    \State \Return $V$
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
 
@@
 
-\begin{algorithm}
-  \caption{Given a subcomplex $C$ and an integer $r$, returns the visibility from every point of $C$ up to distance $r$. The main axis is supposed to be $z$, while $x,y$ are the auxiliary axes.}
-  \label{alg:visibility}
-  \begin{algorithmic}
-    \Function{Visibility}{$C$: Subcomplex, $r$: Integer}
-    \State $\Omega \gets \Call{Star}{C}$ \Comment{Lattice map of the star of the studied cell complex}
-    \State $Directions \gets \Call{GetAllPrimalDirections}{r}$
-    \State $V: \text{vector of boolean} \gets [0, \ldots, 0]$ \Comment{length $Size(Directions) \times \#C.pointels$}
-    \State $low, high \gets \Call{BoundingBoxZ}{\Omega}$
-    \ForAll{$d$ in $Directions$}
-    \ForAll{shift $S$ in $\Omega$}
-    \State $R \gets [low, high]$
-    \ForAll{pair $P$ in $\Call{Star}{\text{d}}$}
-    \State $R \gets R \cap \Call{Translations}{P.intervals,\Omega[S + P.shift]}$
-    \EndFor
-    \State \Call{UpdateVisibility}{$V$, $R$}
-    \EndFor
-    \EndFor
-    \State \Return $V$
-    \EndFunction
-  \end{algorithmic}
-\end{algorithm}
+Figure~\ref{fig:visibility-algorithm-evolution} shows an example of
+execution of this algorithm in an elementary case. It reduces to
+determining all the possible inclusions by translation of sequences of
+intervals in another sequence of intervals (note that for
+pairwise visibility, it is enough to consider all the possible
+inclusions by translation of one interval in another sequence of
+intervals), and then intersecting progressively the results. Of
+course, the process is stopped as soon as the intersection is
+empty. Some results of visible points are displayed on
+figure~\ref{fig:visibility-results} on 3d shapes.
 
-In order to compute the visibility, we first compute $\Omega = \text{Star}(C)$. Then for each primal direction of
-coordinates at most $r$, we look at all the possible positions this specific direction does link 2 visible points
-of the cell complex. In order to do so, for each shift in $\Omega$, we compute the positions where points are
-visible using the same method as presented in~\ref{fig:visibility-algorithm-evolution}. Some results of visible
-points are present in figure~\ref{fig:visibility-results}.
+%% In order to compute the visibility, we first compute $\Omega = \text{Star}(C)$. Then for each primal direction of
+%% coordinates at most $r$, we look at all the possible positions this specific direction does link 2 visible points
+%% of the cell complex. In order to do so, for each shift in $\Omega$, we compute the positions where points are
+%% visible using the same method as presented in~\ref{fig:visibility-algorithm-evolution}. Some results of visible
+%% points are present in figure~\ref{fig:visibility-results}.
 
@@
 
-To efficiently compute the intersection of 2 lists of intervals $K$ and $L$, we go through the first 2 unvisited
-elements of the 2 lists. If they don't overlap (i.e.\ the start and end of the 1st interval are both smaller than
-the start of the other), then we can discard the smaller interval. Else, we construct the intersection of these
-2 intervals as one of the resulting intervals. We then can skip the interval with the smallest end. If both
-intervals have the same end, then both intervals can be skipped. Doing this computation until one of the lists
-is empty returns the intersection of both lists of intervals.
+To efficiently compute the intersection of two sequences of intervals
+$K$ and $L$ (Algorithm~\ref{alg:intersection}), we go through the
+first $2$ unvisited elements of the $2$ lists. If they do not overlap
+(i.e.\ the start and end of the 1st interval are both smaller than the
+start of the other), then we can discard the smaller interval. Else,
+we construct the intersection of these 2 intervals as one of the
+resulting intervals. We then can skip the interval with the smallest
+end. If both intervals have the same end, then both intervals can be
+skipped. Doing this computation until one of the lists is empty
+returns the intersection of both lists of intervals.
 
@@
   \end{tabular}
-  \caption{Examples of visibility on a fandisk and a torus knot. First one is on the edge
-    of a fandisk, where the visibility stops at the edges. The other one is in the interior
-    of a torus knot, where we can see that the visibility is feature-aware and doesn't see
-    the other side of the torus' branch.}
+  \caption{Examples of visibilities from a source point:
+    (left) the visibility is stopped at the sharp edge, (right) the
+    visibility does not cross the gap between the two parts.}
   \label{fig:visibility-results}
@@
   \input{pointelscomptime.tikz}
-  \caption{Computation Time of Visibility as a Function of pointels amount. We compare the computation time of
-    the naive breadth first visibility algorithm against our version using intervals. We input the same radius to
-    both versions (10, 20, 30) and test it on 6 different figures (goursat, torus, rcube, sphere9, leopold, d20)
-    with various gridsteps, giving us figures with pointel amounts ranging from 520 to 390235.}
+  \caption{Computation time of visibility as a function of the number
+    of pointels. We compare the computation time of the naive breadth
+    first visibility algorithm against our algorithm using
+    intervals. We input the same maximal radius to both versions (10,
+    20, 30) and test it on 6 different figures (goursat, torus, rcube,
+    sphere9, leopold, d20) with various gridsteps, giving us figures
+    with pointel amounts ranging from 520 to 390235.}
   \label{fig:meanvisibility-computationComplexity}

### 2025-04-25 DGMM2025/computation.tex
Working on 3

@@
 
-\begin{figure}
-  \begin{tikzpicture}
-    \centering
-    \begin{axis}[
-        width=0.8\textwidth,
-        legend columns=3,
-        xlabel={Gridstep},
-        ylabel={Mean distance},
-        x dir=reverse,
-        legend pos=north west,
-        ymajorgrids=true,
-        grid style=dashed,
-        ymax=70,
-        ymode=log,
-        xmode=log,
-        log ticks with fixed point,
-      ]
-
-      \addplot[
-        color=cyan,
-      ] coordinates {
-        (0.0625,7.61948)(0.125,5.49755)(0.25,3.97418)(0.375,3.00921)(0.5,2.85702)(0.625,2.34448)(0.75,1.85023)(0.875,2.16868)(1.0,1.85023)
-      };
-      \addlegendentry{sphere1}
-      \addplot[
-        color=red,
-      ] coordinates {
-        (0.0625,38.1045)(0.125,26.8765)(0.25,19.6747)(0.375,16.6192)(0.5,14.0867)(0.625,12.5062)(0.75,11.3734)(0.875,10.2845)(1,8.90781)
-      };
-      \addlegendentry{goursat}
-      \addplot[
-        color=violet,
-      ] coordinates {
-        (0.0625,25.5024)(0.125,18.2364)(0.25,12.3975)(0.375,9.41303)(0.5,8.69558)(0.625,7.37667)(0.75,6.82131)(0.875,6.05735)(1,6.33877)
-      };
-      \addlegendentry{torus}
-      \addplot[
-        color=MyGreen,
-      ] coordinates {
-        (0.0625,27.9287)(0.125,17.5104)(0.25,10.8007)(0.375,8.69514)(0.5,7.26074)(0.625,6.2309)(0.75,5.6897)(0.875,5.28197)(1,4.96098)
-      };
-      \addlegendentry{leopold}
-      \addplot[
-        color=yellow!80!black,
-      ] coordinates {
-        (0.0625,41.9816)(0.125,27.7104)(0.25,18.2339)(0.375,14.6475)(0.5,12.3618)(0.625,9.55647)(0.75,9.83208)(0.875,7.51861)(1,7.99732)
-      };
-      \addlegendentry{rcube}
-      \addplot [
-        color=black,
-        thick,
-        domain=0.0625:1,
-        samples=100,
-      ] {x^(-0.5)};
-      \addlegendentry{$\sqrt{h}=\sqrt{\frac{1}{x}}$}
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Mean Visibility Distance as a Function of Grid Resolution}
-  \label{fig:meanvisibility-gridstep}
+\begin{figure}[t]
+  \input{pointelscomptime.tikz}
+  \caption{ \label{fig:meanvisibility-computationComplexity}Computation
+    time of visibility as a function of the number of pointels. We
+    compare the computation time of the naive breadth first visibility
+    algorithm against our algorithm using intervals. We input the same
+    maximal radius to both versions (10, 20, 30) and test it on 6
+    different figures (goursat, torus, rcube, sphere9, leopold, d20)
+    with various gridsteps, giving us figures with pointel amounts
+    ranging from 520 to 390235.}
 \end{figure}
 
-\begin{figure}[t]
-  \input{pointelscomptime.tikz}
-  \caption{Computation time of visibility as a function of the number
-    of pointels. We compare the computation time of the naive breadth
-    first visibility algorithm against our algorithm using
-    intervals. We input the same maximal radius to both versions (10,
-    20, 30) and test it on 6 different figures (goursat, torus, rcube,
-    sphere9, leopold, d20) with various gridsteps, giving us figures
-    with pointel amounts ranging from 520 to 390235.}
-  \label{fig:meanvisibility-computationComplexity}
+\begin{figure}
+  \input{mean-distance.tikz}
+  \caption{  \label{fig:meanvisibility-gridstep}. Mean Visibility Distance as a Function of Grid Resolution}
 \end{figure}

### 2025-04-25 DGMM2025/computation.tex
Working on 3 (almost done)

@@
 \begin{figure}[t]
+  \centering
   \input{pointelscomptime.tikz}
@@
     time of visibility as a function of the number of pointels. We
-    compare the computation time of the naive breadth first visibility
+    compare the running time of the naive breadth first visibility
     algorithm against our algorithm using intervals. We input the same
     maximal radius to both versions (10, 20, 30) and test it on 6
-    different figures (goursat, torus, rcube, sphere9, leopold, d20)
-    with various gridsteps, giving us figures with pointel amounts
-    ranging from 520 to 390235.}
+    different figures (goursat, torus, rcube, sphere9, leopold,
+    ``D20'') with various gridsteps, ($\#$ pointels ranging from 520
+    to 390235.}
 \end{figure}
@@
 \begin{figure}
+  \centering
   \input{mean-distance.tikz}
-  \caption{  \label{fig:meanvisibility-gridstep}. Mean Visibility Distance as a Function of Grid Resolution}
+  \caption{  \label{fig:meanvisibility-gridstep}. Mean distance of visibility as a function of the gridstep $h$.}
 \end{figure}

### 2025-04-25 DGMM2025/computation.tex
Working on 3 (almost done)

@@
 
+We have plotted on Fig.\ref{fig:meanvisibility-computationComplexity}
+the running times to compute global visibility of both \cite[Algorithm
+  3]{lachaud:2022-jmiv} and our algorithm. Timings are very
+similar. Our algorithm is faster for smaller maximal radii (up to 20),
+while the other is slightly faster for bigger radii. We have also
+measured the (discrete) average visibility distance along digitization
+of smooth shapes (Fig.~\ref{fig:meanvisibility-gridstep}). It follows
+a law proportionnal to $\sqrt{h}$. As shown in the next section, for
+real 3d images, a maximal radius below 10 is sufficient for normal and
+curvature estimation.
+
 \begin{figure}[t]
@@
   \input{mean-distance.tikz}
-  \caption{  \label{fig:meanvisibility-gridstep}. Mean distance of visibility as a function of the gridstep $h$.}
+  \caption{\label{fig:meanvisibility-gridstep} Mean distance of visibility as a function of the gridstep $h$ (see text).}
 \end{figure}

### 2025-04-25 DGMM2025/normalsandcurvature.tex

--- 2025-04-25 DGMM2025/normalsandcurvature.tex
@@
 \begin{figure}
+    \centering
     \begin{tabular}{c c}
@@
             \begin{axis}[
-                width=0.4\textwidth,
+                width=0.53\textwidth,
                 xlabel={Gridstep},
@@
                 };
-                \addlegendentry{ellipsoid};
                 \addplot[
@@
                 };
-                \addlegendentry{goursat};
                 \addplot[
@@
                 };
-                \addlegendentry{rcube}
                 \addplot[
@@
                 };
-                \addlegendentry{sphere9}
+                \addplot[
+                    color=black,
+                    thick,
+                    domain=0.1:1,
+                    samples=200,
+                ] {0.1*x^(0.5)};
             \end{axis}
@@
                 [
-                width=0.5\textwidth,
+                width=0.53\textwidth,
                 xlabel={Gridstep},
@@
                 };
-                \addlegendentry{ellipsoid}
                 \addplot[
@@
                 };
-                \addlegendentry{goursat}
                 \addplot[
@@
                 };
-                \addlegendentry{sphere9}
+                \addplot[
+                    color=black,
+                    thick,
+                    domain=0.1:1,
+                    samples=200,
+                ] {0.1*x^(0.5)};
             \end{axis}
         \end{tikzpicture} \\
+        \multicolumn{2}{c}{
+            \begin{tikzpicture}
+                \begin{axis}[
+                    hide axis,
+                    xmin=0, xmax=1,
+                    ymin=0, ymax=1,
+                    legend columns=5,
+                    legend style={
+                        at={(0.5,-0.2)},
+                        anchor=north,
+                        draw=none,
+                        column sep=15pt
+                    }
+                ]
+            \addlegendimage{color=cyan}
+            \addlegendentry{ellipsoid}
+            \addlegendimage{color=red}
+            \addlegendentry{goursat}
+            \addlegendimage{color=MyGreen}
+            \addlegendentry{rcube}
+            \addlegendimage{color=orange}
+            \addlegendentry{sphere9}
+
+            \addlegendimage{color=black,thick};
+            \addlegendentry{$0.1\sqrt{h}$}
+                \end{axis}
+            \end{tikzpicture}
+        } \\
     \end{tabular}

### 2025-04-25 DGMM2025/computation.tex
quickfixes

@@
     2d cell complex (here the star of a given curve) as a lattice
-    map. From 65 cells (with two coordinates) on the left, we get 11
+    map. From 63 cells (with two coordinates) on the left, we get 11
     intervals on the right.}
@@
 We have plotted on Fig.\ref{fig:meanvisibility-computationComplexity}
-the running times to compute global visibility of both \cite[Algorithm
+the running times to compute global visibility of both~\cite[Algorithm
   3]{lachaud:2022-jmiv} and our algorithm. Timings are very
@@
     ``D20'') with various gridsteps, ($\#$ pointels ranging from 520
-    to 390235.}
+    to 390235).}
 \end{figure}

### 2025-04-25 DGMM2025/normalsandcurvature.tex
legend fixing + adjusted trendlines
paragraph Experimental validation

@@
 
-\paragraph{Experimental validation.} [TO COMPLETE]
+\paragraph{Experimental validation.}
 Figure~\ref{fig:normals-estimation} shows an example
 of our normals compared to normals computed with the integral invariant (II) estimator~\cite{Lachaud:2017-lnm}.
+In order to compare quantitatively the different normal estimators, we compute the
+root mean square error (RMSE) and the maximum error $E_{\max}$ of the
+normals computed on a digital surface with respect to the normals computed
+on the continuous surface. We use 4 different digital surfaces (ellipsoid,
+goursat, rcube and sphere9). We see that the RMSE and $E_{\max}$ errors of our
+estimator are convergent with respect to the grid resolution with a
+rate of convergence of $h^{\frac{2}{3}}$ for the RMSE and $h^{\frac{1}{2}}$ for
+$E_{\max}$.
 
@@
                     samples=200,
-                ] {0.1*x^(0.5)};
+                ] {0.1*x^(0.66)} node[pos=0.2, anchor=south west] {$h^{\frac{2}{3}}$};
             \end{axis}
@@
                     samples=200,
-                ] {0.1*x^(0.5)};
+                ] {0.1*x^(0.5)} node[pos=0.5, anchor=north east] {$h^{\frac{1}{2}}$};
             \end{axis}
@@
 
-            \addlegendimage{color=black,thick};
-            \addlegendentry{$0.1\sqrt{h}$}
                 \end{axis}

### 2025-04-25 DGMM2025/normalsandcurvature.tex
forgot ref

@@
 normals computed on a digital surface with respect to the normals computed
-on the continuous surface. We use 4 different digital surfaces (ellipsoid,
+on the continuous surface (Figure~\ref{fig:errors-normals}). We use 4 different digital surfaces (ellipsoid,
 goursat, rcube and sphere9). We see that the RMSE and $E_{\max}$ errors of our

### 2025-04-25 DGMM2025/introduction.tex
typos fixing

@@
     $O(n^4)$~\cite{durand:2002-tog}. Exact 3d visibility between
-    polygons and occluding polygons is often casted into 5d Plücker
+    polygons and occluding polygons is often cast into 5d Plücker
     space~\cite{nirenstein:2002-ewr}, which nicely represents 3d lines
@@
 
-    To increase efficiency, several authors have casted the
+    To increase efficiency, several authors have cast the
     visibility problem into a digital space, generally $\Z^3$ or its
-    decomposition into cubical cells. Visibility is simplified as the
-    question whether there is a connected digital straight line
+    decomposition into cubical cells. Visibility is simplified as
+    whether there is a connected digital straight line
     joining a pair of cells without occluding cell(s)
-    (e.g. Soille~\cite{soille:1994-prl} uses Bresenham
+    (e.g.\ Soille~\cite{soille:1994-prl} uses Bresenham
     segments). Coeurjolly \emph{et al.}~\cite{coeurjolly:2004-prl}
@@
     be viewed as an inclusion problem between sets of lattice points
-    in this form. Indeed cells surounding $X$ can be encoded as
+    in this form. Indeed, cells surounding $X$ can be encoded as
     lattice points (Khalimsky coding), as well as the cells covering

### 2025-04-25 DGMM2025/normalsandcurvature.tex
typos fixing

--- 2025-04-25 DGMM2025/normalsandcurvature.tex
@@
 In order to compare quantitatively the different normal estimators, we compute the
-root mean square error (RMSE) and the maximum error $E_{\max}$ of the
+root-mean-square error (RMSE) and the maximum error $E_{\max}$ of the
 normals computed on a digital surface with respect to the normals computed
-on the continuous surface. We use 4 different digital surfaces (ellipsoid,
+on the continuous surface (Figure~\ref{fig:errors-normals}). We use 4 different digital surfaces (ellipsoid,
 goursat, rcube and sphere9). We see that the RMSE and $E_{\max}$ errors of our
@@
 features (although it tends to smooth curvatures) since it does
-not use information from across the gap. However some oscillations
+not use information from across the gap. However, some oscillations
 of the curvatures are distinguishable especially along the flat

### 2025-04-25 DGMM2025/visibility.tex
typos fixing

@@
     $\bar{\tau}$. The \emph{star} of a cell $\sigma$ is the subcomplex
-    $\Star{\sigma}:=\{\tau \in \mathcal{C}, \sigma \subset \bar{\tau}
+    $\Star{\sigma}\coloneqq\{\tau \in \mathcal{C}, \sigma \subset \bar{\tau}
     \}$. It is naturally extended to any subcomplex $K$ by union,
-    i.e. $\Star{K} := \cup_{\sigma \in K} \Star{\sigma}$, and more
-    generally to any subset $Y$ of $\R^d$ as $\Star{Y}:=\{ c \in \C,
+    i.e. $\Star{K} \coloneqq \cup_{\sigma \in K} \Star{\sigma}$, and more
+    generally to any subset $Y$ of $\R^d$ as $\Star{Y}\coloneqq\{ c \in \C,
     \bar{c} \cap Y \neq \emptyset \}$. The \emph{body} $\|K\|$ of $K$
-    is its realization in $\R^d$, i.e. $\|K\|:=\cup_{c \in K} c$. One
+    is its realization in $\R^d$, i.e. $\|K\|\coloneqq\cup_{c \in K} c$. One
     can check that $\Star{K}=\Star{\|K\|}$, so these definitions are
@@
     This definition corresponds to the concept of tangency presented
-    in \cite{lachaud:2022-jmiv}, limited to pair of points. One can
+    in~\cite{lachaud:2022-jmiv}, limited to pairs of points. One can
     check that $p$ and $q$ must belong to $Z$ to be visible.
@@
 
-    This characteristic has implications for the applicability of
-    \cite[Algorithm 3]{lachaud:2022-jmiv}, which is a breadth-first
+    This characteristic has implications for the applicability of~\cite[Algorithm 3]{lachaud:2022-jmiv}, which is a breadth-first
     like algorithm for computing all the points of $X$ visible in $X$

### 2025-04-25 DGMM2025/normalsandcurvature.tex
added II values and remove orcid

@@
                     color=cyan,
+                    mark=halfcircle
                 ] coordinates {
@@
                 };
+
+                \addplot[
+                    color=cyan,
+                    mark=square
+                ] coordinates {
+                    (0.125,0.00669781)(0.250,0.0120283)(0.375,0.0165559)(0.500,0.0263742)(0.625,0.0270529)(0.750,0.0361097)(0.875,0.0501562)(1.000,0.04348)
+                };
                 \addplot[
                     color=red,
+                    mark=halfcircle
                 ] coordinates {
@@
                 };
+
+                \addplot[
+                    color=red,
+                    mark=square
+                ] coordinates {
+                    (0.125,0.0157673)(0.250,0.024652)(0.375,0.0343723)(0.500,0.0463823)(0.625,0.051336)(0.750,0.0763857)(0.875,0.0758734)(1.000,0.0617788)
+
+                };
                 \addplot[
                     color=MyGreen,
+                    mark=halfcircle
                 ] coordinates {
@@
                 };
+
+                \addplot[
+                    color=MyGreen,
+                    mark=square
+                ] coordinates {
+                    (0.125,0.0140342)(0.250,0.0229046)(0.375,0.0304815)(0.500,0.0466803)(0.625,0.0559396)(0.750,0.0328143)(0.875,0.100956)(1.000,0.0944342)
+
+                };
                 \addplot[
                     color=orange,
+                    mark=halfcircle
                 ] coordinates {
                     (0.125,0.0106125)(0.250,0.0223176)(0.375,0.032738)(0.500,0.0365776)(0.625,0.0362568)(0.750,0.0181232)(0.875,0.0303189)(1.000,0.0263066)
+                };
+
+                \addplot[
+                    color=orange,
+                    mark=square
+                ] coordinates {
+                    (0.125,0.00364692)(0.250,0.00928532)(0.375,0.0168347)(0.500,0.0231946)(0.625,0.0220619)(0.750,0.0340007)(0.875,0.0533849)(1.000,0.0691569)
+
                 };
@@
                 };
+
+                \addplot[
+                    color=cyan,
+                    mark=square
+                ] coordinates {
+                    (0.125,0.0198319)(0.250,0.0370639)(0.375,0.0415253)(0.500,0.0840702)(0.625,0.0623331)(0.750,0.0898241)(0.875,0.133761)(1.000,0.0869342)
+                };
                 \addplot[
                     color=red,
+                    mark=halfcircle
                 ] coordinates {
@@
                 };
+
+                \addplot[
+                    color=red,
+                    mark=square
+                ] coordinates {
+
+                    (0.125,0.02986)(0.250,0.0502663)(0.375,0.0717319)(0.500,0.0846663)(0.625,0.0966577)(0.750,0.123886)(0.875,0.139487)(1.000,0.132201)
+                };
                 \addplot[
                     color=MyGreen,
+                    mark=halfcircle
                 ] coordinates {
@@
                 };
+
+                \addplot[
+                    color=MyGreen,
+                    mark=square
+                ] coordinates {
+
+                    (0.125,0.0325697)(0.250,0.0486132)(0.375,0.0750567)(0.500,0.0918979)(0.625,0.11031)(0.750,0.0755826)(0.875,0.168386)(1.000,0.174149)
+                };
                 \addplot[
                     color=orange,
+                    mark=halfcircle
                 ] coordinates {
                     (0.125,0.0313599)(0.250,0.044124)(0.375,0.0643389)(0.500,0.0684951)(0.625,0.0853552)(0.750,0.0532733)(0.875,0.064386)(1.000,0.0873334)
+                };
+
+                \addplot[
+                    color=orange,
+                    mark=square
+                ] coordinates {
+
+                    (0.125,0.0178225)(0.250,0.0373191)(0.375,0.0497523)(0.500,0.0684615)(0.625,0.0536034)(0.750,0.0618511)(0.875,0.129302)(1.000,0.12792)
                 };
@@
                     ymin=0, ymax=1,
-                    legend columns=5,
+                    legend columns=3,
                     legend style={
@@
                         draw=none,
-                        column sep=15pt
+                        column sep=15pt,
                     }
                 ]
+                    \addlegendimage{mark=halfcircle}
+                    \addlegendentry{VN}
+                    \addlegendimage{mark=square}
+                    \addlegendentry{II}
                     \addlegendimage{color=cyan}

### 2025-08-17 DGMM2025/computation.tex
typos fixing
p1 corrections camera ready

@@
 
-Let $(\ve_j)_{j=1,\dots}$ be the canonical basis of $\Z^d$.  We may
+Let $(\ve_j)_{j=1,\dots,d}$ be the canonical basis of $\Z^d$.  We may
 choose an arbitrary projection \emph{axis} $j \in
@@
 can collect all the cells of $K$ that projects onto the same
-points. Let $p \in K$. Then $\pi^{-1}_j(p)$ is a set of cells having
+points. Let $p \in K$. Then $\pi^{-1}_j(p) \cap \Star{K}$ is a set of cells having
 all the same coordinates except along coordinate $j$. This set can be
 ordered increasingly and stored as a list of integer intervals (see
-Fig.~\ref{fig:lattice-representation} for an illustration).
+Figure~\ref{fig:lattice-representation} for an illustration).
 
@@
 integer. We denote by $\mathbb{L}$ the set of sequences of
-intervals. An integer $k$ belongs to $L$ iff $\exists i$ such that
+intervals. An integer $k$ belongs to $L$ iff there exists $i$ such that
 $a_i \Le k \Le b_i$. For a finite set of integers, there is a unique
@@
 generally along the axis where $C$ is the most elongated. In order to
-compute visibility up to a given distance $r$, we consider all non
-null primitive vectors $D$ with infinity norm no greater than $r$.
+compute visibility up to a given distance $r$, we consider all non-null
+primitive vectors $D$ with infinity norm no greater than $r$.
 For each vector $\vv$, we compute the lattice map $M_\vv$ of its
@@
 
-We have plotted on Fig.\ref{fig:meanvisibility-computationComplexity}
+We have plotted on Figure~\ref{fig:meanvisibility-computationComplexity}
 the running times to compute global visibility of both~\cite[Algorithm
@@
 measured the (discrete) average visibility distance along digitization
-of smooth shapes (Fig.~\ref{fig:meanvisibility-gridstep}). It follows
+of smooth shapes (Figure~\ref{fig:meanvisibility-gridstep}). It follows
 a law proportionnal to $\sqrt{h}$. As shown in the next section, for

### 2025-08-17 DGMM2025/normalsandcurvature.tex
p1 corrections camera ready

@@
 a user-given scale $\sigma$. If $\sigma$ is proportionnal to the
-average length between visible points (so some
+average distance between visible points (so some
 $\Theta\left(\sqrt{h}\right)$), then this estimator is observed to be
@@
         \raisebox{18mm}{II} &
-        \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat-edge} &
-        \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat} \\
+        \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat-edge-small} &
+        \includegraphics[width=0.3\textwidth]{pictures/cps-IIN-flat-small} \\
         %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
@@
         \raisebox{18mm}{Ours} &
-        \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat-edge} &
-        \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat} \\
+        \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat-edge-small} &
+        \includegraphics[width=0.3\textwidth]{pictures/cps-VN-flat-small} \\
         %% \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
@@
         \raisebox{18mm}{II} &
-        \includegraphics[width=0.43\textwidth]{pictures/tie256-IIN-flat-edge} &
-        \includegraphics[width=0.43\textwidth]{pictures/tie256-IIN-flat} \\
+        \includegraphics[width=0.43\textwidth]{pictures/tie256-IIN-flat-edge-small} &
+        \includegraphics[width=0.43\textwidth]{pictures/tie256-IIN-flat-small} \\
         %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-II} &
@@
         \raisebox{18mm}{Ours} &
-        \includegraphics[width=0.43\textwidth]{pictures/tie256-VN-flat-edge} &
-        \includegraphics[width=0.43\textwidth]{pictures/tie256-VN-flat} \\
+        \includegraphics[width=0.43\textwidth]{pictures/tie256-VN-flat-edge-small} &
+        \includegraphics[width=0.43\textwidth]{pictures/tie256-VN-flat-small} \\
         %% \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-NV} &
@@
             \raisebox{18mm}{$\kappa_1$} &
-            \MyZoom{pictures/d20-k1-II.jpg} &
-            \MyZoom{pictures/d20-k1-CTriv.jpg}&
-            \MyZoom{pictures/d20-k1-VN.jpg}\\ \hline
+            \MyZoom{pictures/d20-k1-II-small.jpg} &
+            \MyZoom{pictures/d20-k1-CTriv-small.jpg}&
+            \MyZoom{pictures/d20-k1-VN-small.jpg}\\ \hline
             \raisebox{18mm}{$\kappa_2$} &
-            \MyZoom{pictures/d20-k2-II.jpg} &
-            \MyZoom{pictures/d20-k2-CTriv.jpg}&
-            \MyZoom{pictures/d20-k2-VN.jpg}\\ \hline
+            \MyZoom{pictures/d20-k2-II-small.jpg} &
+            \MyZoom{pictures/d20-k2-CTriv-small.jpg}&
+            \MyZoom{pictures/d20-k2-VN-small.jpg}\\ \hline
             \raisebox{18mm}{$H$} &
-            \MyZoom{pictures/d20-H-II.jpg} &
-            \MyZoom{pictures/d20-H-CTriv.jpg}&
-            \MyZoom{pictures/d20-H-VN.jpg}\\ \hline
+            \MyZoom{pictures/d20-H-II-small.jpg} &
+            \MyZoom{pictures/d20-H-CTriv-small.jpg}&
+            \MyZoom{pictures/d20-H-VN-small.jpg}\\ \hline
             \raisebox{18mm}{$G$} &
-            \MyZoom{pictures/d20-G-II.jpg} &
-            \MyZoom{pictures/d20-G-CTriv.jpg}&
-            \MyZoom{pictures/d20-G-VN.jpg}\\ \hline
+            \MyZoom{pictures/d20-G-II-small.jpg} &
+            \MyZoom{pictures/d20-G-CTriv-small.jpg}&
+            \MyZoom{pictures/d20-G-VN-small.jpg}\\ \hline
         \end{tabular}

### 2025-08-17 DGMM2025/template/samplepaper.tex
p1 corrections camera ready

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%
\begin{document}
%
\title{Contribution Title}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Figure~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.

\begin{credits}
\subsubsection{\ackname} A bold run-in heading in small font size at the end of the paper is
used for general acknowledgments, for example: This study was funded
by X (grant number Y).

\subsubsection{\discintname}
It is now necessary to declare any competing interests or to specifically
state that the authors have no competing interests. Please place the
statement with a bold run-in heading in small font size beneath the
(optional) acknowledgments\footnote{If EquinOCS, our proceedings submission
system, is used, then the disclaimer can be provided directly in the system.},
for example: The authors have no competing interests to declare that are
relevant to the content of this article. Or: Author A has received research
grants from Company W. Author B has received a speaker honorarium from
Company X and owns stock in Company Y. Author C is a member of committee Z.
\end{credits}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}, last accessed 2023/10/25
\end{thebibliography}
\end{document}

### 2025-08-17 DGMM2025/visibility.tex
p1 corrections camera ready
p2 corrections camera ready

@@
     defined and valid in arbitrary dimension $d$. They will however be
-    illustrated in 2d for clarity, while experiments willl be
+    illustrated in 2d for clarity, while experiments will be
     performed on 3d digital shapes.  Let $\Z^d$ be the $d$-dimensional
@@
       \caption{Examples of visibility and non visibility in 2D within
-        the set $X$ (represented with black disks $\bullet$).}
+        the set $X$ (represented with black dots $\bullet$).}
       \label{fig:visibility-2d}
